### 2016-11-04 paper/conclusion.tex
CVPR draft.

\section{Conclusions}

The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation. Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. Humans are the bottleneck and minimizing the manual labor is the goal.
We have addressed this problem through training a convolutional neural network to detect ambiguous regions from labeled data---in effect, by finding a non-linear mapping between image and segmentation data. This allows us to identify merge and split errors with better performance than existing systems. Our experiments have shown that guided proofreading has the potential to reduce the bottleneck in the analysis of large connectomics datasets. To encourage testing of our proposed architecture and replicate our experiments, we provide our framework and data as free and open research at (link omitted for review).

### 2016-11-04 paper/evaluation.tex
CVPR draft.

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/results_mouse.png}
\end{center}
  \vspace{-4mm}
   \caption{Performance evaluation of the classifiers on two mouse brain datasets measured as adapted Rand error (lower scores are better). We compare guided proofreading (GP), guided proofreading with active label suggestion (GP*) and focused proofreading. Proofreading is performed automatically (autom., with probability threshold $p_t=.95$), simulated as a perfect user (sim.), or by novice and expert users as indicated. The first row of images shows the results of a user study and includes comparisons to the interactive proofreading software Dojo by Haehn \etal \cite{haehn_dojo_2014}. GP* is able to correct the segmentation further than other methods. The second row shows the results of the simulated user compared to automatic GP* and FP performance. The bottom right graph compares automatic GP* and simulated GP* per individual correction. The blue dashed line here indicates the moment the probability threshold $p_t$ is reached. The simulated user is able to correct the initial segmentation beyond this threshold while automatic GP* then introduces errors.}
\label{fig:results_mouse}
\end{figure*}

\section{Evaluation}
\label{sec:evaluation}

We evaluate guided proofreading (GP) on multiple real-world connectomics datasets of different species. In particular, we evaluate GP on two datasets of mouse brain and three datasets of fruitfly brain (drosophila). For comparison, we choose the fully interactive proofreading software \textit{Dojo} by Haehn \etal~\cite{haehn_dojo_2014} as well as the aided proofreading framework \textit{focused proofreading} (FP) by Plaza~\cite{focused_proofreading}. We first describe the evalation on mouse brain data and then the evaluation on drosophila brain.

\subsection{Mouse Brain}

Mouse brain is a common target for connectomics research because the structural proportions are similar to human brains~\cite{jeff_science}. For our first experiment we recruited novice and expert participants as part of a quantitative user study. Our second experiment is performed on a larger dataset and we evaluate a simulated user.
\\~\\
\textbf{User study.} Recently, Haehn \etal evaluated the interactive proofreading tools Raveler, Mojo, and Dojo as part of an experiment with novice users~\cite{haehn_dojo_2014}. The participants corrected an automatic segmentation with merge and split errors. The dataset was the most representative sub-volume (based on object size histograms) of a larger connectomics dataset and $400x400x10$ voxels in size. The participants were given a fixed time frame of 30 minutes to perform the correction interactively. While participants clearly struggled with the proofreading task, the best performing tool in their evaluation was Dojo. The dataset including manually labeled ground truth and the results of Haehn \etal are publicly available. This means we are able to use their findings as a baseline for comparison of GP for novices. In particular, we use the best performing user of Dojo who was truly an outlier as reported by Haehn \etal.

Since interactive proofreading most likely yields lower performance than aided proofreading, we also compare against FP by Plaza~\cite{focused_proofreading} which is integrated in Raveler and freely available. For FP we consulted an expert to obtain the best possible parameters as shown in table \ref{tab:parameters}. Besides performance by novices, we are also interested in expert proofreading performance. Therefore, we design between-subjects experiments for 20 novice users and separately, for 6 expert users using the exact same conditions as Haehn \etal. The recruiting, consent and debriefing process is further described in the supplementary material. We randomly assign 10 novices to GP with active label suggestion (GP*) and 10 novices to FP. For the expert experiment, we assign accordingly.
In addition to human performance, we also evaluate automatic GP, automatic GP with active label suggestion (GP*) and automatic FP. Due to the automatic nature, we do not enforce the 30 minute time limit but we stop once our probability threshold of $p_t=.95$ is reached. This value was observed as stable in previous experiments using automatic GP (see supplementary material). To measure proofreading performance in comparison to ground truth, we use the adapted Rand error (aRE) metric~\cite{RAND}. aRE is a measure of dissimilarity, related to introduced errors, meaning lower scores are better.

The results of our comparisons are shown in the first row of Fig.~\ref{fig:results_mouse}. In all cases, GP* is able to correct the segmentation further than other methods (aRE measures: automatic GP XX, GP* XX, FP XX, novice Dojo XX, GP* XX, FP XX, expert Dojo XX, GP* XX, FP XX). This is not surprising since guided proofreading works for both merge and split errors while FP does not and in interactive Dojo the majority of time is spent finding errors which is minimized for aided proofreading solutions. In fact, the average correction time for novices is for GP* 3.6 (expert X), for FP Y (expert YY), and for Dojo 30 (expert ZZ) seconds.
\\~\\
\textbf{Simulated experiment.} For our second experiment with mouse brain data, we proofread the last 50 slices of the blue 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} which we also used for testing in section~\ref{sec:methods}. The data was not seen by the network before and includes $2048x2048x50$ voxels with a total number of 17,560 labeled objects. Since an interactive evaluation of such a large dataset would consume a significant amount of time, we restrict our experiment to a simulated (perfect) user and to automatic corrections, both with GP, GP* and FP. Similar to our comparison study, the simulated user assess a stream of errors by comparing the adapted Rand error measure before and after each performed correction. The simulated user is designed to be perfect and only accepts corrections if the measure is reduced. This time, we do not enforce a time limit to see the lower bound of possible corrections. For automatic GP and GP*, we use our defined probability threshold $p_t=.95$.

The results of this experiment are shown in the second row of Fig.~\ref{fig:results_mouse}. GP* is again able to correct the segmentation further than other methods (aRE measures: automatic GP XX, GP* XX, FP XX, simulated GP* XX, FP XX). Again, the results are not surprising since GP* can correct merge and split errors.

\subsection{Drosophila Brain}

The drosophila brain is analyzed by connectomics researchers because of its small size and hence, a reasonable target to obtain a complete wiring diagram. Despite the size, fruit flies exhibit complex behaviors and are in general well studied. We evaluate the performance of our guided proofreading classifiers on three different datasets of adult fly brain. The datasets are publicly available as part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI)\footnote{The MICCAI CREMI challenge data is available at  http://www.cremi.org}. Each dataset consists of $1250x1250x125$ voxels of training data (A,B,C) as well as testing data (A+,B+,C+) of the same dimensions. Manually labeled ground truth is also available for A,B, and C but not for the testing data.

Since drosophila brain exhibits different cell structures than mouse brain, we retrain the guided proofreading classifiers (and our automatic segmentation pipeline) as well as focused proofreading combined on the three training datasets. We use 300 slices of the A,B,C samples for training and validation, and 75 slices for testing. This results in YYY correct and ZZZ split error patches (respectively, XXX and YYY for testing). The architecture and all parameters of our classifiers stay the same. The trained GP classifier exhibits a reasonable performance on the testing data as seen in Fig.~\ref{fig:roc}.

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/results_fruitfly.png}
\end{center}
  \vspace{-4mm}
   \caption{Results of guided proofreading with active label suggestion (GP*) and focused proofreading performed automatically on three drosophila datasets. The datasets are part of the MICCAI 2016 CREMI challenge and publicly available. We measure performance as adapted Rand error (the lower, the better). GP* is able to correct the initial segmentation further than FP. Our GP* scores places us XXnd on the CREMI leaderboard.}
\label{fig:results_fruitfly}
\end{figure}

We then use the trained GP* and FP classifiers to evaluate proofreading automatically. Since ground truth labeling is not available, the evaluation is performed by submitting our results to the CREMI leaderboard. Again, we use adapted Rand error to quantify the performance. Fig.~\ref{fig:results_fruitfly} shows the results for each of the A+,B+, and C+ datasets. The performance of GP* is significantly better than FP and places us XXnd on the CREMI leaderboard.

### 2016-11-04 paper/guidedproofreading_review.tex
CVPR draft.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{Guided Proofreading of Automatic Segmentations in Connectomics}

\author{Daniel Haehn\\
Institution1\\
Institution1 address\\
{\tt\small haehn@seas.harvard.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
Automatic cell image segmentation methods in connectomics produce merge and split errors, which require correction through proofreading. Previous research has identified the visual search for these errors as the bottleneck in interactive proofreading. To aid error correction, we develop two classifiers to recommend candidate merge and split errors and their corrections to the user. These classifiers are informed by training a convolutional neural network with known errors in automatic segmentations against expert-labeled ground truth. Our classifiers detect potentially-erroneous regions by considering a large context region around a segmentation boundary. Corrections can then be performed as yes/no decisions 
resulting in faster correction times than previous methods. We evaluate our approach on connectomics datasets of different species and compare correction performance of novice and expert users against different existing systems. We report significant improvements on pure automatic and pure manual proofreading.
\end{abstract}

%%%%%%%%% BODY TEXT
\input{introduction}

\input{related_work}

\input{method}

\input{evaluation}

\input{conclusion}

{\small
\bibliographystyle{ieee}
\bibliography{connectomics}
}

\end{document}

### 2016-11-04 paper/introduction.tex
CVPR draft.

\section{Introduction}

In connectomics, neuroscientists annotate neurons and their connectivity within 3D volumes to gain insight into the functional structure of the brain. Rapid progress in automatic sample preparation and electron microscopy (EM) acquisition techniques has made it possible to image large volumes of brain tissue at $\approx4\, nm$ per pixel to identify cells, synapses, and vesicles. For $40\, nm$ thick sections, a $1\, mm^3$ volume of brain contains $10^{15}$ voxels, or 1 petabyte of data. With so much data, manual annotation is infeasible, and automatic annotation methods are needed ~\cite{jain2010,Liu2014,GALA2014,kaynig2015large}.

Automatic annotation by segmentation and classification of brain tissue is challenging~\cite{isbi_challenge}. The state of the art uses supervised learning with convolutional neural networks~\cite{Ciresan:2012f}, or potentially even unsupervised learning~\cite{BogovicHJ13}. Typically, cell membranes are detected in 2D images, and the resulting region segmentation is grouped into geometrically-consistent cells across registered sections. Cells may also be segmented across registered sections in 3D directly. Using dynamic programming techniques~\cite{Masci:2013a} and a GPU cluster, these classifiers can segment $\approx1$ terabyte of data per hour ~\cite{kasthuri2015saturated}. This is sufficient to keep up with the 2D data capture process on state-of-the-art electron microscopes (though 3D registration is still an expensive offline operation).

All automatic methods make errors, and we are left with large data which needs \emph{proofreading} by humans. This crucial task serves two purposes: 1) to correct errors in the segmentation, and 2) to provide a large body of labeled data to train better automatic segmentation methods. Recent proofreading tools provide intuitive user interfaces to browse segmentation data in 2D and 3D and to identify and manually correct errors ~\cite{markus_proofreading,raveler,mojo2,haehn_dojo_2014}. Many kinds of errors exist, such as inaccurate boundaries, but the most common are \emph{split errors}, where a single segment is labeled as two, and \emph{merge errors}, where two segments are labeled as one (Fig.~\ref{fig:merge_and_slit_errors}). With user interaction, split errors can be joined, and the missing boundary in a merge error can be defined with manually-seeded watersheds~\cite{haehn_dojo_2014}. However, even with semi-automatic correction tools, the visual inspection to find errors in the first place takes the majority of the time.

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/merge_and_split_errors.png}
\end{center}
\vspace{-4mm}
   \caption{The most common proofreading corrections are fixing split errors (red arrows) and merge errors (yellow arrow). A fixed segmentation matches the cell borders.}
\label{fig:merge_and_slit_errors}
\end{figure}

Our goal is to add automatic detection of split and merge errors to proofreading tools. Instead of the user visually inspecting the whole data volume carefully to spot errors, we design automatic classifiers that detect split and merge errors in 2D segmentations. Then, a proofreading tool can recommend regions with a high probability of an error to the user, and suggest corrections to accept or reject. We call this process \textit{guided proofreading} (GP).

As our main contribution, we introduce classifiers to detect merge- and split errors based on a convolutional neural network (CNN). We believe that this is the first time that deep learning is applied to the task of proofreading --- especially in the field of connectomics. Our classifiers work on top of any existing automatic segmentation method to find potential errors and suggest corrections. Given a membrane segmentation from a fast automatic method, our classifiers operate on the boundaries of whole cell regions. Compared to techniques that must analyze every input pixel, we reduce the data analysis to the boundaries only. Explicitly, we train a CNN to detect only split errors. We then reuse the same network to also detect merge errors by generating possible boundaries within a cell and inverting the split error score. Correction suggestion for both types of errors is then trivial and our technique therefor reduces the proofreading operation to simple yes/no decisions.

We further propose a greedy algorithm to perform proofreading automatically and measure performance as the adapted Rand error which is a common metric for segmentation comparison~\cite{RAND}. 
Our system is integrated into an existing proofreading workflow for large connectomics data. For this, we also explore an active label suggestion approach in addition to the ranking obtained by guided proofreading. We quantitatively validate automatic and human-driven variations of guided proofreading on five different real-world connectomics datasets of mouse as well as fruitfly (drosophila) brain. To study the performance of novice and expert proofreaders, we perform a between-subjects experiment and ask participants to proofread a publicly available dataset. For comparison, we establish two baselines: a recently published fully interactive proofreading tool named \textit{Dojo} by Haehn~\etal~\cite{haehn_dojo_2014} and semi-automatic \textit{focused proofreading} (FP) approach by Plaza~\cite{focused_proofreading}. In all experiments, we significantly outperform both interactive proofreading as well as Plaza's method. As a consequence, we are able to provide tools to proofread segmentations more efficiently, and so better tackle large volumes of connectomics imagery.

%The reason why we work on top of an existing segmentation rather than improving the underlying technique, is to explore the error space in a non-linear way. The real world analogy would be inspecting something with a second set of eyes and different expertise.

### 2016-11-04 paper/method.tex
CVPR draft.

\section{Method}
\label{sec:methods}

We first describe our classifier for detecting split errors which is based on a convolutional neural network (CNN). We detail the CNN architecture, input features and the training method. We then describe how the same classifier can be used to detect merge errors and how we create potential corrections. The classifiers are integrated into an existing proofreading workflow as reported after. Finally, we explore an active label suggestion method which reorders the ranking obtained by our classifiers and maximizes the information gain provided by each potential correction.

\subsection{Split Error Detection}

We build a split error classifier with output $p$ using a convolutional neural network (CNN) to check whether an edge within an existing automatic segmentation is valid ($p=0$) or not ($p=1$). Rather than analyzing every input pixel, the classifier operates only on segment boundaries which requires less pixel context and is faster. Our approach was inspired by Bogovic \etal~\cite{BogovicHJ13} but works with 2D slices rather than 3D volumes. This enables proofreading prior or in parallel to an expensive alignment of individual EM images.
\\~\\
\textbf{Convolutional Neural Network Architecture.} Split error detection of a given boundary is really a binary classification task since the boundary is either correct or erroneous. However, in reality the score $p$ is between 0 and 1. The classification complexity arises from hundreds of different cell types in connectomics data rather than from the classification decision. Intuitively, this yields a wider (meaning more filters) rather than a deeper (meaning more layers) architecture. We explored different architectural configurations - including residual networks~\cite{resnet} - by performing a brute force parameter search and comparing precision and recall (see supplementary materials). Our final CNN configuration for split error detection is composed of four convolutional layers, each followed by max pooling as well as dropout regularization to prevent overfitting due to limited training data. Fig. \ref{fig:architecture} shows the CNN architecture for split error detection.
\\~\\
\textbf{Classifier Inputs.} To train the CNN for split error detection, we take boundary context information into consideration for the decision making process. For this, we grab a $75x75$ pixel patch at the center of an existing boundary. This covers approximately $80\%$ of all boundaries in real-world connectomics data with nanometer resolution. If the boundary edge is not fully covered, we sample up to 10 non-overlapping patches along the boundary and combine the resulting score by weighted averaging based on boundary length coverage per patch. In their paper, Bogovich \etal propose to use grayscale image data, corresponding boundary probabilities, and  a single binary mask combining the two neighboring labels as features for their recursive neural network~\cite{BogovicHJ13}. We are building on this set of features as inputs for our CNN and create a stacked pixel patch. However, we observed that the boundary probability information generated from EM images is often misleading due to noise or artefacts in the data. This can result in merge errors within the automatic segmentation. To better direct our classifier to train on the true boundary edge, we extract the border between two segments. We then dilate this border by 5 pixels to consider slight edge ambiguities and use this additional binary mask as another feature to create a 4-channel input patch. Fig. \ref{fig:cnn_inputs} shows examples of correct and erroneous feature patches and their corresponding automatic segmentation and ground truth.

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/cnn_inputs.png}
\end{center}
  \vspace{-4mm}
   \caption{Example inputs for learning correct splits and split errors as reflected in the segmentation relative to the ground truth. Image, membrane probabilities, merged binary labels, and a dilated border mask are combined to 4-channel input patches.}
\label{fig:cnn_inputs}
\end{figure}

\textbf{Training.} To initially train our network, we use the blue 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels). The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse. The resolution of our dataset is $3\, nm$ per pixel, and the section thickness is $30\, nm$. The image data and a manually-labeled expert segmentation is publicly available as ground truth for the entire dataset\footnote{The Kasthuri 3-cylinder mouse cortex volume is available at  https://software.rc.fas.harvard.edu/lichtman/vast/}. We use the first 250 sections of the data for training and validation and the last 50 for testing. We use a state-of-the-art method to create a dense automatic segmentation of the data. To generate training data, we identify correct regions and split errors in the automatic segmentation by intersection with ground truth regions. This is required since extracellular space is not labeled in the ground truth but in our dense automatic segmentation. From these regions, we sample 120,000 correct and 120,000 split error patches with 4-channels as described above. The patches are normalized and to further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$. The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research as well as a brute force parameter search within a limited range (see supplementary material). The final parameters and training results are listed in table~\ref{tab:parameters}. For baseline comparison, we also list the parameters and training results of focused proofreading in this table but elaborate on these further in section \ref{sec:evaluation}. Our CNN configuration results in approximately 170,000 learnable parameters. We assume that training has converged if the validation loss does not decrease for 50 epochs.

\begin{table}[h]
%\resizebox{\textwidth}{!}{%
\tiny
\begin{tabular}{@{}c|c|c|c|c|c|c@{}}
& \textbf{cost [m]} & \textbf{Val. loss} & \textbf{Val. acc.} & \textbf{Test acc.} & \textbf{Prec./Recall} & \textbf{F1 Score} \\ 
\hspace{1mm}
\begin{tabular}{@{}l@{}}
\textbf{Guided Proofreading} \\ Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2-4: 48 \\ Dense units: 512 \\ Learning rate: 0.03-0.00001\\ Momentum: 0.9-0.999\\Mini-Batchsize: 128\\~\\
 \end{tabular}
 & 383  & 0.0845  & 0.969  & 0.94  & 0.94/0.94  & 0.94 \\ 
\hline 
\begin{tabular}{@{}l@{}}
\\
\textbf{Focused Proofreading} \\ 
Iterations: 3 \\
Learning strategy: 2\\
Mito agglomeration: Off\\
Threshold: 0.2
 \end{tabular}
 & 43  & ?  & ?  & 0.839  & ?/?  & ? \\ 
\end{tabular} 
\vspace{1mm}
\caption{Training parameters, cost and results of our guided proofreading classifier versus focused proofreading by Plaza \cite{focused_proofreading}. Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 graphics card). While the training of our classifier is more expensive, testing accuracy is superior. }
\label{tab:parameters}
\end{table}

For performance comparison on data of a different species, in particular on fruitfly brain (drosophila), we retrain our network. The training procedure is according to our initial training and network architecture as well as parameters are not changed. We further elaborate on the drosophila datasets in section~\ref{sec:evaluation}. Fig.~\ref{fig:roc} displays receiver operating characteristics (ROC) for  guided proofreading trained on mouse and drosophila data, as well as our comparison baseline focused proofreading trained on these datasets respectively.

\begin{figure}[h]
  \vspace{-5mm}
\begin{center}
  \includegraphics[width=\linewidth]{gfx/roc.pdf}
\end{center}
  \vspace{-10mm}
   \caption{ROC performance of guided proofreading (GP) and focused proofreading (FP) trained separately on mouse and drosophila brain images. The area under the curve indicates better performance for GP.}
\label{fig:roc}
\end{figure}

\subsection{Merge Error Detection}

Identification and correction of merge errors is more challenging, because we must look inside segmentation regions for missing or incomplete boundaries and then propose the correct boundary. However, we can reuse the same trained CNN for this task. Similar to guided volume editing by Karimov~\etal~\cite{karimov_guided_volume_editing} we generate potential borders within a segment. For each segmentation label, we dilate the label by 20 pixel and generate 30 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. For watershed, we use the inverted gray scale EM image as features. This yields 30 corresponding splits. Dilation of the segment prior to watershed is motivated by our observation that the generated split then actually hogs the real membrane boundary. These boundaries are then individually rated using our split error classifier. For this, we invert the probability score meaning that a correct split (previously encoded as $p=0$) is most likely a candidate for a merge error (now encoded as $p=1$). In other words, if a generated boundary is ranked as correct, it probably should be in the segmentation. Fig. \ref{fig:merge_error} illustrates this procedure.

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/merge_error.png}
\end{center}
  \vspace{-4mm}
   \caption{Merge errors are identified by generating randomly seeded watershed borders within a dilated label segment. These borders then are individually rated using the split error CNN by inverting the probability score. This way, a confident rating for a correct split most likely indicates the missing border of the merge error and can be used for correcting the labeling.}
\label{fig:merge_error}
\end{figure}

\subsection{Error Correction}

We use the proposed classifiers in combination to perform corrections of split and merge errors in automatic segmentations. For this, we first perform merge error detection for all existing segments in a data set and store the inverted ranking $1-p$. We then sort the rankings and loop through all of them in greedy fashion, starting with the most likely error. If the inverted score $1-p$ of a merge error is higher than a threshold $p_t$, we mark this merge error for correction. The merge error detection yields the potential new boundary and we can modify the segmentation data to create a new segment accordingly. Depending on the variation of guided proofreading as described in section~\ref{sec:evaluation}, we either perform the correction directly (automatic GP) or we have a user accept or reject the correction (simulated GP or human novice/expert).
Once all merge errors are corrected, we perform split error detection. For this, we perform split error detection and store the ranking $p$ for all existing segments in the for merge errors corrected segmentation. We then sort the rankings and again loop through all of them - the most likely error first. If the score $p$ is higher than a threshold $p_t$, we mark the split error for correction. Potential split errors are identified at the border of two segments. This reduces the correction to merging the segments and is therefore trivial. Similarly to merge errors, we either perform the correction directly or present a user with a yes/no decision. Our experiments have shown that the threshold $p_t$ is the same for merge and split errors which makes sense for a balanced classifier. The only exception is when a user drives the correction process: we then set $p_t$ for split errors to 0 to let the user inspect every possible split error. Inspecting all merge errors is not possible for users due to the sheer amount of generated borders.

\subsection{Application}

Guided proofreading is integrated into an existing workflow for large connectomics data. The GP system is web-based and is designed with a minimalistic user interface showing three components. First, we show the outline of the current labeling of a cell boundary and its proposed correction on top of the EM image data. For the user, it is not possible to distinguish the current labeling and the proposed correction to avoid selection bias. Second, we show a solid overlay of the current and proposed labeling. And finally, to provide context, we show a larger area of the EM image where the potentially erroneous region is highlighted. User interaction is simple and involves one mouse click on either the current labeling or the correction. After interaction, the next potential error is shown. We provide a screenshot of the application as part of the supplementary material.

\subsection{Active Label Suggestion}

In an interactive setting, one way to present patches to the user for proofreading is to order them by the confidence probability of the GP classifier. However, in an active learning setting, where the network is retrained repeatedly on new label evidence, this approach is less likely to decrease segmentation error as, with the new labels, we are only reinforcing what the network already has a high confidence in.
Instead, we apply active label suggestion to guide the user into labeling patches which will be more informative to retraining, and so overall decrease VI faster within the proofreading cycle of label $\rightarrow$ train $\rightarrow$ label. For each patch, we remove the softmax classification layer and look at the activation weights associated with the last dense layer. These become a high-dimensional feature vector. Then, we adapt Anon~\etal~\cite{ANON} to provide label suggestions based on features from the learned CNN, which is based on maximizing the average information gain provided by a candidate patch to label.
A second consideration is that each patch labeled by the user provides evidence to other patches, e.g., correcting a split error redefines an entire boundary, from which multiple candidate patch labelings could have been drawn. As such, when the user labels a patch, we consider all `knock-on' effect patches as also being labeled, and feed these into the active label suggestion system similarly.
In section \ref{sec:evaluation}, we report the difference in performance from using active label suggestion rather than confidence ordering when presenting patches to the user. These results are without retraining the network after new labelings: this should improve results, but would have to be batched to reduce computational load; hence, we leave this for future work.

### 2016-11-04 paper/related_work.tex
CVPR draft.

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/architecture.png}
\end{center}
  \vspace{-4mm}
   \caption{We build the guided proofreading classifiers using a traditional CNN architecture. The network is based on four convolutional layers, each followed by max pooling as well as dropout regularization. The 4-channel input patches are rated as either correct splits or as split errors.}
\label{fig:architecture}
\end{figure*}

\section{Related Work}

Proofreading is performed on top of an existing automatic segmentation. First, this section gives an overview of state-of-the-art automatic segmentation methods. Then, we discuss interactive proofreading tools and recent developments in computer-aided proofreading systems.

\textbf{Automatic Segmentation.} Multi-terabyte EM brain volumes require automatic segmentation~\cite{jain2010,Liu2014,NunezIglesias2013Machine,GALA2014}, but can be hard to classify due to ambiguous intercellular space: the 2013 IEEE ISBI neurites 3D segmentation challenge~\cite{isbi_challenge} showed that existing algorithms which learn from expert-segmented training data still exhibit high error rates.

NeuroProof \cite{neuroproof2013} tries to decrease error rates with interactive learning of agglomeration of over-segmentations of images, based on a random forest classifier. Vazquez-Reina \etal~\cite{amelio_segmentation} propose automatic 3D segmentation by taking whole EM volumes into account rather than a per section approach, then solving a fusion problem with a global context. Kaynig \etal~\cite{kaynig10} propose a random forest classifier coupled with an anisotropic smoothing prior in a conditional random field framework with 3D segment fusion. It is also possible to learn segmentation classification features directly from images with CNNs. Ronneberger \etal~\cite{RonnebergerFB15} use a contracting/expanding CNN path architecture to enable precise boundary localization with small amounts of training data. Lee \etal~\cite{lee2015recursive} recursively train very deep networks with 2D and 3D filters to detect boundaries. Bogovic \etal~\cite{BogovicHJ13} learn 3D features, and show even that unsupervised learning can produce better features than hand-designs. Our work was inspired by this paper and we extend the features reported by Bogovic \etal for our guided proofreading classifiers as described in section \ref{sec:methods}.
These approaches make good progress; however, in general, proofreading is required to improve them through generating more ground-truth segmentations.

\textbf{Interactive Proofreading.} While proofreading is very time consuming, it is fairly easy for humans to perform corrections through splitting and merging segments. One way to perform such corrections is by using expert tools such as Raveler introduced by Chklovskii~\etal~\cite{chklovskii2010, raveler}. This software offers many parameters for tweaking the proofreading process. Created in 2010, Raveler is still used today by professional full-time proofreaders and many similar systems exist as stand-alone products or plugins to existing visualization system,~\eg V3D~\cite{proofreading_bottleneck} or AVIZO~\cite{markus_proofreading}. In contrast to these expert tools, recent works attack the problem of proofreading massive datasets by novices through crowd-sourcing~\cite{saalfeld09,anderson2011,Giuly2013DP2}. A very popular platform is EyeWire presented by Kim \etal~\cite{eyewire_nature}. EyeWire is set up as an online game and participants earn virtual rewards for merging oversegmented labeling to reconstruct the retina cells.
A range of proofreading tools exist in-between expert systems and online games such as Mojo and \textit{Dojo} developed by Haehn \etal~\cite{haehn_dojo_2014,Neuroblocks}. Mojo provides a simple scribble interface for error correction, and Dojo extends this for distributed proofreading via a minimalistic web-based user interface. The authors define requirements for general proofreading tools, and then evaluate the accuracy and speed of Raveler, Mojo, and Dojo through a quantitative user study (Sec. 3 and 4)~\cite{haehn_dojo_2014}. In this paper, we use the Dojo system as a baseline for interactive proofreading and extend the experiment reported by Haehn \etal, where Raveler, Mojo, and Dojo are compared in terms of accuracy and speed.
All interactive proofreading solutions require the user to find potential errors manually which takes the majority of time~\cite{proofreading_bottleneck,haehn_dojo_2014}. Recent works propose computer-aided proofreading systems which help with this visual search task.

%Most relevant methods here use heuristics to analyze the image data to find potential errors. 
\textbf{Computer-aided Proofreading.} To reduce the time spent looking for errors, Plaza proposed \textit{focused proofreading} (FP) ~\cite{focused_proofreading}. His approach finds split errors by analyzing segment size ratios across slices and then offers yes/no questions to correct these errors. Plaza reports that additional processing beyond FP is required to find merge errors. His method is freely available as open source software and is integrated into Raveler. This makes it feasible for us to use FP as a baseline for evaluating guided proofreading as described in section \ref{sec:evaluation}. A similar approach was published by Karimov \etal as guided volume editing~\cite{karimov_guided_volume_editing}. Measuring differences in histogram distributions in image data enables to find potential split and merge errors in the corresponding segmentation. For merge errors, the authors generate possible boundaries using watershed which inspired our approach as described in section \ref{sec:methods}. Guided volume editing was designed to let expert users correct labeled computer-tomography datasets by performing several interactions per correction. While focused proofreading and guided volume editing both use a heuristical approach to analyze the image data, Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}. The authors track uncertainty throughout the automatic labeling by training a conditional random field. This method is really a segmentation technique but it is possible to use the uncertainty information to present potential regions for proofreading. Uzunbas' paper describes a great idea but requires further work to overcome the requirement of isotropic volumes, a property not given for most connectomics datasets. Our approach, guided proofreading, works on isotropic as well as anisotropic data, and finds merge and split errors.

### 2016-11-04 matlab/ActiveLabelSuggestion.m
The matlab active learning bridge.

@@ -1,0 +1,31 @@
+function [SLabels] = ActiveLabelSuggestion(GInv, CandIdx, LabelFlag)
+
+%%% [length(LabelFlag),length(LabelFlag)] == size(GInv)
+%%% CandIdx should be a subset of [1:length(LabelFlag)];
+
+LIdx = find(LabelFlag==1);
+ULIdx = find(LabelFlag~=1);
+
+CandIdx = setdiff(CandIdx,LIdx);
+OrgPredUnc = diag(GInv);
+
+%%% estimate the updated predictive variance
+    VarRed = ones(length(CandIdx),1)*-1e10;        
+    for j=1:length(CandIdx)
+        %%% for rank 1 update
+            GInvTemp = GInv;
+            GITemp = GInvTemp(:,CandIdx(j));
+            PredUnc = diag(GInvTemp)-1/(1+GInvTemp(CandIdx(j),CandIdx(j)))*(GITemp.^2);
+        %%% for rank 1 update
+        VarRed(j) = sum(OrgPredUnc(ULIdx)-PredUnc(ULIdx))/length(ULIdx);
+    end
+%%% estimate updated predictive variance
+
+[~,VarLabel] = sort(VarRed,'descend');
+SLabels = CandIdx(VarLabel);
+
+% GInvUpdate = GInv;
+% for j=1:length(SLabels)
+%     GITemp = GInvUpdate(:,SLabels(j));
+%     GInvUpdate = GInvUpdate-1/(1+GInvUpdate(SLabels(j),SLabels(j)))*(GITemp*GITemp');
+% end

### 2016-11-04 matlab/BuildALSApproximation.m

@@ -1,0 +1,31 @@
+function BInv = BuildALSApproximation( LGReg, Lambda, StartingLabelFlags )
+% Build the structures needed for Kwang In's active label suggestion
+% approximation
+
+% Kwang In's example uses a sub-sampled matrix, but apparently it will work
+% at full resolution quickly enough for small (< 10000) datasets.
+% As we won't need anything greater, let's go for the full hog.
+
+
+B = Lambda * full(LGReg) + diag(StartingLabelFlags);
+
+% build inverse full regularization matrix
+try
+	CholB = chol(B);
+	CholBInv = inv(CholB);
+	BInv = CholBInv*CholBInv';
+catch
+    BInv = inv(B + 1e-9 * eye(size(B)) );
+end
+
+% Inputs:
+% - GInv is BInv.
+% - SubCandIdx is an array of indices of labelled examples into the full array
+% E.G., a 10-large number, with items 5,6 labelled, SubCandIdx would
+% contain [5,6];
+% - SubLabelFlag is full length, e.g, [0,0,0,0,1,1,0,0,0,0].
+%
+% Outputs:
+% - SLabels, a list of indices in descending order of variance.
+%[SLabels] = ActiveLabelSuggestion(GInv, SubCandIdx, SubLabelFlag);
+

### 2016-11-04 matlab/BuildLGRegularizer.m

@@ -1,0 +1,28 @@
+function LGReg = BuildLGRegularizer( x, ManDim, KNSize )
+
+addpath './LGComp/';
+
+%%% parameters for LG
+%    LGParam.ManDim    = 17;   %%% 5:5:20
+%    LGParam.KNSize    = 30;   %%% [10:30]: small # data points(<1000) [20:60]: large # data points
+%    LGParam.Lambda    = 1e-8; %%% 1e-9:1e-5 (orders of 10 increases)
+%%% parameters for LG
+
+[NumDataPoints,~] = size(x);
+
+kNN = 200;
+if( kNN > NumDataPoints )
+    kNN = NumDataPoints;
+end
+
+if( KNSize > NumDataPoints )
+    KNSize = NumDataPoints;
+end
+
+%[NNIdx,KDistanceSq] = GetKNN(Data.x, 4000);  % To compute LapParam.SigmaSq & ILapParam.SigmaSq
+[NNIdx,KDistanceSq] = GetKNN(x, kNN);
+
+%%% building LG regularizer
+    LGNNIdx = NNIdx(:,1:KNSize);
+    [LGReg] = ConstructLGOpr(x, LGNNIdx, ManDim);
+%%% building LG regularizer

### 2016-11-04 matlab/LGComp/BackwardPCA.m

@@ -1,0 +1,15 @@
+function [Original] = BackwardPCA(Feature, Backward, Mean, LatDim)
+
+Backward = Backward(:,1:LatDim);
+
+[ISize, FSize] = size(Backward);
+[FNum, FeatureSize] = size(Feature);
+
+if FSize ~= FeatureSize
+    display('Incompatible model..');
+    return;
+end
+
+Original = Backward*Feature';
+Original = Original';
+Original = (Original+repmat(Mean,FNum,1));

### 2016-11-04 matlab/LGComp/ComputeGaussianKernelL.m

@@ -1,0 +1,10 @@
+function [K] = ComputeGaussianKernel(Input, SigmaSq)
+
+[NumTrnPtns,TrnInputSize] = size(Input);
+K = zeros(NumTrnPtns,NumTrnPtns);
+LineNormSq = sum(Input.^2,2)';
+for i=1:NumTrnPtns,
+    InnerProduct = Input(i,:)*Input';
+    DistanceSq = abs(LineNormSq(i)+LineNormSq-2*InnerProduct);
+    K(i,:) = exp(-DistanceSq/SigmaSq);
+end

### 2016-11-04 matlab/LGComp/ComputeLinearX.m

@@ -1,0 +1,17 @@
+function [X] = ComputeLinearX(Nodes)
+
+[NumNodes,Dim] = size(Nodes);
+CoordCombSize = Dim+1;
+
+X = zeros(NumNodes,CoordCombSize);
+
+for NIdx = 1:NumNodes
+    RIdx = 1;
+
+    for i=1:Dim
+        X(NIdx,RIdx) = Nodes(NIdx,i);
+        RIdx = RIdx+1;
+    end
+
+    X(NIdx,RIdx) = 1;
+end

### 2016-11-04 matlab/LGComp/ConstructLGOpr.m

@@ -1,0 +1,84 @@
+function [L] = ConstructLGOpr(Nodes, NNIdx, ManDim)
+
+[NumNodes,AmbDim] = size(Nodes);
+
+%%% sparse version
+    BlSpMatSize = 300000;
+    MaxNumNN = size(NNIdx,2);
+    NumNonzero = NumNodes*MaxNumNN^2;
+    BlSpMatNum = ceil(NumNonzero/BlSpMatSize);
+    BlSpL = cell(BlSpMatNum,1);
+%%% sparse version
+
+SpMatIdx = 1;
+SpEleCounter = 1;
+SpRowIdx = zeros(BlSpMatSize,1);
+SpColIdx = zeros(BlSpMatSize,1);
+LVal = zeros(BlSpMatSize,1);
+for i=1:NumNodes
+    NumNeighbors = find(NNIdx(i,:)<=0,1);
+    if ~isempty(NumNeighbors)
+        NumNeighbors = NumNeighbors-1;
+    else
+        NumNeighbors = length(NNIdx(i,:));
+    end
+    G = Nodes(NNIdx(i,1:NumNeighbors),:);   
+
+    CtBase = Nodes(i,:);
+    [NG,TS] = GetNormalCoordGDim(CtBase, G, ManDim);
+    [NBase,TS] = GetNormalCoordGGivenTS(CtBase,TS);
+    BaseIndexInG = find(NNIdx(i,1:NumNeighbors)==i,1);
+    
+    %%% Adaptively choose the SigmaSq
+        %%% recalculate distances for normal coordinates
+            NGNormSq = sum(NG.^2,2)';
+            NBaseNormSq = sum(NBase.^2,2)';
+            DistSq = NG*NBase';
+            DistSq = DistSq';
+            DistSq = abs(NGNormSq-2*DistSq+NBaseNormSq);
+        %%% recalculate distances for normal coordinates
+        RParam = mean(sqrt(DistSq))*0.1;
+        %RParam = mean(sqrt(DistSq))*0.01;
+        RParam = RParam^2;
+    %%% Adaptively choose the SigmaSq
+    [LocalL] = ConstructLocalRegOperatorGaussianBZLN(NG, RParam, BaseIndexInG);
+    for j=1:NumNeighbors
+        GRIdx = NNIdx(i,j);
+
[…]

### 2016-11-04 matlab/LGComp/ConstructLocalRegOperatorGaussianBZLN.m

@@ -1,0 +1,55 @@
+function [L] = ConstructLocalRegOperatorGaussianBZLN(Nodes, SigmaSq, BaseIndexInG)
+
+% [K] = ComputeGaussianKernel(Nodes, SigmaSq);
+[K] = ComputeGaussianKernelL(Nodes, SigmaSq);
+
+%%% construct the null operator
+    IndMat = zeros(size(K));
+    IndMat(:,BaseIndexInG) = 1;
+    LIdxMat = eye(size(K))-IndMat;
+    %%% add linear functions to the null space
+%         [X] = ComputeLinearX(Nodes);
+%         X = X(:,1:end-1);
+        X = Nodes;
+        try
+            %spparms('spumoni',2)
+            %PInvX = inv(X'*X)*X';
+            PInvX = (X'*X) \ X';
+        catch
+            PInvX = pinv(X);
+        end
+        LIdxMat = X*PInvX*LIdxMat;
+%         LIdxMat = X*pinv(X)*LIdxMat;
+        LIdxMat = eye(size(LIdxMat))-IndMat-LIdxMat;
+    %%% add linear functions to the null space
+%%% construct the null operator
+
+%%% unregularized
+    try
+%         L = inv(K);
+        L = pinv(K);
+%         SMALLNUM = 1e-11;
+%         L = inv(K+SMALLNUM*eye(size(K)));
+    catch
+        L = pinv(K);
+    end
+%     try
+%         L = pinv(K);
+%     catch
+%         SMALLNUM = 1e-11;
+%         L = inv(K+SMALLNUM*eye(size(K)));
+%     end
+%%% unregularized
+% %%% partially regularized
+%     lambda = 1e-7;
+%     L = inv(K+lambda*eye(size(K)));    
+% %%% partially regularized
+% %%% fully regularized
+%     lambda = 1e-5;
+%     T = inv(K+lambda*eye(size(K)));
+%     L = T'*K*T;
+% %%% fully regularized
+
+%%% subtract out the null space
+    L = LIdxMat'*L*LIdxMat;
+%%% subtract out the null space

### 2016-11-04 matlab/LGComp/ForwardPCA.m

@@ -1,0 +1,19 @@
+function [Feature] = ForwardPCA(Input, Forward, Mean, LatDim)
+
+[FSize, ISize] = size(Forward);
+[INum, InputSize] = size(Input);
+
+if ISize ~= InputSize
+    display('Incompatible model..');
+    return;
+end
+
+Forward = Forward(1:LatDim,:);
+
+CenteredInput = (Input-repmat(Mean,INum, 1));
+% CenteredInput = Input;
+% Feature = Forward*CenteredInput';
+% Feature = Feature';
+Feature = CenteredInput*Forward';
+
+clear CenteredInput;

### 2016-11-04 matlab/LGComp/GetKNN.m

@@ -1,0 +1,56 @@
+function [StoredIdx, KDistance, Input, Stored] = GetKNN(Input, K, Stored)
+
+if nargin >= 3
+    [NumTstPtns,TstInputSize] = size(Input);
+    [NumStoredPtns,StoredInputSize] = size(Stored);
+    if TstInputSize==StoredInputSize
+        StoredIdx = zeros(NumTstPtns,K);
+        KDistance = zeros(NumTstPtns,K);
+        StoredNormSq = sum(Stored.^2,2)';
+        TstNormSq = sum(Input.^2,2)';
+        for i=1: NumTstPtns
+            InnerProduct = Input(i,:)*Stored';
+            DistanceSq = abs(StoredNormSq-2*InnerProduct+TstNormSq(i));
+%             Distance = sqrt(DistanceSq);
+            Distance = DistanceSq;
+            if K>1
+                [Sorted, KIndex] = sort(Distance, 'ascend');
+                StoredIdx(i,:) = KIndex(1:K);
+                KDistance(i,:) = Sorted(1:K);
+            else
+                KDistance(i) = min(Distance);
+                Temp = find(Distance==KDistance(i));
+                StoredIdx(i) = Temp(1);
+            end
+            if mod(i,1000) == 0
+                display(sprintf('Pattern: %d/%d', i, NumTstPtns));
+                pause(0.01);
+            end
+        end
+    else
+        display('Model incompatible..');
+    end
+else    
+    [NumTstPtns,TstInputSize] = size(Input);
+    StoredIdx = zeros(NumTstPtns,K);
+    KDistance = zeros(NumTstPtns,K);
+    TstNormSq = sum(Input.^2,2)';
+    for i=1: NumTstPtns
+        InnerProduct = Input(i,:)*Input';
+        DistanceSq = abs(TstNormSq-2*InnerProduct+TstNormSq(i));
+        Distance = sqrt(DistanceSq);
+        if K>1
+            [Sorted, KIndex] = sort(Distance, 'ascend');
+            StoredIdx(i,:) = KIndex(1:K);
+            KDistance(i,:) = Sorted(1:K);
+        else
+            KDistance(i) = min(Distance);
+            Temp = find(Distance==KDistance(i));
+            StoredIdx(i) = Temp(1);
+        end
+%         if mod(i,1000) == 0
+%             display(sprintf('Pattern: %d/%d', i, NumTstPtns));
+%             pause(0.01);
+%         end
+    end
+end

### 2016-11-04 matlab/LGComp/GetNNStructure.m

@@ -1,0 +1,59 @@
+function [StNodes] = GetNNStructure(Input, K)
+
+StNodes.Nodes.x = Input;
+
+%%% alternative
+%     [NumNodes,SizeNode] = size(Input);
+% %     [StNodes.NNIdx,StNodes.KDistance] = getKNN5(Input',K);
+%     [StNodes.NNIdx,StNodes.KDistance] = NGetTransInvKNN(Input',K);
+% 
+%     StNodes.NNIdx = StNodes.NNIdx';
+%     StNodes.NNIdx = single(StNodes.NNIdx);
+%     StNodes.KDistance = StNodes.KDistance';
+% 
+%     for i=1:NumNodes
+%         [SVal,SIdx] = sort(StNodes.KDistance(i,:),'ascend');
+%         StNodes.KDistance(i,:) = StNodes.KDistance(i,SIdx);
+%         StNodes.NNIdx(i,:) = StNodes.NNIdx(i,SIdx);
+%     end
+%     
+%     StNodes.NNIdx(:,2:end) = StNodes.NNIdx(:,1:end-1);
+%     StNodes.KDistance(:,2:end) = StNodes.KDistance(:,1:end-1);
+% 
+%     for i=1:NumNodes
+%         StNodes.NNIdx(i,1) = i;
+%     end
+%     StNodes.KDistance(:,1) = 0;
+%%% alternative
+
+%%% original
+    [StNodes.NNIdx, StNodes.KDistance, Temp] = GetKNN(StNodes.Nodes.x, K, StNodes.Nodes.x);
+%%% original
+
+StNodes.KNNFlag = 1;
+% %%% For each node, to obtain the indices of nodes whose nearest neighbors include that node
+%     [NumNodes,Dim] = size(StNodes.Nodes.x);
+%     StNodes.NumINN = zeros(1,NumNodes);
+%     for i=1:NumNodes
+%         StNodes.NumINN(i) = length(find(StNodes.NNIdx==i));
+%     end
+%     for i=1:NumNodes
+%         if StNodes.NumINN(i) ~= 0
+%             StNodes.INNIdx{i} = zeros(1,StNodes.NumINN(i));
+%             StNodes.INNLocalIdx{i} = zeros(1,StNodes.NumINN(i));
+%         end
+%         INNCounter = 0;
+%         for j=1:NumNodes
+%             LocalIdx = find(StNodes.NNIdx(j,:)==i);
+%             if ~isempty(LocalIdx)
+%                 INNCounter = INNCounter+1;
[…]

### 2016-11-04 matlab/LGComp/GetNormalCoordGDim.m

@@ -1,0 +1,18 @@
+function [NCoordsRef,TS] = GetNormalCoordGDim(CtBase, CtRef, ManDim)
+
+[NumRef,SizeSpRef] = size(CtRef);
+
+%%% estimate tangent space
+    [TS.Forward, TS.Backward, TS.MeanVector, EValues] = TrainingPCAWrap(CtRef);
+    TS.NCoordDim = ManDim;
+%%% estimate tangent space
+[NCoordBase] = ForwardPCA(CtBase, TS.Forward, TS.MeanVector, TS.NCoordDim);
+TS.Base = NCoordBase;
+%%% project data onto the tangent space        
+    [NCoordsRef] = ForwardPCA(CtRef, TS.Forward, TS.MeanVector, TS.NCoordDim);
+%%% project data onto the tangent space        
+%%% center at base
+    for i=1:NumRef
+        NCoordsRef(i,:) = NCoordsRef(i,:)-TS.Base;
+    end
+%%% center at base    

### 2016-11-04 matlab/LGComp/GetNormalCoordGGivenTS.m

@@ -1,0 +1,32 @@
+function [NCoordsRef,TS] = GetNormalCoordGGivenTS(CtRef,TS)
+
+% TRUNCLIMIT = 0.1e-5;
+[NumRef,SizeSpRef] = size(CtRef);
+
+%%% get direction vectors in normal coordinates
+    %%% project data onto the tangent space
+        [NCoordsRef] = ForwardPCA(CtRef, TS.Forward, TS.MeanVector, TS.NCoordDim);
+    %%% project data onto the tangent space
+    %%% center at base
+        for i=1:NumRef
+            NCoordsRef(i,:) = NCoordsRef(i,:)-TS.Base;
+        end
+    %%% center at base    
+%%% get direction vectors in normal coordinates
+
+% %%% calculate geodesic distances
+%     GDist = zeros(1,NumRef);
+%     for i=1:NumRef
+%         GDist(i) = GeodesicDistinS(CtBase,CtRef(i,:),R);
+%         if GDist(i)<TRUNCLIMIT
+%             GDist(i) = 0;
+%         end
+%     end
+% %%% calculate geodesic distances
+% %%% resize vectors
+%     for i=1:NumRef
+%         if GDist(i)>0
+%             NCoordsRef(i,:) = NCoordsRef(i,:)/norm(NCoordsRef(i,:),2)*GDist(i);
+%         end
+%     end
+% %%% resize vectors

### 2016-11-04 matlab/LGComp/PerformLocalPCA.m

@@ -1,0 +1,12 @@
+function [LPCA] = PerformLocalPCA(Data, NNIdx)
+
+[NumDps,SizeDps] = size(Data);
+LPCA.EMat = zeros(NumDps,SizeDps,SizeDps);
+LPCA.Means = zeros(NumDps,SizeDps);
+
+for i=1:NumDps
+    LKNNs = Data(NNIdx(i,:),:);
+    [Forward, Backward, MeanVector, EValues] = TrainingPCAWrap(LKNNs);
+    LPCA.EMat(i,:,:) = Forward;
+    LPCA.Means(i,:) = MeanVector;
+end

### 2016-11-04 matlab/LGComp/SemiSupLearn.m

@@ -1,0 +1,39 @@
+function [f,L] = SemiSupLearn(Labels, L, Lambda)  % K on paper is L here.
+
+[SizeL,~] = size(L);
+[NumNodes] = length(Labels.y);
+
+if SizeL ~= NumNodes
+    error('L size should be the same as Y');
+    return;
+end
+
+A = Lambda*L;
+c = zeros(NumNodes,1);  % c is Ly
+
+% Looping?!
+% Can we do this? A + diag(Labels.LFlag)
+% c is just Labels.y (implicitly LFlag will be set correctly on passing in)
+for u=1:NumNodes
+    if Labels.LFlag(u) > 0
+        c(u) = Labels.y(u);
+        A(u,u) = A(u,u)+1;
+    end
+end
+
+f = A\c;
+
+
+% Inverse of A (inv(A)) and extracting the diagonal component of the
+% result will capture the 'invariance' - the larger the value, the less
+% certain (larger the variance). Sample this for k largest values to pick
+% sample.
+
+% If not invertible, add along diagonal very small values (1e-9) and then
+% invert.
+
+%try
+%    InvA = inv(A);
+%catch
+%    InvA = inv(A+1e-9*eye(size(A)));
+%end

### 2016-11-04 matlab/LGComp/TrainingPCA.m

@@ -1,0 +1,43 @@
+function [Forward, Backward, MeanVector, EValues] = TrainingPCA(Data)
+
+[NumPtns, OutputSize] = size(Data);
+MeanVector = mean(Data,1);
+for i=1:NumPtns
+    Data(i,:) = Data(i,:)-MeanVector;
+end
+%     Data = (Data-repmat(MeanVector,NumPtns,1));
+
+%     Cov = Data'*Data;
+%     if NumPtns>1
+%         Cov = Cov/(NumPtns-1);
+%     end
+Cov = cov(Data);
+[evecs,evals] = eig(Cov);
+evals = diag(evals)';
+
+if OutputSize > 1
+    if evals(1)<evals(end)
+        evecs = fliplr(evecs);
+        evals = fliplr(evals);
+    else
+        display('ho.');
+    end
+end
+
+Forward = evecs';
+Backward = Forward';
+EValues = evals;
+
+%     StdDev = sqrt(Evals);
+%     for i=1:LatDim,
+%         Forward(i,:) = Forward(i,:)/StdDev(i);
+%     end
+%     for i=1:LatDim,
+%         Backward(:,i) = Backward(:,i)*StdDev(i);
+%     end
+
+%     a=diag(Backward*Forward);
+%     a(1:20)
+%     clear a;
+
+clear evecs evals Cov;

### 2016-11-04 matlab/LGComp/TrainingPCAInDual.m

@@ -1,0 +1,34 @@
+function [Forward, Backward, MeanVector, EValues] = TrainingPCAInDual(Data)
+
+[NumPtns, OutputSize] = size(Data);
+
+ADimData = min(NumPtns,OutputSize);
+
+MeanVector = mean(Data,1);
+for i=1:NumPtns
+    Data(i,:) = Data(i,:)-MeanVector;
+end
+
+K = Data*Data';
+[evecs,evals] = eig(K);
+evals = diag(evals)';
+
+if OutputSize > 1
+    if evals(1)<evals(end)
+        evecs = fliplr(evecs);
+        evals = fliplr(evals);
+    else
+        display('ho.');
+    end
+end
+
+for i=1:NumPtns
+    if evals(i)>0
+        evecs(:,i) = evecs(:,i)/sqrt(evals(i));
+    end
+end
+
+Forward = evecs'*Data;
+Forward = Forward(1:ADimData,:);
+EValues = evals(1:ADimData)/(NumPtns-1);
+Backward = Forward';

### 2016-11-04 matlab/LGComp/TrainingPCAWrap.m

@@ -1,0 +1,9 @@
+function [Forward, Backward, MeanVector, EValues] = TrainingPCAWrap(Data)
+
+[NumPtns, OutputSize] = size(Data);
+
+if NumPtns > OutputSize*2;
+    [Forward, Backward, MeanVector, EValues] = TrainingPCA(Data);
+else
+    [Forward, Backward, MeanVector, EValues] = TrainingPCAInDual(Data);
+end

### 2016-11-04 matlab/RegressLG.m

@@ -1,0 +1,16 @@
+function LGf = RegressLG( LGReg, y, LFlag, Lambda )
+
+addpath './LGComp/';
+
+%%% parameters for LG
+%    LGParam.ManDim    = 17;   %%% 5:5:20
+%    LGParam.KNSize    = 30;   %%% [10:30]: small # data points(<1000) [20:60]: large # data points
+%    LGParam.Lambda    = 1e-8; %%% 1e-9:1e-5 (orders of 10 increases)
+%%% parameters for LG
+
+Labels.y = y;
+Labels.LFlag = LFlag;
+
+%%% solving LG system
+    [LGf,LGReg] = SemiSupLearn(Labels, LGReg, Lambda);
+%%% solving LG system

### 2016-11-04 matlab/UpdateALSApproximation.m

@@ -1,0 +1,12 @@
+function BInv = UpdateALSApproximation( BInv, SLabels )
+
+% Update ALS approximation matrix
+% Inputs:
+% - BInv is the approximation matrix
+% - SLabels is a list of newly added label indices since the last update
+% Outputs:
+% - Updated BInv
+for k=1:length(SLabels)
+    GITemp = BInv(:,SLabels(k));
+    BInv = BInv-1/(1+BInv(SLabels(k),SLabels(k)))*(GITemp*GITemp');
+end

### 2016-11-04 raveler/ray/ray/__init__.py

@@ -1,0 +1,18 @@
+"""
+Ray
+===
+
+    Ray is a Python package for nD image segmentation. 
+"""
+
+import sys, logging
+if sys.version_info[:2] < (2,6):
+    logging.warning('Ray has not been tested on Python versions prior to 2.6'+
+        ' (%d.%d detected).'%sys.version_info[:2])
+
+__author__ = 'Juan Nunez-Iglesias <jni@janelia.hhmi.org>, '+\
+             'Ryan Kennedy <kenry@cis.upenn.edu>'
+del sys, logging
+
+__all__ = ['agglo', 'morpho', 'evaluate', 'viz', 'imio', 'classify',
+    'stack_np', 'app_logger', 'option_manager', 'features']

### 2016-11-04 raveler/ray/ray/agglo.py

@@ -1,0 +1,1167 @@
+# built-ins
+from itertools import combinations, izip, repeat, product
+import itertools as it
+import argparse
+import random
+import sys
+import logging
+import json
+from copy import deepcopy
+from math import isnan
+
+import pdb
+
+# libraries
+from numpy import array, mean, zeros, zeros_like, uint8, int8, where, unique, \
+    ones_like, finfo, size, double, transpose, newaxis, uint32, nonzero, \
+    median, exp, ceil, dot, log2, float, ones, arange, inf, flatnonzero, \
+    intersect1d, dtype, squeeze, sqrt, reshape, setdiff1d, argmin, sign, \
+    concatenate, nan, __version__ as numpyversion, unravel_index, bincount
+import numpy as np
+from scipy.stats import sem
+from scipy.sparse import lil_matrix
+from scipy.misc import comb as nchoosek
+from scipy.ndimage.measurements import label
+from networkx import Graph, biconnected_components
+from networkx.algorithms.traversal.depth_first_search import dfs_preorder_nodes
+from networkx.algorithms.components.connected import connected_components
+
+# local modules
+import morpho
+import iterprogress as ip
+from ncut import ncutW
+from mergequeue import MergeQueue
+from evaluate import contingency_table, split_vi, xlogx
+import features
+import classify
+from classify import DefaultRandomForest, get_classifier, \
+    unique_learning_data_elements, concatenate_data_elements
+
+arguments = argparse.ArgumentParser(add_help=False)
+arggroup = arguments.add_argument_group('Agglomeration options')
+arggroup.add_argument('-t', '--thresholds', nargs='+', default=[128],
+    type=float, metavar='FLOAT',
+    help='''The agglomeration thresholds. One output file will be written
+        for each threshold.'''
+)
+arggroup.add_argument('-l', '--ladder', type=int, metavar='SIZE',
+    help='Merge any bodies smaller than SIZE.'
+)
+arggroup.add_argument('-p', '--pre-ladder', action='store_true', default=True,
+    help='Run ladder before normal agglomeration (default).'
+)
+arggroup.add_argument('-L', '--post-ladder', 
+    action='store_false', dest='pre_ladder',
+    help='Run ladder after normal agglomeration instead of before (SLOW).'
+)
+arggroup.add_argument('-s', '--strict-ladder', type=int, metavar='INT', 
+    default=1,
+    help='''Specify the strictness of the ladder agglomeration. Level 1
+        (default): merge anything smaller than the ladder threshold as 
[…]

### 2016-11-04 raveler/ray/ray/features/base.py

@@ -1,0 +1,101 @@
+import numpy as np
+
+class Null(object):
+    def __init__(self, *args, **kwargs):
+        self.default_cache = 'feature-cache'
+
+    def __call__(self, g, n1, n2=None):
+        return self.compute_features(g, n1, n2)
+
+    def write_fm(self, json_fm={}):
+        return json_fm
+
+    def compute_features(self, g, n1, n2=None):
+        if n2 is None:
+            c1 = g.node[n1][self.default_cache]
+            return self.compute_node_features(g, n1, c1)
+        if len(g.node[n1]['extent']) > len(g.node[n2]['extent']):
+            n1, n2 = n2, n1 # smaller node first
+        c1, c2, ce = [d[self.default_cache] for d in 
+                            [g.node[n1], g.node[n2], g[n1][n2]]]
+        return np.concatenate((
+            self.compute_node_features(g, n1, c1),
+            self.compute_node_features(g, n2, c2),
+            self.compute_edge_features(g, n1, n2, ce),
+            self.compute_difference_features(g, n1, n2, c1, c2)
+        ))
+    def create_node_cache(self, *args, **kwargs):
+        return np.array([])
+    def create_edge_cache(self, *args, **kwargs):
+        return np.array([])
+    def update_node_cache(self, *args, **kwargs):
+        pass
+    def update_edge_cache(self, *args, **kwargs):
+        pass
+    def pixelwise_update_node_cache(self, *args, **kwargs):
+        pass
+    def pixelwise_update_edge_cache(self, *args, **kwargs):
+        pass
+    def compute_node_features(self, *args, **kwargs):
+        return np.array([])
+    def compute_edge_features(self, *args, **kwargs):
+        return np.array([])
+    def compute_difference_features(self, *args, **kwargs):
+        return np.array([])
+
+
+class Composite(Null):
+    def __init__(self, children=[], *args, **kwargs):
+        super(Composite, self).__init__()
+        self.children = children
+ 
+    def write_fm(self, json_fm={}):
+        for child in self.children:
+            json_fm.update(child.write_fm(json_fm))
+        return json_fm
+   
+    def create_node_cache(self, *args, **kwargs):
+        return [c.create_node_cache(*args, **kwargs) for c in self.children]
+
+    def create_edge_cache(self, *args, **kwargs):
+        return [c.create_edge_cache(*args, **kwargs) for c in self.children]
+    
+    def update_node_cache(self, g, n1, n2, dst, src):
[…]

### 2016-11-04 raveler/ray/ray/features/convex_hull.py

@@ -1,0 +1,142 @@
+# python standard library
+import logging
+import itertools as it
+
+# numpy/scipy
+import numpy as np
+from scipy import ndimage as nd
+from scipy.misc.common import factorial
+from numpy.linalg import det
+try:
+    from scipy.spatial import Delaunay
+except ImportError:
+    logging.warning('Unable to load scipy.spatial.Delaunay. '+
+        'Convex hull features not available.')
+
+# local imports
+from . import base
+
+class Manager(base.Null):
+    def __init__(self, *args, **kwargs):
+        super(Manager, self).__init__()
+
+    def write_fm(self, json_fm={}):
+        if 'feature_list' not in json_fm:
+            json_fm['feature_list'] = []
+        json_fm['feature_list'].append('convex-hull')
+        json_fm['convex-hull'] = {}
+        return json_fm
+
+    def convex_hull_ind(self, g, n1, n2=None):
+        m = np.zeros_like(g.watershed); 
+        if n2 is not None:
+            m.ravel()[list(g[n1][n2]['boundary'])]=1
+        else:
+            m.ravel()[list(g.node[n1]['extent'])] = 1
+        m = m - nd.binary_erosion(m) #Only need border
+        ind = np.np.array(np.nonzero(m)).T
+        return ind
+
+
+    def convex_hull_vol(self, ind, g):
+        # Compute the convex hull of the region
+        try:
+            tri = Delaunay(ind)
+        except:
+            # Just triangulate bounding box
+            mins = ind.min(axis=0)
+            maxes = ind.max(axis=0)
+            maxes[maxes==mins] += 1
+            ind = np.array(list(it.product(*tuple(np.array([mins,maxes]).T))))
+            tri = Delaunay(ind)
+        vol = 0
+        for simplex in tri.vertices:
+            pts = tri.points[simplex].T
+            pts = pts - np.repeat(pts[:,0][:, np.newaxis], pts.shape[1], axis=1)
+            pts = pts[:,1:]
+            vol += abs(1/float(factorial(pts.shape[0])) * det(pts))
+            return vol,tri 
+
+    def create_node_cache(self, g, n):
+        vol, tri = self.convex_hull_vol(self.convex_hull_ind(g,n), g)
+        return np.array([tri,vol])
+
+    def create_edge_cache(self, g, n1, n2):
+        vol, tri = self.convex_hull_vol(self.convex_hull_ind(g,n1,n2), g)
[…]

### 2016-11-04 raveler/ray/ray/features/histogram.py

@@ -1,0 +1,194 @@
+import numpy as np
+
+from . import base
+ 
+class Manager(base.Null):
+    def __init__(self, nbins=4, minval=0.0, maxval=1.0, 
+            compute_percentiles=[], oriented=False, 
+            compute_histogram=True, use_neuroproof=False, *args, **kwargs):
+        super(Manager, self).__init__()
+        self.minval = minval
+        self.maxval = maxval
+        self.nbins = nbins
+        self.oriented = oriented
+        self.compute_histogram = compute_histogram
+        self.use_neuroproof = use_neuroproof
+
+        try:
+            _ = len(compute_percentiles)
+        except TypeError: # single percentile value given
+            compute_percentiles = [compute_percentiles]
+        self.compute_percentiles = compute_percentiles
+   
+    @classmethod
+    def load_dict(cls, fm_info):
+        obj = cls(
+            fm_info['nbins'],
+            fm_info['minval'], 
+            fm_info['maxval'],
+            fm_info['compute_percentiles'],
+            fm_info['oriented'],
+            fm_info['compute_histogram'],
+            fm_info['use_neuroproof'])
+        return obj
+ 
+    def write_fm(self, json_fm={}):
+        if 'feature_list' not in json_fm:
+            json_fm['feature_list'] = []
+        json_fm['feature_list'].append('histogram')
+        json_fm['histogram'] = {
+            'minval' : self.minval, 
+            'maxval' : self.maxval, 
+            'nbins' : self.nbins, 
+            'oriented' : self.oriented, 
+            'compute_histogram' : self.compute_histogram, 
+            'use_neuroproof' : self.use_neuroproof, 
+            'compute_percentiles' : self.compute_percentiles
+        } 
+        return json_fm
+
+    def histogram(self, vals):
+        if vals.ndim == 1:
+            h = np.histogram(vals, bins=self.nbins, 
+                             range=(self.minval,self.maxval))
+            return h[0].astype(np.double)[np.newaxis, :]
+        elif vals.ndim == 2:
+            return np.concatenate(
+                    [self.histogram(vals_i) for vals_i in vals.T], axis=0)
+        else:
+            raise ValueError('HistogramFeatureManager.histogram expects '+
+                'either a 1-d or 2-d np.array of probabilities. '+
+                'Got %i-d np.array.'% vals.ndim)
+
[…]

### 2016-11-04 raveler/ray/ray/features/moments.py

@@ -1,0 +1,144 @@
+import numpy as np
+from scipy.misc import comb as nchoosek
+from . import base
+
+class Manager(base.Null):
+    def __init__(self, nmoments=4, use_diff_features=True, oriented=False, 
+            normalize=False, *args, **kwargs):
+        super(Manager, self).__init__()
+        self.nmoments = nmoments
+        self.use_diff_features = use_diff_features
+        self.oriented = oriented
+        self.normalize = normalize
+
+    @classmethod
+    def load_dict(cls, fm_info):
+        obj = cls(fm_info['nmoments'], fm_info['use_diff'],
+                    fm_info['oriented'], fm_info['normalize'])
+        return obj
+
+    def write_fm(self, json_fm={}):
+        if 'feature_list' not in json_fm:
+            json_fm['feature_list'] = []
+        json_fm['feature_list'].append('moments')
+        json_fm['moments'] = {
+            'nmoments' : self.nmoments,
+            'use_diff' : self.use_diff_features,
+            'oriented' : self.oriented,
+            'normalize' : self.normalize
+        }
+        return json_fm
+
+    def compute_moment_sums(self, ar, idxs):
+        values = ar[idxs][...,np.newaxis]
+        return (values ** np.arange(self.nmoments+1)).sum(axis=0).T
+
+    def create_node_cache(self, g, n):
+        node_idxs = list(g.node[n]['extent'])
+        if self.oriented:
+            ar = g.max_probabilities_r
+        else:
+            ar = g.non_oriented_probabilities_r
+        return self.compute_moment_sums(ar, node_idxs)
+
+    def create_edge_cache(self, g, n1, n2):
+        edge_idxs = list(g[n1][n2]['boundary'])
+        if self.oriented:
+            ar = g.oriented_probabilities_r
+        else:
+            ar = g.non_oriented_probabilities_r
+        return self.compute_moment_sums(ar, edge_idxs)
+
+    def update_node_cache(self, g, n1, n2, dst, src):
+        dst += src
+
+    def update_edge_cache(self, g, e1, e2, dst, src):
+        dst += src
+
+    def pixelwise_update_node_cache(self, g, n, dst, idxs, remove=False):
+        if len(idxs) == 0: return
+        a = -1.0 if remove else 1.0
+        if self.oriented:
+            ar = g.max_probabilities_r
+        else:
[…]

### 2016-11-04 raveler/ray/ray/features/orientation.py

@@ -1,0 +1,125 @@
+import numpy as np
+from numpy.linalg import eig, norm
+from . import base
+
+class Manager(base.Null):
+    def __init__(self, *args, **kwargs):
+        super(Manager, self).__init__()
+
+    def write_fm(self, json_fm={}):
+        if 'feature_list' not in json_fm:
+            json_fm['feature_list'] = []
+        json_fm['feature_list'].append('orientation')
+        json_fm['orientation'] = {} 
+        return json_fm
+
+    def create_node_cache(self, g, n):
+        # Get subscripts of extent (morpho.unravel_index was slow)
+        M = np.zeros_like(g.watershed); 
+        M.ravel()[list(g.node[n]['extent'])] = 1 
+        ind = np.array(np.nonzero(M)).T
+        # Get second moment matrix
+        smm = np.cov(ind.T)/float(len(ind))
+        try:
+            # Get eigenvectors
+            val,vec = eig(smm)
+            idx = np.argsort(val)[::-1]
+            val = val[idx]
+            vec = vec[idx,:]
+            return [val,vec,ind]
+        except:
+            n = g.watershed.ndim
+            return [np.array([0]*n), np.zeros((n,n)), ind]
+        return [val, vec, ind]
+
+    def create_edge_cache(self, g, n1, n2):
+        # Get subscripts of extent (morpho.unravel_index was slow)
+        M = np.zeros_like(g.watershed); 
+        M.ravel()[list(g[n1][n2]['boundary'])] = 1 
+        ind = np.array(np.nonzero(M)).T
+        # Get second moment matrix
+        smm = np.cov(ind.T)/float(len(ind))
+        try:
+            # Get eigenvectors
+            val,vec = eig(smm)
+            idx = np.argsort(val)[::-1]
+            val = val[idx]
+            vec = vec[idx,:]
+            return [val, vec, ind]
+        except:
+            n = g.watershed.ndim
+            return [np.array([0]*n), np.zeros((n,n)), ind]
+
+    def update_node_cache(self, g, n1, n2, dst, src):
+        c = self.create_node_cache(g, n1)
+        for i, e in enumerate(c):
+            dst[i] = e
+
+    def update_edge_cache(self, g, e1, e2, dst, src):
+        c = self.create_edge_cache(g, *e1)
+        for i, e in enumerate(c):
+            dst[i] = e
+
[…]

### 2016-11-04 raveler/ray/ray/features/squiggliness.py

@@ -1,0 +1,53 @@
+import numpy as np
+from . import base
+
+def compute_bounding_box(indices, shape):
+    d = len(shape)
+    unraveled_indices = np.concatenate(
+        np.unravel_index(list(indices), shape)).reshape((-1,d), order='F')
+    m = unraveled_indices.min(axis=0)
+    M = unraveled_indices.max(axis=0) + np.ones(d)
+    return m, M
+
+class Manager(base.Null):
+    def __init__(self, ndim=3, *args, **kwargs):
+        super(Manager, self).__init__()
+        self.ndim = ndim
+
+    def write_fm(self, json_fm={}):
+        if 'feature_list' not in json_fm:
+            json_fm['feature_list'] = []
+        json_fm['feature_list'].append('squiggliness')
+        json_fm['squiggliness'] = {'ndim': self.ndim}
+        return json_fm
+
+    # cache is min and max coordinates of bounding box
+    def create_edge_cache(self, g, n1, n2):
+        edge_idxs = g[n1][n2]['boundary']
+        return np.concatenate(
+            compute_bounding_box(edge_idxs, g.segmentation.shape))
+
+    def update_edge_cache(self, g, e1, e2, dst, src):
+        dst[:self.ndim] = np.concatenate(
+            (dst[np.newaxis,:self.ndim], src[np.newaxis,:self.ndim]),
+            axis=0).min(axis=0)
+        dst[self.ndim:] = np.concatenate(
+            (dst[np.newaxis,self.ndim:], src[np.newaxis,self.ndim:]),
+            axis=0).max(axis=0)
+
+    def pixelwise_update_edge_cache(self, g, n1, n2, dst, idxs, remove=False):
+        if remove:
+            pass
+            # dst = self.create_edge_cache(g, n1, n2)
+        if len(idxs) == 0: return
+        b = np.concatenate(
+            self.compute_bounding_box(idxs, g.segmentation.shape))
+        self.update_edge_cache(g, (n1,n2), None, dst, b)
+
+    def compute_edge_features(self, g, n1, n2, cache=None):
+        if cache is None: 
+            cache = g[n1][n2][self.default_cache]
+        m, M = cache[:self.ndim], cache[self.ndim:]
+        plane_surface = np.sort(M-m)[1:].prod() * (3.0-g.pad_thickness)
+        return np.array([len(g[n1][n2]['boundary']) / plane_surface])
+

### 2016-11-04 raveler/ray/ray/iterprogress.py

@@ -1,0 +1,63 @@
+import logging
+
+class NoProgressBar(object):
+    def __init__(self, *args, **kwargs): pass
+    def start(self, *args, **kwargs): pass
+    def update(self, *args, **kwargs): pass
+    def update_i(self, *args, **kwargs): pass
+    def finish(self, *args, **kwargs): pass
+    def set_title(self, *args, **kwargs): pass
+
+def with_progress(collection, length=None, title=None, pbar=NoProgressBar()):
+    if length is None:
+        length = len(collection)
+    if title is not None:
+        pbar.set_title(title)
+    pbar.start(length)
+    for elem in collection:
+        yield elem
+        pbar.update()
+
+try:
+    from progressbar import ProgressBar, Percentage, Bar, ETA, RotatingMarker
+except ImportError:
+    logging.warning(' progressbar package not installed. Progress cannot be '+
+        'shown. See http://pypi.python.org/simple/progressbar or type '+
+        '"sudo easy_install progressbar" to fix.')
+    StandardProgressBar = NoProgressBar
+else:
+    class StandardProgressBar(object):
+        def __init__(self, title='Progress: '):
+            self.title = title
+            self.is_finished = False
+
+        def start(self, total, widgets=None):
+            if widgets is None:
+                widgets = [self.title, RotatingMarker(), ' ',
+                            Percentage(), ' ', Bar(marker='='), ' ', ETA()]
+            self.pbar = ProgressBar(widgets=widgets, maxval=total)
+            self.pbar.start()
+            self.i = 0
+
+        def update(self, step=1):
+            self.i += step
+            self.pbar.update(self.i)
+            if self.i == self.pbar.maxval:
+                self.finish()
+
+        def update_i(self, value):
+            self.i = value
+            self.pbar.update(value)
+            if value == self.pbar.maxval:
+                self.finish()
+
+        def finish(self):
+            if self.is_finished:
+                pass
+            else:
+                self.pbar.finish()
+                self.is_finished = True
+
+        def set_title(self, title):
+            self.title = title
+

### 2016-11-04 raveler/ray/ray/mergequeue.py

@@ -1,0 +1,64 @@
+
+from heapq import heapify, heappush, heappop
+from iterprogress import NoProgressBar, StandardProgressBar
+
+class MergeQueue(object):
+    def __init__(self, items=[], length=None, with_progress=False, 
+                                            prog_title='Agglomerating... '):
+        if length is None:
+            self.num_valid_items = len(items)
+        else:
+            self.num_valid_items = length
+        self.original_length = self.num_valid_items
+        self.q = items
+        heapify(self.q)
+        self.is_null_queue = len(items) == 0
+        if with_progress:
+            self.pbar = StandardProgressBar(prog_title)
+        else:
+            self.pbar = NoProgressBar()
+
+    def __len__(self):
+        return self.num_valid_items
+
+    def finish(self):
+        self.pbar.finish()
+
+    def is_empty(self):
+        return len(self.q) == 0
+
+    def peek(self):
+        return self.q[0]
+
+    def pop(self):
+        self.pop = self.pop_no_start
+        self.pbar.start(self.original_length)
+        return self.pop_no_start()
+
+    def pop_no_start(self):
+        try:
+            while not self.q[0][1]:
+                _ = heappop(self.q)
+        except IndexError:
+            raise IndexError('pop from empty merge queue')
+        item = heappop(self.q)
+        self.invalidate(item)
+        self.pbar.update_i(self.original_length - self.num_valid_items)
+        return item
+
+    def push(self, item):
+        self.is_null_queue = False
+        self.push = self.push_next
+        self.push_next(item)
+
+    def push_next(self, item):
+        heappush(self.q, item)
+        self.num_valid_items += 1
+
+    def invalidate(self, item):
+        if item[1]:
+            self.num_valid_items -= 1
+        item[1] = False
+
+    def _total_len(self):
+        return len(self.q)

### 2016-11-04 raveler/ray/ray/morpho.py

@@ -1,0 +1,427 @@
+#!/usr/bin/env python
+
+import sys, os, argparse
+from numpy import   shape, reshape, \
+                    array, zeros, zeros_like, ones, ones_like, arange, \
+                    double, \
+                    int8, int16, int32, int64, uint8, uint16, uint32, uint64, \
+                    uint, \
+                    iinfo, isscalar, \
+                    unique, \
+                    where, unravel_index, newaxis, \
+                    ceil, floor, prod, cumprod, \
+                    concatenate, \
+                    ndarray, minimum, bincount, dot, nonzero, concatenate, \
+                    setdiff1d, inf, flatnonzero
+import itertools
+import re
+from collections import defaultdict, deque as queue
+from scipy.ndimage import filters, grey_dilation, generate_binary_structure, \
+        maximum_filter, minimum_filter
+from scipy.ndimage import distance_transform_cdt
+from scipy.ndimage.measurements import label, find_objects
+from scipy.ndimage.morphology import binary_opening, binary_closing, \
+    binary_dilation, grey_opening, grey_closing, \
+    generate_binary_structure, iterate_structure
+#from scipy.spatial.distance import cityblock as manhattan_distance
+import iterprogress as ip
+
+try:
+    import skimage.morphology
+    skimage_available = True
+except ImportError:
+    logging.warning('Unable to load skimage.')
+    skimage_available = False
+
+zero3d = array([0,0,0])
+
+def manhattan_distance(a, b):
+    return sum(abs(a-b))
+
+def diamond_se(radius, dimension):
+    se = generate_binary_structure(dimension, 1)
+    return iterate_structure(se, radius)
+    
+def complement(a):
+    return a.max()-a
+
+def morphological_reconstruction(marker, mask, connectivity=1):
+    """Perform morphological reconstruction of the marker into the mask.
+    
+    See the Matlab image processing toolbox documentation for details:
+    http://www.mathworks.com/help/toolbox/images/f18-16264.html
+    """
+    sel = generate_binary_structure(marker.ndim, connectivity)
+    diff = True
+    while diff:
+        markernew = grey_dilation(marker, footprint=sel)
+        markernew = minimum(markernew, mask)
+        diff = (markernew-marker).max() > 0
+        marker = markernew
+    return marker
+
[…]

### 2016-11-04 raveler/ray/ray/option_manager.py

@@ -1,0 +1,154 @@
+import argparse
+import json
+
+class OptionConfig:
+    def __init__(self, description, default_val, required, dtype, warning, verify_fn):
+        self.description = description
+        self.default_val = default_val
+        self.required = required
+        self.dtype = dtype
+        self.warning = warning
+        self.verify_fn = verify_fn
+
+class OptionNamespace:
+    def __init__(self):
+        pass
+    def get_value(self, name):
+        name = name.replace('-', '_')
+        if name in self.__dict__:
+            return self.__dict__[name]
+        else:
+            raise Exception("Option attribute: " + name + " does not exist")
+
+    def __contains__(self, key):
+        key = key.replace('-', '_')
+        return key in self.__dict__
+
+class OptionManager:
+    def __init__(self, master_logger, arg_parser):
+        self.master_logger = master_logger
+        self.options_config = {}
+        self.options = OptionNamespace()
+        self.arg_parser = arg_parser
+
+    def load_config(self, file_name, args=None):
+        json_data = None
+        
+        if file_name is None:
+            self.master_logger.warning("Configuration file not supplied, using flags only")
+        else:
+            try:
+                json_file = open(file_name)
+                json_data = json.load(json_file)
+                json_file.close()        
+            except Exception:
+                self.master_logger.warning("error in opening" + file_name + " , using flags only")
+
+        args_dict = None
+        if args:
+            args_dict = args.__dict__
+
+        for name, option in self.options_config.items():
+            option_val = None
+            if json_data is not None and name in json_data:
+                option_val = json_data[name]
+ 
+            overridden = False
+            #nametemp = name.replace('-','_') 
+            nametemp = name
+            if args_dict and nametemp in args_dict and args_dict[nametemp] is not None:
+                option_val = args_dict[nametemp]
+                overridden = True           
+
+            if option.required and option_val is None:
+                raise Exception(name + " needs to be specified")
+            elif option.warning and option_val is None:
+                self.master_logger.warning(name + " was not specified")
+            elif option_val is None:
+                self.master_logger.debug(name + " was not specified and set to default "
+                    + str(option.default_val))
+            elif option_val is not None and overridden:
+                self.master_logger.debug(name + " was overridden by command line to "
+                    + str(option_val))
+            else:
+                self.master_logger.debug(name + " was set to " + str(option_val))
+               
+            if option_val is not None:
[…]

### 2016-11-04 raveler/ray/ray/pixel.py

@@ -1,0 +1,147 @@
+import imio, option_manager, app_logger, session_manager
+import os
+import sys
+import glob
+import h5py
+import numpy
+import json
+import traceback
+
+def image_stack_verify(options_parser, options, master_logger):
+    if options.image_stack is not None:
+        if options.image_stack.endswith('.png'):
+            images = glob.glob(options.image_stack)
+            if len(images) == 0:
+                raise Exception("No images found at " + options.image_stack)
+        else:            
+            if not os.path.exists(options.image_stack):
+                raise Exception("Image volume does not exist at " + options.image_stack)
+
+def gen_pixel_verify(options_parser, options, master_logger):
+    if options.gen_pixel:
+        if options.ilp_file is None:
+            raise Exception("Generating pixel probabilities cannot be done without an ILP")
+        if "extract-ilp-prediction" in options and not options.extract_ilp_prediction and options.image_stack is None:
+            raise Exception("Image volume needs to be supplied to generate pixel probabilities")
+
+def pixelprob_file_verify(options_parser, options, master_logger):
+    if options.pixelprob_file is not None:
+        if not os.path.exists(options.pixelprob_file):
+            raise Exception("Pixel prob file " + options.ilp_file + " not found")
+
+def ilp_file_verify(options_parser, options, master_logger):
+    if options.ilp_file is not None:
+        if not os.path.exists(options.ilp_file):
+            raise Exception("ILP file " + options.ilp_file + " not found")
+
+def create_pixel_options(options_parser, standalone=True):
+    options_parser.create_option("image-stack", "image file(s) (h5 or png format)", 
+        required=standalone, verify_fn=image_stack_verify,
+         shortcut='I', warning=True) 
+
+    options_parser.create_option("pixelprob-name", "Name for pixel classification", 
+        default_val="pixel_boundpred.h5", required=False, dtype=str, verify_fn=None, num_args=None,
+        shortcut=None, warning=False, hidden=(not standalone)) 
+ 
+    
+    options_parser.create_option("ilp-file", "ILP file containing pixel classifier", 
+        default_val=None, required=standalone, dtype=str, verify_fn=ilp_file_verify, num_args=None,
+        shortcut=None, warning=False, hidden=False) 
+    
+    if not standalone:
[…]

### 2016-11-04 raveler/ray/ray/segmentation_pipeline.py

@@ -1,0 +1,378 @@
+#!/usr/bin/env python
+
+
+import sys
+import os
+import argparse
+import h5py
+import numpy
+import shutil
+import logging
+import json
+from skimage import morphology as skmorph
+from scipy.ndimage import label
+import traceback
+
+import imio, agglo, morpho, classify, evaluate, app_logger, \
+    session_manager, pixel, features
+
+import pdb
+
+try:
+    from ray import stack_np
+except ImportError:
+    np_installed = False   
+else:
+    np_installed = True
+
+try:
+    import syngeo
+except ImportError:
+    logging.warning('Could not import syngeo. ' +
+                                        'Synapse-aware mode not available.')
+
+def grab_boundary(prediction, channels, master_logger):
+    boundary = None
+    master_logger.debug("Grabbing boundary labels: " + str(channels))
+    for channel_id in channels:
+        if boundary is None:
+            boundary = prediction[...,channel_id] 
+        else:
+            boundary += prediction[...,channel_id]
+
+    return boundary
+
+
+def gen_supervoxels(session_location, options, prediction_file, master_logger):
+    master_logger.debug("Generating supervoxels")
+    if not os.path.isfile(prediction_file):
+        raise Exception("Training file not found: " + prediction_file)
+
+    prediction = imio.read_image_stack(prediction_file, group='/volume/prediction', single_channel=False)
+
+    if options.extract_ilp_prediction:
+        prediction = prediction.transpose((2, 1, 0))
+
+    boundary = grab_boundary(prediction, options.bound_channels, master_logger) 
+
+    master_logger.debug("watershed seed value threshold: " + str(options.seed_val))
+    seeds = label(boundary<=options.seed_val)[0]
+
+    if options.seed_size > 0:
+        master_logger.debug("Removing small seeds")
+        seeds = morpho.remove_small_connected_components(seeds, options.seed_size)
+        master_logger.debug("Finished removing small seeds")
+
+    master_logger.info("Starting watershed")
+    supervoxels = skmorph.watershed(boundary, seeds)
+    master_logger.info("Finished watershed")
+
+    if options.synapse_file is not None:
+        master_logger.info("Processing synapses")
+        pre_post_pairs = syngeo.io.raveler_synapse_annotations_to_coords(
+            options.synapse_file)
+        synapse_volume = syngeo.io.volume_synapse_view(pre_post_pairs, boundary.shape)
+        supervoxels = morpho.split_exclusions(boundary, supervoxels, synapse_volume, 
[…]

### 2016-11-04 raveler/ray/ray/session_manager.py

@@ -1,0 +1,93 @@
+import argparse
+import os
+import sys
+import datetime
+import getpass
+
+import option_manager 
+
+class Session:
+    def __init__(self, name, description, master_logger, applogger, option_fn=None):
+        self.master_logger = master_logger
+        
+        self.session_location = None
+        self.start_time = str(datetime.datetime.now())
+        self.end_time = None
+        self.options_parser = None       
+ 
+        parser = argparse.ArgumentParser(description=description, 
+            formatter_class=argparse.RawDescriptionHelpFormatter)
+        
+        parser.add_argument('session_location', type=str, help="Directory for session")
+        parser.add_argument('--config-file', '-c', help='json config file') 
+        parser.add_argument('-v', '--verbose', action='store_true', default=False,
+            help='Print runtime information about execution.')
+        parser.add_argument('--regression', action="store_true", default=False, 
+                help=argparse.SUPPRESS) 
+
+        # create json and command line options 
+        self.options_parser = option_manager.OptionManager(master_logger, parser)
+
+        if option_fn is not None:
+            option_fn(self.options_parser)
+        parser.epilog = self.options_parser.help_message()
+
+        args = parser.parse_args()
+
+        self.regression = args.regression
+        self.verbose = args.verbose
+        self.session_location = args.session_location
+        self.config_file = args.config_file
+
+        # set verbosity 
+        if self.verbose:
+            applogger.set_debug_console()
+
+        if not os.path.exists(self.session_location):
+            os.makedirs(self.session_location)
+
+        # check for old files 
+        if os.path.exists(self.session_location + "/.running"):
+            raise Exception("Session " + self.session_location + " incomplete")
+        if os.path.exists(self.session_location + "/.finished"):
+            master_logger.warning("Overwriting previous session: " + self.session_location)
+            os.remove(self.session_location + "/.finished")
+
+        # set log name
+        log_filename = self.session_location + "/." + name + ".log"
+        applogger.set_log_file(log_filename, self.regression)
+
+        # load the options from the config file and args    
+        self.options = self.options_parser.load_config(self.config_file, args)
+        self.master_logger.info("Options loaded and verified")
+        
+
+        self.export_config()
+            
+        with open(self.session_location + "/.running", 'w'):
+            pass
+
+    def export_config(self):
+        config_data = {}
+        meta_data = {}
+        meta_data["version"] = 1.0
+        meta_data["user"] = getpass.getuser()
[…]

### 2016-11-04 raveler/ray/ray/stack_np.py

@@ -1,0 +1,195 @@
+# built-ins
+import libNeuroProofRag as neuroproof
+import morpho
+import json
+
+import pdb
+
+from numpy import zeros_like, array, double, zeros
+import numpy
+
+def get_prob_handle(classifier):
+    def get_prob(features):
+        prediction = classifier.predict_proba(array(features))[0,1]
+        return float(prediction)
+    return get_prob
+
+class Stack:
+    """Region adjacency graph for segmentation of nD volumes."""
+
+    def __init__(self, watershed=numpy.array([]), probabilities=numpy.array([]),
+                single_channel=True, classifier=None, synapse_file=None, feature_info=None,
+                master_logger=None): 
+        """Create a graph from a watershed volume and image volume.
+        
+        """
+
+        self.depth, self.height, self.width = watershed.shape
+        self.master_logger = master_logger
+        self.all_syn_locs = None 
+
+        self.watershed = morpho.pad(watershed, 0)
+
+        self.watershed = self.watershed.astype(numpy.double)    
+
+        probs = probabilities.astype(numpy.double)
+
+
+        self.stack = neuroproof.build_stack(self.watershed)
+
+        self.fmgr = self.stack.get_feature_mgr()
+        num_channels = 1
+
+        if single_channel:
+            self.probabilities = morpho.pad(probs, 0)
+            neuroproof.add_prediction_channel(self.stack, self.probabilities)
+        else:
+            num_channels = probabilities.shape[probabilities.ndim-1]
+            for channel in range(0,num_channels):
+                curr_prob = morpho.pad(probs[...,channel], 0)
+                neuroproof.add_prediction_channel(self.stack, curr_prob)
+                
+        if classifier is not None:
+            self.fmgr.set_python_rf_function(get_prob_handle(classifier))
+            if feature_info is not None:
+                for feature in feature_info['feature_list']:
+                    desc = feature_info[feature]
+                    if feature == "histogram":
+                        self.fmgr.add_hist_feature(desc["nbins"], desc["compute_percentiles"], False) 
+                    elif feature == "moments":
+                        self.fmgr.add_moment_feature(desc["nmoments"], desc["use_diff"]) 
+                    elif feature == "inclusiveness":
+                        self.fmgr.add_inclusiveness_feature(True) 
+                    else:
+                        raise Exception("Feature " + feature + " not supported in NeuroProof") 
+            else:
[…]

### 2016-11-04 raveler/ray/ray/stitch.py

@@ -1,0 +1,115 @@
+#!/usr/bin/env python
+
+import sys, os, argparse
+import pdb
+from agglo import Rag
+from imio import read_image_stack
+from morpho import juicy_center
+from numpy import zeros, bool, hstack, vstack, newaxis, array, savetxt
+from scipy.ndimage.filters import median_filter, gaussian_filter
+from scipy.ndimage.measurements import label
+from ray import single_arg_read_image_stack
+
+class EvalAction(argparse.Action):
+    def __call__(parser, namespace, values, option_string=None):
+        setattr(namespace, self.dest, eval(values))
+    
+def is_one_to_one_mapping(array1, array2):
+    pixelmap = dict()
+    for p1, p2 in zip(array1.ravel(), array2.ravel()):
+        try:
+            pixelmap[p1].add(p2)
+        except KeyError:
+            pixelmap[p1] = set([p2])
+    return all([len(m)==1 for m in pixelmap.values()])
+
+def crop_probs_and_ws(crop, probs, ws):
+    xmin, xmax, ymin, ymax, zmin, zmax = crop
+    probs = probs[xmin:xmax, ymin:ymax, zmin:zmax]
+    ws = label(ws[xmin:xmax, ymin:ymax, zmin:zmax])[0]
+    return probs, ws
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(
+        description='Test whether stitching will work for various overlaps.'
+    )
+    parser.add_argument('fin', nargs='+', 
+        help='The boundary probability map file(s).'
+    )
+    parser.add_argument('fout', 
+        help='The output filename.'
+    )
+    parser.add_argument('-I', '--invert-image', action='store_true',
+        default=False,
+        help='Invert the probabilities before segmenting.'
+    )
+    parser.add_argument('-M', '--low-memory', action='store_true',
+        help='Use low memory mode.'
+    )
+    parser.add_argument('-x', '--xy-crop', action=EvalAction, default=[None]*4,
+        help='Specify a crop in the first and second array dimensions.'
+    )
+    parser.add_argument('-w', '--watershed', metavar='WS_FN',
+        type=single_arg_read_image_stack,
+        help='Use a precomputed watershed volume from file.'
+    )
+    parser.add_argument('-t', '--thresholds', nargs='+', default=[128],
+        type=float, metavar='FLOAT',
+        help='''The agglomeration thresholds. One output file will be written
+            for each threshold.'''
+    )
[…]

### 2016-11-04 raveler/ray/ray/test_package.py

@@ -1,0 +1,203 @@
+#!/usr/bin/env python
+
+import unittest
+import os
+import sys
+import shutil
+
+np_installed = True
+
+try:
+    import libNeuroProofRag as neuroproof
+except ImportError:
+    np_installed = False
+
+class testPackages(unittest.TestCase):
+    def testRaveler(self):
+        self.assertTrue(os.path.exists("/usr/local/raveler-hdf"))
+    
+    def testSyngeo(self):
+        syngeo_installed = True
+        try:
+            import syngeo
+        except ImportError:
+            syngeo_installed = False
+        self.assertTrue(syngeo_installed)   
+ 
+    def testVigra(self):
+        vigra_installed = True
+        try:
+            import vigra 
+        except ImportError:
+            vigra_installed = False
+        self.assertTrue(vigra_installed)
+
+    def testNeuroProof(self):
+        self.assertTrue(np_installed)
+
+    def testIlastik(self):
+        found_exe = False
+        for dir in os.getenv("PATH").split(':'):                                           
+            if (os.path.exists(os.path.join(dir, "ilastik_batch_fast"))):
+                found_exe = True
+                break
+        self.assertTrue(found_exe)
+
+        
+class testModules(unittest.TestCase):
+    def gen_watershed(self):
+        from ray import imio
+        import numpy
+        from skimage import morphology as skmorph
+        from scipy.ndimage import label
+
+        self.datadir = os.path.abspath(os.path.dirname(sys.modules["ray"].__file__)) + "/testdata/"
+
+        prediction = imio.read_image_stack(self.datadir +"pixelprobs.h5",
+                group='/volume/prediction', single_channel=False)
+        
+        boundary = prediction[...,0]
+        seeds = label(boundary==0)[0]
+        supervoxels = skmorph.watershed(boundary, seeds)
+        return supervoxels, boundary, prediction
+
+    def testNPRFBuild(self):
+        if not np_installed:
+            self.assertTrue(np_installed)
+        from ray import stack_np
+        from ray import classify
+        self.datadir = os.path.abspath(os.path.dirname(sys.modules["ray"].__file__)) + "/testdata/"
+
+        cl = classify.get_classifier()
+        fm_info = cl.load_from_disk(self.datadir + "agglomclassifier_np.rf.h5")
+
[…]

### 2016-11-04 raveler/ray/ray/util.py

@@ -1,0 +1,19 @@
+import json
+import itertools as it
+
+all_sizes = [0.7, 1.0, 1.6, 3.5, 5.0]
+all_types = ['Color', 'Texture', 'Edge', 'Orientation']
+
+full_feature_set = list(it.product(all_types, all_sizes))
+default_feature_set = list(it.product(all_types[:-1], all_sizes[1:-1]))
+
+def write_segmentation_pipeline_json(jsonfn, ilfn, ilbfns, outdir='.'):
+    if isinstance(ilbfns, str) or isinstance(ilbfns, unicode):
+        ilbfns = [ilbfns]
+    d = {}
+    d['images'] = [{'name': ilbfn} for ilbfn in ilbfns]
+    d['session'] = ilfn
+    d['output_dir'] = outdir
+    d['features'] = default_feature_set
+    with open(jsonfn, 'w') as f:
+        json.dump(d, f)

### 2016-11-04 raveler/ray/ray/viz.py

@@ -1,0 +1,234 @@
+from annotefinder import AnnoteFinder
+from math import ceil
+import numpy as np
+import scipy
+import evaluate
+import morpho
+import matplotlib
+from scipy.ndimage import label
+plt = matplotlib.pyplot
+cm = plt.cm
+from itertools import cycle
+
+label=scipy.ndimage.measurements.label
+center_of_mass=scipy.ndimage.measurements.center_of_mass
+
+###########################
+# VISUALIZATION FUNCTIONS #
+###########################
+
+def imshow_grey(im):
+    return plt.imshow(im, cmap=plt.cm.gray, interpolation='nearest')
+
+def imshow_jet(im):
+    return plt.imshow(im, cmap=plt.cm.jet, interpolation='nearest')
+
+def imshow_rand(im):
+    rcmap = matplotlib.colors.ListedColormap(np.concatenate(
+        (np.zeros((1,3)), np.random.rand(ceil(im.max()), 3))
+    ))
+    return plt.imshow(im, cmap=rcmap, interpolation='nearest')
+
+def draw_seg(seg, im):
+    out = zeros_like(img)
+    labels = unique(seg)
+    if (seg==0).any():
+        labels = labels[1:]
+    for u in labels:
+        color = img[seg==u].mean(axis=0)
+        out[seg==u] = color
+    return out
+
+def inspect_segs_3D(*args, **kwargs):
+    """Show corresponding slices side by side in multiple segmentations."""
+    z = 0
+    if kwargs.has_key('z'):
+        z = kwargs['z']
+    axis=-1
+    if kwargs.has_key('axis'):
+        axis = kwargs['axis']
+    numplots = 0
+    im = None
+    if kwargs.has_key('image'):
+        im = kwargs['image']
+        numplots += 1
+    fignum = 1
+    if kwargs.has_key('fignum'):
+        fignum = kwargs['fignum']
+    prob = None
+    if kwargs.has_key('prob'):
+        prob = kwargs['prob']
+        numplots += 1
+    numplots += len(args)
+    plot_arrangements = []
+    for i in range(1,4):
+        for j in range(i,4):
+            plot_arrangements.append((i*j, i,j))
+    # first plot arrangement 
+    plot_arrangement = [(i,j) for p,i,j in plot_arrangements
[…]

### 2016-11-04 raveler/ray/setup.py

@@ -1,0 +1,17 @@
+#from distutils.core import setup
+from setuptools import setup, find_packages
+
+
+
+setup(name = "ray",
+    version = "1.0",
+    description = "Ray is a python library for performance and evaluation of image segmentation, distributed under the open-source MIT license. It supports n-dimensional images (images, volumes, videos, videos of volumes...) and multiple channels per image.",
+    author = "Juan Nunez-Iglesias",
+    url = "https://github.com/jni/ray",
+    author_email = 'jni@janelia.hhmi.org',
+    packages = ['ray', 'ray.features'],
+    package_data = {'ray': ['testdata/*.*', 'testdata/original_grayscales/*'] },
+    install_requires = ['scikit-learn', 'progressbar', 'scikits-image>=0.5', 'matplotlib', 'h5py>=1.5.0', 'networkx>=1.6', 'scipy>=0.10.0',  'numpy>=1.6.0', 'f2py'
+              ],
+    scripts = ["bin/ray-segmentation-pipeline", "bin/ray-train", "bin/ray-test-package", "bin/ray-pixel", "bin/comparestacks"]
+)

### 2016-11-04 raveler/save_raveler_format.py

@@ -1,0 +1,78 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+
+from numpy import *
+from ray import imio, morpho, evaluate as ev
+from scipy.ndimage import binary_dilation, generate_binary_structure
+import getopt
+import errno
+import os
+import sys
+import json
+import argparse
+
+import pdb
+
+
+larva_gt='/groups/flyem/proj/data/larva_fib_groundtruth_round2.h5'
+medulla_gt='/groups/flyem/proj/data/larva_fib_groundtruth_round2.h5'
+
+class Error(Exception):
+    """Base-class for exceptions in this module."""
+
+class UsageError(Error):
+    def __init__(self, msg):
+        self.msg = msg
+
+def main(argv):
+    parser = argparse.ArgumentParser(description='Perform VI accuracy comparison between two stacks')
+    parser.add_argument('--stack1', type=str, help='Stack compared against base stack (stack path or h5)', dest='stack1', required=True)
+    parser.add_argument('--synapsejson', type=str, help='JSON file with synapse annotations', dest='synapsejson', default='')
+    parser.add_argument('--grayscale', type=str, help='grayscale h5 volume', dest='grayscale', required=True)
+    parser.add_argument('--outdir', type=str, help='raveler output directory', dest='outdir', required=True)
+    
+    parser.add_argument('--relabel1', action='store_true', default=False, help='Relabel ids in stack 1 to prevent memory issues', dest='relabel1')
+    parser.add_argument('--relabelbase', action='store_true', default=False, help='Relabel ids in stack base to prevent memory issues', dest='relabelbase')
+    parser.add_argument('--filtersize', type=int, default=1000, help='Size below which comparisons are not made', dest='filtersize')
+    parser.add_argument('--VIthres', type=float, default=0.02, help='VI difference below which is unimportant', dest='VIthres')
+    parser.add_argument('--stack1_outjson', type=str, default='stack1_merged.json', help='output json file name for stack 1 (outputs over-merged bodies in stack 1)', dest='stack1_outjson')
+    parser.add_argument('--stackbase_outjson', type=str, default='stackbase_merged.json', help='output json file name for stack base (outputs over-merged bodies in stack base)', dest='stackbase_outjson')
+
[…]

### 2016-11-13 gp/legacy.py
New probabilities dont require the 33 pixel border.

@@ -827,6 +827,8 @@ class Legacy(object):
       if verbose:
         print len(patches), 'generated in', time.time()-t0, 'seconds.'
 
+      # return patches
+
       t0 = time.time()
       grouped_patches = Patch.group(patches)
       if verbose:
@@ -1121,7 +1123,7 @@ class Legacy(object):
     def dojoVI(gt, seg):
       # total_vi = 0
       slice_vi = []    
-      for i in range(10):
+      for i in range(gt.shape[0]):
           current_vi = Util.vi(gt[i].astype(np.int64), seg[i].astype(np.int64))
           # total_vi += current_vi
           slice_vi.append(current_vi)

### 2016-11-13 gp/patch.py

@@ -188,7 +188,7 @@ class Patch(object):
     patches = []
     hist = Util.get_histogram(segmentation.astype(np.uint64))
     labels = len(hist)
-
+    # print 'labels', labels
     batch_count = 0
     
 
@@ -198,6 +198,7 @@ class Patch(object):
         continue
 
       if hist[l] < min_pixels:
+
         continue
 
       neighbors = Util.grab_neighbors(segmentation, l)
@@ -210,8 +211,14 @@ class Patch(object):
         if hist[n] < min_pixels:
           continue
 
+        
+          
+
         # print 'grabbing', l, n
         p_l, p_n = Patch.grab(image, prob, segmentation, l, n, sample_rate, oversampling=oversampling)
+
+        # if l == 5 and n ==6:
+        #   print p_l, p_n
 
         patches += p_l
         patches += p_n
@@ -367,6 +374,7 @@ class Patch(object):
 
       if len(border_yx) < 2:
         # somehow border detection did not work
+        # print 'no border', l,n
         return patches
       # print image.shape
       # plt.imshow(image)
@@ -393,7 +401,7 @@ class Patch(object):
             
                     if distance.euclidean(patch_centers[-1],sample_point) < patch_size[0]:
                       # sample to close
-                      # print 'sample to close', patch_centers[-1], sample_point
+                      # print 'sample to close', l, n
                       continue
 
                   patch_centers.append(sample_point)
@@ -409,6 +417,9 @@ class Patch(object):
 
       # # if len(patch_centers) > 1:
       # #   print 'PC', patch_centers
+
+      # if l==5 and n==6:
+      #   print 'HERE'
           
       for i,c in enumerate(patch_centers):
 
@@ -443,18 +454,20 @@ class Patch(object):
 
           ### workaround to not sample white border of probability map
           # if skip_boundaries:
-          if bbox[0] <= 33:
-              # return None
-              continue
-          if bbox[1] >= border.shape[0]-33:
-              # return None
-              continue
-          if bbox[2] <= 33:
-              # return None
-              continue
-          if bbox[3] >= border.shape[1]-33:
-              # return None
-              continue
+          # if l==5 and n==6:
+          #   print 'HERE2', bbox
+          # if bbox[0] <= 33:
+          #     # return None
+          #     continue
+          # if bbox[1] >= border.shape[0]-33:
+          #     # return None
+          #     continue
+          # if bbox[2] <= 33:
+          #     # return None
[…]

### 2016-11-13 gp/stats.py

@@ -21,12 +21,12 @@ from util import Util
 class Stats(object):
 
   @staticmethod
-  def analyze_users(FP_USERS, gold, rhoana, oracle=None, clampX=500, filename=None):
+  def analyze_users(FP_USERS, gold, rhoana, oracle=None, clampX=500, filename=None, DATADIR = '/home/d/GPSTUDY/'):
 
     def VI(gt, seg):
       # total_vi = 0
       slice_vi = []    
-      for i in range(10):
+      for i in range(gt.shape[0]):
           current_vi = Util.vi(gt[i].astype(np.int64), seg[i].astype(np.int64))
           # total_vi += current_vi
           slice_vi.append(current_vi)
@@ -39,7 +39,7 @@ class Stats(object):
 
     print 'No. users', len(FP_USERS)
 
-    DATADIR = '/home/d/GPSTUDY/'
+    
 
     newrhoana = 'ui_results.p'
     times = 'times.p'
@@ -150,8 +150,8 @@ class Stats(object):
     if clampX:
       plt.xlim(0,clampX)
 
-    plt.axhline(y=0.4763612343909136, color='gray', linestyle='-.', linewidth=3, label='Initial Segmentation')
-    plt.axhline(y=0.33414926373414477, color='gray', linestyle='--', linewidth=3, label='Best Possible')
+    plt.axhline(y=0.4763612343909136, color='gray', linestyle=':', linewidth=2, label='Initial Segmentation')
+    plt.axhline(y=0.33414926373414477, color='gray', linestyle='--', linewidth=2, label='Best Possible')
     plt.xlabel('Correction')
     plt.ylabel('Variation of Information')
     # legend = ax.legend(loc='upper right')
@@ -217,7 +217,7 @@ class Stats(object):
     print len(merge_errors), ' merge errors found.'
 
     # we need to create a bigM for the dojo volume
-    bigM_dojo_file = output_folder + '/bigM_dojo_test.p'
+    bigM_dojo_file = output_folder + '/bigM_dojo_test2.p'
     if os.path.exists(bigM_dojo_file):
       print 'Loading dojo bigM from file..'
       with open(bigM_dojo_file, 'rb') as f:
@@ -231,7 +231,7 @@ class Stats(object):
 
 
     print
-    dojo_vi_95_file = output_folder + '/dojo_vi_95_t5.p'
[…]

### 2016-11-13 paper/guidedproofreading_review.tex
Changed Paper ID
Paper rewrite.

@@
 
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{0947} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 %%%%%%%%% TITLE
-\title{Guided Proofreading of Automatic Segmentations in Connectomics}
+\title{Guided Proofreading of Automatic Segmentations for Connectomics}
 
@@
 We evaluate our approach on connectomics datasets of different species and compare correction performance of novice and expert users against different existing systems.
-We report significant improvements on pure automatic and pure manual proofreading.
+We report significant improvements compared to pure automatic and pure manual proofreading.
 \end{abstract}
@@
 
+\input{results}
+
 \input{conclusion}

### 2016-11-13 paper/introduction.tex
Paper rewrite.

@@
 With user interaction, split errors can be joined, and the missing boundary in a merge error can be defined with manually-seeded watersheds~\cite{haehn_dojo_2014}.
-However, even with semi-automatic correction tools, the visual inspection to find errors in the first place takes the majority of the time.
+However, even with semi-automatic correction tools, the visual inspection to find errors takes the majority of the time~\cite{proofreading_bottleneck}.
 
@@
 Our goal is to add automatic detection of split and merge errors to proofreading tools.
-Instead of the user visually inspecting the whole data volume carefully to spot errors, we design automatic classifiers that detect split and merge errors in 2D segmentations.
-Then, a proofreading tool can recommend regions with a high probability of an error to the user, and suggest corrections to accept or reject.
+We design automatic classifiers that detect split and merge errors in 2D segmentations so the user does not need to visually inspect the whole data volume to spot errors.
+A proofreading tool then recommends regions with a high probability of an error to the user, and suggest corrections to accept or reject.
 We call this process \textit{guided proofreading} (GP).
@@
 As our main contribution, we introduce classifiers to detect merge- and split errors based on a convolutional neural network (CNN).
-We believe that this is the first time that deep learning is applied to the task of proofreading --- especially in the field of connectomics.
+We believe that this is the first time that deep learning is applied to the task of proofreading.
 Our classifiers work on top of any existing automatic segmentation method to find potential errors and suggest corrections.
@@
 Compared to techniques that must analyze every input pixel, we reduce the data analysis to the boundaries only.
-Explicitly, we train a CNN to detect only split errors.
+First, we train a CNN to detect only split errors.
+The output of this network is a probability whether a boundary between two segments is valid or not.
 We then reuse the same network to also detect merge errors by generating possible boundaries within a cell and inverting the split error score.
-Correction suggestion for both types of errors is then trivial and our technique therefor reduces the proofreading operation to simple yes/no decisions.
+We create corrections for both types of errors which can be accepted or rejected.
+This reduces the proofreading operation to simple yes/no decisions.
 
-We further propose a greedy algorithm to perform proofreading automatically and measure performance as the adapted Rand error which is a common metric for segmentation comparison~\cite{RAND}. 
+We further propose a greedy algorithm to perform proofreading automatically.
+Possible erroneous regions are sorted by their score and the algorithm sequentially corrects merge errors and split errors until a configurable threshold is reached.
+If ground truth data is available, we can use a selection oracle to drive this algorithm.
+The oracle only accepts corrections which improve the automatic segmentation.
+
+This way,
+
+ and measure performance as the adapted Rand error which is a common metric for segmentation comparison~\cite{RAND}. 
 Our system is integrated into an existing proofreading workflow for large connectomics data.
@@
 In all experiments, we significantly outperform both interactive proofreading as well as Plaza's method.
+
 As a consequence, we are able to provide tools to proofread segmentations more efficiently, and so better tackle large volumes of connectomics imagery.

### 2016-11-13 paper/related_work.tex
Paper rewrite.

@@
 
-Proofreading is performed on top of an existing automatic segmentation.
-First, this section gives an overview of state-of-the-art automatic segmentation methods.
-Then, we discuss interactive proofreading tools and recent developments in computer-aided proofreading systems.
-
 \textbf{Automatic Segmentation.} Multi-terabyte EM brain volumes require automatic segmentation~\cite{jain2010,Liu2014,NunezIglesias2013Machine,GALA2014}, but can be hard to classify due to ambiguous intercellular space: the 2013 IEEE ISBI neurites 3D segmentation challenge~\cite{isbi_challenge} showed that existing algorithms which learn from expert-segmented training data still exhibit high error rates.
@@
 Lee \etal~\cite{lee2015recursive} recursively train very deep networks with 2D and 3D filters to detect boundaries.
+
 Bogovic \etal~\cite{BogovicHJ13} learn 3D features, and show even that unsupervised learning can produce better features than hand-designs.
 Our work was inspired by this paper and we extend the features reported by Bogovic \etal for our guided proofreading classifiers as described in section \ref{sec:methods}.
-These approaches make good progress; however, in general, proofreading is required to improve them through generating more ground-truth segmentations.
+These approaches make good progress; however, in general, proofreading is required to correct errors.
 
@@
 This software offers many parameters for tweaking the proofreading process.
-Created in 2010, Raveler is still used today by professional full-time proofreaders and many similar systems exist as stand-alone products or plugins to existing visualization system,~\eg V3D~\cite{proofreading_bottleneck} or AVIZO~\cite{markus_proofreading}.
+Created in 2010, Raveler is still used today by professional full-time proofreaders.
+Many similar systems exist as stand-alone products or plugins to existing visualization system,~\eg V3D~\cite{proofreading_bottleneck} or AVIZO~\cite{markus_proofreading}.
+
 In contrast to these expert tools, recent works attack the problem of proofreading massive datasets by novices through crowd-sourcing~\cite{saalfeld09,anderson2011,Giuly2013DP2}.
@@
 This makes it feasible for us to use FP as a baseline for evaluating guided proofreading as described in section \ref{sec:evaluation}.
+
 A similar approach was published by Karimov \etal as guided volume editing~\cite{karimov_guided_volume_editing}.
@@
 Guided volume editing was designed to let expert users correct labeled computer-tomography datasets by performing several interactions per correction.
+
 While focused proofreading and guided volume editing both use a heuristical approach to analyze the image data, Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}.
@@
 This method is really a segmentation technique but it is possible to use the uncertainty information to present potential regions for proofreading.
-Uzunbas' paper describes a great idea but requires further work to overcome the requirement of isotropic volumes, a property not given for most connectomics datasets.
+Their method requires further work to overcome the requirement of isotropic volumes, a property not given for most connectomics datasets.
 Our approach, guided proofreading, works on isotropic as well as anisotropic data, and finds merge and split errors.

### 2016-11-13 paper/related_work.tex
Related work review.

@@
 
-NeuroProof \cite{neuroproof2013} tries to decrease error rates with interactive learning of agglomeration of over-segmentations of images, based on a random forest classifier.
-Vazquez-Reina \etal~\cite{amelio_segmentation} propose automatic 3D segmentation by taking whole EM volumes into account rather than a per section approach, then solving a fusion problem with a global context.
+Many works tackle this problem.
+NeuroProof \cite{neuroproof2013} decreases error rates by learning a agglomeration on over-segmentations of images, based on a random forest classifier.
+Vazquez-Reina \etal~\cite{amelio_segmentation} take whole EM volumes into account rather than a per section approach, then solve a fusion problem with a global context.
 Kaynig \etal~\cite{kaynig10} propose a random forest classifier coupled with an anisotropic smoothing prior in a conditional random field framework with 3D segment fusion.
+Bogovic \etal~\cite{BogovicHJ13} learn 3D features unsupervised, and show that they can be better than by-hand designs.
+
 It is also possible to learn segmentation classification features directly from images with CNNs.
@@
 
-Bogovic \etal~\cite{BogovicHJ13} learn 3D features, and show even that unsupervised learning can produce better features than hand-designs.
-Our work was inspired by this paper and we extend the features reported by Bogovic \etal for our guided proofreading classifiers as described in section \ref{sec:methods}.
-These approaches make good progress; however, in general, proofreading is required to correct errors.
+All these approaches make good progress; however, in general, proofreading is still required to correct errors.
+
+%Inspired by Bogovic \etal, we extend their features for our guided proofreading classifiers (Section \ref{sec:methods}).
 
 \textbf{Interactive Proofreading.} While proofreading is very time consuming, it is fairly easy for humans to perform corrections through splitting and merging segments.
-One way to perform such corrections is by using expert tools such as Raveler introduced by Chklovskii~\etal~\cite{chklovskii2010, raveler}.
-This software offers many parameters for tweaking the proofreading process.
-Created in 2010, Raveler is still used today by professional full-time proofreaders.
-Many similar systems exist as stand-alone products or plugins to existing visualization system,~\eg V3D~\cite{proofreading_bottleneck} or AVIZO~\cite{markus_proofreading}.
+One expert tool is Raveler, introduced by Chklovskii~\etal~\cite{chklovskii2010, raveler}.
+Raveler is used today by professional proofreaders, and it offers many parameters for tweaking the process.
+Similar systems exist as products or plugins to visualization systems,~\eg V3D~\cite{proofreading_bottleneck} or AVIZO~\cite{markus_proofreading}.
 
-In contrast to these expert tools, recent works attack the problem of proofreading massive datasets by novices through crowd-sourcing~\cite{saalfeld09,anderson2011,Giuly2013DP2}.
-A very popular platform is EyeWire presented by Kim \etal~\cite{eyewire_nature}.
-EyeWire is set up as an online game and participants earn virtual rewards for merging oversegmented labeling to reconstruct the retina cells.
-A range of proofreading tools exist in-between expert systems and online games such as Mojo and \textit{Dojo} developed by Haehn \etal~\cite{haehn_dojo_2014,Neuroblocks}.
-Mojo provides a simple scribble interface for error correction, and Dojo extends this for distributed proofreading via a minimalistic web-based user interface.
+Recent papers have attacked the problem of proofreading massive datasets through crowdsourcing with novices~\cite{saalfeld09,anderson2011,Giuly2013DP2}.
+One popular platform is EyeWire, by Kim \etal~\cite{eyewire_nature}, where participants earn virtual rewards for merging oversegmented labeling to reconstruct retina cells.
+
+Between expert systems and online games sit Mojo and \textit{Dojo}, by Haehn \etal~\cite{haehn_dojo_2014,Neuroblocks}, which use simple scribble interfaces for error correction.
+Dojo extends this to distributed proofreading via a minimalistic web-based user interface.
 The authors define requirements for general proofreading tools, and then evaluate the accuracy and speed of Raveler, Mojo, and Dojo through a quantitative user study (Sec.
@@
 In this paper, we use the Dojo system as a baseline for interactive proofreading and extend the experiment reported by Haehn \etal, where Raveler, Mojo, and Dojo are compared in terms of accuracy and speed.
-All interactive proofreading solutions require the user to find potential errors manually which takes the majority of time~\cite{proofreading_bottleneck,haehn_dojo_2014}.
-Recent works propose computer-aided proofreading systems which help with this visual search task.
+
+All interactive proofreading solutions require the user to find potential errors manually, which takes the majority of the time~\cite{proofreading_bottleneck,haehn_dojo_2014}.
+Recent works propose computer-aided proofreading systems which help reduce the time spent in this visual search task.
 
 %Most relevant methods here use heuristics to analyze the image data to find potential errors. 
-\textbf{Computer-aided Proofreading.} To reduce the time spent looking for errors, Plaza proposed \textit{focused proofreading} (FP) ~\cite{focused_proofreading}.
-His approach finds split errors by analyzing segment size ratios across slices and then offers yes/no questions to correct these errors.
+\textbf{Computer-aided Proofreading.} Plaza proposed \textit{focused proofreading} (FP) ~\cite{focused_proofreading}, which finds split errors by analyzing segment size ratios across slices, then offers a yes/no choice to the user to correct these errors.
 Plaza reports that additional processing beyond FP is required to find merge errors.
-His method is freely available as open source software and is integrated into Raveler.
-This makes it feasible for us to use FP as a baseline for evaluating guided proofreading as described in section \ref{sec:evaluation}.
+This method is open source and is integrated into Raveler.
+We use FP as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).
 
-A similar approach was published by Karimov \etal as guided volume editing~\cite{karimov_guided_volume_editing}.
-Measuring differences in histogram distributions in image data enables to find potential split and merge errors in the corresponding segmentation.
-For merge errors, the authors generate possible boundaries using watershed which inspired our approach as described in section \ref{sec:methods}.
-Guided volume editing was designed to let expert users correct labeled computer-tomography datasets by performing several interactions per correction.
+A similar approach by Karimov \etal, known as guided volume editing~\cite{karimov_guided_volume_editing}, measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation.
+This was designed to let expert users correct labeled computer-tomography datasets, using several interactions per correction.
+To correct merge errors, the authors generate possible boundaries using watershed, which inspired our merge error approach (Sec.~\ref{sec:methods}).
 
-While focused proofreading and guided volume editing both use a heuristical approach to analyze the image data, Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}.
+While focused proofreading and guided volume editing both use heuristics to analyze image data, Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}.
 The authors track uncertainty throughout the automatic labeling by training a conditional random field.
-This method is really a segmentation technique but it is possible to use the uncertainty information to present potential regions for proofreading.
+This segmentation technique produces uncertainty estimates, which can be used to present potential regions for proofreading to the user.
 Their method requires further work to overcome the requirement of isotropic volumes, a property not given for most connectomics datasets.

### 2016-11-13 paper/related_work.tex
More explicit FP comparison in related work.

@@
 3 and 4)~\cite{haehn_dojo_2014}.
-In this paper, we use the Dojo system as a baseline for interactive proofreading and extend the experiment reported by Haehn \etal, where Raveler, Mojo, and Dojo are compared in terms of accuracy and speed.
+Dojo had the highest performance.
+In this paper, we use Dojo as a baseline for interactive proofreading, and so we extend the Haehn \etal experiment.
 
@@
 %Most relevant methods here use heuristics to analyze the image data to find potential errors. 
-\textbf{Computer-aided Proofreading.} Plaza proposed \textit{focused proofreading} (FP) ~\cite{focused_proofreading}, which finds split errors by analyzing segment size ratios across slices, then offers a yes/no choice to the user to correct these errors.
-Plaza reports that additional processing beyond FP is required to find merge errors.
-This method is open source and is integrated into Raveler.
-We use FP as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).
+\textbf{Computer-aided Proofreading.} Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}.
+The authors track uncertainty throughout the automatic labeling by training a conditional random field.
+This segmentation technique produces uncertainty estimates, which can be used to present potential regions for proofreading to the user.
+While it works on isotropic volumes, more work is needed to apply it to anisotropic volumes, like most connectomics datasets.
 
-A similar approach by Karimov \etal, known as guided volume editing~\cite{karimov_guided_volume_editing}, measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation.
-This was designed to let expert users correct labeled computer-tomography datasets, using several interactions per correction.
+%Their method requires further work to overcome the requirement of isotropic volumes, a property not given for most connectomics datasets.
+Our approach, guided proofreading, works on isotropic as well as anisotropic data, and finds merge and split errors.
+
+Karimov \etal propose guided volume editing~\cite{karimov_guided_volume_editing}, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation.
+This lets expert users correct labeled computer-tomography datasets, using several interactions per correction.
 To correct merge errors, the authors generate possible boundaries using watershed, which inspired our merge error approach (Sec.~\ref{sec:methods}).
 
-While focused proofreading and guided volume editing both use heuristics to analyze image data, Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}.
-The authors track uncertainty throughout the automatic labeling by training a conditional random field.
-This segmentation technique produces uncertainty estimates, which can be used to present potential regions for proofreading to the user.
-Their method requires further work to overcome the requirement of isotropic volumes, a property not given for most connectomics datasets.
-Our approach, guided proofreading, works on isotropic as well as anisotropic data, and finds merge and split errors.
+Most closely related to our approach is the work of Plaza, who proposed \textit{focused proofreading} (FP) ~\cite{focused_proofreading}.
+FP finds split errors by analyzing segment size ratios across slices, then offers a yes/no choice to the user to correct these errors.
+Plaza reports that additional processing beyond FP is required to find merge errors.
+This method builds upon NeuroProof \cite{neuroproof2013} as its agglomerator, and is open source with integrated into Raveler.
+As the closest related work, we wish to use FP as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).
+However, as Haehn \etal showed that Raveler is less performant than Dojo for novice users, we separate the backend split suggestions from the expert-level front end, and present our own interface (Sec.~\ref{sec:evaluation}).

### 2016-11-13 paper/introduction.tex
Intro.

@@
 For $40\, nm$ thick sections, a $1\, mm^3$ volume of brain contains $10^{15}$ voxels, or 1 petabyte of data.
-With so much data, manual annotation is infeasible, and automatic annotation methods are needed ~\cite{jain2010,Liu2014,GALA2014,kaynig2015large}.
+With so much data, manual annotation is infeasible, and automatic annotation methods are needed~\cite{jain2010,Liu2014,GALA2014,kaynig2015large}.
 
@@
 A proofreading tool then recommends regions with a high probability of an error to the user, and suggest corrections to accept or reject.
-We call this process \textit{guided proofreading} (GP).
+We call this process \textit{guided proofreading}.
 
-As our main contribution, we introduce classifiers to detect merge- and split errors based on a convolutional neural network (CNN).
+In this paper, we introduce classifiers to detect merge- and split errors based on a convolutional neural network (CNN).
 We believe that this is the first time that deep learning is applied to the task of proofreading.
@@
 
-We further propose a greedy algorithm to perform proofreading automatically.
-Possible erroneous regions are sorted by their score and the algorithm sequentially corrects merge errors and split errors until a configurable threshold is reached.
-If ground truth data is available, we can use a selection oracle to drive this algorithm.
+We further propose a greedy algorithm to perform proofreading.
+Possible erroneous regions are sorted by their score and the algorithm iteratively suggests a correction for each region.
+A user then works through this stream of regions and corrections.
+In a  forced choice setting, the user chooses one of two possibilities to advance.
+This choice can be also performed automatically by running the algorithm until a configurable threshold is reached.
+In addition, if ground truth data is available, we can use a selection oracle to drive the forced choice selection.
 The oracle only accepts corrections which improve the automatic segmentation.
+This equals perfect proofreading.
 
-This way,
+We evaluate our method automatically using a threshold and a selection oracle on multiple real-world connectomics datasets.
+To evaluate the forced choice setting, we perform a quantitative user study.
+The study targets non-experts with no previous experience of proofreading electron microscopy data.
+We ask the participants to proofread a small segmentation volume in a fixed time frame by performing yes/no decisions.
+The user study is designed as a between-subjects experiment and compares guided proofreading against two other methods: a recently published fully interactive proofreading tool named \textit{Dojo} by Haehn~\etal~\cite{haehn_dojo_2014} and semi-automatic \textit{focused proofreading} approach by Plaza~\cite{focused_proofreading}.
+We also asked four domain experts to use guided proofreading and focused proofreading for additional comparison.
 
- and measure performance as the adapted Rand error which is a common metric for segmentation comparison~\cite{RAND}. 
-Our system is integrated into an existing proofreading workflow for large connectomics data.
-For this, we also explore an active label suggestion approach in addition to the ranking obtained by guided proofreading.
-We quantitatively validate automatic and human-driven variations of guided proofreading on five different real-world connectomics datasets of mouse as well as fruitfly (drosophila) brain.
-To study the performance of novice and expert proofreaders, we perform a between-subjects experiment and ask participants to proofread a publicly available dataset.
-For comparison, we establish two baselines: a recently published fully interactive proofreading tool named \textit{Dojo} by Haehn~\etal~\cite{haehn_dojo_2014} and semi-automatic \textit{focused proofreading} (FP) approach by Plaza~\cite{focused_proofreading}.
-In all experiments, we significantly outperform both interactive proofreading as well as Plaza's method.
-
+Our first contribution is a classifier for split error detection based on a convolutional neural network.
+The classifier performs well even when trained with little amounts of training data.
+This is important since generating ground truth labels in connectomics is done by manually labeling pixels which is very time-consuming.
+Our second contribution is a mechanism to identify merge-errors by re-using our split error classifier.
+Merge errors are less common than split errors in the usually oversegmented automatic labelings.
+However, interactive correction of merge errors by drawing split lines is more cumbersome than correcting split errors.
+Our method reduces this to a single click by providing the potential correction.
+The split and merge error identification is executed as a greedy algorithm to perform corrections of segmentation volume, the third contribution of this paper.
+The algorithm can be driven automatically with a threshold, by an oracle based on ground truth and interactively in a forced choice setting.
+Our final contribution is our quantitative user study.
+We present statistically significant results showing that novice and expert users of guided proofreading are able to proofread a given dataset better and faster than with existing interactive and semi-automatic proofreading tools.
 As a consequence, we are able to provide tools to proofread segmentations more efficiently, and so better tackle large volumes of connectomics imagery.

### 2016-11-13 gp/stats.py

@@ -26,7 +26,7 @@ class Stats(object):
     def VI(gt, seg):
       # total_vi = 0
       slice_vi = []    
-      for i in range(gt.shape[0]):
+      for i in range(len(gt)):
           current_vi = Util.vi(gt[i].astype(np.int64), seg[i].astype(np.int64))
           # total_vi += current_vi
           slice_vi.append(current_vi)

### 2016-11-13 paper/introduction.tex
Introduction (might be too long) and changed a bit in related work.

@@
 
-Automatic annotation by segmentation and classification of brain tissue is challenging~\cite{isbi_challenge}.
+%Automatic annotation by segmentation and classification of brain tissue is challenging~\cite{isbi_challenge}.
 The state of the art uses supervised learning with convolutional neural networks~\cite{Ciresan:2012f}, or potentially even unsupervised learning~\cite{BogovicHJ13}.
@@
 
-All automatic methods make errors, and we are left with large data which needs \emph{proofreading} by humans.
+Automatic annotation by segmentation and classification of brain tissue is challenging~\cite{isbi_challenge} and all the methods make errors.
+This means we are left with large data which needs \emph{proofreading} by humans.
 This crucial task serves two purposes: 1) to correct errors in the segmentation, and 2) to provide a large body of labeled data to train better automatic segmentation methods.
@@
 Our goal is to add automatic detection of split and merge errors to proofreading tools.
-We design automatic classifiers that detect split and merge errors in 2D segmentations so the user does not need to visually inspect the whole data volume to spot errors.
+We design automatic classifiers that detect split and merge errors in segmentations so the user does not need to visually inspect the whole data volume to spot errors.
 A proofreading tool then recommends regions with a high probability of an error to the user, and suggest corrections to accept or reject.
@@
 Given a membrane segmentation from a fast automatic method, our classifiers operate on the boundaries of whole cell regions.
-Compared to techniques that must analyze every input pixel, we reduce the data analysis to the boundaries only.
+Compared to techniques that must analyze every input pixel, we reduce the data analysis to the boundaries.
 First, we train a CNN to detect only split errors.
@@
 A user then works through this stream of regions and corrections.
-In a  forced choice setting, the user chooses one of two possibilities to advance.
+In a forced choice setting, the user either selects a correction or skips it to advance to the next region.
 This choice can be also performed automatically by running the algorithm until a configurable threshold is reached.
@@
 
-We evaluate our method automatically using a threshold and a selection oracle on multiple real-world connectomics datasets.
+We evaluate our method automatically by threshold and oracle on multiple real-world connectomics datasets.
 To evaluate the forced choice setting, we perform a quantitative user study.
@@
 We ask the participants to proofread a small segmentation volume in a fixed time frame by performing yes/no decisions.
-The user study is designed as a between-subjects experiment and compares guided proofreading against two other methods: a recently published fully interactive proofreading tool named \textit{Dojo} by Haehn~\etal~\cite{haehn_dojo_2014} and semi-automatic \textit{focused proofreading} approach by Plaza~\cite{focused_proofreading}.
+The user study is designed as a between-subjects experiment and compares guided proofreading against two other methods: a recently published fully interactive proofreading tool named \textit{Dojo} by Haehn~\etal~\cite{haehn_dojo_2014} and the semi-automatic \textit{focused proofreading} approach by Plaza~\cite{focused_proofreading}.
 We also asked four domain experts to use guided proofreading and focused proofreading for additional comparison.
@@
 The classifier performs well even when trained with little amounts of training data.
-This is important since generating ground truth labels in connectomics is done by manually labeling pixels which is very time-consuming.
-Our second contribution is a mechanism to identify merge-errors by re-using our split error classifier.
-Merge errors are less common than split errors in the usually oversegmented automatic labelings.
-However, interactive correction of merge errors by drawing split lines is more cumbersome than correcting split errors.
+This is important since generating ground truth labels in connectomics requires manually labeling pixels and is very time-consuming.
+Our second contribution is a mechanism to identify merge-errors by re-using the split error classifier.
+Merge errors are usually less common than split errors in the oversegmented automatic labelings.
+However, they require more interaction during correction since split lines need to be manually drawn.
 Our method reduces this to a single click by providing the potential correction.
-The split and merge error identification is executed as a greedy algorithm to perform corrections of segmentation volume, the third contribution of this paper.
+The split and merge error identification is executed as a greedy algorithm to correct segmentation volumes, the third contribution of this paper.
 The algorithm can be driven automatically with a threshold, by an oracle based on ground truth and interactively in a forced choice setting.

### 2016-11-13 paper/related_work.tex
Introduction (might be too long) and changed a bit in related work.

@@
 This lets expert users correct labeled computer-tomography datasets, using several interactions per correction.
-To correct merge errors, the authors generate possible boundaries using watershed, which inspired our merge error approach (Sec.~\ref{sec:methods}).
+To correct merge errors, the authors create a large number of superpixels within a single segment and then successively group them based on dissimilarities.
+We were inspired by this approach but generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.
+\ref{sec:methods}).
 
-Most closely related to our approach is the work of Plaza, who proposed \textit{focused proofreading} (FP) ~\cite{focused_proofreading}.
-FP finds split errors by analyzing segment size ratios across slices, then offers a yes/no choice to the user to correct these errors.
-Plaza reports that additional processing beyond FP is required to find merge errors.
-This method builds upon NeuroProof \cite{neuroproof2013} as its agglomerator, and is open source with integrated into Raveler.
-As the closest related work, we wish to use FP as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).
-However, as Haehn \etal showed that Raveler is less performant than Dojo for novice users, we separate the backend split suggestions from the expert-level front end, and present our own interface (Sec.~\ref{sec:evaluation}).
+Most closely related to our approach is the work of Plaza, who proposed \textit{focused proofreading}~\cite{focused_proofreading}.
+This method generates affinity scores by analyzing a region adjacency graph across slices, then finds the largest affinities based on a defined impact score.
+This yields edges of potential split errors which can be presented to the proofreader.
+Plaza reports that additional manual work is required to find and correct merge errors.
+Focused proofreading builds upon NeuroProof \cite{neuroproof2013} as its agglomerator, and is open source with integration into Raveler.
+As the closest related work, we wish to use this method as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).
+However, as Haehn \etal showed that Raveler is less performant than Dojo for novice users, we separate the backend affinity score calculation from the expert-level front end, and present our own interface (Sec.~\ref{sec:evaluation}).

### 2016-11-14 paper/evaluation.tex
Update intro, rel. work and methods.

@@
 We first describe the evalation on mouse brain data and then the evaluation on drosophila brain.
+
+\textbf{Training.} To initially train our network, we use the blue 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels).
+The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse.
+The resolution of our dataset is $3\, nm$ per pixel, and the section thickness is $30\, nm$.
+The image data and a manually-labeled expert segmentation is publicly available as ground truth for the entire dataset\footnote{The Kasthuri 3-cylinder mouse cortex volume is available at  https://software.rc.fas.harvard.edu/lichtman/vast/}.
+We use the first 250 sections of the data for training and validation and the last 50 for testing.
+We use a state-of-the-art method to create a dense automatic segmentation of the data.
+To generate training data, we identify correct regions and split errors in the automatic segmentation by intersection with ground truth regions.
+This is required since extracellular space is not labeled in the ground truth but in our dense automatic segmentation.
+From these regions, we sample 120,000 correct and 120,000 split error patches with 4-channels as described above.
+The patches are normalized and to further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$.
+The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research as well as a brute force parameter search within a limited range (see supplementary material).
+The final parameters and training results are listed in table~\ref{tab:parameters}.
+For baseline comparison, we also list the parameters and training results of focused proofreading in this table but elaborate on these further in section \ref{sec:evaluation}.
+Our CNN configuration results in approximately 170,000 learnable parameters.
+We assume that training has converged if the validation loss does not decrease for 50 epochs.
+
+\begin{table}[h]
+%\resizebox{\textwidth}{!}{%
+\tiny
+\begin{tabular}{@{}c|c|c|c|c|c|c@{}}
+& \textbf{cost [m]} & \textbf{Val. loss} & \textbf{Val. acc.} & \textbf{Test acc.} & \textbf{Prec./Recall} & \textbf{F1 Score} \\ 
+\hspace{1mm}
+\begin{tabular}{@{}l@{}}
+\textbf{Guided Proofreading} \\ Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2-4: 48 \\ Dense units: 512 \\ Learning rate: 0.03-0.00001\\ Momentum: 0.9-0.999\\Mini-Batchsize: 128\\~\\
+ \end{tabular}
+ & 383  & 0.0845  & 0.969  & 0.94  & 0.94/0.94  & 0.94 \\ 
+\hline 
+\begin{tabular}{@{}l@{}}
+\\
+\textbf{Focused Proofreading} \\ 
+Iterations: 3 \\
+Learning strategy: 2\\
+Mito agglomeration: Off\\
+Threshold: 0.2
+ \end{tabular}
+ & 43  & ?  & ?  & 0.839  & ?/?  & ? \\ 
+\end{tabular} 
+\vspace{1mm}
+\caption{Training parameters, cost and results of our guided proofreading classifier versus focused proofreading by Plaza \cite{focused_proofreading}.
+Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 graphics card).
+While the training of our classifier is more expensive, testing accuracy is superior.
+}
+\label{tab:parameters}
+\end{table}
+
+For performance comparison on data of a different species, in particular on fruitfly brain (drosophila), we retrain our network.
+The training procedure is according to our initial training and network architecture as well as parameters are not changed.
+We further elaborate on the drosophila datasets in section~\ref{sec:evaluation}.
+Fig.~\ref{fig:roc} displays receiver operating characteristics (ROC) for  guided proofreading trained on mouse and drosophila data, as well as our comparison baseline focused proofreading trained on these datasets respectively.
+
+\begin{figure}[h]
+  \vspace{-5mm}
+\begin{center}
+  \includegraphics[width=\linewidth]{gfx/roc.pdf}
+\end{center}
+  \vspace{-10mm}
+   \caption{ROC performance of guided proofreading (GP) and focused proofreading (FP) trained separately on mouse and drosophila brain images.
+The area under the curve indicates better performance for GP.}
+\label{fig:roc}
+\end{figure}
 

### 2016-11-14 paper/introduction.tex
Update intro, rel. work and methods.

@@
 
-In connectomics, neuroscientists annotate neurons and their connectivity within 3D volumes to gain insight into the functional structure of the brain.
+%In connectomics, neuroscientists annotate neurons and their connectivity within 3D volumes to gain insight into the functional structure of the brain.
 Rapid progress in automatic sample preparation and electron microscopy (EM) acquisition techniques has made it possible to image large volumes of brain tissue at $\approx4\, nm$ per pixel to identify cells, synapses, and vesicles.
@@
 This is sufficient to keep up with the 2D data capture process on state-of-the-art electron microscopes (though 3D registration is still an expensive offline operation).
+In connectomics, neuroscientists annotate neurons and their connectivity within 3D volumes to gain insight into the functional structure of the brain.
+Rapid progress in automatic sample preparation and electron microscopy (EM) acquisition techniques has made it possible to image large volumes of brain tissue at nanometer resolution.
+A typical voxel size is $4\times4\times40~\text{nm}^3$.
+For a $1~\text{mm}^3$ volume, this resolution results in 1 petabyte of data.
+With so much data, manual annotation is not feasible, and automatic annotation methods are needed~\cite{jain2010,Liu2014,GALA2014,kaynig2015large}.
 
-Automatic annotation by segmentation and classification of brain tissue is challenging~\cite{isbi_challenge} and all the methods make errors.
+Automatic annotation by segmentation and classification of brain tissue is challenging~\cite{isbi_challenge} and all available methods make errors.
 This means we are left with large data which needs \emph{proofreading} by humans.
@@
 \begin{center}
-  \includegraphics[width=\linewidth]{gfx/merge_and_split_errors.png}
+  \includegraphics[width=\linewidth]{gfx/merge_and_split_errors.pdf}
 \end{center}

### 2016-11-14 paper/method.tex
Update intro, rel. work and methods.

@@
 
-We first describe our classifier for detecting split errors which is based on a convolutional neural network (CNN).
+%We first describe our classifier for detecting split errors which is based on a convolutional neural network (CNN).
 We detail the CNN architecture, input features and the training method.
@@
 Finally, we explore an active label suggestion method which reorders the ranking obtained by our classifiers and maximizes the information gain provided by each potential correction.
-
 \subsection{Split Error Detection}
@@
 Rather than analyzing every input pixel, the classifier operates only on segment boundaries which requires less pixel context and is faster.
-Our approach was inspired by Bogovic \etal~\cite{BogovicHJ13} but works with 2D slices rather than 3D volumes.
+In contrast to Bogovic \etal~\cite{BogovicHJ13}, we work with 2D slices rather than 3D volumes.
 This enables proofreading prior or in parallel to an expensive alignment of individual EM images.
@@
 \textbf{Classifier Inputs.} To train the CNN for split error detection, we take boundary context information into consideration for the decision making process.
-For this, we grab a $75x75$ pixel patch at the center of an existing boundary.
+For this, we use a $75\times75$ pixel patch at the center of an existing boundary.
 This covers approximately $80\%$ of all boundaries in real-world connectomics data with nanometer resolution.
 If the boundary edge is not fully covered, we sample up to 10 non-overlapping patches along the boundary and combine the resulting score by weighted averaging based on boundary length coverage per patch.
-In their paper, Bogovich \etal propose to use grayscale image data, corresponding boundary probabilities, and  a single binary mask combining the two neighboring labels as features for their recursive neural network~\cite{BogovicHJ13}.
-We are building on this set of features as inputs for our CNN and create a stacked pixel patch.
-However, we observed that the boundary probability information generated from EM images is often misleading due to noise or artefacts in the data.
+Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data, corresponding boundary probabilities, and a single binary mask combining the two neighboring labels as features for our CNN.
+However, we observed that the boundary probability information generated from EM images is often misleading due to noise or artifacts in the data.
 This can result in merge errors within the automatic segmentation.
 To better direct our classifier to train on the true boundary edge, we extract the border between two segments.
-We then dilate this border by 5 pixels to consider slight edge ambiguities and use this additional binary mask as another feature to create a 4-channel input patch.
+We then dilate this border by 5 pixels to consider slight edge ambiguities and use this binary mask as an additional feature to create a stacked 4-channel input patch.
 Fig.
@@
 \begin{center}
-  \includegraphics[width=\linewidth]{gfx/cnn_inputs.png}
+  \includegraphics[width=\linewidth]{gfx/cnn_inputs.pdf}
 \end{center}
@@
 
-\textbf{Training.} To initially train our network, we use the blue 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels).
-The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse.
-The resolution of our dataset is $3\, nm$ per pixel, and the section thickness is $30\, nm$.
-The image data and a manually-labeled expert segmentation is publicly available as ground truth for the entire dataset\footnote{The Kasthuri 3-cylinder mouse cortex volume is available at  https://software.rc.fas.harvard.edu/lichtman/vast/}.
-We use the first 250 sections of the data for training and validation and the last 50 for testing.
-We use a state-of-the-art method to create a dense automatic segmentation of the data.
-To generate training data, we identify correct regions and split errors in the automatic segmentation by intersection with ground truth regions.
-This is required since extracellular space is not labeled in the ground truth but in our dense automatic segmentation.
-From these regions, we sample 120,000 correct and 120,000 split error patches with 4-channels as described above.
-The patches are normalized and to further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$.
-The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research as well as a brute force parameter search within a limited range (see supplementary material).
-The final parameters and training results are listed in table~\ref{tab:parameters}.
-For baseline comparison, we also list the parameters and training results of focused proofreading in this table but elaborate on these further in section \ref{sec:evaluation}.
-Our CNN configuration results in approximately 170,000 learnable parameters.
-We assume that training has converged if the validation loss does not decrease for 50 epochs.
-
-\begin{table}[h]
-%\resizebox{\textwidth}{!}{%
-\tiny
-\begin{tabular}{@{}c|c|c|c|c|c|c@{}}
-& \textbf{cost [m]} & \textbf{Val. loss} & \textbf{Val. acc.} & \textbf{Test acc.} & \textbf{Prec./Recall} & \textbf{F1 Score} \\ 
-\hspace{1mm}
-\begin{tabular}{@{}l@{}}
-\textbf{Guided Proofreading} \\ Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2-4: 48 \\ Dense units: 512 \\ Learning rate: 0.03-0.00001\\ Momentum: 0.9-0.999\\Mini-Batchsize: 128\\~\\
- \end{tabular}
- & 383  & 0.0845  & 0.969  & 0.94  & 0.94/0.94  & 0.94 \\ 
-\hline 
-\begin{tabular}{@{}l@{}}
-\\
-\textbf{Focused Proofreading} \\ 
-Iterations: 3 \\
-Learning strategy: 2\\
-Mito agglomeration: Off\\
-Threshold: 0.2
- \end{tabular}
- & 43  & ?  & ?  & 0.839  & ?/?  & ? \\ 
-\end{tabular} 
-\vspace{1mm}
-\caption{Training parameters, cost and results of our guided proofreading classifier versus focused proofreading by Plaza \cite{focused_proofreading}.
-Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 graphics card).
-While the training of our classifier is more expensive, testing accuracy is superior.
-}
-\label{tab:parameters}
-\end{table}
-
-For performance comparison on data of a different species, in particular on fruitfly brain (drosophila), we retrain our network.
-The training procedure is according to our initial training and network architecture as well as parameters are not changed.
-We further elaborate on the drosophila datasets in section~\ref{sec:evaluation}.
-Fig.~\ref{fig:roc} displays receiver operating characteristics (ROC) for  guided proofreading trained on mouse and drosophila data, as well as our comparison baseline focused proofreading trained on these datasets respectively.
-
-\begin{figure}[h]
-  \vspace{-5mm}
-\begin{center}
-  \includegraphics[width=\linewidth]{gfx/roc.pdf}
-\end{center}
-  \vspace{-10mm}
-   \caption{ROC performance of guided proofreading (GP) and focused proofreading (FP) trained separately on mouse and drosophila brain images.
-The area under the curve indicates better performance for GP.}
-\label{fig:roc}
-\end{figure}
-
 \subsection{Merge Error Detection}
 
-Identification and correction of merge errors is more challenging, because we must look inside segmentation regions for missing or incomplete boundaries and then propose the correct boundary.
+Identification and correction of merge errors is more challenging than finding and fixing split errors, because we must look inside segmentation regions for missing or incomplete boundaries and then propose the correct boundary.
 However, we can reuse the same trained CNN for this task.
 Similar to guided volume editing by Karimov~\etal~\cite{karimov_guided_volume_editing} we generate potential borders within a segment.
-For each segmentation label, we dilate the label by 20 pixel and generate 30 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
+For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
 For watershed, we use the inverted gray scale EM image as features.
-This yields 30 corresponding splits.
-Dilation of the segment prior to watershed is motivated by our observation that the generated split then actually hogs the real membrane boundary.
+This yields 50 candidate splits.
+
+Dilation of the segment prior to watershed is motivated by our observation that the generated split likely attaches to the real membrane boundary.
 These boundaries are then individually rated using our split error classifier.
-For this, we invert the probability score meaning that a correct split (previously encoded as $p=0$) is most likely a candidate for a merge error (now encoded as $p=1$).
+For this, we invert the probability score such that a correct split (previously encoded as $p=0$) is most likely a candidate for a merge error (now encoded as $p=1$).
 In other words, if a generated boundary is ranked as correct, it probably should be in the segmentation.
@@
 \begin{center}
-  \includegraphics[width=\linewidth]{gfx/merge_error.png}
+  \includegraphics[width=\linewidth]{gfx/merge_error.pdf}
 \end{center}
@@
 We use the proposed classifiers in combination to perform corrections of split and merge errors in automatic segmentations.
-For this, we first perform merge error detection for all existing segments in a data set and store the inverted ranking $1-p$.
-We then sort the rankings and loop through all of them in greedy fashion, starting with the most likely error.
-If the inverted score $1-p$ of a merge error is higher than a threshold $p_t$, we mark this merge error for correction.
-The merge error detection yields the potential new boundary and we can modify the segmentation data to create a new segment accordingly.
-Depending on the variation of guided proofreading as described in section~\ref{sec:evaluation}, we either perform the correction directly (automatic GP) or we have a user accept or reject the correction (simulated GP or human novice/expert).
-Once all merge errors are corrected, we perform split error detection.
-For this, we perform split error detection and store the ranking $p$ for all existing segments in the for merge errors corrected segmentation.
-We then sort the rankings and again loop through all of them - the most likely error first.
-If the score $p$ is higher than a threshold $p_t$, we mark the split error for correction.
-Potential split errors are identified at the border of two segments.
-This reduces the correction to merging the segments and is therefore trivial.
-Similarly to merge errors, we either perform the correction directly or present a user with a yes/no decision.
+For this, we first perform merge error detection for all existing segments in a dataset and store the inverted rankings $1-p$ as well as potential corrections.
+After that, we perform split error detection and store the ranking $p$ for all neighboring segments in the segmentation.
+We then sort the merge and split error rankings individually from highest to lowest.
+For error correction, we first loop through the potential merge error regions and then through the potential split error regions.
+During this process, each error is now subject to a yes/no decision which can be provided in different ways:
+\\~\\
+\textbf{Selection oracle.} If ground data is available, the selection oracle \textit{knows} whether a possible correction improves an automatic segmentation.
+This is realized by simply applying the correction and comparing the outcome using a defined measure.
+The oracle only accepts corrections which improve the automatic segmentation - others get
+discarded. This equals perfect proofreading.
+\\~\\
+\textbf{Automatic selection with threshold.} The decision whether to accept or reject a potential correction is done by comparing rankings to a threshold $p_t$.
+If the inverted score $1-p$ of a merge error is higher than a threshold $1-p_t$, the correction is accepted.
+Similarly, a correction is accepted for a split error if the ranking $p$ is higher than $p_t$.
 Our experiments have shown that the threshold $p_t$ is the same for merge and split errors which makes sense for a balanced classifier.
-The only exception is when a user drives the correction process: we then set $p_t$ for split errors to 0 to let the user inspect every possible split error.
+\\~\\
+\textbf{Forced choice setting.} A user is presented with the choices of either accepting or rejecting a correction.
+This way, all potential split errors are looked at.
 Inspecting all merge errors is not possible for users due to the sheer amount of generated borders.
+We therefor only present merge errors which satisfy $1-p_t$.
+\\~\\
+In all cases, a decision has to be made to advance to the next possible erroneous region.
+If a merge error correction was accepted, the newly found boundary is added to the segmentation data.
+This partially updates the merge error and split error ranking in respect of the new segment.
+If a split error correction was accepted, two segments are merged in the segmentation data and the disappearing segment is removed from all error rankings.
+We then perform merge error detection on the now larger segment and update the ranking.
+We also update the split error rankings to include all new neighbors and re-sort.
+The error with the next highest ranking is now subject to the yes/no decision.
 
-\subsection{Application}
+\subsection{User Interface}
 
 Guided proofreading is integrated into an existing workflow for large connectomics data.
-The GP system is web-based and is designed with a minimalistic user interface showing three components.
-First, we show the outline of the current labeling of a cell boundary and its proposed correction on top of the EM image data.
+The system is web-based and is designed with a minimalistic user interface showing three components.
+We show the outline of the current labeling of a cell boundary and its proposed correction on top of the EM image data.
 For the user, it is not possible to distinguish the current labeling and the proposed correction to avoid selection bias.
-Second, we show a solid overlay of the current and proposed labeling.
-And finally, to provide context, we show a larger area of the EM image where the potentially erroneous region is highlighted.
+We also show a solid overlay of the current and the proposed labeling.
+In addition, we show the image without overlays to provide an unoccluded view.
 User interaction is simple and involves one mouse click on either the current labeling or the correction.
 After interaction, the next potential error is shown.
-We provide a screenshot of the application as part of the supplementary material.
+Figure \ref{fig:ui} shows the user interface.
 
-\subsection{Active Label Suggestion}
+\begin{figure}[h]
+\begin{center}
+  \includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
+\end{center}
+  \vspace{-4mm}
+   \caption{Segmentation correction with the guided proofreading user interface.
+An image without overlays is shown on the left.
+A split error (right) and its correction (center) are the possible choices for the user.
+Hovering highlights the current selection with a yellow border and a mouse click confirms it and advances to the next potential error.}
+\label{fig:ui}
+\end{figure}
 
-In an interactive setting, one way to present patches to the user for proofreading is to order them by the confidence probability of the GP classifier.
+%
+%\subsection{Active Label Suggestion}
+%
+%In an interactive setting, one way to present patches to the user for proofreading is to order them by the confidence probability of the GP classifier.
 However, in an active learning setting, where the network is retrained repeatedly on new label evidence, this approach is less likely to decrease segmentation error as, with the new labels, we are only reinforcing what the network already has a high confidence in.
-Instead, we apply active label suggestion to guide the user into labeling patches which will be more informative to retraining, and so overall decrease VI faster within the proofreading cycle of label $\rightarrow$ train $\rightarrow$ label.
+%Instead, we apply active label suggestion to guide the user into labeling patches which will be more informative to retraining, and so overall decrease VI faster within the proofreading cycle of label $\rightarrow$ train $\rightarrow$ label.
 For each patch, we remove the softmax classification layer and look at the activation weights associated with the last dense layer.
@@
 Then, we adapt Anon~\etal~\cite{ANON} to provide label suggestions based on features from the learned CNN, which is based on maximizing the average information gain provided by a candidate patch to label.
-A second consideration is that each patch labeled by the user provides evidence to other patches, e.g., correcting a split error redefines an entire boundary, from which multiple candidate patch labelings could have been drawn.
+%A second consideration is that each patch labeled by the user provides evidence to other patches, e.g., correcting a split error redefines an entire boundary, from which multiple candidate patch labelings could have been drawn.
 As such, when the user labels a patch, we consider all `knock-on' effect patches as also being labeled, and feed these into the active label suggestion system similarly.
-In section \ref{sec:evaluation}, we report the difference in performance from using active label suggestion rather than confidence ordering when presenting patches to the user.
+%In section \ref{sec:evaluation}, we report the difference in performance from using active label suggestion rather than confidence ordering when presenting patches to the user.
 These results are without retraining the network after new labelings: this should improve results, but would have to be batched to reduce computational load; hence, we leave this for future work.

### 2016-11-14 paper/introduction.tex
Intro edit.

@@
 This is sufficient to keep up with the 2D data capture process on state-of-the-art electron microscopes (though 3D registration is still an expensive offline operation).
+
 In connectomics, neuroscientists annotate neurons and their connectivity within 3D volumes to gain insight into the functional structure of the brain.
 Rapid progress in automatic sample preparation and electron microscopy (EM) acquisition techniques has made it possible to image large volumes of brain tissue at nanometer resolution.
-A typical voxel size is $4\times4\times40~\text{nm}^3$.
-For a $1~\text{mm}^3$ volume, this resolution results in 1 petabyte of data.
+With a voxel size of $4\times4\times40~\text{nm}^3$, a $1~\text{mm}^3$ volume is 1 petabyte of data.
 With so much data, manual annotation is not feasible, and automatic annotation methods are needed~\cite{jain2010,Liu2014,GALA2014,kaynig2015large}.
@@
 Automatic annotation by segmentation and classification of brain tissue is challenging~\cite{isbi_challenge} and all available methods make errors.
-This means we are left with large data which needs \emph{proofreading} by humans.
-This crucial task serves two purposes: 1) to correct errors in the segmentation, and 2) to provide a large body of labeled data to train better automatic segmentation methods.
+This leads to the results being \emph{proofread} by humans.
+This crucial task serves two purposes: 1) to correct errors in the segmentation, and 2) to increase the body of labeled data from which to train better automatic segmentation methods.
 Recent proofreading tools provide intuitive user interfaces to browse segmentation data in 2D and 3D and to identify and manually correct errors ~\cite{markus_proofreading,raveler,mojo2,haehn_dojo_2014}.
@@
 
-Our goal is to add automatic detection of split and merge errors to proofreading tools.
+Our goal is to automatically detect split and merge errors to reduce visual inspection time.
+Further, we wish to propose corrections to the user to accept or reject, to reduce correction time.
+We name this process \textit{guided proofreading}.
+
+First, we learn a classifier for split errors with a convolutional neural network (CNN).
+This takes as input patches of membrane segmentation probabilities, cell segmentation masks, and boundary masks, and outputs a probabiltiy score.
+As we must process large data, this classifier only operates on the boundaries between cells, which reduces computation over methods which analyze every pixel.
+For merge errors, we invert and reuse the split classification network, instead asking it to rate a series of generated candidate boundaries which hypothesize a split.
+We compute corrections for both types of errors.
+
+Second, we propose a greedy algorithm for guided proofreading.
+Possible erroneous regions are sorted by their score, and a correction is generated for each region.
+Then, a user works through this list of regions and corrections.
+In a forced choice setting, the user either selects a correction or skips it to advance to the next region.
+In an automatic setting, errors with a high probability can be automatically corrected first, given an appropriate probability threshold, after which the user would take over.
+Finally, to test the limits of performance, we create an oracle with ground truth knowledge, who accepts corrections only when they improve the segmentation.
+This equals perfect proofreading.
+
+Third, we evaluate these methods on multiple connectomics datasets.
+For the forced choice setting, we perform a quantitative user study with 20 novice users who have no previous experience of proofreading EM data.
+We ask participants to proofread a small segmentation volume in a fixed time frame.
+In a between-subjects design, we compare guided proofreading to both the manual interactive proofreading tool \textit{Dojo} by Haehn~\etal~\cite{haehn_dojo_2014}, and the semi-automatic \textit{focused proofreading} approach by Plaza~\cite{focused_proofreading}.
+We also asked two domain experts to use guided proofreading and focused proofreading for comparison.
+
+We state our contributions:
+\begin{itemize}
+\item A CNN-based boundary classifier for split errors, plus a merge error classifier which inverts the split error classifier.
+This is used to propose merge error corrections, which removes the need to manually draw the missing edge.
+These classifiers perform well with small amounts of training data, which is expensive to collect for connectomics data.
+\item A guided proofreading approach to correcting segmentation volumes, and an assessment scenario comparing forced-choice interaction with automatic and oracle proofreading.
+\item A quantitative user study assessing guided proofreading, which shows that our method is able to reduce segmentation error faster than state-of-the-art semi-automatic tools, across both novice and expert users.
+\end{itemize}
+Our method applies to all existing automatic segmentation methods which produce a label map.
+As such, we believe that guided proofreading is a promising direction to proofread segmentations more efficiently, and so help better tackle large volumes of connectomics imagery.
+
+%Our goal is to add automatic detection of split and merge errors to proofreading tools.
 We design automatic classifiers that detect split and merge errors in segmentations so the user does not need to visually inspect the whole data volume to spot errors.
@@
 We call this process \textit{guided proofreading}.
-
-In this paper, we introduce classifiers to detect merge- and split errors based on a convolutional neural network (CNN).
+%
+%In this paper, we introduce classifiers to detect merge- and split errors based on a convolutional neural network (CNN).
 We believe that this is the first time that deep learning is applied to the task of proofreading.
@@
 This reduces the proofreading operation to simple yes/no decisions.
-
-We further propose a greedy algorithm to perform proofreading.
+%
+%We further propose a greedy algorithm to perform proofreading.
 Possible erroneous regions are sorted by their score and the algorithm iteratively suggests a correction for each region.
@@
 This equals perfect proofreading.
-
-We evaluate our method automatically by threshold and oracle on multiple real-world connectomics datasets.
+%
+%We evaluate our method automatically by threshold and oracle on multiple real-world connectomics datasets.
 To evaluate the forced choice setting, we perform a quantitative user study.
@@
 We also asked four domain experts to use guided proofreading and focused proofreading for additional comparison.
-
-Our first contribution is a classifier for split error detection based on a convolutional neural network.
+%
+%Our first contribution is a classifier for split error detection based on a convolutional neural network.
 The classifier performs well even when trained with little amounts of training data.
@@
 As a consequence, we are able to provide tools to proofread segmentations more efficiently, and so better tackle large volumes of connectomics imagery.
-
-%The reason why we work on top of an existing segmentation rather than improving the underlying technique, is to explore the error space in a non-linear way.
-The real world analogy would be inspecting something with a second set of eyes and different expertise.

### 2016-11-14 paper/introduction.tex
Minor intro fixes, plus minor related work fixes.

@@
 This takes as input patches of membrane segmentation probabilities, cell segmentation masks, and boundary masks, and outputs a probabiltiy score.
-As we must process large data, this classifier only operates on the boundaries between cells, which reduces computation over methods which analyze every pixel.
-For merge errors, we invert and reuse the split classification network, instead asking it to rate a series of generated candidate boundaries which hypothesize a split.
+As we must process large data, this classifier only operates on cell boundaries, which reduces computation over methods which analyze every pixel.
+For merge errors, we invert and reuse the split classification network, instead asking it to rate a set of generated candidate boundaries which hypothesize a split.
 We compute corrections for both types of errors.
@@
 In an automatic setting, errors with a high probability can be automatically corrected first, given an appropriate probability threshold, after which the user would take over.
-Finally, to test the limits of performance, we create an oracle with ground truth knowledge, who accepts corrections only when they improve the segmentation.
+Finally, to test the limits of performance, we create an oracle with knowledge of the ground truth, which only accepts corrections when they improve the segmentation.
 This equals perfect proofreading.

### 2016-11-14 paper/related_work.tex
Update intro, rel. work and methods.
Minor intro fixes, plus minor related work fixes.

@@
 \begin{center}
-\includegraphics[width=\linewidth]{gfx/architecture.png}
+\includegraphics[width=\linewidth]{gfx/architecture.pdf}
 \end{center}
@@
 NeuroProof \cite{neuroproof2013} decreases error rates by learning a agglomeration on over-segmentations of images, based on a random forest classifier.
-Vazquez-Reina \etal~\cite{amelio_segmentation} take whole EM volumes into account rather than a per section approach, then solve a fusion problem with a global context.
+Vazquez-Reina \etal~\cite{amelio_segmentation} consider whole EM volumes rather than a per section approach, then solve a fusion problem with a global context.
 Kaynig \etal~\cite{kaynig10} propose a random forest classifier coupled with an anisotropic smoothing prior in a conditional random field framework with 3D segment fusion.
@@
 All these approaches make good progress; however, in general, proofreading is still required to correct errors.
-
-%Inspired by Bogovic \etal, we extend their features for our guided proofreading classifiers (Section \ref{sec:methods}).
-
+\\~\\
 \textbf{Interactive Proofreading.} While proofreading is very time consuming, it is fairly easy for humans to perform corrections through splitting and merging segments.
@@
 Recent works propose computer-aided proofreading systems which help reduce the time spent in this visual search task.
-
-%Most relevant methods here use heuristics to analyze the image data to find potential errors. 
+\\~\\
 \textbf{Computer-aided Proofreading.} Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}.
 The authors track uncertainty throughout the automatic labeling by training a conditional random field.
-This segmentation technique produces uncertainty estimates, which can be used to present potential regions for proofreading to the user.
-While it works on isotropic volumes, more work is needed to apply it to anisotropic volumes, like most connectomics datasets.
+This segmentation technique produces uncertainty estimates, which inform potential regions for proofreading to the user.
+While this applies to isotropic volumes, more work is needed to apply it to anisotropic volumes, like most connectomics datasets.
 

### 2016-11-14 paper/conclusion.tex
Evaluation in the works.

@@
 
-The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation.
+%The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation.
 Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task.
 Humans are the bottleneck and minimizing the manual labor is the goal.
-We have addressed this problem through training a convolutional neural network to detect ambiguous regions from labeled data---in effect, by finding a non-linear mapping between image and segmentation data.
+%We have addressed this problem through training a convolutional neural network to detect ambiguous regions from labeled data---in effect, by finding a non-linear mapping between image and segmentation data.
 This allows us to identify merge and split errors with better performance than existing systems.

### 2016-11-14 gp/legacy.py
Fix bug.

@@ -648,7 +648,7 @@ class Legacy(object):
     def dojoVI(gt, seg):
       # total_vi = 0
       slice_vi = []    
-      for i in range(10):
+      for i in range(len(gt)):
           current_vi = Util.vi(gt[i].astype(np.int64), seg[i].astype(np.int64))
           # total_vi += current_vi
           slice_vi.append(current_vi)
@@ -720,7 +720,7 @@ class Legacy(object):
       def dojoVI(gt, seg):
         # total_vi = 0
         slice_vi = []    
-        for i in range(10):
+        for i in range(len(gt)):
             current_vi = Util.vi(gt[i].astype(np.int64), seg[i].astype(np.int64))
             # total_vi += current_vi
             slice_vi.append(current_vi)
@@ -910,7 +910,7 @@ class Legacy(object):
     def dojoVI(gt, seg):
       # total_vi = 0
       slice_vi = []    
-      for i in range(10):
+      for i in range(len(gt)):
           current_vi = Util.vi(gt[i].astype(np.int64), seg[i].astype(np.int64))
           # total_vi += current_vi
           slice_vi.append(current_vi)
@@ -1123,7 +1123,7 @@ class Legacy(object):
     def dojoVI(gt, seg):
       # total_vi = 0
       slice_vi = []    
-      for i in range(gt.shape[0]):
+      for i in range(len(gt)):
           current_vi = Util.vi(gt[i].astype(np.int64), seg[i].astype(np.int64))
           # total_vi += current_vi
           slice_vi.append(current_vi)

### 2016-11-14 paper/evaluation.tex

--- 2016-11-04 paper/evaluation.tex
@@
-\begin{figure*}[t]
-\begin{center}
-\includegraphics[width=\linewidth]{gfx/results_mouse.png}
-\end{center}
-  \vspace{-4mm}
-   \caption{Performance evaluation of the classifiers on two mouse brain datasets measured as adapted Rand error (lower scores are better).
+%\begin{figure*}[t]
+%\begin{center}
+%\includegraphics[width=\linewidth]{gfx/results_mouse.png}
+%\end{center}
+%  \vspace{-4mm}
+%   \caption{Performance evaluation of the classifiers on two mouse brain datasets measured as adapted Rand error (lower scores are better).
 We compare guided proofreading (GP), guided proofreading with active label suggestion (GP*) and focused proofreading.
@@
 The simulated user is able to correct the initial segmentation beyond this threshold while automatic GP* then introduces errors.}
-\label{fig:results_mouse}
-\end{figure*}
+%\label{fig:results_mouse}
+%\end{figure*}
 
@@
 
-We evaluate guided proofreading (GP) on multiple real-world connectomics datasets of different species.
-In particular, we evaluate GP on two datasets of mouse brain and three datasets of fruitfly brain (drosophila).
-For comparison, we choose the fully interactive proofreading software \textit{Dojo} by Haehn \etal~\cite{haehn_dojo_2014} as well as the aided proofreading framework \textit{focused proofreading} (FP) by Plaza~\cite{focused_proofreading}.
-We first describe the evalation on mouse brain data and then the evaluation on drosophila brain.
+We evaluate guided proofreading on multiple different real-world connectomics datasets of different species.
+We perform experiments for error correction based on a selection oracle, automatic selection with threshold, and the forced choice setting.
+The latter is designed as a between-subjects user study with novice and expert participants.
 
-\subsection{Mouse Brain}
+\subsection{Datasets}
 
-Mouse brain is a common target for connectomics research because the structural proportions are similar to human brains~\cite{jeff_science}.
+The following serial section electron microscopy datasets are used for the evaluation of our method. 
+\\~\\
+\textbf{L.
+Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels).
+The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse.
+The resolution of our dataset is $3\times3\, \text{nm}^2$ per pixel, and the section thickness is $30\, \text{nm}$.
+The image data and a manually-labeled expert segmentation is publicly available as ground truth for the entire dataset\footnote{The Kasthuri 3-cylinder mouse cortex volume is available at  https://software.rc.fas.harvard.edu/lichtman/vast/.}.
+\\~\\
+\textbf{AC4 subvolume.} This dataset is part of a publicly available dataset of mouse cortex that was published for the ISBI 2013 challenge "SNEMI3D: 3D Segmentation of neurites in EM images".
+The resolution of this dataset is $6\times6\times30~\text{nm}^3\text{/voxel}$.
+Haehn~\etal cut the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes~\cite{haehn_dojo_2014}.
+This subvolume was used for Haehn~\etal~experiment on interactive proofreading tools for connectomics.
+The data, labeled ground truth and findings of their study are published online\footnote{The AC4 subvolume and results of the interactive proofreading experiment are available at http://rhoana.org/dojo/.}.
+\\~\\
+\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI) three datasets (each $1250\times1250\times125$ voxels) were made publicly available including manually labeled ground truth\footnote{The MICCAI CREMI challenge data is available at http://www.cremi.org.}.
+The volumes are part of adult fruit fly (Drosophila melanogaster) brain.
+The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$.
+\\~\\
+\textbf{Automatic segmentation pipeline.}
+We use a state-of-the-art method to create a dense automatic segmentation of the data.
+Membrane probabilities are generated using a convolutional neural network based on the U-net architecture~\cite{RonnebergerFB15}.
+The probabilities are used to seed watershed and generate an oversegmentation using superpixels.
+Agglomeration is then performed by the GALA active learning classifier~\cite{nunez2014graph}.
+
+\subsection{Classifier Training}
+
+To train our split error classifier, we use the L.
+Cylinder dataset.
+We use the first 250 sections of the data for training and validation.
+For n-fold cross validation, we select one quarter of this data and re-select after each epoch.
+We minimize cross-entropy loss and update using stochastic gradient descent with Nesterov momentum \cite{nesterov}.
+To generate training data, we identify correct regions and split errors in the automatic segmentation by intersection with ground truth regions.
+This is required since extracellular space is not labeled in the ground truth but in our dense automatic segmentation.
+From these regions, we sample 112,760 correct and 112,760 split error patches with 4-channels as described above.
+The patches are normalized and to further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$.
+The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research as well as a brute force parameter search within a limited range (see supplementary material).
+The final parameters are listed in the first row of table~\ref{tab:parameters}.
+Our CNN configuration results in approximately 170,000 learnable parameters.
+We assume that training has converged if the validation loss does not decrease for 50 epochs.
+We test the CNN by generating a balanced set of 8,780 correct and 8,780 error patches using unseen data of the left cylinder dataset and report testing results in the second row of table~\ref{tab:parameters}.
+
+\begin{table}[h]
+%\resizebox{\textwidth}{!}{%
+\small
+\begin{tabular}{l|l}
+\begin{tabular}{l}
+\textbf{Guided Proofreading}\\~\\
+\textbf{Parameters} \\ 
+Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2-4: 48 \\ Dense units: 512 \\ Learning rate: 0.03-0.00001\\ Momentum: 0.9-0.999\\Mini-Batchsize: 128\\~\\
+ \end{tabular}
+&
+\begin{tabular}{l}
+\textbf{Focused Proofreading}\\~\\
+\textbf{Parameters} \\ 
+Iterations: 3 \\
+Learning strategy: 2\\
+Mito agglomeration: Off\\
+Threshold: 0.0\\
+~\\
+~\\
+~\\
+~\\
+ \end{tabular}
+ \\
+ \hline 
+ \\
+ \begin{tabular}{l}
+\textbf{Results} \\ cost [m]: 383 \\ Val. loss: 0.0845 \\ Val. acc.: 0.969 \\ Test. acc.: 0.94 \\ Prec./Recall: 0.94/0.94 \\ F1 Score: 0.94
+ \end{tabular}
+&
+\begin{tabular}{l}
+\textbf{Results} \\ cost [m]: 217 \\ ~ \\ ~ \\ Test. acc.: 0.99 \\ Prec./Recall: ?/? \\ F1 Score: ?
+ \end{tabular}
+\end{tabular} 
+\vspace{1mm}
+\caption{Training parameters, cost and results of our guided proofreading classifier versus focused proofreading by Plaza \cite{focused_proofreading}.
+Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 graphics card).}%While the training of our classifier is more expensive, testing accuracy is superior.
+}
+\label{tab:parameters}
+\end{table}
+
+\subsection{Baseline comparison}
+
+\textbf{Interactive proofreading.} According to the comparison of Haehn~\etal~, the best performing proofreading tool for novices is Dojo.
+We use the publicly available findings of their user study as a baseline comparison.
+
+\textbf{Computer-aided proofreading.} FP
+
+\subsection{Experiments}
+
+\textbf{Selection oracle evaluation.}
+
+\textbf{Automatic method evaluation.}
+
+\textbf{Forced choice user experiment.}
+
+%\textbf{Training.}
+
+%For baseline comparison, we also list the parameters and training results of focused proofreading in this table but elaborate on these further in section \ref{sec:evaluation}.
+
+%
+%\begin{table}[h]
+%%\resizebox{\textwidth}{!}{%
+%\tiny
+%\begin{tabular}{@{}c|c|c|c|c|c|c@{}}
+%& \textbf{cost [m]} & \textbf{Val. loss} & \textbf{Val. acc.} & \textbf{Test acc.} & \textbf{Prec./Recall} & \textbf{F1 Score} \\ 
+%\hspace{1mm}
+%\begin{tabular}{@{}l@{}}
+%\textbf{Guided Proofreading} \\ Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2-4: 48 \\ Dense units: 512 \\ Learning rate: 0.03-0.00001\\ Momentum: 0.9-0.999\\Mini-Batchsize: 128\\~\\
+% \end{tabular}
+% & 383  & 0.0845  & 0.969  & 0.94  & 0.94/0.94  & 0.94 \\ 
+%\hline 
+%\begin{tabular}{@{}l@{}}
+%\\
+%\textbf{Focused Proofreading} \\ 
+%Iterations: 3 \\
+%Learning strategy: 2\\
+%Mito agglomeration: Off\\
+%Threshold: 0.2
+% \end{tabular}
+% & 43  & ?  & ?  & 0.839  & ?/?  & ? \\ 
+%\end{tabular} 
+%\vspace{1mm}
+%\caption{Training parameters, cost and results of our guided proofreading classifier versus focused proofreading by Plaza \cite{focused_proofreading}.
+Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 graphics card).
+While the training of our classifier is more expensive, testing accuracy is superior.
+}
+%\label{tab:parameters}
+%\end{table}
+
+%For performance comparison on data of a different species, in particular on fruitfly brain (drosophila), we retrain our network.
+The training procedure is according to our initial training and network architecture as well as parameters are not changed.
+We further elaborate on the drosophila datasets in section~\ref{sec:evaluation}.
+Fig.~\ref{fig:roc} displays receiver operating characteristics (ROC) for  guided proofreading trained on mouse and drosophila data, as well as our comparison baseline focused proofreading trained on these datasets respectively.
+%
+%\begin{figure}[h]
+%  \vspace{-5mm}
+%\begin{center}
+%  \includegraphics[width=\linewidth]{gfx/roc.pdf}
+%\end{center}
+%  \vspace{-10mm}
+%   \caption{ROC performance of guided proofreading (GP) and focused proofreading (FP) trained separately on mouse and drosophila brain images.
+The area under the curve indicates better performance for GP.}
+%\label{fig:roc}
+%\end{figure}
+
+%\subsection{Mouse Brain}
+%
+%Mouse brain is a common target for connectomics research because the structural proportions are similar to human brains~\cite{jeff_science}.
 For our first experiment we recruited novice and expert participants as part of a quantitative user study.
 Our second experiment is performed on a larger dataset and we evaluate a simulated user.
-\\~\\
-\textbf{User study.} Recently, Haehn \etal evaluated the interactive proofreading tools Raveler, Mojo, and Dojo as part of an experiment with novice users~\cite{haehn_dojo_2014}.
+%\\~\\
+%\textbf{User study.} Recently, Haehn \etal evaluated the interactive proofreading tools Raveler, Mojo, and Dojo as part of an experiment with novice users~\cite{haehn_dojo_2014}.
 The participants corrected an automatic segmentation with merge and split errors.
@@
 In particular, we use the best performing user of Dojo who was truly an outlier as reported by Haehn \etal.
-
-Since interactive proofreading most likely yields lower performance than aided proofreading, we also compare against FP by Plaza~\cite{focused_proofreading} which is integrated in Raveler and freely available.
+%
+%Since interactive proofreading most likely yields lower performance than aided proofreading, we also compare against FP by Plaza~\cite{focused_proofreading} which is integrated in Raveler and freely available.
 For FP we consulted an expert to obtain the best possible parameters as shown in table \ref{tab:parameters}.
@@
 For the expert experiment, we assign accordingly.
-In addition to human performance, we also evaluate automatic GP, automatic GP with active label suggestion (GP*) and automatic FP.
+%In addition to human performance, we also evaluate automatic GP, automatic GP with active label suggestion (GP*) and automatic FP.
 Due to the automatic nature, we do not enforce the 30 minute time limit but we stop once our probability threshold of $p_t=.95$ is reached.
@@
 aRE is a measure of dissimilarity, related to introduced errors, meaning lower scores are better.
-
-The results of our comparisons are shown in the first row of Fig.~\ref{fig:results_mouse}.
+%
+%The results of our comparisons are shown in the first row of Fig.~\ref{fig:results_mouse}.
 In all cases, GP* is able to correct the segmentation further than other methods (aRE measures: automatic GP XX, GP* XX, FP XX, novice Dojo XX, GP* XX, FP XX, expert Dojo XX, GP* XX, FP XX).
@@
 In fact, the average correction time for novices is for GP* 3.6 (expert X), for FP Y (expert YY), and for Dojo 30 (expert ZZ) seconds.
-\\~\\
-\textbf{Simulated experiment.} For our second experiment with mouse brain data, we proofread the last 50 slices of the blue 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} which we also used for testing in section~\ref{sec:methods}.
+%\\~\\
+%\textbf{Simulated experiment.} For our second experiment with mouse brain data, we proofread the last 50 slices of the blue 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} which we also used for testing in section~\ref{sec:methods}.
 The data was not seen by the network before and includes $2048x2048x50$ voxels with a total number of 17,560 labeled objects.
@@
 For automatic GP and GP*, we use our defined probability threshold $p_t=.95$.
-
-The results of this experiment are shown in the second row of Fig.~\ref{fig:results_mouse}.
+%
+%The results of this experiment are shown in the second row of Fig.~\ref{fig:results_mouse}.
 GP* is again able to correct the segmentation further than other methods (aRE measures: automatic GP XX, GP* XX, FP XX, simulated GP* XX, FP XX).
 Again, the results are not surprising since GP* can correct merge and split errors.
-
-\subsection{Drosophila Brain}
-
-The drosophila brain is analyzed by connectomics researchers because of its small size and hence, a reasonable target to obtain a complete wiring diagram.
+%
+%\subsection{Drosophila Brain}
+%
+%The drosophila brain is analyzed by connectomics researchers because of its small size and hence, a reasonable target to obtain a complete wiring diagram.
 Despite the size, fruit flies exhibit complex behaviors and are in general well studied.
@@
 Manually labeled ground truth is also available for A,B, and C but not for the testing data.
-
-Since drosophila brain exhibits different cell structures than mouse brain, we retrain the guided proofreading classifiers (and our automatic segmentation pipeline) as well as focused proofreading combined on the three training datasets.
+%
+%Since drosophila brain exhibits different cell structures than mouse brain, we retrain the guided proofreading classifiers (and our automatic segmentation pipeline) as well as focused proofreading combined on the three training datasets.
 We use 300 slices of the A,B,C samples for training and validation, and 75 slices for testing.
@@
 The trained GP classifier exhibits a reasonable performance on the testing data as seen in Fig.~\ref{fig:roc}.
-
-\begin{figure}[h]
-\begin{center}
-  \includegraphics[width=\linewidth]{gfx/results_fruitfly.png}
-\end{center}
-  \vspace{-4mm}
-   \caption{Results of guided proofreading with active label suggestion (GP*) and focused proofreading performed automatically on three drosophila datasets.
+%
+%\begin{figure}[h]
+%\begin{center}
+%  \includegraphics[width=\linewidth]{gfx/results_fruitfly.png}
+%\end{center}
+%  \vspace{-4mm}
+%   \caption{Results of guided proofreading with active label suggestion (GP*) and focused proofreading performed automatically on three drosophila datasets.
 The datasets are part of the MICCAI 2016 CREMI challenge and publicly available.
@@
 Our GP* scores places us XXnd on the CREMI leaderboard.}
-\label{fig:results_fruitfly}
-\end{figure}
-
-We then use the trained GP* and FP classifiers to evaluate proofreading automatically.
+%\label{fig:results_fruitfly}
+%\end{figure}
+%
+%We then use the trained GP* and FP classifiers to evaluate proofreading automatically.
 Since ground truth labeling is not available, the evaluation is performed by submitting our results to the CREMI leaderboard.

### 2016-11-14 paper/introduction.tex

@@
 We ask participants to proofread a small segmentation volume in a fixed time frame.
-In a between-subjects design, we compare guided proofreading to both the manual interactive proofreading tool \textit{Dojo} by Haehn~\etal~\cite{haehn_dojo_2014}, and the semi-automatic \textit{focused proofreading} approach by Plaza~\cite{focused_proofreading}.
-We also asked two domain experts to use guided proofreading and focused proofreading for comparison.
+In a between-subjects design, we compare guided proofreading to the semi-automatic \textit{focused proofreading} approach by Plaza~\cite{focused_proofreading}.
+In addition, we compare against the manual interactive proofreading tool \textit{Dojo} by Haehn~\etal~\cite{haehn_dojo_2014}.
+We also asked four domain experts to use guided proofreading and focused proofreading for comparison.
 

### 2016-11-14 cylinderFP.py
Restricted XP to ten slices :(.

@@ -53,7 +53,7 @@ with open(bigM_cylinder_file, 'rb') as f:
 #
 # run auto split correction
 #
-cylinder_vi_95_file = OUTDIR + '/cylinder_vi_95.p'
+cylinder_vi_95_file = OUTDIR + '/cylinder_vi_95_NEW.p'
 
 split_vis = OUTDIR + '/cylinder_split_auto95_vis.p'
 
@@ -99,7 +99,7 @@ print '   Median VI improvement', original_median_VI-cylinder_vi_95[1]
 #
 # run oracle split correction
 #
-cylinder_vi_95_file = OUTDIR + '/cylinder_vi_simuser.p'
+cylinder_vi_95_file = OUTDIR + '/cylinder_vi_simuser_NEW.p'
 
 split_vis = OUTDIR + '/cylinder_split_simuser_vis.p'
 

### 2016-11-14 cylinderGP.py

@@ -60,7 +60,7 @@ else:
 #
 # run auto merge correction
 #
-cylinder_vi_95_file = OUTDIR + '/cylinder_vi_95_w_merge.p'
+cylinder_vi_95_file = OUTDIR + '/cylinder_vi_95_w_merge_NEW.p'
 
 merge_vis = OUTDIR + '/cylinder_merge_auto95_vis.p'
 split_vis = OUTDIR + '/cylinder_split_auto95_vis.p'
@@ -125,7 +125,7 @@ print '   Median VI improvement', original_median_VI-cylinder_vi_95[1]
 #
 # run auto merge correction
 #
-cylinder_vi_95_file = OUTDIR + '/cylinder_vi_00_w_merge.p'
+cylinder_vi_95_file = OUTDIR + '/cylinder_vi_00_w_merge_NEW.p'
 
 merge_vis = OUTDIR + '/cylinder_merge_auto00_vis.p'
 split_vis = OUTDIR + '/cylinder_split_auto00_vis.p'
@@ -196,7 +196,7 @@ print '   Median VI improvement', original_median_VI-cylinder_vi_95[1]
 #
 # run oracle merge correction
 #
-cylinder_vi_95_file = OUTDIR + '/cylinder_vi_simuser_w_merge.p'
+cylinder_vi_95_file = OUTDIR + '/cylinder_vi_simuser_w_merge_NEW.p'
 
 merge_vis = OUTDIR + '/cylinder_merge_simuser_vis.p'
 split_vis = OUTDIR + '/cylinder_split_simuser_vis.p'

### 2016-11-14 gp/util.py
CREMI xp.

@@ -14,6 +14,28 @@ import tifffile as tif
 class Util(object):
 
   @staticmethod
+  def read_cremi_section(DATADIR, z, verbose=True):
+    image = sorted(glob.glob(DATADIR+'image/*'))
+    probs = sorted(glob.glob(DATADIR+'prob/*'))
+    gold = sorted(glob.glob(DATADIR+'gold/*'))
+    rhoana = sorted(glob.glob(DATADIR+'rhoana/*'))
+
+    image = tif.imread(image[z])
+    prob = tif.imread(probs[z])
+    gold = tif.imread(gold[z])
+    rhoana = mh.imread(rhoana[z])
+
+    #convert ids from rgb to single channel
+    rhoana_single = np.zeros((rhoana.shape[0], rhoana.shape[1]), dtype=np.uint64)
+    rhoana_single[:, :] = rhoana[:,:,0]*256*256 + rhoana[:,:,1]*256 + rhoana[:,:,2]
+
+    # relabel the segmentations
+    gold = Util.relabel(gold)
+    rhoana_single = Util.relabel(rhoana_single)
+
+    return image, prob, gold, rhoana_single
+
+  @staticmethod
   def read_section(path, z, verbose=True):
     '''
     '''

### 2016-11-14 patchgenCREMI.py

@@ -1,0 +1,114 @@
+import cPickle as pickle
+import gp
+import glob
+import mahotas as mh
+import numpy as np
+import os
+import time
+
+
+def generate_patches(start_slice, end_slice):
+
+    patch_index = 0
+
+    all_patches_count = 0
+    patch_list = []
+    all_error_patches = []
+    all_correct_patches = []
+    
+    for z in range(start_slice, end_slice):
+
+        t0 = time.time()
+        print 'working on slice', z
+        input_image, input_prob, input_gold, input_rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+
+
+        error_patches, patches = gp.Patch.patchify_maxoverlap(input_image, input_prob, np.zeros((1,1250,1250),dtype=np.bool), input_rhoana, input_gold, sample_rate=1)
+        
+        print 'Generated', len(error_patches), 'split error patches and', len(patches), ' correct patches in', time.time()-t0, 'seconds.'
+        
+        patch_list.append(patches)
+        all_error_patches += error_patches
+        all_correct_patches += patches
+        
+    with open('/n/regal/pfister_lab/haehn/CREMITEST/e_p.p', 'wb') as f:
+      pickle.dump(all_error_patches, f)
+
+    with open('/n/regal/pfister_lab/haehn/CREMITEST/p.p', 'wb') as f:
+      pickle.dump(all_correct_patches, f)
+    
+    NO_PATCHES = len(all_error_patches) + len(all_correct_patches)
+
+    print 'We have a total of',NO_PATCHES,'patches.'
+    print 'Errors:',len(all_error_patches)
+    print 'Correct:',len(all_correct_patches)    
+    
+    PATCH_BYTES = 75*75
+    P_SIZE = (NO_PATCHES, 4, 75,75) # rather than raveled right now
+    
+    p_rgba = np.zeros(P_SIZE, dtype=np.float32)
+    
+
+    p_target = np.zeros(NO_PATCHES)
+
+
+    i = 0
+    for p in all_error_patches:
+
+        p_rgba[i][0] = p['image']
+        p_rgba[i][1] = 1. - p['prob'] ### INVERT PROB
+        p_rgba[i][2] = p['merged_array']
+        p_rgba[i][3] = p['larger_border_overlap']  
+        
[…]

### 2016-11-14 gp/patch.py
Handle no mask cases properly.

@@ -236,8 +236,14 @@ class Patch(object):
                       ignore_zero_neighbor=True, patch_size=(75,75), clamp_result=True):
     '''
     '''
+    no_mask=False
     # grab the mask border
-    mask_borders = mh.labeled.borders(mask)
+    if mask.max() == 0.:
+      # ignore borders
+      print 'no mask'
+      no_mask = True
+    else:
+      mask_borders = mh.labeled.borders(mask)
     
     # fill segmentation using max overlap and relabel it
     fixed = Util.propagate_max_overlap(segmentation, gold)
@@ -249,12 +255,14 @@ class Patch(object):
     # grab borders of segmentation and fixed
     segmentation_borders = mh.labeled.borders(segmentation)
     fixed_borders = mh.labeled.borders(fixed)
-    fixed_borders[mask_borders == 1] = 0
+    if not no_mask:
+      fixed_borders[mask_borders == 1] = 0
     
     
     bad_borders = np.array(segmentation_borders)
     bad_borders[fixed_borders == 1] = 0
-    bad_borders[mask_borders == 1] = 0
+    if not no_mask:
+      bad_borders[mask_borders == 1] = 0
 
 
 

### 2016-11-14 paper/guidedproofreading_review.tex
Edited abstract

@@
 \usepackage{cvpr}
+\usepackage{microtype}
 \usepackage{times}
@@
 \begin{abstract}
-Automatic cell image segmentation methods in connectomics produce merge and split errors, which require correction through proofreading.
-Previous research has identified the visual search for these errors as the bottleneck in interactive proofreading.
-To aid error correction, we develop two classifiers to recommend candidate merge and split errors and their corrections to the user.
-These classifiers are informed by training a convolutional neural network with known errors in automatic segmentations against expert-labeled ground truth.
-Our classifiers detect potentially-erroneous regions by considering a large context region around a segmentation boundary.
-Corrections can then be performed as yes/no decisions
-resulting in faster correction times than previous methods.
-We evaluate our approach on connectomics datasets of different species and compare correction performance of novice and expert users against different existing systems.
-We report significant improvements compared to pure automatic and pure manual proofreading.
+%
+Automatic cell image segmentation methods in connectomics produce merge and
+split errors, which require correction through proofreading. Previous research
+has identified the visual search for these errors as the bottleneck in
+interactive proofreading. To aid error correction, we develop two classifiers
+that automatically recommend candidate merge and splits to the user. These
+classifiers use a convolutional neural network (CNN) that has been trained with
+errors in automatic segmentations against expert-labeled ground truth. Our
+classifiers detect potentially-erroneous regions by considering a large context
+region around a segmentation boundary. Corrections can then be performed by a
+user with yes/no decisions  resulting in faster correction times than previous
+proofreading methods. We also present a fully-automatic mode that uses a
+threshold to make merge/split decisions. Extensive experiments using the
+automatic approach and comparing performance of novice and expert users
+demonstrate that our method performs favorably agains state-of-the-art
+proofreading methods on different connectomics datasets.
+%
 \end{abstract}

### 2016-11-14 paper/evaluation.tex
More updates.

@@
 \\~\\
-\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI) three datasets (each $1250\times1250\times125$ voxels) were made publicly available including manually labeled ground truth\footnote{The MICCAI CREMI challenge data is available at http://www.cremi.org.}.
+\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI) six datasets (each $1250\times1250\times125$ voxels) were made publicly available\footnote{The MICCAI CREMI challenge data is available at http://www.cremi.org.}.
+Since only three include manually labeled ground truth, we use these three volumes for our experiments.
 The volumes are part of adult fruit fly (Drosophila melanogaster) brain.
@@
 
-\textbf{Interactive proofreading.} According to the comparison of Haehn~\etal~, the best performing proofreading tool for novices is Dojo.
+\textbf{Interactive proofreading.} According to the comparison of Haehn~\etal~, the best performing proofreading tool for novices is Dojo~\cite{haehn_dojo_2014}.
 We use the publicly available findings of their user study as a baseline comparison.
+More specifically, we use the data of the Dojo user with the reported best performance.
 
-\textbf{Computer-aided proofreading.} FP
+\textbf{Computer-aided proofreading.}
 

### 2016-11-14 mergepatchesCREMI.py
Add merger for cremi patches.

@@ -1,0 +1,64 @@
+import numpy as np
+
+#
+#
+#
+
+basedir = '/n/regal/pfister_lab/haehn/CREMITEST/'
+
+trainA = basedir + 'trainA.npz.npy'
+trainA_targets = basedir + 'trainA_targets.npz.npy'
+trainB = basedir + 'trainB.npz.npy'
+trainB_targets = basedir + 'trainB_targets.npz.npy'
+trainC = basedir + 'trainC.npz.npy'
+trainC_targets = basedir + 'trainC_targets.npz.npy'
+
+counter = 0
+
+trainA = np.load(trainA, mmap_mode='r')
+trainA_count = trainA.shape[0]
+
+trainB = np.load(trainB, mmap_mode='r')
+trainB_count = trainB.shape[0]
+
+trainC = np.load(trainC, mmap_mode='r')
+trainC_count = trainC.shape[0]
+
+all_count = trainA_count + trainB_count + trainC_count
+
+#
+# allocate large array
+# 
+PATCH_BYTES = 75*75
+NO_PATCHES = all_count
+P_SIZE = (NO_PATCHES, 4, 75,75) # rather than raveled right now
+
+p_rgba = np.zeros(P_SIZE, dtype=np.float32)
+
+p_rgba[0:trainA_count] = trainA
+p_rgba[trainA_count:trainA_count+trainB_count] = trainB
+p_rgba[trainB_count:trainB_count+trainC_count] = trainC
+
+# now store this bad boy
+np.save(basedir+'train.npy', p_rgba)
+
+print 'STORED BIG BOY!'
+p_rgba = None # free them all
+
+#
+# same for targets
+#
+trainA_targets = np.load(trainA_targets)
+trainB_targets = np.load(trainB_targets)
+trainC_targets = np.load(trainC_targets)
+
+p_target = np.zeros(NO_PATCHES)
+
+p_target[0:trainA_count] = trainA_targets
+p_target[trainA_count:trainA_count+trainC_count] = trainB_targets
+p_target[trainB_count:trainB_count+trainC_count] = trainC_targets
+
+# now store this lady boy
+np.save(basedir+'train_targets.npy', p_target)
+
+print 'ALL DONE!'

### 2016-11-14 slurm/mergerCREMI.py

@@ -1,0 +1,85 @@
+import numpy as np
+
+#
+#
+#
+
+basedir = '/n/regal/pfister_lab/haehn/FINAL/IPMLB_before_NP/'
+
+train1 = basedir + 'train1.npz'
+train1_targets = basedir + 'train1_targets.npz'
+train2 = basedir + 'train2b.npz.npy'
+train2_targets = basedir + 'train2b_targets.npz.npy'
+train3 = basedir + 'train3b.npz.npy'
+train3_targets = basedir + 'train3b_targets.npz.npy'
+train4 = basedir + 'train4.npz'
+train4_targets = basedir + 'train4_targets.npz'
+train5 = basedir + 'train5b.npz.npy'
+train5_targets = basedir + 'train5b_targets.npz.npy'
+
+counter = 0
+
+train1 = np.load(train1, mmap_mode='r')
+train1_count = train1['rgba'].shape[0]
+
+train2 = np.load(train2, mmap_mode='r')
+train2_count = train2.shape[0]
+
+train3 = np.load(train3, mmap_mode='r')
+train3_count = train3.shape[0]
+
+train4 = np.load(train4, mmap_mode='r')
+train4_count = train4['rgba'].shape[0]
+
+train5 = np.load(train5, mmap_mode='r')
+train5_count = train5.shape[0]
+
+all_count = train1_count + train2_count + train3_count + train4_count + train5_count
+
+#
+# allocate large array
+# 
+PATCH_BYTES = 75*75
+NO_PATCHES = all_count
+P_SIZE = (NO_PATCHES, 4, 75,75) # rather than raveled right now
+
+p_rgba = np.zeros(P_SIZE, dtype=np.float32)
+
+p_rgba[0:train1_count] = train1['rgba']
+p_rgba[train1_count:train1_count+train2_count] = train2
+p_rgba[train2_count:train2_count+train3_count] = train3
+p_rgba[train3_count:train3_count+train4_count] = train4['rgba']
+p_rgba[train4_count:train4_count+train5_count] = train5
+
+# now store this bad boy
+np.save(basedir+'train.npy', p_rgba)
+
+print 'STORED BIG BOY!'
+train1 = None
+train2 = None
+train3 = None
+train4 = None
+train5 = None
+p_rgba = None # free them all
+
+#
+# same for targets
+#
+train1_targets = np.load(train1_targets)
+train2_targets = np.load(train2_targets)
+train3_targets = np.load(train3_targets)
+train4_targets = np.load(train4_targets)
[…]

### 2016-11-14 paper/evaluation.tex

@@
 We evaluate guided proofreading on multiple different real-world connectomics datasets of different species.
+All datasets were acquired using either via serial section electron microscopy (ssEM) or serial section transmission electron microscopy (ssTEM).
 We perform experiments for error correction based on a selection oracle, automatic selection with threshold, and the forced choice setting.
@@
 
-The following serial section electron microscopy datasets are used for the evaluation of our method. 
-\\~\\
 \textbf{L.
 Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels).
-The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse.
+The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse and was acquired using ssEM.
 The resolution of our dataset is $3\times3\, \text{nm}^2$ per pixel, and the section thickness is $30\, \text{nm}$.
@@
 \textbf{AC4 subvolume.} This dataset is part of a publicly available dataset of mouse cortex that was published for the ISBI 2013 challenge "SNEMI3D: 3D Segmentation of neurites in EM images".
-The resolution of this dataset is $6\times6\times30~\text{nm}^3\text{/voxel}$.
-Haehn~\etal cut the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes~\cite{haehn_dojo_2014}.
+The resolution of this dataset is $6\times6\times30~\text{nm}^3\text{/voxel}$ and it was acquired using ssEM.
+Haehn~\etal found the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes~\cite{haehn_dojo_2014}.
 This subvolume was used for Haehn~\etal~experiment on interactive proofreading tools for connectomics.
-The data, labeled ground truth and findings of their study are published online\footnote{The AC4 subvolume and results of the interactive proofreading experiment are available at http://rhoana.org/dojo/.}.
+We use the data, labeled ground truth and findings of their study which are published online\footnote{The AC4 subvolume and results of the interactive proofreading experiment are available at http://rhoana.org/dojo/.}.
 \\~\\
-\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI) six datasets (each $1250\times1250\times125$ voxels) were made publicly available\footnote{The MICCAI CREMI challenge data is available at http://www.cremi.org.}.
+\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI) six ssTEM datasets (each $1250\times1250\times125$ voxels) were made publicly available\footnote{The MICCAI CREMI challenge data is available at http://www.cremi.org.}.
 Since only three include manually labeled ground truth, we use these three volumes for our experiments.
@@
 The patches are normalized and to further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$.
-The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research as well as a brute force parameter search within a limited range (see supplementary material).
-The final parameters are listed in the first row of table~\ref{tab:parameters}.
+The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research, and a brute force parameter search within a limited range (see supplementary material).
+The first row of table~\ref{tab:parameters} lists the final parameters.
 Our CNN configuration results in approximately 170,000 learnable parameters.
@@
 
-\subsection{Baseline comparison}
+\subsection{Baseline Comparisons}
 
-\textbf{Interactive proofreading.} According to the comparison of Haehn~\etal~, the best performing proofreading tool for novices is Dojo~\cite{haehn_dojo_2014}.
+\textbf{Interactive proofreading.} A comparison of interactive proofreading tools by Haehn~\etal~ concludes that novices perform best when using Dojo~\cite{haehn_dojo_2014}.
 We use the publicly available findings of their user study as a baseline comparison.
@@
 
-\textbf{Computer-aided proofreading.}
+\textbf{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}.
+Focused proofreading performs graph analysis on output from NeuroProof \cite{neuroproof2013}.
+For training, we therefore replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities.
+We obtained the best possible parameters for NeuroProof by consulting the developers and report them in table \ref{tab:parameters}.
 

### 2016-11-14 paper/introduction.tex

@@
 In an automatic setting, errors with a high probability can be automatically corrected first, given an appropriate probability threshold, after which the user would take over.
-Finally, to test the limits of performance, we create an oracle with knowledge of the ground truth, which only accepts corrections when they improve the segmentation.
+Finally, to test the limits of performance, we create an oracle that only accepts corrections improving the segmentation based on knowledge of the ground truth.
 This equals perfect proofreading.
@@
 \item A CNN-based boundary classifier for split errors, plus a merge error classifier which inverts the split error classifier.
-This is used to propose merge error corrections, which removes the need to manually draw the missing edge.
-These classifiers perform well with small amounts of training data, which is expensive to collect for connectomics data.
+This is used to propose merge error corrections, removing the need to manually draw the missing edge.
+These classifiers perform well without much training data, which is expensive to collect for connectomics data.
 \item A guided proofreading approach to correcting segmentation volumes, and an assessment scenario comparing forced-choice interaction with automatic and oracle proofreading.
@@
 Our method applies to all existing automatic segmentation methods which produce a label map.
-As such, we believe that guided proofreading is a promising direction to proofread segmentations more efficiently, and so help better tackle large volumes of connectomics imagery.
+As such, we believe that guided proofreading is a promising direction to proofread segmentations more efficiently to help better tackle large volumes of connectomics imagery.
 

### 2016-11-14 paper/method.tex

@@
 In contrast to Bogovic \etal~\cite{BogovicHJ13}, we work with 2D slices rather than 3D volumes.
-This enables proofreading prior or in parallel to an expensive alignment of individual EM images.
+This enables proofreading prior or in parallel to a computationally expensive alignment of individual EM images.
 \\~\\
@@
 However, in reality the score $p$ is between 0 and 1.
-The classification complexity arises from hundreds of different cell types in connectomics data rather than from the classification decision.
-Intuitively, this yields a wider (meaning more filters) rather than a deeper (meaning more layers) architecture.
+The classification complexity arises from hundreds of different cell types in connectomics data rather than from the classification decision itself.
+Intuitively, this yields a wider architecture with more filters rather than a deeper architecture with more layers.
 We explored different architectural configurations - including residual networks~\cite{resnet} - by performing a brute force parameter search and comparing precision and recall (see supplementary materials).
@@
 This covers approximately $80\%$ of all boundaries in real-world connectomics data with nanometer resolution.
-If the boundary edge is not fully covered, we sample up to 10 non-overlapping patches along the boundary and combine the resulting score by weighted averaging based on boundary length coverage per patch.
+If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary and combine the resulting score by weighted averaging based on boundary length coverage per patch.
 Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data, corresponding boundary probabilities, and a single binary mask combining the two neighboring labels as features for our CNN.
@@
 This can result in merge errors within the automatic segmentation.
-To better direct our classifier to train on the true boundary edge, we extract the border between two segments.
+To better direct our classifier to train on the true boundary, we extract the border between two segments.
 We then dilate this border by 5 pixels to consider slight edge ambiguities and use this binary mask as an additional feature to create a stacked 4-channel input patch.
@@
 \end{center}
-  \vspace{-4mm}
+ % \vspace{-4mm}
    \caption{Example inputs for learning correct splits and split errors as reflected in the segmentation relative to the ground truth.
@@
 For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
-For watershed, we use the inverted gray scale EM image as features.
+For watershed, we use the inverted grayscale EM image as features.
 This yields 50 candidate splits.
 
-Dilation of the segment prior to watershed is motivated by our observation that the generated split likely attaches to the real membrane boundary.
+Dilation of the segment prior to watershed is motivated by our observation that the generated split tends to attach to the real membrane boundary.
 These boundaries are then individually rated using our split error classifier.
@@
 \end{center}
-  \vspace{-4mm}
+%  \vspace{-4mm}
    \caption{Merge errors are identified by generating randomly seeded watershed borders within a dilated label segment.
@@
 \\~\\
-\textbf{Selection oracle.} If ground data is available, the selection oracle \textit{knows} whether a possible correction improves an automatic segmentation.
-This is realized by simply applying the correction and comparing the outcome using a defined measure.
+\textbf{Selection oracle.} If ground truth data is available, the selection oracle \textit{knows} whether a possible correction improves an automatic segmentation.
+This is realized by simply comparing the outcome of a correction using a defined measure.
 The oracle only accepts corrections which improve the automatic segmentation - others get
@@
 Similarly, a correction is accepted for a split error if the ranking $p$ is higher than $p_t$.
-Our experiments have shown that the threshold $p_t$ is the same for merge and split errors which makes sense for a balanced classifier.
+Our experiments have shown that the threshold $p_t$ is the same for merge and split errors which makes sense for a balanced classifier, trained on equal numbers of correct and error patches.
 \\~\\
 \textbf{Forced choice setting.} A user is presented with the choices of either accepting or rejecting a correction.
-This way, all potential split errors are looked at.
+This way, all potential split errors are seen.
 Inspecting all merge errors is not possible for users due to the sheer amount of generated borders.
-We therefor only present merge errors which satisfy $1-p_t$.
+We therefore only present merge errors which satisfy $1-p_t$.
 \\~\\
@@
 If a merge error correction was accepted, the newly found boundary is added to the segmentation data.
-This partially updates the merge error and split error ranking in respect of the new segment.
+This partially updates the merge error and split error ranking with respect to the new segment.
 If a split error correction was accepted, two segments are merged in the segmentation data and the disappearing segment is removed from all error rankings.
@@
 The system is web-based and is designed with a minimalistic user interface showing three components.
-We show the outline of the current labeling of a cell boundary and its proposed correction on top of the EM image data.
+We show the outline of the current labeling of a cell boundary and its proposed correction overlaying the EM image data.
 For the user, it is not possible to distinguish the current labeling and the proposed correction to avoid selection bias.
@@
 A split error (right) and its correction (center) are the possible choices for the user.
-Hovering highlights the current selection with a yellow border and a mouse click confirms it and advances to the next potential error.}
+Hovering highlights the current selection with a yellow border, and a mouse click confirms it by advancing to the next potential error.}
 \label{fig:ui}

### 2016-11-14 mergepatchesCREMItest.py
Add merger for test patches.

@@ -1,0 +1,64 @@
+import numpy as np
+
+#
+#
+#
+
+basedir = '/n/regal/pfister_lab/haehn/CREMITEST/'
+
+testA = basedir + 'testA.npz.npy'
+testA_targets = basedir + 'testA_targets.npz.npy'
+testB = basedir + 'testB.npz.npy'
+testB_targets = basedir + 'testB_targets.npz.npy'
+testC = basedir + 'testC.npz.npy'
+testC_targets = basedir + 'testC_targets.npz.npy'
+
+counter = 0
+
+testA = np.load(testA, mmap_mode='r')
+testA_count = testA.shape[0]
+
+testB = np.load(testB, mmap_mode='r')
+testB_count = testB.shape[0]
+
+testC = np.load(testC, mmap_mode='r')
+testC_count = testC.shape[0]
+
+all_count = testA_count + testB_count + testC_count
+
+#
+# allocate large array
+# 
+PATCH_BYTES = 75*75
+NO_PATCHES = all_count
+P_SIZE = (NO_PATCHES, 4, 75,75) # rather than raveled right now
+
+p_rgba = np.zeros(P_SIZE, dtype=np.float32)
+
+p_rgba[0:testA_count] = testA
+p_rgba[testA_count:testA_count+testB_count] = testB
+p_rgba[testB_count:testB_count+testC_count] = testC
+
+# now store this bad boy
+np.save(basedir+'test.npy', p_rgba)
+
+print 'STORED BIG BOY!'
+p_rgba = None # free them all
+
+#
+# same for targets
+#
+testA_targets = np.load(testA_targets)
+testB_targets = np.load(testB_targets)
+testC_targets = np.load(testC_targets)
+
+p_target = np.zeros(NO_PATCHES)
+
+p_target[0:testA_count] = testA_targets
+p_target[testA_count:testA_count+testC_count] = testB_targets
+p_target[testB_count:testB_count+testC_count] = testC_targets
+
+# now store this lady boy
+np.save(basedir+'test_targets.npy', p_target)
+
+print 'ALL DONE!'

### 2016-11-14 paper/evaluation.tex
Add more stuff.

@@
 
-\textbf{Selection oracle evaluation.}
+\textbf{Selection oracle evaluation.} We use the selection oracle as described in section~\ref{sec:errorcorrection} for the decision whether to accept or reject a correction.
+The purpose of this experiment is to investigate how many corrections are required to reach the best possible outcome.
+This is a direct comparison of the guided proofreading and focused proofreading classifiers but can only be performed if ground truth data is available.
+We perform this experiment on all datasets listed above.
+\\~\\
+\textbf{Automatic method evaluation.} For this experiment we accept all suggested corrections if the rankings are above a configured threshold $p_t=.95$ (Sec.~\ref{sec:errorcorrection}.
+We observed this value as stable in previous experiments with the guided proofreading classifiers (see supplementary material).
+We compare against the focused proofreading classifier and perform this experiment on all reported datasets.
 
-\textbf{Automatic method evaluation.}
-
-\textbf{Forced choice user experiment.}
+\textbf{Forced choice user experiment.} We conduct a quantitative user study to evaluate the forced choice setting as described in section~\ref{sec:errorcorrection}.
+In particular, we evaluate how participants perform while correcting an automatic segmentation using the guided proofreading and focused proofreading tools.
+We designed a between-subjects experiment and asked the participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes.
+Because we wanted to first study how completely inexperienced users perform, we recruited participants with no experience in electron microscopy data or proofreading of such through flyers, mailing lists, and personal interaction.
+Based on sample size calculation theory, we estimated the study sample size as ten users per proofreading tool including four potential dropouts \cite{samplesize1, samplesize2}.
+Nevertheless, all twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30).
+To enable comparison against the interactive proofreading study by~Haehn~\etal~, we use the same dataset and the same time limit.
+Second, we wanted to study expert performance using guided proofreading and focused proofreading.
 

### 2016-11-14 paper/evaluation.tex
First take on evaluation done.

@@
 More specifically, we use the data of the Dojo user with the reported best performance.
-
+\\~\\
 \textbf{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}.
@@
 We obtained the best possible parameters for NeuroProof by consulting the developers and report them in table \ref{tab:parameters}.
+Rather than using Raveler as the frontend, we use our own interface (Figure \ref{fig:ui}).
+This way, the comparison is based on the classifier rather than on user interface.
 
@@
 We compare against the focused proofreading classifier and perform this experiment on all reported datasets.
-
+\\~\\
 \textbf{Forced choice user experiment.} We conduct a quantitative user study to evaluate the forced choice setting as described in section~\ref{sec:errorcorrection}.
 In particular, we evaluate how participants perform while correcting an automatic segmentation using the guided proofreading and focused proofreading tools.
-We designed a between-subjects experiment and asked the participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes.
-Because we wanted to first study how completely inexperienced users perform, we recruited participants with no experience in electron microscopy data or proofreading of such through flyers, mailing lists, and personal interaction.
+We designed a single factor between-subject experiment with the factor \textit{proofreading classifier} and asked participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes.
+To enable comparison against the interactive proofreading study by~Haehn~\etal~, we use the exact same study conditions such as dataset and time limit.
+The experiment was performed on the same machine with standard, off-the-shelf hardware.
+All participants received monetary compensation for their time.
+\begin{itemize}
+\item \textbf{Novice Performance.} First we wanted to study how completely inexperienced users perform.
+We recruited participants with no experience in electron microscopy data or proofreading of such through flyers, mailing lists, and personal interaction.
 Based on sample size calculation theory, we estimated the study sample size as ten users per proofreading tool including four potential dropouts \cite{samplesize1, samplesize2}.
 Nevertheless, all twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30).
-To enable comparison against the interactive proofreading study by~Haehn~\etal~, we use the same dataset and the same time limit.
-Second, we wanted to study expert performance using guided proofreading and focused proofreading.
+Each study session started off with the participants signing the consent form and with a five minute standardized explanation of the task.
+The participants then were asked to do a 3 minute proofreading task on separate but representative data using focused proofreading.
+The participants were allowed to ask questions during this time.
+The classifier did not matter in this case since the user interface was the same.
+The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment.
+After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation \cite{NASATLX}.
+\item \textbf{Expert Performance.} We recruited 4 domain experts to evaluate performance of guided proofreading and focused proofreading.
+We obtained study consent and randomly assigned 2 experts to proofread using each classifier.
+The experts also did the 3 minute test run on different data prior to proofreading for 30 minutes.
+After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire as well.
+\end{itemize}
 
-%\textbf{Training.}
+\textbf{Evaluation metric.} For each experiment, we measure the similarity between proofread segmentations and the manual ground truth labelings using \textit{variation of information} (VI).
+VI is a measure of the distance between two clusterings, closely related to mutual information, but lower being better.
+We calculate VI and treat it as a continuous variable during analysis.
 

### 2016-11-15 patchgenCREMI.py
pg cremi.

@@ -103,12 +103,17 @@ def run(PATCH_PATH, start_slice, end_slice, filename):
     np.save(PATCH_PATH+filename+'_targets.npz', shuffled[1])
     print 'Done!'
 
-
-run('/n/regal/pfister_lab/haehn/CREMITEST/', 0, 17, 'trainA')
-run('/n/regal/pfister_lab/haehn/CREMITEST/', 17, 25, 'testA')
-run('/n/regal/pfister_lab/haehn/CREMITEST/', 25, 25+17, 'trainB')
-run('/n/regal/pfister_lab/haehn/CREMITEST/', 25+17, 50, 'testB')
-run('/n/regal/pfister_lab/haehn/CREMITEST/', 50, 50+17, 'trainC')
-run('/n/regal/pfister_lab/haehn/CREMITEST/', 50+17, 75, 'testC')
+run('/n/regal/pfister_lab/haehn/CREMITEST2/', 0, 50, 'trainA')
+# run('/n/regal/pfister_lab/haehn/CREMITEST2/', 17, 25, 'testA')
+run('/n/regal/pfister_lab/haehn/CREMITEST2/', 100,150, 'trainB')
+# run('/n/regal/pfister_lab/haehn/CREMITEST2/', 25+17, 50, 'testB')
+run('/n/regal/pfister_lab/haehn/CREMITEST2/', 200,250, 'trainC')
+# run('/n/regal/pfister_lab/haehn/CREMITEST2/', 50+17, 75, 'testC')
+# run('/n/regal/pfister_lab/haehn/CREMITEST2/', 0, 17, 'trainA')
+# run('/n/regal/pfister_lab/haehn/CREMITEST2/', 17, 25, 'testA')
+# run('/n/regal/pfister_lab/haehn/CREMITEST2/', 25, 25+17, 'trainB')
+# run('/n/regal/pfister_lab/haehn/CREMITEST2/', 25+17, 50, 'testB')
+# run('/n/regal/pfister_lab/haehn/CREMITEST2/', 50, 50+17, 'trainC')
+# run('/n/regal/pfister_lab/haehn/CREMITEST2/', 50+17, 75, 'testC')
 
 #run('/n/regal/pfister_lab/haehn/FINAL/IPMLB_before_NP', 10, 20, 'train', False)

### 2016-11-15 gp/nets/cnn.py
CREMI.

@@ -24,7 +24,7 @@ class CNN(object):
         kwargs['max_epochs'] = 2000
         kwargs['train_split'] = TrainSplit(eval_size=0.25)
         kwargs['on_epoch_finished'] = [
-                AdjustVariable('update_learning_rate', start=0.03, stop=0.00001),
+                AdjustVariable('update_learning_rate', start=0.003, stop=0.00001),
                 AdjustVariable('update_momentum', start=0.9, stop=0.999),
                 EarlyStopping(patience=50),
             ]

### 2016-11-15 paper/guidedproofreading_review.tex
Edited introduction

@@
 % run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,linkcolor=blue,citecolor=blue,bookmarks=false]{hyperref}
 
@@
 proofreading methods. We also present a fully-automatic mode that uses a
-threshold to make merge/split decisions. Extensive experiments using the
-automatic approach and comparing performance of novice and expert users
+probability threshold to make merge/split decisions. Extensive experiments using
+the automatic approach and comparing performance of novice and expert users
 demonstrate that our method performs favorably agains state-of-the-art

### 2016-11-15 paper/introduction.tex
Edited introduction

@@
 
-In connectomics, neuroscientists annotate neurons and their connectivity within 3D volumes to gain insight into the functional structure of the brain.
-Rapid progress in automatic sample preparation and electron microscopy (EM) acquisition techniques has made it possible to image large volumes of brain tissue at nanometer resolution.
-With a voxel size of $4\times4\times40~\text{nm}^3$, a $1~\text{mm}^3$ volume is 1 petabyte of data.
-With so much data, manual annotation is not feasible, and automatic annotation methods are needed~\cite{jain2010,Liu2014,GALA2014,kaynig2015large}.
+In connectomics, neuroscientists annotate neurons and their connectivity within
+3D volumes to gain insight into the functional structure of the brain. Rapid
+progress in automatic sample preparation and electron microscopy (EM)
+acquisition techniques has made it possible to image large volumes of brain
+tissue at nanometer resolution. With a voxel size of
+$4\times4\times40~\text{nm}^3$, a cubic millimeter volume is one petabyte of
+data. With so much data, manual annotation is not feasible, and automatic
+annotation methods are needed~\cite{jain2010,Liu2014,GALA2014,kaynig2015large}.
 
-Automatic annotation by segmentation and classification of brain tissue is challenging~\cite{isbi_challenge} and all available methods make errors.
-This leads to the results being \emph{proofread} by humans.
-This crucial task serves two purposes: 1) to correct errors in the segmentation, and 2) to increase the body of labeled data from which to train better automatic segmentation methods.
-Recent proofreading tools provide intuitive user interfaces to browse segmentation data in 2D and 3D and to identify and manually correct errors ~\cite{markus_proofreading,raveler,mojo2,haehn_dojo_2014}.
-Many kinds of errors exist, such as inaccurate boundaries, but the most common are \emph{split errors}, where a single segment is labeled as two, and \emph{merge errors}, where two segments are labeled as one (Fig.~\ref{fig:merge_and_slit_errors}).
-With user interaction, split errors can be joined, and the missing boundary in a merge error can be defined with manually-seeded watersheds~\cite{haehn_dojo_2014}.
-However, even with semi-automatic correction tools, the visual inspection to find errors takes the majority of the time~\cite{proofreading_bottleneck}.
+Automatic annotation by segmentation and classification of brain tissue is
+challenging~\cite{isbi_challenge} and all available methods make errors. This
+requires that the results are being \emph{proofread} by humans. This crucial
+task serves two purposes: 1) to correct errors in the segmentation, and 2) to
+increase the body of labeled data from which to train better automatic
+segmentation methods. Recent proofreading tools provide intuitive user
+interfaces to browse segmentation data in 2D and 3D and to identify and manually
+correct errors~\cite{markus_proofreading,raveler,mojo2,haehn_dojo_2014}. Many
+kinds of errors exist, such as inaccurate boundaries, but the most common are
+\emph{split errors}, where a single segment is labeled as two, and \emph{merge
+errors}, where two segments are labeled as one
+(Fig.~\ref{fig:merge_and_slit_errors}). With user interaction, split errors can
+be joined, and the missing boundary in a merge error can be defined with
+manually-seeded watersheds~\cite{haehn_dojo_2014}. However, the visual
+inspection to find errors takes the majority of the time, even with
+semi-automatic correction tools~\cite{proofreading_bottleneck}.
 
@@
 
-Our goal is to automatically detect split and merge errors to reduce visual inspection time.
-Further, we wish to propose corrections to the user to accept or reject, to reduce correction time.
-We name this process \textit{guided proofreading}.
+Our goal is to automatically detect split and merge errors to reduce visual
+inspection time. Further, to reduce correction time we wish to propose
+corrections to the user to accept or reject. We call this process \textit{guided
+proofreading}.
 
-First, we learn a classifier for split errors with a convolutional neural network (CNN).
-This takes as input patches of membrane segmentation probabilities, cell segmentation masks, and boundary masks, and outputs a probabiltiy score.
-As we must process large data, this classifier only operates on cell boundaries, which reduces computation over methods which analyze every pixel.
-For merge errors, we invert and reuse the split classification network, instead asking it to rate a set of generated candidate boundaries which hypothesize a split.
-We compute corrections for both types of errors.
+We learn a classifier for split errors with a convolutional neural network
+(CNN). This takes as input patches of membrane segmentation probabilities, cell
+segmentation masks, and boundary masks, and outputs a probability score. As we
+must process large data, this classifier only operates on cell boundaries, which
+reduces computation over methods that analyze every pixel. For merge errors, we
+invert and reuse the split classification network, instead asking it to rate a
+set of generated candidate boundaries that hypothesize a split. We compute
+corrections for both types of errors.
 
-Second, we propose a greedy algorithm for guided proofreading.
-Possible erroneous regions are sorted by their score, and a correction is generated for each region.
-Then, a user works through this list of regions and corrections.
-In a forced choice setting, the user either selects a correction or skips it to advance to the next region.
-In an automatic setting, errors with a high probability can be automatically corrected first, given an appropriate probability threshold, after which the user would take over.
-Finally, to test the limits of performance, we create an oracle that only accepts corrections improving the segmentation based on knowledge of the ground truth.
-This equals perfect proofreading.
+We also propose a greedy algorithm for guided proofreading. Possible erroneous
+regions are sorted by their score, and a correction is generated for each
+region. Then, a user works through this list of regions and corrections. In a
+forced choice setting, the user either selects a correction or skips it to
+advance to the next region. In an automatic setting, errors with a high
+probability can be automatically corrected first, given an appropriate
+probability threshold, after which the user would take over. Finally, to test
+the limits of performance, we create an oracle that only accepts corrections
+improving the segmentation based on knowledge of the ground truth. This equals
+perfect proofreading.
 
-Third, we evaluate these methods on multiple connectomics datasets.
-For the forced choice setting, we perform a quantitative user study with 20 novice users who have no previous experience of proofreading EM data.
-We ask participants to proofread a small segmentation volume in a fixed time frame.
-In a between-subjects design, we compare guided proofreading to the semi-automatic \textit{focused proofreading} approach by Plaza~\cite{focused_proofreading}.
-In addition, we compare against the manual interactive proofreading tool \textit{Dojo} by Haehn~\etal~\cite{haehn_dojo_2014}.
-We also asked four domain experts to use guided proofreading and focused proofreading for comparison.
+We evaluate these methods on multiple connectomics datasets. For the forced
+choice setting, we perform a quantitative user study with 20 novice users who
+have no previous experience of proofreading EM data. We ask participants to
+proofread a small segmentation volume in a fixed time frame. In a
+between-subjects design, we compare guided proofreading to the semi-automatic
+\textit{focused proofreading} approach by Plaza~\cite{focused_proofreading}. In
+addition, we compare against the manual interactive proofreading tool
+\textit{Dojo} by Haehn~\etal~\cite{haehn_dojo_2014}. We also asked four domain
+experts to use guided proofreading and focused proofreading for comparison.
 
-We state our contributions:
-\begin{itemize}
-\item A CNN-based boundary classifier for split errors, plus a merge error classifier which inverts the split error classifier.
-This is used to propose merge error corrections, removing the need to manually draw the missing edge.
-These classifiers perform well without much training data, which is expensive to collect for connectomics data.
-\item A guided proofreading approach to correcting segmentation volumes, and an assessment scenario comparing forced-choice interaction with automatic and oracle proofreading.
-\item A quantitative user study assessing guided proofreading, which shows that our method is able to reduce segmentation error faster than state-of-the-art semi-automatic tools, across both novice and expert users.
-\end{itemize}
-Our method applies to all existing automatic segmentation methods which produce a label map.
-As such, we believe that guided proofreading is a promising direction to proofread segmentations more efficiently to help better tackle large volumes of connectomics imagery.
+In this paper, we make the following contributions.
+%
+First, we present a CNN-based boundary classifier for split errors, plus a merge
+error classifier that inverts the split error classifier. This is used to
+propose merge error corrections, removing the need to manually draw the missing
+edge. These classifiers perform well without much training data, which is
+expensive to collect for connectomics data.
+%
+Second, we developed a guided proofreading approach to correcting segmentation
+volumes, and an assessment scenario comparing forced-choice interaction with
+automatic and oracle proofreading.
+%
+Furthermore, we present the results of a quantitative user study assessing
+guided proofreading, which shows that our method is able to reduce segmentation
+error faster than state-of-the-art semi-automatic tools for both novice and
+expert users.
+%
+Our method is applicable to all existing automatic segmentation methods that
+produce a label map. As such, we believe that guided proofreading is a promising
+direction to proofread segmentations more efficiently to better tackle large
+volumes of connectomics imagery.
 

### 2016-11-15 paper/evaluation.tex
Edited until result section

@@
 
-We evaluate guided proofreading on multiple different real-world connectomics datasets of different species.
+We evaluate guided proofreading extensively on multiple different real-world connectomics datasets of different species.
 All datasets were acquired using either via serial section electron microscopy (ssEM) or serial section transmission electron microscopy (ssTEM).
@@
 The resolution of our dataset is $3\times3\, \text{nm}^2$ per pixel, and the section thickness is $30\, \text{nm}$.
-The image data and a manually-labeled expert segmentation is publicly available as ground truth for the entire dataset\footnote{The Kasthuri 3-cylinder mouse cortex volume is available at  https://software.rc.fas.harvard.edu/lichtman/vast/.}.
+The image data and a manually-labeled expert segmentation is publicly available as ground truth for the entire dataset\footnote{https://software.rc.fas.harvard.edu/lichtman/vast/}.
 \\~\\
@@
 The resolution of this dataset is $6\times6\times30~\text{nm}^3\text{/voxel}$ and it was acquired using ssEM.
-Haehn~\etal found the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes~\cite{haehn_dojo_2014}.
-This subvolume was used for Haehn~\etal~experiment on interactive proofreading tools for connectomics.
-We use the data, labeled ground truth and findings of their study which are published online\footnote{The AC4 subvolume and results of the interactive proofreading experiment are available at http://rhoana.org/dojo/.}.
+Haehn~\etal~\cite{haehn_dojo_2014} found the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes and used it for their experiments on interactive proofreading tools for connectomics.
+We use their publicly available data, labeled ground truth, and study findings~\footnote{http://rhoana.org/dojo/}.
 \\~\\
-\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI) six ssTEM datasets (each $1250\times1250\times125$ voxels) were made publicly available\footnote{The MICCAI CREMI challenge data is available at http://www.cremi.org.}.
+\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets (each $1250\times1250\times125$ voxels) were made publicly available~\footnote{http://www.cremi.org}.
 Since only three include manually labeled ground truth, we use these three volumes for our experiments.
@@
 For n-fold cross validation, we select one quarter of this data and re-select after each epoch.
-We minimize cross-entropy loss and update using stochastic gradient descent with Nesterov momentum \cite{nesterov}.
+We minimize cross-entropy loss and update using stochastic gradient descent with Nesterov momentum~\cite{nesterov}.
 To generate training data, we identify correct regions and split errors in the automatic segmentation by intersection with ground truth regions.
@@
 From these regions, we sample 112,760 correct and 112,760 split error patches with 4-channels as described above.
-The patches are normalized and to further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$.
+The patches are normalized.
+To further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$.
 The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research, and a brute force parameter search within a limited range (see supplementary material).
@@
 \begin{tabular}{l}
-\textbf{Results} \\ cost [m]: 217 \\ ~ \\ ~ \\ Test. acc.: 0.99 \\ Prec./Recall: ?/? \\ F1 Score: ?
+\textbf{Results} \\ cost [m]: 217 \\ ~ \\ ~ \\ Test. acc.: 0.99 \\ Prec./Recall: \HP{add}?/? \\ F1 Score: \HP{add}?
  \end{tabular}
@@
 \vspace{1mm}
-\caption{Training parameters, cost and results of our guided proofreading classifier versus focused proofreading by Plaza \cite{focused_proofreading}.
-Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 graphics card).}%While the training of our classifier is more expensive, testing accuracy is superior.
+\caption{Training parameters, cost, and results of our guided proofreading classifier versus focused proofreading by Plaza~\cite{focused_proofreading}.
+Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 GPU).\HP{Maybe split this into two tables?}}%While the training of our classifier is more expensive, testing accuracy is superior.
 }
@@
 We use the publicly available findings of their user study as a baseline comparison.
-More specifically, we use the data of the Dojo user with the reported best performance.
+More specifically, we use the data of the Dojo user with the reported best performance as a baseline.
 \\~\\
 \textbf{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}.
-Focused proofreading performs graph analysis on output from NeuroProof \cite{neuroproof2013}.
+Focused proofreading performs graph analysis on output from NeuroProof~\cite{neuroproof2013}.
 For training, we therefore replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities.
-We obtained the best possible parameters for NeuroProof by consulting the developers and report them in table \ref{tab:parameters}.
-Rather than using Raveler as the frontend, we use our own interface (Figure \ref{fig:ui}).
-This way, the comparison is based on the classifier rather than on user interface.
+We obtained the best possible parameters for NeuroProof by consulting the developers and report them in table~\ref{tab:parameters}.
+Rather than using Raveler as the frontend, we use our own interface (Fig.~\ref{fig:ui}).
+This way, the comparison is based on the classifier rather than on the user interface.
 
@@
 
-\textbf{Selection oracle evaluation.} We use the selection oracle as described in section~\ref{sec:errorcorrection} for the decision whether to accept or reject a correction.
+\textbf{Selection oracle evaluation.} We use the selection oracle as described in Sec.~\ref{sec:errorcorrection} for the decision whether to accept or reject a correction.
 The purpose of this experiment is to investigate how many corrections are required to reach the best possible outcome.
@@
 \\~\\
-\textbf{Forced choice user experiment.} We conduct a quantitative user study to evaluate the forced choice setting as described in section~\ref{sec:errorcorrection}.
+\textbf{Forced choice user experiments.} We conducted a quantitative user study to evaluate the forced choice setting as described in Sec.~\ref{sec:errorcorrection}.
 In particular, we evaluate how participants perform while correcting an automatic segmentation using the guided proofreading and focused proofreading tools.
 We designed a single factor between-subject experiment with the factor \textit{proofreading classifier} and asked participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes.
-To enable comparison against the interactive proofreading study by~Haehn~\etal~, we use the exact same study conditions such as dataset and time limit.
-The experiment was performed on the same machine with standard, off-the-shelf hardware.
+To enable comparison against the interactive proofreading study by~Haehn~\etal~\cite{haehn_dojo_2014}, we use the exact same study conditions, dataset, and time limit.
+The experiment was performed on a machine with standard, off-the-shelf hardware.
 All participants received monetary compensation for their time.
-\begin{itemize}
-\item \textbf{Novice Performance.} First we wanted to study how completely inexperienced users perform.
-We recruited participants with no experience in electron microscopy data or proofreading of such through flyers, mailing lists, and personal interaction.
-Based on sample size calculation theory, we estimated the study sample size as ten users per proofreading tool including four potential dropouts \cite{samplesize1, samplesize2}.
+
+\textbf{Novice Study Design.} We recruited participants with no experience in electron microscopy data or proofreading through flyers, mailing lists, and personal interaction.
+Based on sample size calculation theory, we estimated the study sample size as ten users per proofreading tool including four potential dropouts~\cite{samplesize1,samplesize2}.
 Nevertheless, all twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30).
@@
 The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment.
-After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation \cite{NASATLX}.
-\item \textbf{Expert Performance.} We recruited 4 domain experts to evaluate performance of guided proofreading and focused proofreading.
+After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
+
+\textbf{Expert Study Design.} We recruited 4 domain experts to evaluate performance of guided proofreading and focused proofreading.
 We obtained study consent and randomly assigned 2 experts to proofread using each classifier.
@@
 After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire as well.
-\end{itemize}
 

### 2016-11-15 paper/method.tex
Add more stuff.
Edited until result section

@@
 
-We build a split error classifier with output $p$ using a convolutional neural network (CNN) to check whether an edge within an existing automatic segmentation is valid ($p=0$) or not ($p=1$).
-Rather than analyzing every input pixel, the classifier operates only on segment boundaries which requires less pixel context and is faster.
+We build a split error classifier with output $p$ using a CNN to check whether an edge within an existing automatic segmentation is valid ($p=0$) or not ($p=1$).
+Rather than analyzing every input pixel, the classifier operates only on segment boundaries, which requires less pixel context and is faster.
 In contrast to Bogovic \etal~\cite{BogovicHJ13}, we work with 2D slices rather than 3D volumes.
@@
 \\~\\
-\textbf{Convolutional Neural Network Architecture.} Split error detection of a given boundary is really a binary classification task since the boundary is either correct or erroneous.
+\textbf{Convolutional Neural Network Architecture.} Split error detection of a given boundary is a binary classification task since the boundary is either correct or erroneous.
 However, in reality the score $p$ is between 0 and 1.
@@
 Intuitively, this yields a wider architecture with more filters rather than a deeper architecture with more layers.
-We explored different architectural configurations - including residual networks~\cite{resnet} - by performing a brute force parameter search and comparing precision and recall (see supplementary materials).
+We explored different architectural configurations--including residual networks~\cite{resnet}--by performing a brute force parameter search and comparing precision and recall (see supplementary materials).
 Our final CNN configuration for split error detection is composed of four convolutional layers, each followed by max pooling as well as dropout regularization to prevent overfitting due to limited training data.
-Fig.
-\ref{fig:architecture} shows the CNN architecture for split error detection.
+Fig.~\ref{fig:architecture} shows the CNN architecture for split error detection.
 \\~\\
@@
 If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary and combine the resulting score by weighted averaging based on boundary length coverage per patch.
-Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data, corresponding boundary probabilities, and a single binary mask combining the two neighboring labels as features for our CNN.
-However, we observed that the boundary probability information generated from EM images is often misleading due to noise or artifacts in the data.
-This can result in merge errors within the automatic segmentation.
-To better direct our classifier to train on the true boundary, we extract the border between two segments.
-We then dilate this border by 5 pixels to consider slight edge ambiguities and use this binary mask as an additional feature to create a stacked 4-channel input patch.
-Fig.
-\ref{fig:cnn_inputs} shows examples of correct and erroneous feature patches and their corresponding automatic segmentation and ground truth.
+%
+Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data,
+corresponding boundary probabilities, and a single binary mask combining the two
+neighboring labels as features for our CNN. However, we observed that the
+boundary probability information generated from EM images is often misleading
+due to noise or artifacts in the data. This can result in merge errors within
+the automatic segmentation. To better direct our classifier to train on the true
+boundary, we extract the border between two segments. We then dilate this border
+by 5 pixels to consider slight edge ambiguities and use this binary mask as an
+additional feature to create a stacked 4-channel input patch.
+Fig.~\ref{fig:cnn_inputs} shows examples of correct and erroneous feature
+patches and their corresponding automatic segmentation and ground truth.
 
@@
 \subsection{Error Correction}
+\label{sec:errorcorrection}
 
@@
 This is realized by simply comparing the outcome of a correction using a defined measure.
-The oracle only accepts corrections which improve the automatic segmentation - others get
+The oracle only accepts corrections which improve the automatic segmentation---others get
 discarded. This equals perfect proofreading.
@@
 Similarly, a correction is accepted for a split error if the ranking $p$ is higher than $p_t$.
-Our experiments have shown that the threshold $p_t$ is the same for merge and split errors which makes sense for a balanced classifier, trained on equal numbers of correct and error patches.
+Our experiments have shown that the threshold $p_t$ is the same for merge and split errors for a balanced classifier that has been trained on equal numbers of correct and error patches.
 \\~\\
@@
 Inspecting all merge errors is not possible for users due to the sheer amount of generated borders.
-We therefore only present merge errors which satisfy $1-p_t$.
+We therefore only present merge errors that satisfy $1-p_t$.
 \\~\\
@@
 
-Guided proofreading is integrated into an existing workflow for large connectomics data.
-The system is web-based and is designed with a minimalistic user interface showing three components.
+Our guided proofreading is integrated into an existing workflow for large connectomics data.
+The system is web-based and is designed with a user-friendly user interface (Fig.\ref{fig:ui}) showing three components.
 We show the outline of the current labeling of a cell boundary and its proposed correction overlaying the EM image data.
@@
 After interaction, the next potential error is shown.
-Figure \ref{fig:ui} shows the user interface.
 
@@
   \vspace{-4mm}
-   \caption{Segmentation correction with the guided proofreading user interface.
+   \caption{Our guided proofreading user interface for Segmentation correction.
 An image without overlays is shown on the left.

### 2016-11-15 paper/related_work.tex
Edited until result section

@@
 
-\textbf{Automatic Segmentation.} Multi-terabyte EM brain volumes require automatic segmentation~\cite{jain2010,Liu2014,NunezIglesias2013Machine,GALA2014}, but can be hard to classify due to ambiguous intercellular space: the 2013 IEEE ISBI neurites 3D segmentation challenge~\cite{isbi_challenge} showed that existing algorithms which learn from expert-segmented training data still exhibit high error rates.
+\textbf{Automatic Segmentation.} Multi-terabyte EM brain volumes require automatic segmentation~\cite{jain2010,Liu2014,NunezIglesias2013Machine,GALA2014}, but can be hard to classify due to ambiguous intercellular space: the 2013 IEEE ISBI neurites 3D segmentation challenge~\cite{isbi_challenge} showed that existing algorithms that learn from expert-segmented training data still exhibit high error rates.
 
 Many works tackle this problem.
-NeuroProof \cite{neuroproof2013} decreases error rates by learning a agglomeration on over-segmentations of images, based on a random forest classifier.
-Vazquez-Reina \etal~\cite{amelio_segmentation} consider whole EM volumes rather than a per section approach, then solve a fusion problem with a global context.
+NeuroProof~\cite{neuroproof2013} decreases error rates by learning an agglomeration on over-segmentations of images based on a random forest classifier.
+Vazquez-Reina \etal~\cite{amelio_segmentation} consider whole EM volumes rather than a per-section approach, then solve a fusion problem with a global context.
 Kaynig \etal~\cite{kaynig10} propose a random forest classifier coupled with an anisotropic smoothing prior in a conditional random field framework with 3D segment fusion.
@@
 Lee \etal~\cite{lee2015recursive} recursively train very deep networks with 2D and 3D filters to detect boundaries.
-
+%
 All these approaches make good progress; however, in general, proofreading is still required to correct errors.
@@
 Recent papers have attacked the problem of proofreading massive datasets through crowdsourcing with novices~\cite{saalfeld09,anderson2011,Giuly2013DP2}.
-One popular platform is EyeWire, by Kim \etal~\cite{eyewire_nature}, where participants earn virtual rewards for merging oversegmented labeling to reconstruct retina cells.
+One popular platform is EyeWire, by Kim \etal~\cite{eyewire_nature}, where participants earn virtual rewards for merging over-segmented labelings to reconstruct retina cells.
 
-Between expert systems and online games sit Mojo and \textit{Dojo}, by Haehn \etal~\cite{haehn_dojo_2014,Neuroblocks}, which use simple scribble interfaces for error correction.
-Dojo extends this to distributed proofreading via a minimalistic web-based user interface.
-The authors define requirements for general proofreading tools, and then evaluate the accuracy and speed of Raveler, Mojo, and Dojo through a quantitative user study (Sec.
-3 and 4)~\cite{haehn_dojo_2014}.
-Dojo had the highest performance.
-In this paper, we use Dojo as a baseline for interactive proofreading, and so we extend the Haehn \etal experiment.
+Between expert systems and online games sit Mojo and Dojo, by Haehn
+\etal~\cite{haehn_dojo_2014,Neuroblocks}, which use simple scribble interfaces
+for error correction. Dojo extends this to distributed proofreading via a
+minimalistic web-based user interface. The authors define requirements for
+general proofreading tools, and then evaluate the accuracy and speed of Raveler,
+Mojo, and Dojo through a quantitative user study (Sec. 3 and
+4)~\cite{haehn_dojo_2014}. Dojo had the highest performance. In this paper, we
+use Dojo as a baseline for interactive proofreading.
 
-All interactive proofreading solutions require the user to find potential errors manually, which takes the majority of the time~\cite{proofreading_bottleneck,haehn_dojo_2014}.
-Recent works propose computer-aided proofreading systems which help reduce the time spent in this visual search task.
+All interactive proofreading solutions require the user to find potential errors manually, which takes the majority of time~\cite{proofreading_bottleneck,haehn_dojo_2014}.
+Recent papers propose computer-aided proofreading systems which help reduce the time spent in this visual search task.
 \\~\\
-\textbf{Computer-aided Proofreading.} Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}.
+\textbf{Computer-aided Proofreading.} Uzunbas \etal~\cite{uzunbas} showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method.
 The authors track uncertainty throughout the automatic labeling by training a conditional random field.
 This segmentation technique produces uncertainty estimates, which inform potential regions for proofreading to the user.
-While this applies to isotropic volumes, more work is needed to apply it to anisotropic volumes, like most connectomics datasets.
+While this applies to isotropic volumes, more work is needed to apply it to anisotropic volumes that exist for most connectomics datasets.
 
@@
 
-Karimov \etal propose guided volume editing~\cite{karimov_guided_volume_editing}, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation.
+Karimov \etal~\cite{karimov_guided_volume_editing} propose guided volume editing, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation.
 This lets expert users correct labeled computer-tomography datasets, using several interactions per correction.
 To correct merge errors, the authors create a large number of superpixels within a single segment and then successively group them based on dissimilarities.
-We were inspired by this approach but generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.
-\ref{sec:methods}).
+We were inspired by this approach but generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}).
 
-Most closely related to our approach is the work of Plaza, who proposed \textit{focused proofreading}~\cite{focused_proofreading}.
-This method generates affinity scores by analyzing a region adjacency graph across slices, then finds the largest affinities based on a defined impact score.
-This yields edges of potential split errors which can be presented to the proofreader.
-Plaza reports that additional manual work is required to find and correct merge errors.
-Focused proofreading builds upon NeuroProof \cite{neuroproof2013} as its agglomerator, and is open source with integration into Raveler.
-As the closest related work, we wish to use this method as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).
-However, as Haehn \etal showed that Raveler is less performant than Dojo for novice users, we separate the backend affinity score calculation from the expert-level front end, and present our own interface (Sec.~\ref{sec:evaluation}).
+Most closely related to our approach is the work of
+Plaza~\cite{focused_proofreading}, who proposed \textit{focused proofreading}.
+This method generates affinity scores by analyzing a region adjacency graph
+across slices, then finds the largest affinities based on a defined impact
+score. This yields edges of potential split errors which can be presented to the
+proofreader. Plaza reports that additional manual work is required to find and
+correct merge errors. Focused proofreading builds upon
+NeuroProof~\cite{neuroproof2013} as its agglomerator, and is open source with
+integration into Raveler. As the closest related work, we wish to use this
+method as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).
+However, we separate the backend affinity score calculation from the
+expert-level front end, and present our own user-friendly interface
+(Sec.~\ref{sec:evaluation}).

### 2016-11-15 gp/legacy.py
Wrong path.

@@ -983,6 +983,7 @@ class Legacy(object):
               # print 'found', l, n, slice, max_in_slice
           
       if superMax < sureness_threshold:
+        print superMax
         break
 
 

### 2016-11-15 patchgenCREMI.py

@@ -20,7 +20,7 @@ def generate_patches(start_slice, end_slice):
 
         t0 = time.time()
         print 'working on slice', z
-        input_image, input_prob, input_gold, input_rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+        input_image, input_prob, input_gold, input_rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/'), z)
 
 
         error_patches, patches = gp.Patch.patchify_maxoverlap(input_image, input_prob, np.zeros((1,1250,1250),dtype=np.bool), input_rhoana, input_gold, sample_rate=1)

### 2016-11-15 gp/stats.py
Add some test plots.

@@ -21,7 +21,7 @@ from util import Util
 class Stats(object):
 
   @staticmethod
-  def analyze_users(FP_USERS, gold, rhoana, oracle=None, clampX=500, filename=None, DATADIR = '/home/d/GPSTUDY/'):
+  def analyze_users(FP_USERS, gold, rhoana, oracle=None, clampX=500, clampY=False, filename=None, DATADIR = '/home/d/GPSTUDY/', skipoutput=False, data='dojo', hline=-1 ):
 
     def VI(gt, seg):
       # total_vi = 0
@@ -36,6 +36,15 @@ class Stats(object):
     init_mean_vi = VI(gold, rhoana)[0]
     init_median_vi = VI(gold, rhoana)[1]
     init_vi_per_slice = VI(gold, rhoana)[2]
+
+    dojo_best_vi = 0.33414926373414477
+    cylinder_best_vi = 0.27683609273291143
+    if data == 'dojo':
+      best_vi = dojo_best_vi  
+      clampY = [0.32, 0.55]
+    else:
+      best_vi = cylinder_best_vi
+      clampY = [0.25, 0.5]
 
     print 'No. users', len(FP_USERS)
 
@@ -52,9 +61,10 @@ class Stats(object):
     fp_vis =[]
 
     for i,f in enumerate(FP_USERS):
-        with open(DATADIR+FP_USERS[i]+'/'+newrhoana, 'rb') as f:
-            fp_newrhoana = pickle.load(f)
-            fp_outputs.append(fp_newrhoana)
+        if not skipoutput:
+          with open(DATADIR+FP_USERS[i]+'/'+newrhoana, 'rb') as f:
+              fp_newrhoana = pickle.load(f)
+              fp_outputs.append(fp_newrhoana)
         with open(DATADIR+FP_USERS[i]+'/'+times, 'rb') as f:
             fp_time = pickle.load(f)
             fp_time = [int(v) for v in fp_time]
@@ -65,6 +75,8 @@ class Stats(object):
         with open(DATADIR+FP_USERS[i]+'/'+correction_vis, 'rb') as f:
             fp_correction_vis = pickle.load(f) 
             fp_vis.append(fp_correction_vis)
+
+    # return None, None, fp_vis
 
     fp_times_mean = []
     for t in fp_times:
@@ -146,21 +158,26 @@ class Stats(object):
 
     fig = plt.figure(figsize=(10,7))
     # fig, ax = plt.subplots()
-    plt.ylim([0.32, 0.55])
+    if clampY:
[…]

### 2016-11-15 gp/stats.py
Try bigger font.

@@ -174,7 +174,7 @@ class Stats(object):
 
     font = {'family' : 'sans-serif',
             'weight' : 'normal',
-            'size'   : 22}
+            'size'   : 48}
 
     plt.rc('font', **font)
     plt.rc('legend',**{'fontsize':22})

### 2016-11-15 gp/stats.py
ANother gfx.

@@ -174,10 +174,10 @@ class Stats(object):
 
     font = {'family' : 'sans-serif',
             'weight' : 'normal',
-            'size'   : 48}
+            'size'   : 36}
 
     plt.rc('font', **font)
-    plt.rc('legend',**{'fontsize':22})
+    plt.rc('legend',**{'fontsize':26})
 
     for u in fp_vi_per_c_per_user:
         plt.plot(u, linewidth=3)

### 2016-11-15 gp/stats.py
Ready for patch merging.

@@ -170,11 +170,11 @@ class Stats(object):
     plt.xlabel('Correction')
     plt.ylabel('Variation of Information')
     ax = plt.gca()
-    legend = ax.legend(loc='upper left')
+    legend = ax.legend(loc='lower right')
 
     font = {'family' : 'sans-serif',
             'weight' : 'normal',
-            'size'   : 36}
+            'size'   : 40}
 
     plt.rc('font', **font)
     plt.rc('legend',**{'fontsize':26})

### 2016-11-15 mergepatchesCREMI.py

@@ -4,7 +4,7 @@ import numpy as np
 #
 #
 
-basedir = '/n/regal/pfister_lab/haehn/CREMITEST/'
+basedir = '/n/regal/pfister_lab/haehn/CREMITEST2/'
 
 trainA = basedir + 'trainA.npz.npy'
 trainA_targets = basedir + 'trainA_targets.npz.npy'
@@ -15,32 +15,32 @@ trainC_targets = basedir + 'trainC_targets.npz.npy'
 
 counter = 0
 
-# trainA = np.load(trainA, mmap_mode='r')
-# trainA_count = trainA.shape[0]
+trainA = np.load(trainA, mmap_mode='r')
+trainA_count = trainA.shape[0]
 
-# trainB = np.load(trainB, mmap_mode='r')
-# trainB_count = trainB.shape[0]
+trainB = np.load(trainB, mmap_mode='r')
+trainB_count = trainB.shape[0]
 
-# trainC = np.load(trainC, mmap_mode='r')
-# trainC_count = trainC.shape[0]
+trainC = np.load(trainC, mmap_mode='r')
+trainC_count = trainC.shape[0]
 
-# all_count = trainA_count + trainB_count + trainC_count
+all_count = trainA_count + trainB_count + trainC_count
 
-# #
-# # allocate large array
-# # 
-# PATCH_BYTES = 75*75
-# NO_PATCHES = all_count
-# P_SIZE = (NO_PATCHES, 4, 75,75) # rather than raveled right now
+#
+# allocate large array
+# 
+PATCH_BYTES = 75*75
+NO_PATCHES = all_count
+P_SIZE = (NO_PATCHES, 4, 75,75) # rather than raveled right now
 
-# p_rgba = np.zeros(P_SIZE, dtype=np.float32)
+p_rgba = np.zeros(P_SIZE, dtype=np.float32)
 
-# p_rgba[0:trainA_count] = trainA
-# p_rgba[trainA_count:trainA_count+trainB_count] = trainB
-# p_rgba[trainB_count:trainB_count+trainC_count] = trainC
+p_rgba[0:trainA_count] = trainA
+p_rgba[trainA_count:trainA_count+trainB_count] = trainB
+p_rgba[trainB_count:trainB_count+trainC_count] = trainC
 
-# # now store this bad boy
-# np.save(basedir+'train.npy', p_rgba)
+# now store this bad boy
+np.save(basedir+'train.npy', p_rgba)
 
 # print 'STORED BIG BOY!'
 p_rgba = None # free them all

### 2016-11-15 paper/results.tex
Testing plot layouts.

\section{Results and Discussion}

We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.

\subsection{Selection Oracle}

\subsection{Automatic Method}

\subsection{Force Choice User Experiment}

The initial segmentation for AC4 had a VI of XXX.

\textbf{Novice Performance.} 
\\~\\
\textbf{Expert Performance.}
\\~\\
\textbf{Subjective Responses.} All subjective responses were recorded using the NASA-TLX workload index. The workload index asks study participants to state their mental, physical, temporal demands, as well as rate their performance, effort, and frustration on a scale with 21 graduations. Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading. However, these differences were not statistically significant. This is not surprising since the user interface was the same for both control groups.

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
        \caption{A gull}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{gfx/gpusers.pdf}
        \caption{A tiger}
        \label{fig:tiger}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
        \caption{A gull}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
        \caption{A tiger}
        \label{fig:tiger}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
%    \begin{subfigure}[b]{0.15\textwidth}
%        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
%        \caption{A mouse}
%        \label{fig:mouse}
%    \end{subfigure}
    \caption{Pictures of animals}\label{fig:animals}
\end{figure*}
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.48\linewidth}
        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
        \caption{A gull}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.49\linewidth}
        \includegraphics[width=\textwidth]{gfx/gpusers.pdf}
        \caption{A tiger}
        \label{fig:tiger}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
%    \begin{subfigure}[b]{0.15\textwidth}
%        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
%        \caption{A mouse}
%        \label{fig:mouse}
%    \end{subfigure}
    \caption{Pictures of animals}\label{fig:animals}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.49\linewidth}
        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
        \caption{A gull}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)

    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.49\linewidth}
        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
        \caption{A mouse}
        \label{fig:mouse}
    \end{subfigure}
    \caption{Pictures of animals}\label{fig:animals}
\end{figure}

### 2016-11-15 paper/introduction.tex
Review changes; minor issues.

@@
 Automatic annotation by segmentation and classification of brain tissue is
-challenging~\cite{isbi_challenge} and all available methods make errors. This
-requires that the results are being \emph{proofread} by humans. This crucial
+challenging~\cite{isbi_challenge} and all available methods make errors, so 
+the results must be \emph{proofread} by humans. This crucial
 task serves two purposes: 1) to correct errors in the segmentation, and 2) to
@@
 Our goal is to automatically detect split and merge errors to reduce visual
-inspection time. Further, to reduce correction time we wish to propose
+inspection time. Further, to reduce correction time, we propose
 corrections to the user to accept or reject. We call this process \textit{guided
@@
 invert and reuse the split classification network, instead asking it to rate a
-set of generated candidate boundaries that hypothesize a split. We compute
-corrections for both types of errors.
+set of generated candidate boundaries that hypothesize a split. %We compute
+%corrections for both types of errors.
 
 We also propose a greedy algorithm for guided proofreading. Possible erroneous
-regions are sorted by their score, and a correction is generated for each
+regions are sorted by their score, and a candidate correction is generated for each
 region. Then, a user works through this list of regions and corrections. In a
@@
 advance to the next region. In an automatic setting, errors with a high
-probability can be automatically corrected first, given an appropriate
+probability are automatically corrected first, given an appropriate
 probability threshold, after which the user would take over. Finally, to test
-the limits of performance, we create an oracle that only accepts corrections
-improving the segmentation based on knowledge of the ground truth. This equals
-perfect proofreading.
+the limits of performance, we create an oracle which only accepts corrections
+that improve the segmentation, based on knowledge of the ground truth. This is
+guided proofreading with a perfect user.
 
@@
 
-In this paper, we make the following contributions.
+This paper makes the following contributions.
 %
@@
 %
-Furthermore, we present the results of a quantitative user study assessing
-guided proofreading, which shows that our method is able to reduce segmentation
+Third, we present the results of a quantitative user study assessing
+guided proofreading. Our method is able to reduce segmentation
 error faster than state-of-the-art semi-automatic tools for both novice and
 expert users.
-%
-Our method is applicable to all existing automatic segmentation methods that
-produce a label map. As such, we believe that guided proofreading is a promising
-direction to proofread segmentations more efficiently to better tackle large
+
+Guided proofreading is applicable to all existing automatic segmentation methods that
+produce a label map. As such, we believe that our approach is a promising
+direction to proofread segmentations more efficiently and better tackle large
 volumes of connectomics imagery.

### 2016-11-15 paper/related_work.tex
Review changes; minor issues.

@@
 Raveler is used today by professional proofreaders, and it offers many parameters for tweaking the process.
-Similar systems exist as products or plugins to visualization systems,~\eg V3D~\cite{proofreading_bottleneck} or AVIZO~\cite{markus_proofreading}.
+Similar systems exist as products or plugins to visualization systems,~\eg, V3D~\cite{proofreading_bottleneck} and AVIZO~\cite{markus_proofreading}.
 
@@
 general proofreading tools, and then evaluate the accuracy and speed of Raveler,
-Mojo, and Dojo through a quantitative user study (Sec. 3 and
-4)~\cite{haehn_dojo_2014}. Dojo had the highest performance. In this paper, we
+Mojo, and Dojo through a quantitative user study (Sec.~3 and
+4, ~\cite{haehn_dojo_2014}). Dojo had the highest performance. In this paper, we
 use Dojo as a baseline for interactive proofreading.
 
-All interactive proofreading solutions require the user to find potential errors manually, which takes the majority of time~\cite{proofreading_bottleneck,haehn_dojo_2014}.
-Recent papers propose computer-aided proofreading systems which help reduce the time spent in this visual search task.
+All interactive proofreading solutions require the user to find potential errors manually, which takes the majority of the time~\cite{proofreading_bottleneck,haehn_dojo_2014}.
+Recent papers propose computer-aided proofreading systems to reduce the time spent in this visual search task.
 \\~\\
@@
 This segmentation technique produces uncertainty estimates, which inform potential regions for proofreading to the user.
-While this applies to isotropic volumes, more work is needed to apply it to anisotropic volumes that exist for most connectomics datasets.
+While this applies to isotropic volumes, more work is needed to apply it to the typically anisotropic connectromics dataset volumes.
 
@@
 To correct merge errors, the authors create a large number of superpixels within a single segment and then successively group them based on dissimilarities.
-We were inspired by this approach but generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}).
+We were inspired by this approach, but instead we generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}).
 
@@
 method as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).
-However, we separate the backend affinity score calculation from the
-expert-level front end, and present our own user-friendly interface
+However, we separate the backend affinity score calculation from the Raveler
+expert-level front end, and present our own novice-friendly interface
 (Sec.~\ref{sec:evaluation}).

### 2016-11-15 paper/method.tex
Section 3 review.

@@
 In contrast to Bogovic \etal~\cite{BogovicHJ13}, we work with 2D slices rather than 3D volumes.
-This enables proofreading prior or in parallel to a computationally expensive alignment of individual EM images.
+This enables proofreading prior or in parallel to a computationally expensive stitching and 3D alignment of individual EM images.
 \\~\\
 \textbf{Convolutional Neural Network Architecture.} Split error detection of a given boundary is a binary classification task since the boundary is either correct or erroneous.
-However, in reality the score $p$ is between 0 and 1.
+However, in reality, the score $p$ is between 0 and 1.
 The classification complexity arises from hundreds of different cell types in connectomics data rather than from the classification decision itself.
 Intuitively, this yields a wider architecture with more filters rather than a deeper architecture with more layers.
-We explored different architectural configurations--including residual networks~\cite{resnet}--by performing a brute force parameter search and comparing precision and recall (see supplementary materials).
-Our final CNN configuration for split error detection is composed of four convolutional layers, each followed by max pooling as well as dropout regularization to prevent overfitting due to limited training data.
-Fig.~\ref{fig:architecture} shows the CNN architecture for split error detection.
+We explored different architectural configurations---including residual networks~\cite{resnet}---by performing a brute force parameter search and comparing precision and recall (see supplementary materials).
+Our final CNN configuration for split error detection is composed of four convolutional layers, each followed by max pooling as well as dropout regularization to prevent overfitting due to limited training data (Fig.~\ref{fig:architecture}).
 \\~\\
-\textbf{Classifier Inputs.} To train the CNN for split error detection, we take boundary context information into consideration for the decision making process.
-For this, we use a $75\times75$ pixel patch at the center of an existing boundary.
-This covers approximately $80\%$ of all boundaries in real-world connectomics data with nanometer resolution.
-If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary and combine the resulting score by weighted averaging based on boundary length coverage per patch.
-%
+\textbf{Classifier Inputs.} To train the CNN, we consider boundary context in the decision making process by using a $75\times75$ pixel patch at the center of an existing boundary.
+This size covers approximately $80\%$ of all boundaries in the 6~nm Mouse S1 AC3 Open Connectome Project dataset.
+If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary, and combine the resulting score by averaging weighted by the boundary length coverage per patch.
+
 Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data,
 corresponding boundary probabilities, and a single binary mask combining the two
-neighboring labels as features for our CNN. However, we observed that the
+neighboring labels as inputs to our CNN. However, we observed that the
 boundary probability information generated from EM images is often misleading
@@
 the automatic segmentation. To better direct our classifier to train on the true
-boundary, we extract the border between two segments. We then dilate this border
+boundary, we extract the border between two segments. Then, we dilate this border
 by 5 pixels to consider slight edge ambiguities and use this binary mask as an
-additional feature to create a stacked 4-channel input patch.
-Fig.~\ref{fig:cnn_inputs} shows examples of correct and erroneous feature
+additional input. This creates a stacked 4-channel input patch.
+Fig.~\ref{fig:cnn_inputs} shows examples of correct and erroneous input
 patches and their corresponding automatic segmentation and ground truth.
 
-\begin{figure}[h]
+\begin{figure}[t]
 \begin{center}
@@
  % \vspace{-4mm}
-   \caption{Example inputs for learning correct splits and split errors as reflected in the segmentation relative to the ground truth.
-Image, membrane probabilities, merged binary labels, and a dilated border mask are combined to 4-channel input patches.}
+   \caption{Example inputs for learning correct splits and split errors, as per a candidate segmentation versus the ground truth.
+Image, membrane probabilities, merged binary labels, and a dilated border mask provide 4-channel input patches.}
 \label{fig:cnn_inputs}
@@
 However, we can reuse the same trained CNN for this task.
-Similar to guided volume editing by Karimov~\etal~\cite{karimov_guided_volume_editing} we generate potential borders within a segment.
+Similar to guided volume editing by Karimov~\etal~\cite{karimov_guided_volume_editing}, we generate potential borders within a segment.
 For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
-For watershed, we use the inverted grayscale EM image as features.
+We perform watershed on the inverted grayscale EM image.
 This yields 50 candidate splits.
 
-Dilation of the segment prior to watershed is motivated by our observation that the generated split tends to attach to the real membrane boundary.
+Dilation of the segment prior to watershed is motivated by our observation that the generated splits tend to attach to real membrane boundaries.
 These boundaries are then individually rated using our split error classifier.
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \begin{center}
@@
 %  \vspace{-4mm}
-   \caption{Merge errors are identified by generating randomly seeded watershed borders within a dilated label segment.
-These borders then are individually rated using the split error CNN by inverting the probability score.
-This way, a confident rating for a correct split most likely indicates the missing border of the merge error and can be used for correcting the labeling.}
+   \caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment.
+Then, each border is individually rated using the split error CNN by inverting the probability score.
+A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.\JT{Candidate to improve.}}
 \label{fig:merge_error}
@@
 After that, we perform split error detection and store the ranking $p$ for all neighboring segments in the segmentation.
-We then sort the merge and split error rankings individually from highest to lowest.
-For error correction, we first loop through the potential merge error regions and then through the potential split error regions.
+Then, we sort the merge and split error rankings separately from highest to lowest.
+For error correction, first we loop through the potential merge error regions and then through the potential split error regions.
 During this process, each error is now subject to a yes/no decision which can be provided in different ways:
-\\~\\
-\textbf{Selection oracle.} If ground truth data is available, the selection oracle \textit{knows} whether a possible correction improves an automatic segmentation.
+
+\paragraph{Selection oracle.} If ground truth data is available, the selection oracle \textit{knows} whether a possible correction improves an automatic segmentation.
 This is realized by simply comparing the outcome of a correction using a defined measure.
 The oracle only accepts corrections which improve the automatic segmentation---others get
-discarded. This equals perfect proofreading.
-\\~\\
-\textbf{Automatic selection with threshold.} The decision whether to accept or reject a potential correction is done by comparing rankings to a threshold $p_t$.
+discarded. This is guided proofreading with a perfect user, and allows us to assess the upper limit of performance.
+
+\paragraph{Automatic selection with threshold.} The decision whether to accept or reject a potential correction is taken by comparing rankings to a threshold $p_t$.
 If the inverted score $1-p$ of a merge error is higher than a threshold $1-p_t$, the correction is accepted.
@@
 Our experiments have shown that the threshold $p_t$ is the same for merge and split errors for a balanced classifier that has been trained on equal numbers of correct and error patches.
-\\~\\
-\textbf{Forced choice setting.} A user is presented with the choices of either accepting or rejecting a correction.
-This way, all potential split errors are seen.
+
+\paragraph{Forced choice setting.} We present a user with the choice to accept or reject a correction.
+All potential split errors are seen.
 Inspecting all merge errors is not possible for users due to the sheer amount of generated borders.
-We therefore only present merge errors that satisfy $1-p_t$.
-\\~\\
-In all cases, a decision has to be made to advance to the next possible erroneous region.
+Therefore, we only present merge errors that satisfy $1-p_t$.
+
+\noindent \newline In all cases, a decision has to be made to advance to the next possible erroneous region.
 If a merge error correction was accepted, the newly found boundary is added to the segmentation data.
@@
 If a split error correction was accepted, two segments are merged in the segmentation data and the disappearing segment is removed from all error rankings.
-We then perform merge error detection on the now larger segment and update the ranking.
-We also update the split error rankings to include all new neighbors and re-sort.
-The error with the next highest ranking is now subject to the yes/no decision.
+Then, we perform merge error detection on the now larger segment and update the ranking.
+We also update the split error rankings to include all new neighbors, and re-sort.
+The error with the next highest ranking then forces a choice.
 
@@
 Our guided proofreading is integrated into an existing workflow for large connectomics data.
-The system is web-based and is designed with a user-friendly user interface (Fig.\ref{fig:ui}) showing three components.
+The system is web-based and is designed with a novice-friendly user interface (Fig.~\ref{fig:ui}).
 We show the outline of the current labeling of a cell boundary and its proposed correction overlaying the EM image data.
@@
 
-\begin{figure}[h]
-\begin{center}
+\begin{figure}[t]
 \includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
-\end{center}
-  \vspace{-4mm}
-   \caption{Our guided proofreading user interface for Segmentation correction.
-An image without overlays is shown on the left.
-A split error (right) and its correction (center) are the possible choices for the user.
-Hovering highlights the current selection with a yellow border, and a mouse click confirms it by advancing to the next potential error.}
+\caption{Our guided proofreading user interface.
+A candidate error region is shown on the left.
+The user must choose between the region being a split error which needs correcting (center) or not (right).
+Hovering highlights the current selection with a yellow border, and a mouse click confirms the choice and advances to the next potential error.\JT{Needs labels on the images; also, removal of black background.}}
 \label{fig:ui}

### 2016-11-15 paper/related_work.tex
Section 3 review.

@@
   \vspace{-4mm}
-   \caption{We build the guided proofreading classifiers using a traditional CNN architecture.
-The network is based on four convolutional layers, each followed by max pooling as well as dropout regularization.
-The 4-channel input patches are rated as either correct splits or as split errors.}
+   \caption{Our guided proofreading classifiers use a traditional CNN architecture of four convolutional layers, each followed by max pooling and dropout regularization.
+The 4-channel input patches are labelled either as correct splits or as split errors.}
 \label{fig:architecture}

### 2016-11-15 paper/evaluation.tex
Section 4 review.

@@
 
-We evaluate guided proofreading extensively on multiple different real-world connectomics datasets of different species.
-All datasets were acquired using either via serial section electron microscopy (ssEM) or serial section transmission electron microscopy (ssTEM).
-We perform experiments for error correction based on a selection oracle, automatic selection with threshold, and the forced choice setting.
-The latter is designed as a between-subjects user study with novice and expert participants.
+We evaluate guided proofreading on multiple different real-world connectomics datasets of different species.
+All datasets were acquired using either serial section electron microscopy (ssEM) or serial section transmission electron microscopy (ssTEM).
+We perform experiments with the selection oracle, with automatic selection with threshold, and in the forced choice setting via a between-subjects user study with both novice and expert participants.
 
@@
 
-\textbf{L.
+\paragraph{L.
 Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels).
-The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse and was acquired using ssEM.
-The resolution of our dataset is $3\times3\, \text{nm}^2$ per pixel, and the section thickness is $30\, \text{nm}$.
-The image data and a manually-labeled expert segmentation is publicly available as ground truth for the entire dataset\footnote{https://software.rc.fas.harvard.edu/lichtman/vast/}.
-\\~\\
-\textbf{AC4 subvolume.} This dataset is part of a publicly available dataset of mouse cortex that was published for the ISBI 2013 challenge "SNEMI3D: 3D Segmentation of neurites in EM images".
-The resolution of this dataset is $6\times6\times30~\text{nm}^3\text{/voxel}$ and it was acquired using ssEM.
-Haehn~\etal~\cite{haehn_dojo_2014} found the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes and used it for their experiments on interactive proofreading tools for connectomics.
-We use their publicly available data, labeled ground truth, and study findings~\footnote{http://rhoana.org/dojo/}.
-\\~\\
-\textbf{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets (each $1250\times1250\times125$ voxels) were made publicly available~\footnote{http://www.cremi.org}.
-Since only three include manually labeled ground truth, we use these three volumes for our experiments.
-The volumes are part of adult fruit fly (Drosophila melanogaster) brain.
+The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse, and was acquired using ssEM.
+The dataset resolution is $3\times3\, \text{nm}^2$ per pixel, with section thickness of $30\, \text{nm}$.
+Image data and a manually-labeled expert `ground truth' segmentation is available publicly for the entire dataset\footnote{\scriptsize{\url{https://software.rc.fas.harvard.edu/lichtman/vast/}}}.
+
+\paragraph{AC4 subvolume.} This is part of a publicly-available dataset of mouse cortex that was published for the ISBI 2013 challenge ``SNEMI3D: 3D Segmentation of neurites in EM images''.
+The dataset resolution is $6\times6\times30~\text{nm}^3\text{/voxel}$ and it was acquired using ssEM.
+Haehn~\etal~\cite{haehn_dojo_2014} found the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes, and used it for their interactive connectomics proofreading tool experiments.
+We use their publicly available data, labeled ground truth, and study findings\footnote{\scriptsize{\url{http://rhoana.org/dojo/}}}.
+
+\paragraph{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets were made publicly available\footnote{\scriptsize{\url{http://www.cremi.org}}},  each $1250\times1250\times125$ voxels.
+Since only three datasets include manually-labeled `ground truth', we use these three volumes for our experiments.
+The volumes are part of an adult fruit fly (Drosophila melanogaster) brain.
 The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$.
-\\~\\
-\textbf{Automatic segmentation pipeline.}
+
+\paragraph{Automatic segmentation pipeline.}
 We use a state-of-the-art method to create a dense automatic segmentation of the data.
-Membrane probabilities are generated using a convolutional neural network based on the U-net architecture~\cite{RonnebergerFB15}.
+Membrane probabilities are generated using a CNN based on the U-net architecture~\cite{RonnebergerFB15}.
 The probabilities are used to seed watershed and generate an oversegmentation using superpixels.
@@
 
-To train our split error classifier, we use the L.
+We train our split error classifier on the L.
 Cylinder dataset.
@@
 To generate training data, we identify correct regions and split errors in the automatic segmentation by intersection with ground truth regions.
-This is required since extracellular space is not labeled in the ground truth but in our dense automatic segmentation.
-From these regions, we sample 112,760 correct and 112,760 split error patches with 4-channels as described above.
+This is required since extracellular space is not labeled in the ground truth, but is in our dense automatic segmentation.
+From these regions, we sample 112,760 correct and 112,760 split error patches with 4-channels (Sec.~\ref{sec:spliterrordetection}).
 The patches are normalized.
-To further augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen $k$.
-The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research, and a brute force parameter search within a limited range (see supplementary material).
-The first row of table~\ref{tab:parameters} lists the final parameters.
+To augment our training data, we rotate patches within each mini-batch by $k*90$ degrees with randomly chosen integer $k$.
+The training parameters such as filter size, number of filters, learning rate, and momentum are the result of intuition and experience, studying recent machine learning research, and a limited brute force parameter search (see supplementary material).
+
+Table~\ref{tab:parameters} lists the final parameters.
 Our CNN configuration results in approximately 170,000 learnable parameters.
 We assume that training has converged if the validation loss does not decrease for 50 epochs.
-We test the CNN by generating a balanced set of 8,780 correct and 8,780 error patches using unseen data of the left cylinder dataset and report testing results in the second row of table~\ref{tab:parameters}.
+We test the CNN by generating a balanced set of 8,780 correct and 8,780 error patches using unseen data of the left cylinder dataset.
 
-\begin{table}[h]
-%\resizebox{\textwidth}{!}{%
-\small
-\begin{tabular}{l|l}
+\begin{table}[t]
+\caption{Training parameters, cost, and results of our guided proofreading classifier versus focused proofreading by Plaza~\cite{focused_proofreading}.
+Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 GPU).}%While the training of our classifier is more expensive, testing accuracy is superior.
+}
+
+\small{
+\begin{tabular}{ll}
+	\toprule
 	\begin{tabular}{l}
-\textbf{Guided Proofreading}\\~\\
-\textbf{Parameters} \\
-Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2-4: 48 \\ Dense units: 512 \\ Learning rate: 0.03-0.00001\\ Momentum: 0.9-0.999\\Mini-Batchsize: 128\\~\\
+		\textbf{Guided Proofreading} \\ \midrule
+		\emph{Parameters} \\ \midrule
+		Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2--4: 48 \\ Dense units: 512 \\ Learning rate: 0.03--0.00001\\ Momentum: 0.9--0.999\\Mini-Batchsize: 128 \\
 	\end{tabular}
@@
 	\begin{tabular}{l}
-\textbf{Focused Proofreading}\\~\\
-\textbf{Parameters} \\
+		\vspace{0.2mm} \\
+		\midrule
+		\emph{Results---Test Set} \\ \midrule Cost [m]: 383 \\ Val. loss: 0.0845 \\ Val. acc.: 0.969 \\ Test. acc.: 0.94 \\ Prec./Recall: 0.94/0.94 \\ F1 Score: 0.94 \\ ~ \\
+	\end{tabular}
+\end{tabular}
+
+\vspace{0.5mm}
+\begin{tabular}{ll}
+	\toprule
+	\begin{tabular}{l}
+		\textbf{Focused Proofreading}\\ \midrule
+		\emph{Parameters} \\ \midrule
 		Iterations: 3 \\
 		Learning strategy: 2\\
-Mito agglomeration: Off\\
+		Mito agglomeration: Off~~~~~~ \\  % Crappy alignment spacing
 		Threshold: 0.0\\
-~\\
-~\\
-~\\
-~\\
- \end{tabular}
- \\
- \hline
- \\
- \begin{tabular}{l}
-\textbf{Results} \\ cost [m]: 383 \\ Val. loss: 0.0845 \\ Val. acc.: 0.969 \\ Test. acc.: 0.94 \\ Prec./Recall: 0.94/0.94 \\ F1 Score: 0.94
 	\end{tabular}
@@
 	\begin{tabular}{l}
-\textbf{Results} \\ cost [m]: 217 \\ ~ \\ ~ \\ Test. acc.: 0.99 \\ Prec./Recall: \HP{add}?/? \\ F1 Score: \HP{add}?
+		\vspace{0.2mm} \\
+		\midrule
+		\emph{Results---Test Set} \\ \midrule cost [m]: 217 \\ Test. acc.: 0.99 \\ Prec./Recall: \HP{add}?/? \\ F1 Score: \HP{add}? \\
 	\end{tabular}
+%	\bottomrule
 \end{tabular}
-\vspace{1mm}
-\caption{Training parameters, cost, and results of our guided proofreading classifier versus focused proofreading by Plaza~\cite{focused_proofreading}.
-Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 GPU).\HP{Maybe split this into two tables?}}%While the training of our classifier is more expensive, testing accuracy is superior.
+\hrule
 }
@@
 
-\textbf{Interactive proofreading.} A comparison of interactive proofreading tools by Haehn~\etal~ concludes that novices perform best when using Dojo~\cite{haehn_dojo_2014}.
+\paragraph{Interactive proofreading.} Haehn~\etal's comparison of interactive proofreading tools concludes that novices perform best when using Dojo~\cite{haehn_dojo_2014}.
 We use the publicly available findings of their user study as a baseline comparison.
-More specifically, we use the data of the Dojo user with the reported best performance as a baseline.
-\\~\\
-\textbf{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}.
-Focused proofreading performs graph analysis on output from NeuroProof~\cite{neuroproof2013}.
-For training, we therefore replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities.
-We obtained the best possible parameters for NeuroProof by consulting the developers and report them in table~\ref{tab:parameters}.
-Rather than using Raveler as the frontend, we use our own interface (Fig.~\ref{fig:ui}).
-This way, the comparison is based on the classifier rather than on the user interface.
+We use the data of all Dojo users in aggregate as a baseline.
+
+\paragraph{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}.
+Focused proofreading performs graph analysis on the output from NeuroProof~\cite{neuroproof2013}, instead of our GALA approach.
+Therefore, for training our focused proofreading baseline, we replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities.
+We obtained the best possible parameters for NeuroProof by consulting the developers (Table~\ref{tab:parameters}).
+Rather than using Raveler as the frontend, we use our own interface (Fig.~\ref{fig:ui}) to compare only the classifier part of Plaza's approach.
 
@@
 
-\textbf{Selection oracle evaluation.} We use the selection oracle as described in Sec.~\ref{sec:errorcorrection} for the decision whether to accept or reject a correction.
+\paragraph{Selection oracle evaluation.} We use the selection oracle as described in Sec.~\ref{sec:errorcorrection} for the decision whether to accept or reject a correction.
 The purpose of this experiment is to investigate how many corrections are required to reach the best possible outcome.
@@
 We perform this experiment on all datasets listed above.
-\\~\\
-\textbf{Automatic method evaluation.} For this experiment we accept all suggested corrections if the rankings are above a configured threshold $p_t=.95$ (Sec.~\ref{sec:errorcorrection}.
+
+\paragraph{Automatic method evaluation.} For this experiment, we accept all suggested corrections if the rankings are above a configured threshold $p_t=.95$ (Sec.~\ref{sec:errorcorrection}).
 We observed this value as stable in previous experiments with the guided proofreading classifiers (see supplementary material).
 We compare against the focused proofreading classifier and perform this experiment on all reported datasets.
-\\~\\
-\textbf{Forced choice user experiments.} We conducted a quantitative user study to evaluate the forced choice setting as described in Sec.~\ref{sec:errorcorrection}.
-In particular, we evaluate how participants perform while correcting an automatic segmentation using the guided proofreading and focused proofreading tools.
-We designed a single factor between-subject experiment with the factor \textit{proofreading classifier} and asked participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes.
+
+\paragraph{Forced choice user experiments.} We conducted a quantitative user study to evaluate the forced choice setting (Sec.~\ref{sec:errorcorrection}).
+In particular, we evaluated how participants perform while correcting an automatic segmentation using the guided proofreading and focused proofreading tools.
+We designed a single factor between-subject experiment with the factor \textit{proofreading classifier}, and asked participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes.
 To enable comparison against the interactive proofreading study by~Haehn~\etal~\cite{haehn_dojo_2014}, we use the exact same study conditions, dataset, and time limit.
-The experiment was performed on a machine with standard, off-the-shelf hardware.
-All participants received monetary compensation for their time.
+The experiment was performed on a machine with standard off-the-shelf hardware.
+All participants received monetary compensation.
 
-\textbf{Novice Study Design.} We recruited participants with no experience in electron microscopy data or proofreading through flyers, mailing lists, and personal interaction.
-Based on sample size calculation theory, we estimated the study sample size as ten users per proofreading tool including four potential dropouts~\cite{samplesize1,samplesize2}.
-Nevertheless, all twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30).
-Each study session started off with the participants signing the consent form and with a five minute standardized explanation of the task.
-The participants then were asked to do a 3 minute proofreading task on separate but representative data using focused proofreading.
+\paragraph{Novice Study Design.} We recruited participants with no experience in electron microscopy data or proofreading, through flyers, mailing lists, and personal interaction.
+Based on sample size calculation theory, we estimated the study needed ten users per proofreading tool including four potential dropouts~\cite{samplesize1,samplesize2}.
+All twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30).
+
+Each study session began with a five minute standardized explanation of the task.
+Then, the participants were asked to perform a 3 minute proofreading task on separate but representative data using focused proofreading.
 The participants were allowed to ask questions during this time.
@@
 
-\textbf{Expert Study Design.} We recruited 4 domain experts to evaluate performance of guided proofreading and focused proofreading.
+\paragraph{Expert Study Design.} We recruited 4 domain experts to evaluate the performance of both guided and focused proofreading.
 We obtained study consent and randomly assigned 2 experts to proofread using each classifier.
-The experts also did the 3 minute test run on different data prior to proofreading for 30 minutes.
-After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire as well.
+The experts performed the 3 minute test run on different data prior to proofreading for 30 minutes.
+After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire.
 
-\textbf{Evaluation metric.} For each experiment, we measure the similarity between proofread segmentations and the manual ground truth labelings using \textit{variation of information} (VI).
-VI is a measure of the distance between two clusterings, closely related to mutual information, but lower being better.
-We calculate VI and treat it as a continuous variable during analysis.
+\paragraph{Evaluation metric.} For each experiment, we measure the similarity between proofread segmentations and the manual `ground truth' labelings using \textit{variation of information} (VI).
+VI is a measure of the distance between two clusterings, closely related to mutual information, where lower means better.
+We treat VI as a continuous variable during analysis.
 

### 2016-11-15 paper/method.tex
Section 4 review.

@@
 \subsection{Split Error Detection}
+\label{sec:spliterrordetection}
 
@@
 This enables proofreading prior or in parallel to a computationally expensive stitching and 3D alignment of individual EM images.
-\\~\\
-\textbf{Convolutional Neural Network Architecture.} Split error detection of a given boundary is a binary classification task since the boundary is either correct or erroneous.
+
+\paragraph{Convolutional Neural Network Architecture.} Split error detection of a given boundary is a binary classification task since the boundary is either correct or erroneous.
 However, in reality, the score $p$ is between 0 and 1.
@@
 Our final CNN configuration for split error detection is composed of four convolutional layers, each followed by max pooling as well as dropout regularization to prevent overfitting due to limited training data (Fig.~\ref{fig:architecture}).
-\\~\\
-\textbf{Classifier Inputs.} To train the CNN, we consider boundary context in the decision making process by using a $75\times75$ pixel patch at the center of an existing boundary.
+
+\paragraph{Classifier Inputs.} To train the CNN, we consider boundary context in the decision making process by using a $75\times75$ pixel patch at the center of an existing boundary.
 This size covers approximately $80\%$ of all boundaries in the 6~nm Mouse S1 AC3 Open Connectome Project dataset.
@@
 
-Our guided proofreading is integrated into an existing workflow for large connectomics data.
-The system is web-based and is designed with a novice-friendly user interface (Fig.~\ref{fig:ui}).
-We show the outline of the current labeling of a cell boundary and its proposed correction overlaying the EM image data.
-For the user, it is not possible to distinguish the current labeling and the proposed correction to avoid selection bias.
+We integrate guided proofreading into an existing large data connectomics workflow.
+The web-based system is designed with a novice-friendly user interface (Fig.~\ref{fig:ui}).
+We show the current labeling of a cell boundary outline and its proposed correction overlayed on EM image data.
+The user is not possible to distinguish the current labeling from the proposed correction to avoid selection bias.
 We also show a solid overlay of the current and the proposed labeling.
@@
 The user must choose between the region being a split error which needs correcting (center) or not (right).
-Hovering highlights the current selection with a yellow border, and a mouse click confirms the choice and advances to the next potential error.\JT{Needs labels on the images; also, removal of black background.}}
+Hovering highlights the current selection with a yellow border, and a mouse click confirms the choice and advances to the next potential error.}
 \label{fig:ui}

### 2016-11-15 paper/results.tex

@@
+\begin{figure*}[t]
+\begin{center}
+\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
+\end{center}
+  \vspace{-4mm}
+   \caption{Performance comparison of focused proofreading by Plaza and our guided proofreading methods on the AC4 subvolume.
+All measurements are reported as median VI, the lower the better.
+We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (indicated by the red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle.
+In all cases, guided proofreading yields better results with less corrections.}
+\label{fig:ac4trails}
+\end{figure*}
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
+\end{center}
+  \vspace{-4mm}
+   \caption{VI distributions of proofreading output across ten slices of the AC4 subvolume. The different decision approaches yield different proofreading performances.}
+\label{fig:ac4trails}
+\end{figure}
+
 \section{Results and Discussion}
 
-We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings.
+%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings.
 Lower VI scores indicate less distance to the ground truth and a better segmentation.
@@
 \subsection{Selection Oracle}
+Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets.
+This is not surprising since all detected merge and split are corrected if they are good corrections.
 
@@
 This is not surprising since the user interface was the same for both control groups.
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.24\textwidth}
-        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
-        \caption{A gull}
-        \label{fig:gull}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.24\textwidth}
-        \includegraphics[width=\textwidth]{gfx/gpusers.pdf}
-        \caption{A tiger}
-        \label{fig:tiger}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.24\textwidth}
-        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
-        \caption{A gull}
-        \label{fig:gull}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.24\textwidth}
-        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
-        \caption{A tiger}
-        \label{fig:tiger}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-%    \begin{subfigure}[b]{0.15\textwidth}
-%        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
-%        \caption{A mouse}
-%        \label{fig:mouse}
-%    \end{subfigure}
-    \caption{Pictures of animals}\label{fig:animals}
-\end{figure*}
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.48\linewidth}
-        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
-        \caption{A gull}
-        \label{fig:gull}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.49\linewidth}
-        \includegraphics[width=\textwidth]{gfx/gpusers.pdf}
-        \caption{A tiger}
-        \label{fig:tiger}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-%    \begin{subfigure}[b]{0.15\textwidth}
-%        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
-%        \caption{A mouse}
-%        \label{fig:mouse}
-%    \end{subfigure}
-    \caption{Pictures of animals}\label{fig:animals}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.49\linewidth}
-        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
-        \caption{A gull}
-        \label{fig:gull}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.49\linewidth}
-        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
-        \caption{A mouse}
-        \label{fig:mouse}
-    \end{subfigure}
-    \caption{Pictures of animals}\label{fig:animals}
-\end{figure}

### 2016-11-15 paper/evaluation.tex
Results almost there.

@@
 \caption{Training parameters, cost, and results of our guided proofreading classifier versus focused proofreading by Plaza~\cite{focused_proofreading}.
-Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 GPU).}%While the training of our classifier is more expensive, testing accuracy is superior.
+Both methods were trained on the same mouse brain dataset using the same hardware (Tesla X GPU).}%While the training of our classifier is more expensive, testing accuracy is superior.
 }
@@
 
-\paragraph{Novice Study Design.} We recruited participants with no experience in electron microscopy data or proofreading, through flyers, mailing lists, and personal interaction.
+\paragraph{Novice study design.} We recruited participants with no experience in electron microscopy data or proofreading, through flyers, mailing lists, and personal interaction.
 Based on sample size calculation theory, we estimated the study needed ten users per proofreading tool including four potential dropouts~\cite{samplesize1,samplesize2}.
@@
 After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
-
-\paragraph{Expert Study Design.} We recruited 4 domain experts to evaluate the performance of both guided and focused proofreading.
+\begin{figure*}[t]
+\begin{center}
+\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
+\end{center}
+  \vspace{-4mm}
+   \caption{Performance comparison of focused proofreading by Plaza and our guided proofreading methods on the AC4 subvolume.
+All measurements are reported as median VI, the lower the better.
+We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (indicated by the red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle.
+In all cases, guided proofreading yields better results with less corrections.}
+\label{fig:ac4trails}
+\end{figure*}
+\paragraph{Expert study design.} We recruited 4 domain experts to evaluate the performance of both guided and focused proofreading.
 We obtained study consent and randomly assigned 2 experts to proofread using each classifier.

### 2016-11-15 paper/results.tex
Results almost there.

@@
-\begin{figure*}[t]
-\begin{center}
-\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
-\end{center}
-  \vspace{-4mm}
-   \caption{Performance comparison of focused proofreading by Plaza and our guided proofreading methods on the AC4 subvolume.
-All measurements are reported as median VI, the lower the better.
-We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (indicated by the red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle.
-In all cases, guided proofreading yields better results with less corrections.}
-\label{fig:ac4trails}
-\end{figure*}
+\section{Results and Discussion}
+
+%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings.
+Lower VI scores indicate less distance to the ground truth and a better segmentation.
+For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
+
+\subsection{Classifier Comparison}
+
+We compare the guided proofreading and focused proofreading classifiers and report precision/recall as well as f1 scores across datasets.
+
+\paragraph{L.
+Cylinder.} Evaluation was performed on previously unseen sections of mouse cortex volume of Kasthuri~\etal~\cite{kasthuri2015saturated}.
+We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches in respect to the ground truth labeling.
+We then ranked each patch using focused proofreading and guided proofreading and compared precision/recall (Table \ref{tab:prcyl}.
+Our method exhibits higher precision and recall for correct and error patches.
+
+\begin{table}[h]
+\caption{Classifier comparison on an unbalanced test set of the L. Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
+
+\small{
+\begin{tabular}{l|c|c|c|c}
+
+ & precision & recall & f1 score & \# \\ 
+\textbf{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
+correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
+split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
+\textbf{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
+correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
+split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
+\end{tabular} 
+}
+\label{tab:prcyl}
+\end{table}
+
+\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors).
+Again, guided proofreading achieves better precision/recall scores (Table \ref{tab:prac4}).
+
+\begin{table}[h]
+\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
+
+\small{
+\begin{tabular}{l|c|c|c|c}
+
+ & precision & recall & f1 score & \# \\ 
+\textbf{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
+correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
+split error & 0.14 & 0.51 & 0.21 & 332 \\ 
+\textbf{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
+correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
+split error & 0.54 & 0.95 & 0.69 & 332 \\ 
+\end{tabular} 
+}
+\label{tab:prac4}
+\end{table}
+
+\subsection{Forced Choice User Experiment}
+We performed a user study to evaluate the forced choice error correction method among novices and experts.
+To perform a reasonable experiment and be comparable to Haehn's~\etal Dojo user study, participants were asked to proofread the AC4 subvolume for 30 minutes.
+Even with computer-aided proofreading methods, correcting the whole volume in this time frame is simply not possible.
+We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation and the ground truth labeling (both provided by Haehn~\etal).
+For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of proofread segmentations against the ground truth labelings.
+The median VI of the initial segmentation in respect to ground truth was 0.476 (SD=0.089).
+Most novices and all experts were able to improve this with focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).
+
+\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to 0.469 (SD=0.87).
+On average, users viewed 423.4 corrections and accepted 45.8 of them with an average time of 4.9 seconds spent per correction.
+Participants using guided proofreading were able to reduce the median VI to 0.424 (SD=0.037).
+Here, users viewed 353.4 corrections on average and accepted 106.9 in 6.2 seconds.
+While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it.
+In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo.
+The slope of VI per correction in Fig.~\ref{fig:ac4trails} shows that guided proofreading enables VI changes with fewer corrections.
+Interestingly, the performance decreases after approximately 300 corrections.
+There are two explanations for this: user fatigue and increasing uncertainty during error suggestion from the classifier.
+Regarding fatigue, we suggest for future experiments to add short breaks after every ten minutes.
+
+\paragraph{Expert performance.} Domain experts were able to improve the initial segmentation in all cases.
+With focused proofreading, the median VI of the automatic segmentation was 0.439 (SD=0.084).
+With guided proofreading, the median VI was 0.396 (SD=0.032) as shown in Fig.~\ref{fig:ac4boxplot}.
+
+\paragraph{Subjective responses.} All subjective responses were recorded using the NASA-TLX workload index.
+Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading.
+However, these differences were not statistically significant.
+This is not surprising since the user interface was the same for both control groups.
+
+\subsection{Automatic Error Correction}
+
+\paragraph{Selection Oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets.
+This is not surprising since all detected merge and split are corrected if the segmentation is improved.
+Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume.
+With focused proofreading, the selection oracle reaches a median VI of 0.353 (SD=0.037) after 1605 corrections.
+With guided proofreading, the oracle reaches a median VI of 0.342 (SD=0.03) after approximately 800 corrections and then stagnates until all regions are proofread.
+Both results are very close to the best possible median VI of 0.334 which we calculated by computing maximum overlap with the ground truth.
+The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires less corrections to reach a reasonable reduction in VI on the AC4 subvolume and Fig.~\ref{fig:ac4boxplot} shows the distribution.
+The results on the L.
+Cylinder dataset (initial VI XX (SD=YY) are similar: Focused proofreading reduces the median VI to XX (SD=YY) after 26,170 corrections.
+Guided proofreading reduces the median VI to XX (SD=YY) after XX corrections.
+
+\paragraph{Automatic Method.}
+
+\subsection{Merge vs. Split Error Detection}
+
+\subsection{Limitations}
 
@@
    \caption{VI distributions of proofreading output across ten slices of the AC4 subvolume. The different decision approaches yield different proofreading performances.}
-\label{fig:ac4trails}
+\label{fig:ac4boxplot}
 \end{figure}
-
-\section{Results and Discussion}
-
-%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings.
-Lower VI scores indicate less distance to the ground truth and a better segmentation.
-For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
-
-\subsection{Selection Oracle}
-Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets.
-This is not surprising since all detected merge and split are corrected if they are good corrections.
-
-\subsection{Automatic Method}
-
-\subsection{Force Choice User Experiment}
-
-The initial segmentation for AC4 had a VI of XXX.
-
-\textbf{Novice Performance.} 
-\\~\\
-\textbf{Expert Performance.}
-\\~\\
-\textbf{Subjective Responses.} All subjective responses were recorded using the NASA-TLX workload index.
-The workload index asks study participants to state their mental, physical, temporal demands, as well as rate their performance, effort, and frustration on a scale with 21 graduations.
-Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading.
-However, these differences were not statistically significant.
-This is not surprising since the user interface was the same for both control groups.

### 2016-11-15 paper/conclusion.tex
Conclusion.

@@
 Humans are the bottleneck and minimizing the manual labor is the goal.
-%We have addressed this problem through training a convolutional neural network to detect ambiguous regions from labeled data---in effect, by finding a non-linear mapping between image and segmentation data.
-This allows us to identify merge and split errors with better performance than existing systems.
-Our experiments have shown that guided proofreading has the potential to reduce the bottleneck in the analysis of large connectomics datasets.
+In this paper, we have trained classifiers to find merge and split errors in automatic segmentations of connectomics data.
+We then reduce the correction of these errors to simple yes/no decisions.
+This allows proofreading with better performance than existing systems.
+Our experiments also show that automatic proofreading works.
+This has the potential to further reduce the manual labor and will be the target of future research.
 To encourage testing of our proposed architecture and replicate our experiments, we provide our framework and data as free and open research at (link omitted for review).

### 2016-11-15 paper/guidedproofreading_review.tex
Edited until result section
Testing plot layouts.
Review changes; minor issues.
Section 3 review.
Section 4 review.
Conclusion.

@@
 \usepackage{amssymb}
-
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{booktabs}
 % Include other packages here, before hyperref.
@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,linkcolor=blue,citecolor=blue,bookmarks=false]{hyperref}
+
+\newcommand{\JT}[1]{\textcolor{blue}{JT: #1}}
+\newcommand{\HP}[1]{\textcolor{red}{HP: #1}}
 
@@
 region around a segmentation boundary. Corrections can then be performed by a
-user with yes/no decisions  resulting in faster correction times than previous
+user with yes/no decisions,  which results in faster correction times than previous
 proofreading methods. We also present a fully-automatic mode that uses a
@@
 the automatic approach and comparing performance of novice and expert users
-demonstrate that our method performs favorably agains state-of-the-art
+demonstrate that our method performs favorably against state-of-the-art
 proofreading methods on different connectomics datasets.

### 2016-11-15 paper/results.tex
Update results.

@@
 
-\subsection{Classifier Comparison}
+\subsection{Precision and Recall}
 
-We compare the guided proofreading and focused proofreading classifiers and report precision/recall as well as f1 scores across datasets.
+We compare the guided proofreading and focused proofreading classifiers and report precision and recall as well as f1 scores across datasets.
 
@@
 We performed a user study to evaluate the forced choice error correction method among novices and experts.
-To perform a reasonable experiment and be comparable to Haehn's~\etal Dojo user study, participants were asked to proofread the AC4 subvolume for 30 minutes.
-Even with computer-aided proofreading methods, correcting the whole volume in this time frame is simply not possible.
-We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation and the ground truth labeling (both provided by Haehn~\etal).
-For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of proofread segmentations against the ground truth labelings.
-The median VI of the initial segmentation in respect to ground truth was 0.476 (SD=0.089).
-Most novices and all experts were able to improve this with focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).
+To be comparable to Haehn's~\etal Dojo user study, participants were asked to proofread the AC4 subvolume for 30 minutes.
+We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation in respect to the ground truth labeling (both provided by Haehn~\etal).
+For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations to ground truth.
+The median VI of the initial segmentation was 0.476 (SD=0.089).
+Most novices and all experts were able to improve upon this score with both, focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).
 
-\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to 0.469 (SD=0.87).
-On average, users viewed 423.4 corrections and accepted 45.8 of them with an average time of 4.9 seconds spent per correction.
-Participants using guided proofreading were able to reduce the median VI to 0.424 (SD=0.037).
-Here, users viewed 353.4 corrections on average and accepted 106.9 in 6.2 seconds.
+\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to $0.469$ ($SD=0.87$).
+On average, users viewed $423.4$ corrections and accepted $45.8$ of them with an average time of $4.9$ seconds spent per correction.
+Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$).
+Here, users viewed on average $353.4$ corrections and accepted $106.9$ in $6.2$ seconds.
 While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it.
-In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo.
-The slope of VI per correction in Fig.~\ref{fig:ac4trails} shows that guided proofreading enables VI changes with fewer corrections.
-Interestingly, the performance decreases after approximately 300 corrections.
+In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo (median VI $0.535$, $SD=0.055$).
+The slope of VI score per correction in Fig.~\ref{fig:ac4trails} shows that guided proofreading enables improvements with fewer corrections than the other tools.
+Interestingly, novice performance decreases after approximately $300$ corrections.
 There are two explanations for this: user fatigue and increasing uncertainty during error suggestion from the classifier.
@@
 \paragraph{Expert performance.} Domain experts were able to improve the initial segmentation in all cases.
-With focused proofreading, the median VI of the automatic segmentation was 0.439 (SD=0.084).
-With guided proofreading, the median VI was 0.396 (SD=0.032) as shown in Fig.~\ref{fig:ac4boxplot}.
+With focused proofreading, the median VI of the automatic segmentation was $0.439$ ($SD=0.084$).
+With guided proofreading, the median VI was $0.396$ ($SD=0.032$) as shown in Fig.~\ref{fig:ac4boxplot}.
 
@@
 
-\paragraph{Selection Oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets.
-This is not surprising since all detected merge and split are corrected if the segmentation is improved.
+\paragraph{Selection Oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split are corrected as long as the segmentation is improved.
 Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume.
-With focused proofreading, the selection oracle reaches a median VI of 0.353 (SD=0.037) after 1605 corrections.
-With guided proofreading, the oracle reaches a median VI of 0.342 (SD=0.03) after approximately 800 corrections and then stagnates until all regions are proofread.
-Both results are very close to the best possible median VI of 0.334 which we calculated by computing maximum overlap with the ground truth.
-The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires less corrections to reach a reasonable reduction in VI on the AC4 subvolume and Fig.~\ref{fig:ac4boxplot} shows the distribution.
+With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1605$ corrections.
+With guided proofreading, the oracle results in a median VI of $0.342$ ($SD=0.03$) after approximately $800$ corrections and then stagnates until all regions are proofread.
+Both results are very close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth).
+The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires less corrections to reach a reasonable reduction in VI.
+Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods.
 The results on the L.
-Cylinder dataset (initial VI XX (SD=YY) are similar: Focused proofreading reduces the median VI to XX (SD=YY) after 26,170 corrections.
-Guided proofreading reduces the median VI to XX (SD=YY) after XX corrections.
+Cylinder dataset (initial VI $XX$ ($SD=YY$) are similar: Focused proofreading reduces the median $VI$ to $XX$ ($SD=YY$) after 26,170 corrections.
+Guided proofreading reduces the median VI to $XX$ ($SD=YY$) after $XX$ corrections.
 
@@
   \vspace{-4mm}
-   \caption{VI distributions of proofreading output across ten slices of the AC4 subvolume. The different decision approaches yield different proofreading performances.}
+   \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume.
+The different decision approaches yield different proofreading performances.
+The performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
 \label{fig:ac4boxplot}

### 2016-11-15 cylinderGP2.py
Update patch generation with clamping.

@@ -1,0 +1,261 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/cylinderNEW/'
+OUTDIR = REGALDIR + 'cylinderGP/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_rhoana = []
+input_gold = []
+for z in range(250, 300):
+    image, prob, mask, gold, rhoana = gp.Util.read_section(DATADIR, z, verbose=False)
+
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_rhoana.append(rhoana)
+    input_gold.append(gold)
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+#
+# load merge errors
+#
+with open(OUTDIR+'all.p', 'rb') as f:
+  merge_errors = pickle.load(f)
+print len(merge_errors), 'merge errors'
+
+#
+# load or create bigM
+#
+bigM_cylinder_file = OUTDIR+'bigM_gp.p'
+if os.path.exists(bigM_cylinder_file):
+  print 'loading bigM'
+  with open(bigM_cylinder_file, 'rb') as f:
+    bigM = pickle.load(f)
+else:
+  print 'creating bigM'
+  bigM = gp.Legacy.create_bigM_without_mask(cnn, input_image, input_prob, input_rhoana, verbose=True, max=1000000)
+  with open(bigM_cylinder_file, 'wb') as f:
+    pickle.dump(bigM, f)  
+
+#
+# run auto merge correction
+#
+cylinder_vi_95_file = OUTDIR + '/cylinder_vi_95_w_merge_NEW.p'
+
+merge_vis = OUTDIR + '/cylinder_merge_auto95_vis.p'
+split_vis = OUTDIR + '/cylinder_split_auto95_vis.p'
+
+merge_fixes = OUTDIR + '/cylinder_merge_auto95_fixes.p'
+split_fixes = OUTDIR + '/cylinder_split_auto95_fixes.p'
+
[…]

### 2016-11-15 cylpatches.py

@@ -12,12 +12,12 @@ for z in range(250,300):
     
     image, prob, mask, gold, rhoana = gp.Util.read_section(os.path.expanduser('~/data/cylinderNEW'),z)
     
-    error_patches, patches = gp.Patch.patchify_maxoverlap(image, prob, mask, rhoana, gold, sample_rate=1, clamp_result=False)
+    error_patches, patches = gp.Patch.patchify_maxoverlap(image, prob, mask, rhoana, gold, sample_rate=1, clamp_result=True)
     
     e_p.append(error_patches)
     p.append(patches)    
 
-OUTDIR = '/n/regal/pfister_lab/haehn/CYLPATCHES/'
+OUTDIR = '/n/regal/pfister_lab/haehn/CYLPATCHES_CLAMPED/'
 
 with open(OUTDIR+'e_p.p', 'wb') as f:
   pickle.dump(e_p, f)

### 2016-11-15 paper/results.tex
Results section complete.

@@
 
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
+\end{center}
+  \vspace{-4mm}
+   \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume with different error correction approaches.
+The performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
+\label{fig:ac4boxplot}
+\end{figure}
 \subsection{Automatic Error Correction}
 
-\paragraph{Selection Oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split are corrected as long as the segmentation is improved.
-Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume.
+\paragraph{Selection oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split are corrected as long as the segmentation is improved.
+Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume (initial median VI $0.476$, $SD=0.089$).
 With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1605$ corrections.
@@
 The results on the L.
-Cylinder dataset (initial VI $XX$ ($SD=YY$) are similar: Focused proofreading reduces the median $VI$ to $XX$ ($SD=YY$) after 26,170 corrections.
-Guided proofreading reduces the median VI to $XX$ ($SD=YY$) after $XX$ corrections.
+Cylinder dataset (initial VI $0.379$, $SD=0.118$) are similar: Focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted).
+Guided proofreading reduces the median VI to $0.2996$ ($SD=0.073$) after $27,491$ corrections ($2,696$ accepted).
 
-\paragraph{Automatic Method.}
+\paragraph{Automatic selection with threshold.} Focused proofreading was not designed to run automatically.
+This explains very poor performance on the AC4 subvolume (VI of $1.9$, $SD=0.496$) and on the L.
+Cylinder dataset (VI of $2.75$, $SD=0.789$).
+For guided proofreading we define the threshold $p_t=0.95$ for both datasets.
+This reduces median VI in the AC4 subvolume to $0.398$ ($SD=0.068$).
+This is an impressive result and comparable to expert performance.
+Guided proofreading also reduces VI in the L.
+Cylinder data to $0.352$ ($SD=0.087$).
 
-\subsection{Merge vs. Split Error Detection}
+\paragraph{Merge Error Detection} Guided proofreading performs merge error detection prior to split error detection.
+The classifier automatically found 10 merge errors in the AC4 subvolume of which 4 reduce VI .
+Automatic selection with $p_t=0.95$ corrected all of these 4 true errors and in addition 2 false ones (precision/recall 0.67/1.00, f1-score 0.80).
+In 50 sections of the L.
+Cylinder dataset 151 merge errors were automatically found of which 17 reduce VI.
+Automatic selection with $p_t=0.95$ corrected 6 true errors and 30 false ones (precision/recall 0.17/0.35, f1-score 0.23).
+\DFH{Not good.
+The split error correction cleans up but still not good, might be bug.
+hard to track down on the large data.}
 
 \subsection{Limitations}
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
-\end{center}
-  \vspace{-4mm}
-   \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume.
-The different decision approaches yield different proofreading performances.
-The performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
-\label{fig:ac4boxplot}
-\end{figure}
+Guided proofreading works on 2D image sections.
+This enables error correction without a computationally expensive alignment process.
+However, the output requires an additional (block-)merging step prior to 3D  analysis.

### 2016-11-15 paper/conclusion.tex
Minor edits.

@@
 This has the potential to further reduce the manual labor and will be the target of future research.
-To encourage testing of our proposed architecture and replicate our experiments, we provide our framework and data as free and open research at (link omitted for review).
+To encourage testing of our proposed architecture and replication of our experiments, we provide our framework and data as free and open research at (link omitted for review).

### 2016-11-15 paper/evaluation.tex
Results section complete.
Minor edits.

@@
 Table~\ref{tab:parameters} lists the final parameters.
-Our CNN configuration results in approximately 170,000 learnable parameters.
+Our CNN configuration results in 171,474 learnable parameters.
 We assume that training has converged if the validation loss does not decrease for 50 epochs.
@@
 We obtained the best possible parameters for NeuroProof by consulting the developers (Table~\ref{tab:parameters}).
-Rather than using Raveler as the frontend, we use our own interface (Fig.~\ref{fig:ui}) to compare only the classifier part of Plaza's approach.
+Rather than using Raveler as the frontend, we use our own interface (Fig.~\ref{fig:ui}) to compare only the classifier from Plaza's approach.
 
@@
 
-\paragraph{Novice study design.} We recruited participants with no experience in electron microscopy data or proofreading, through flyers, mailing lists, and personal interaction.
+\paragraph{Novice study design.} We recruited participants with no experience in electron microscopy data or proofreading through flyers, mailing lists, and personal interaction.
 Based on sample size calculation theory, we estimated the study needed ten users per proofreading tool including four potential dropouts~\cite{samplesize1,samplesize2}.
@@
   \vspace{-4mm}
-   \caption{Performance comparison of focused proofreading by Plaza and our guided proofreading methods on the AC4 subvolume.
+   \caption{Performance comparison of Plaza's focused proofreading and our guided proofreading methods on the AC4 subvolume.
 All measurements are reported as median VI, the lower the better.
 We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (indicated by the red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle.
-In all cases, guided proofreading yields better results with less corrections.}
+In all cases, guided proofreading yields better results with fewer corrections.}
 \label{fig:ac4trails}
@@
 \paragraph{Evaluation metric.} For each experiment, we measure the similarity between proofread segmentations and the manual `ground truth' labelings using \textit{variation of information} (VI).
-VI is a measure of the distance between two clusterings, closely related to mutual information, where lower means better.
+VI is a measure of the distance between two clusterings, closely related to mutual information, where lower means a better match to ground truth.
 We treat VI as a continuous variable during analysis.

### 2016-11-15 paper/results.tex
Add explanation.
Minor edits.

@@
 We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches in respect to the ground truth labeling.
-We then ranked each patch using focused proofreading and guided proofreading and compared precision/recall (Table \ref{tab:prcyl}.
+We then ranked each patch by using focused proofreading, guided proofreading and compared precision/recall (Table \ref{tab:prcyl}.
 Our method exhibits higher precision and recall for correct and error patches.
@@
 To be comparable to Haehn's~\etal Dojo user study, participants were asked to proofread the AC4 subvolume for 30 minutes.
-We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation in respect to the ground truth labeling (both provided by Haehn~\etal).
-For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations to ground truth.
+We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation with respect to the ground truth labeling (both provided by Haehn~\etal).
+For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations relative to ground truth.
 The median VI of the initial segmentation was 0.476 (SD=0.089).
@@
 There are two explanations for this: user fatigue and increasing uncertainty during error suggestion from the classifier.
-Regarding fatigue, we suggest for future experiments to add short breaks after every ten minutes.
+Regarding fatigue, we suggest future experiments short breaks after every ten minutes.
 
@@
    \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume with different error correction approaches.
-The performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
+The variation resulting from performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
 \label{fig:ac4boxplot}
@@
 
-\paragraph{Selection oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split are corrected as long as the segmentation is improved.
+\paragraph{Selection oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split errors are corrected as long as the segmentation is improved.
 Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume (initial median VI $0.476$, $SD=0.089$).
@@
 Both results are very close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth).
-The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires less corrections to reach a reasonable reduction in VI.
+The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires fewer corrections to reach a reasonable reduction in VI.
 Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods.
 The results on the L.
-Cylinder dataset (initial VI $0.379$, $SD=0.118$) are similar: Focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted).
+Cylinder dataset (initial VI $0.379$, $SD=0.118$) are similar.
+Focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted).
 Guided proofreading reduces the median VI to $0.2996$ ($SD=0.073$) after $27,491$ corrections ($2,696$ accepted).
@@
 \paragraph{Merge Error Detection} Guided proofreading performs merge error detection prior to split error detection.
-The classifier automatically found 10 merge errors in the AC4 subvolume of which 4 reduce VI .
-Automatic selection with $p_t=0.95$ corrected all of these 4 true errors and in addition 2 false ones (precision/recall 0.67/1.00, f1-score 0.80).
+The classifier found 10 merge errors in the AC4 subvolume of which 4 reduce VI.
+Automatic selection with $p_t=0.95$ corrected 6 of these errors (precision/recall 0.87/0.80, f1-score 0.80).
+This was not captured in median VI but resulted in a mean VI reduction from $0.512$ ($SD=0.09$) to $0.509$ ($SD=0.086$).
+The selection oracle reduced mean VI with only merge errors to $0.508$ ($SD=0.086$).
+In the forced choice user study, participants marked 1.9 merge errors (experts: 2) merge errors for correction and reduce mean VI to $0.502$ (experts: VI $0.503$, $SD=0.086$).
+This shows how hard it is to identify merge errors and how little they effect VI.
 In 50 sections of the L.
 Cylinder dataset 151 merge errors were automatically found of which 17 reduce VI.
-Automatic selection with $p_t=0.95$ corrected 6 true errors and 30 false ones (precision/recall 0.17/0.35, f1-score 0.23).
-\DFH{Not good.
-The split error correction cleans up but still not good, might be bug.
-hard to track down on the large data.}
+Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (precision/recall 0.82/0.73, f1-score 0.77) without - in sum - any effect on the VI.
 

### 2016-11-15 paper/results.tex
Update F1 score for neuroproof.

@@
 For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations relative to ground truth.
-The median VI of the initial segmentation was 0.476 (SD=0.089).
+The median VI of the initial segmentation was $0.476$ ($SD=0.089$), mean VI was $0.512$ ($SD=0.09$).
 Most novices and all experts were able to improve upon this score with both, focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).
@@
 There are two explanations for this: user fatigue and increasing uncertainty during error suggestion from the classifier.
-Regarding fatigue, we suggest future experiments short breaks after every ten minutes.
+Regarding fatigue, we suggest that future experiments include short breaks after every ten minutes.
 

### 2016-11-15 paper/results.tex
Update.

@@
 The classifier found 10 merge errors in the AC4 subvolume of which 4 reduce VI.
-Automatic selection with $p_t=0.95$ corrected 6 of these errors (precision/recall 0.87/0.80, f1-score 0.80).
+Automatic selection with $p_t=0.95$ corrected 6 of these errors (Prec./Recall 0.87/0.80, f1-score 0.80).
 This was not captured in median VI but resulted in a mean VI reduction from $0.512$ ($SD=0.09$) to $0.509$ ($SD=0.086$).
@@
 Cylinder dataset 151 merge errors were automatically found of which 17 reduce VI.
-Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (precision/recall 0.82/0.73, f1-score 0.77) without - in sum - any effect on the VI.
+Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (Prec./Recall 0.82/0.73, f1-score 0.77) without - in sum - any effect on the VI.
 

### 2016-11-15 patchgenCREMI.py
CREMI getting closer.

@@ -20,7 +20,7 @@ def generate_patches(start_slice, end_slice):
 
         t0 = time.time()
         print 'working on slice', z
-        input_image, input_prob, input_gold, input_rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/'), z)
+        input_image, input_prob, input_gold, input_rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
 
 
         error_patches, patches = gp.Patch.patchify_maxoverlap(input_image, input_prob, np.zeros((1,1250,1250),dtype=np.bool), input_rhoana, input_gold, sample_rate=1)
@@ -103,11 +103,11 @@ def run(PATCH_PATH, start_slice, end_slice, filename):
     np.save(PATCH_PATH+filename+'_targets.npz', shuffled[1])
     print 'Done!'
 
-run('/n/regal/pfister_lab/haehn/CREMITEST2/', 0, 50, 'trainA')
+run('/n/regal/pfister_lab/haehn/CREMITEST2/', 0, 75, 'test')
 # run('/n/regal/pfister_lab/haehn/CREMITEST2/', 17, 25, 'testA')
-run('/n/regal/pfister_lab/haehn/CREMITEST2/', 100,150, 'trainB')
+# run('/n/regal/pfister_lab/haehn/CREMITEST2/', 100,150, 'trainB')
 # run('/n/regal/pfister_lab/haehn/CREMITEST2/', 25+17, 50, 'testB')
-run('/n/regal/pfister_lab/haehn/CREMITEST2/', 200,250, 'trainC')
+# run('/n/regal/pfister_lab/haehn/CREMITEST2/', 200,250, 'trainC')
 # run('/n/regal/pfister_lab/haehn/CREMITEST2/', 50+17, 75, 'testC')
 # run('/n/regal/pfister_lab/haehn/CREMITEST2/', 0, 17, 'trainA')
 # run('/n/regal/pfister_lab/haehn/CREMITEST2/', 17, 25, 'testA')

### 2016-11-15 paper/method.tex
Replace UI.
Fixes.

@@
 \begin{figure}[t]
-\begin{center}
+\centering  
 \includegraphics[width=\linewidth]{gfx/cnn_inputs.pdf}
-\end{center}
- % \vspace{-4mm}
 \caption{Example inputs for learning correct splits and split errors, as per a candidate segmentation versus the ground truth.
@@
 \begin{figure}[t]
-\begin{center}
+\centering
 \includegraphics[width=\linewidth]{gfx/merge_error.pdf}
-\end{center}
-%  \vspace{-4mm}
 \caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment.
 Then, each border is individually rated using the split error CNN by inverting the probability score.
-A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.\JT{Candidate to improve.}}
+A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
 \label{fig:merge_error}
@@
 The user must choose between the region being a split error which needs correcting (center) or not (right).
-Hovering highlights the current selection with a yellow border, and a mouse click confirms the choice and advances to the next potential error.}
+Hovering highlights the current selection with a blue border, and a mouse click confirms the choice and advances to the next potential error.}
 \label{fig:ui}

### 2016-11-15 paper/results.tex
Fix typo.
Fixes.

@@
 
-We compare the guided proofreading and focused proofreading classifiers and report precision and recall as well as f1 scores across datasets.
+We compare guided proofreading and focused proofreading classifiers and report precision and recall as well as f1 scores across datasets.
 
-\paragraph{L.
-Cylinder.} Evaluation was performed on previously unseen sections of mouse cortex volume of Kasthuri~\etal~\cite{kasthuri2015saturated}.
+\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of mouse cortex volume of Kasthuri~\etal~\cite{kasthuri2015saturated}.
 We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches in respect to the ground truth labeling.
@@
 
-\begin{table}[h]
-\caption{Classifier comparison on an unbalanced test set of the L. Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
-
-\small{
-\begin{tabular}{l|c|c|c|c}
-
- & precision & recall & f1 score & \# \\ 
-\textbf{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
-correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
-split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
-\textbf{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
-correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
-split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
+\begin{table}[t]
+\caption{Classifier comparison on an unbalanced test set of the L.~Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrr}
+\toprule
+ & Precision & Recall & F1 score & \# \\ 
+\midrule
+\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
+Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
+Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
+\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
+Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
+Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
+\bottomrule
 \end{tabular} 
@@
 
-\begin{table}[h]
+\begin{table}[t]
 \caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
-
-\small{
-\begin{tabular}{l|c|c|c|c}
-
- & precision & recall & f1 score & \# \\ 
-\textbf{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
-correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
-split error & 0.14 & 0.51 & 0.21 & 332 \\ 
-\textbf{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrr}
+\toprule
+& Precision & Recall & F1 score & \# \\ 
+\midrule
+\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
+Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
+Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
+\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
 correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
 split error & 0.54 & 0.95 & 0.69 & 332 \\ 
+\bottomrule
 \end{tabular} 
@@
 Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods.
-The results on the L.
-Cylinder dataset (initial VI $0.379$, $SD=0.118$) are similar.
+The results on the L.~Cylinder dataset (initial VI $0.379$, $SD=0.118$) are similar.
 Focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted).
@@
 \paragraph{Automatic selection with threshold.} Focused proofreading was not designed to run automatically.
-This explains very poor performance on the AC4 subvolume (VI of $1.9$, $SD=0.496$) and on the L.
-Cylinder dataset (VI of $2.75$, $SD=0.789$).
+This explains very poor performance on the AC4 subvolume (VI of $1.9$, $SD=0.496$) and on the L.~Cylinder dataset (VI of $2.75$, $SD=0.789$).
 For guided proofreading we define the threshold $p_t=0.95$ for both datasets.
@@
 This is an impressive result and comparable to expert performance.
-Guided proofreading also reduces VI in the L.
-Cylinder data to $0.352$ ($SD=0.087$).
+Guided proofreading also reduces VI in the L.~Cylinder data to $0.352$ ($SD=0.087$).
 
@@
 This shows how hard it is to identify merge errors and how little they effect VI.
-In 50 sections of the L.
-Cylinder dataset 151 merge errors were automatically found of which 17 reduce VI.
+In 50 sections of the L.~Cylinder dataset 151 merge errors were automatically found of which 17 reduce VI.
 Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (Prec./Recall 0.82/0.73, f1-score 0.77) without - in sum - any effect on the VI.

### 2016-11-15 paper/evaluation.tex
Update F1 score for neuroproof.
Half-way through results.

@@
 		\midrule
-		\emph{Results---Test Set} \\ \midrule cost [m]: 217 \\ Test. acc.: 0.99 \\ Prec./Recall: \HP{add}?/? \\ F1 Score: \HP{add}? \\
+		\emph{Results---Test Set} \\ \midrule cost [m]: 217 \\ Test. acc.: 0.99 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
 	\end{tabular}
@@
 \begin{figure*}[t]
-\begin{center}
+\centering
 \includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
-\end{center}
-  \vspace{-4mm}
-   \caption{Performance comparison of Plaza's focused proofreading and our guided proofreading methods on the AC4 subvolume.
+\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the AC4 subvolume.
 All measurements are reported as median VI, the lower the better.
-We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (indicated by the red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle.
+We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle.
 In all cases, guided proofreading yields better results with fewer corrections.}
@@
 \end{figure*}
+
 \paragraph{Expert study design.} We recruited 4 domain experts to evaluate the performance of both guided and focused proofreading.

### 2016-11-15 paper/method.tex
Half-way through results.

@@
 
-\paragraph{Convolutional Neural Network Architecture.} Split error detection of a given boundary is a binary classification task since the boundary is either correct or erroneous.
+\paragraph{CNN Architecture.} Boundary split error detection is a binary classification task since the boundary is either correct or erroneous.
 However, in reality, the score $p$ is between 0 and 1.
-The classification complexity arises from hundreds of different cell types in connectomics data rather than from the classification decision itself.
+In connectromics, classification complexity arises from hundreds of different cell types, rather than from the classification decision itself.
 Intuitively, this yields a wider architecture with more filters rather than a deeper architecture with more layers.
-We explored different architectural configurations---including residual networks~\cite{resnet}---by performing a brute force parameter search and comparing precision and recall (see supplementary materials).
-Our final CNN configuration for split error detection is composed of four convolutional layers, each followed by max pooling as well as dropout regularization to prevent overfitting due to limited training data (Fig.~\ref{fig:architecture}).
+We explored different architectures---including residual networks~\cite{resnet}---with brute force parameter searches and precision and recall comparisons (see supplementary materials).
+Our final CNN configuration for split error detection has four convolutional layers, each followed by max pooling with dropout regularization to prevent overfitting due to limited training data (Fig.~\ref{fig:architecture}).
 
@@
 
-Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data,
-corresponding boundary probabilities, and a single binary mask combining the two
-neighboring labels as inputs to our CNN. However, we observed that the
-boundary probability information generated from EM images is often misleading
-due to noise or artifacts in the data. This can result in merge errors within
-the automatic segmentation. To better direct our classifier to train on the true
-boundary, we extract the border between two segments. Then, we dilate this border
-by 5 pixels to consider slight edge ambiguities and use this binary mask as an
-additional input. This creates a stacked 4-channel input patch.
-Fig.~\ref{fig:cnn_inputs} shows examples of correct and erroneous input
-patches and their corresponding automatic segmentation and ground truth.
+Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data, corresponding boundary probabilities, and a single binary mask combining the two neighboring labels as inputs to our CNN.
+However, we observed that the boundary probability information generated from EM images is often misleading due to noise or artifacts in the data.
+This can result in merge errors within the automatic segmentation.
+To better direct our classifier to train on the true boundary, we extract the border between two segments.
+Then, we dilate this border by 5 pixels to consider slight edge ambiguities and use this binary mask as an additional input.
+This creates a stacked 4-channel input patch.
+Fig.~\ref{fig:cnn_inputs} shows examples of correct and erroneous input patches and their corresponding automatic segmentation and ground truth.
 
 \begin{figure}[t]
-\centering  
+\begin{center}
   \includegraphics[width=\linewidth]{gfx/cnn_inputs.pdf}
+\end{center}
+ % \vspace{-4mm}
    \caption{Example inputs for learning correct splits and split errors, as per a candidate segmentation versus the ground truth.
@@
 \begin{figure}[t]
-\centering
+\begin{center}
   \includegraphics[width=\linewidth]{gfx/merge_error.pdf}
+\end{center}
+%  \vspace{-4mm}
    \caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment.

### 2016-11-15 paper/results.tex
Half-way through results.

@@
 
-We compare guided proofreading and focused proofreading classifiers and report precision and recall as well as f1 scores across datasets.
+We compare guided and focused proofreading classifiers and report precision, recall, and F1 scores across datasets.
 
-\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of mouse cortex volume of Kasthuri~\etal~\cite{kasthuri2015saturated}.
-We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches in respect to the ground truth labeling.
-We then ranked each patch by using focused proofreading, guided proofreading and compared precision/recall (Table \ref{tab:prcyl}.
-Our method exhibits higher precision and recall for correct and error patches.
+\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of the mouse cortex volume from Kasthuri~\etal~\cite{kasthuri2015saturated}.
+We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling.
+Then, we ranked each patch by using focused proofreading and guided proofreading, and compare precision/recall (Table \ref{tab:prcyl}).
+Our method exhibits higher precision and recall for correct and erroroneous patches.
 
@@
 \toprule
- & Precision & Recall & F1 score & \# \\ 
+ & Precision & Recall & F1 score & Test \# \\ 
 \midrule
@@
 
-\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors).
-Again, guided proofreading achieves better precision/recall scores (Table \ref{tab:prac4}).
+\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors). Guided proofreading achieves better precision/recall scores (Table \ref{tab:prac4}).
 
@@
 \toprule
-& Precision & Recall & F1 score & \# \\ 
+& Precision & Recall & F1 score & Test \# \\ 
 \midrule
@@
 \emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
-correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
-split error & 0.54 & 0.95 & 0.69 & 332 \\ 
+Correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
+Split error & 0.54 & 0.95 & 0.69 & 332 \\ 
 \bottomrule
@@
 
+\begin{figure*}[t]
+\centering
+\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
+\caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume with different error correction approaches.
+The variation resulting from performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
+\label{fig:ac4boxplot}
+\end{figure*}
+
 \subsection{Forced Choice User Experiment}
 We performed a user study to evaluate the forced choice error correction method among novices and experts.
-To be comparable to Haehn's~\etal Dojo user study, participants were asked to proofread the AC4 subvolume for 30 minutes.
-We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation with respect to the ground truth labeling (both provided by Haehn~\etal).
-For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations relative to ground truth.
-The median VI of the initial segmentation was $0.476$ ($SD=0.089$), mean VI was $0.512$ ($SD=0.09$).
-Most novices and all experts were able to improve upon this score with both, focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).
+To be comparable to Haehn~\etal's Dojo user study~\cite{haehn_dojo_2014}, participants were asked to proofread the AC4 subvolume for 30 minutes.
+We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation with respect to the ground truth labeling (provided in \cite{haehn_dojo_2014}).
+For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations.
+Median VI $=0.476$ ($SD=0.089$), with mean VI $=0.512$ ($SD=0.09$).
+Most novices and all experts were able to improve upon this score with both focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).
 
 \paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to $0.469$ ($SD=0.87$).
-On average, users viewed $423.4$ corrections and accepted $45.8$ of them with an average time of $4.9$ seconds spent per correction.
+On average, users viewed $423.4$ corrections and accepted $45.8$, with an average time of $4.9$ seconds per correction.
 Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$).
-Here, users viewed on average $353.4$ corrections and accepted $106.9$ in $6.2$ seconds.
+Here, users viewed on average $353.4$ corrections and accepted $106.9$, with an average per correction time of $6.2$ seconds.
 While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it.
@@
 Interestingly, novice performance decreases after approximately $300$ corrections.
-There are two explanations for this: user fatigue and increasing uncertainty during error suggestion from the classifier.
-Regarding fatigue, we suggest that future experiments include short breaks after every ten minutes.
+There are two explanations for this: user fatigue, and increasing uncertainty during error suggestion from the classifier.
+%Regarding fatigue, we suggest that future experiments include short breaks after every ten minutes.
 
@@
 With focused proofreading, the median VI of the automatic segmentation was $0.439$ ($SD=0.084$).
-With guided proofreading, the median VI was $0.396$ ($SD=0.032$) as shown in Fig.~\ref{fig:ac4boxplot}.
+With guided proofreading, the median VI was $0.396$ ($SD=0.032$, Fig.~\ref{fig:ac4boxplot}).
 
-\paragraph{Subjective responses.} All subjective responses were recorded using the NASA-TLX workload index.
+\paragraph{Subjective responses.} We used the NASA-TLX workload index to record subjective responses.
 Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading.
 However, these differences were not statistically significant.
-This is not surprising since the user interface was the same for both control groups.
+This is unsurprising as the user interface was the same for both groups.
 
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
-\end{center}
-  \vspace{-4mm}
-   \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume with different error correction approaches.
-The variation resulting from performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
-\label{fig:ac4boxplot}
-\end{figure}
 \subsection{Automatic Error Correction}

### 2016-11-15 paper/results.tex
Second half of results review.

@@
 \includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
-\caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume with different error correction approaches.
-The variation resulting from performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
+\caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across slices of the AC4 subvolume, with different error correction approaches.
+The variation resulting from performance of FP with automatic selection is $4.5\times$ higher than GP (as indicated by the arrow), with median VI of $1.9$ and $SD=0.496$.}
 \label{fig:ac4boxplot}
@@
 In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo (median VI $0.535$, $SD=0.055$).
-The slope of VI score per correction in Fig.~\ref{fig:ac4trails} shows that guided proofreading enables improvements with fewer corrections than the other tools.
+The slope of VI score per correction (Fig.~\ref{fig:ac4trails}) shows that guided proofreading enables improvements with fewer corrections than the other tools.
 Interestingly, novice performance decreases after approximately $300$ corrections.
@@
 
-\paragraph{Selection oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split errors are corrected as long as the segmentation is improved.
-Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume (initial median VI $0.476$, $SD=0.089$).
-With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1605$ corrections.
-With guided proofreading, the oracle results in a median VI of $0.342$ ($SD=0.03$) after approximately $800$ corrections and then stagnates until all regions are proofread.
-Both results are very close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth).
+\paragraph{Selection oracle.} As expected, the selection oracle yields the best performance on all datasets.
+Fig.~\ref{fig:ac4trails} shows VI reduction using the selection oracle on the AC4 subvolume (initial median VI $0.476$, $SD=0.089$).
+With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1600$ corrections.
+With guided proofreading, the oracle reaches a minimum median VI of $0.342$ ($SD=0.03$) after $800$ corrections.
+Both results are close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth).
 The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires fewer corrections to reach a reasonable reduction in VI.
 Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods.
-The results on the L.~Cylinder dataset (initial VI $0.379$, $SD=0.118$) are similar.
-Focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted).
+On the L.~Cylinder dataset (initial VI $0.379$, $SD=0.118$), focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted).
 Guided proofreading reduces the median VI to $0.2996$ ($SD=0.073$) after $27,491$ corrections ($2,696$ accepted).
@@
 \paragraph{Automatic selection with threshold.} Focused proofreading was not designed to run automatically.
-This explains very poor performance on the AC4 subvolume (VI of $1.9$, $SD=0.496$) and on the L.~Cylinder dataset (VI of $2.75$, $SD=0.789$).
-For guided proofreading we define the threshold $p_t=0.95$ for both datasets.
+This explains the poor performance on the AC4 subvolume (VI of $1.9$, $SD=0.496$) and on the L.~Cylinder dataset (VI of $2.75$, $SD=0.789$).
+For guided proofreading, we set $p_t=0.95$ for both datasets.
 This reduces median VI in the AC4 subvolume to $0.398$ ($SD=0.068$).
-This is an impressive result and comparable to expert performance.
+This result is comparable to expert performance.
 Guided proofreading also reduces VI in the L.~Cylinder data to $0.352$ ($SD=0.087$).
@@
 \paragraph{Merge Error Detection} Guided proofreading performs merge error detection prior to split error detection.
-The classifier found 10 merge errors in the AC4 subvolume of which 4 reduce VI.
-Automatic selection with $p_t=0.95$ corrected 6 of these errors (Prec./Recall 0.87/0.80, f1-score 0.80).
-This was not captured in median VI but resulted in a mean VI reduction from $0.512$ ($SD=0.09$) to $0.509$ ($SD=0.086$).
+The classifier found 10 merge errors in the AC4 subvolume, of which 4 reduced VI.
+Automatic selection with $p_t=0.95$ corrected 6 of these errors (Prec./Recall 0.87/0.80, F1-score 0.80).
+This was not captured in median VI, but resulted in a mean VI reduction from $0.512$ ($SD=0.09$) to $0.509$ ($SD=0.086$).
 The selection oracle reduced mean VI with only merge errors to $0.508$ ($SD=0.086$).
-In the forced choice user study, participants marked 1.9 merge errors (experts: 2) merge errors for correction and reduce mean VI to $0.502$ (experts: VI $0.503$, $SD=0.086$).
-This shows how hard it is to identify merge errors and how little they effect VI.
-In 50 sections of the L.~Cylinder dataset 151 merge errors were automatically found of which 17 reduce VI.
-Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (Prec./Recall 0.82/0.73, f1-score 0.77) without - in sum - any effect on the VI.
+In the forced choice user study, novices marked 1.9 merge errors for correction and reduced mean VI to $0.502$ (experts marked 2, VI $0.503$, $SD=0.086$).
+This shows how hard it is to identify merge errors.
+In 50 sections of the L.~Cylinder dataset, 151 merge errors were automatically found of which 17 reduced VI.
+Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (Prec./Recall 0.82/0.73, f1-score 0.77) to negligible VI effect.
 
-\subsection{Limitations}
-Guided proofreading works on 2D image sections.
+%\subsection{Limitations}
+%Guided proofreading works on 2D image sections.
 This enables error correction without a computationally expensive alignment process.

### 2016-11-15 gp/patch.py
New cremi CNN.

@@ -731,20 +731,20 @@ class Patch(object):
   def load_cremi(patch_size=(75,75), verbose=True):
 
 
-    PATCH_PATH = '/n/regal/pfister_lab/haehn/CREMITEST/'
+    PATCH_PATH = '/n/regal/pfister_lab/haehn/CREMITEST2/'
 
     t0 = time.time()
 
     training = np.load(PATCH_PATH+'train.npy', mmap_mode='r')
     training_targets = np.load(PATCH_PATH+'train_targets.npy')
 
-    test = np.load(PATCH_PATH+'test.npy', mmap_mode='r')
-    test_targets = np.load(PATCH_PATH+'test_targets.npy')
+    #test = np.load(PATCH_PATH+'test.npy', mmap_mode='r')
+    #test_targets = np.load(PATCH_PATH+'test_targets.npy')
 
     if verbose:
       print 'Loaded', PATCH_PATH, 'in', time.time()-t0, 'seconds.'
 
-    return training, training_targets.astype(np.uint8), test, test_targets.astype(np.uint8)
+    return training, training_targets.astype(np.uint8)#, test, test_targets.astype(np.uint8)
 
   # @staticmethod
   # def load_cremi(patch_size=(75,75), verbose=True):

### 2016-11-15 paper/related_work.tex

@@
 \begin{figure*}[t]
-\begin{center}
+\centering
 \includegraphics[width=\linewidth]{gfx/architecture.pdf}
-\end{center}
-  \vspace{-4mm}
 \caption{Our guided proofreading classifiers use a traditional CNN architecture of four convolutional layers, each followed by max pooling and dropout regularization.
@@
 All these approaches make good progress; however, in general, proofreading is still required to correct errors.
-\\~\\
-\textbf{Interactive Proofreading.} While proofreading is very time consuming, it is fairly easy for humans to perform corrections through splitting and merging segments.
+
+\paragraph{Interactive Proofreading.} While proofreading is very time consuming, it is fairly easy for humans to perform corrections through splitting and merging segments.
 One expert tool is Raveler, introduced by Chklovskii~\etal~\cite{chklovskii2010, raveler}.
@@
 All interactive proofreading solutions require the user to find potential errors manually, which takes the majority of the time~\cite{proofreading_bottleneck,haehn_dojo_2014}.
-Recent papers propose computer-aided proofreading systems to reduce the time spent in this visual search task.
-\\~\\
-\textbf{Computer-aided Proofreading.} Uzunbas \etal~\cite{uzunbas} showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method.
+Recent papers propose computer-aided proofreading systems to quicken this visual search task.
+
+\paragraph{Computer-aided Proofreading.} Uzunbas \etal~\cite{uzunbas} showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method.
 The authors track uncertainty throughout the automatic labeling by training a conditional random field.

### 2016-11-15 cremiGP.py
Add cremi.

@@ -1,0 +1,263 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
+OUTDIR = REGALDIR + 'cremiGP/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL_CREMILARGE.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_gold = []
+input_rhoana = []
+test_slices = range(15,25) + range(25+15,50) + range(50+15,75)
+for z in test_slices:
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('/home/d/data/CREMIGP/TEST/'), z)
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_gold.append(gold)
+    input_rhoana.append(rhoana)    
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+#
+# load merge errors
+#
+# with open(OUTDIR+'all.p', 'rb') as f:
+#   merge_errors = pickle.load(f)
+# print len(merge_errors), 'merge errors'
+
+#
+# load or create bigM
+#
+bigM_cylinder_file = OUTDIR+'bigM_gp.p'
+if os.path.exists(bigM_cylinder_file):
+  print 'loading bigM'
+  with open(bigM_cylinder_file, 'rb') as f:
+    bigM = pickle.load(f)
+else:
+  print 'creating bigM'
+  bigM = gp.Legacy.create_bigM_without_mask(cnn, input_image, input_prob, input_rhoana, verbose=True, max=1000000)
+  with open(bigM_cylinder_file, 'wb') as f:
+    pickle.dump(bigM, f)  
+
+
+
+# #
+# # run auto merge correction
+# #
+# cylinder_vi_95_file = OUTDIR + '/cylinder_vi_95_w_merge_NEW.p'
+
+# merge_vis = OUTDIR + '/cylinder_merge_auto95_vis.p'
+# split_vis = OUTDIR + '/cylinder_split_auto95_vis.p'
+
+# merge_fixes = OUTDIR + '/cylinder_merge_auto95_fixes.p'
[…]

### 2016-11-15 cremiGP.py
Fix bug.

@@ -27,7 +27,7 @@ input_gold = []
 input_rhoana = []
 test_slices = range(15,25) + range(25+15,50) + range(50+15,75)
 for z in test_slices:
-    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('/home/d/data/CREMIGP/TEST/'), z)
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
     input_image.append(image)
     input_prob.append(255.-prob)
     input_gold.append(gold)

### 2016-11-15 cremiGP.py
use only 5.

@@ -9,7 +9,7 @@ import os
 HOMEDIR = '/n/home05/haehn/'
 REGALDIR = '/n/regal/pfister_lab/haehn/'
 DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
-OUTDIR = REGALDIR + 'cremiGP/'
+OUTDIR = REGALDIR + 'cremiGP2/'
 
 #
 # load cnn
@@ -25,7 +25,7 @@ input_image = []
 input_prob = []
 input_gold = []
 input_rhoana = []
-test_slices = range(15,25) + range(25+15,50) + range(50+15,75)
+test_slices = range(20,25) + range(25+20,50) + range(50+20,75)
 for z in test_slices:
     image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
     input_image.append(image)

### 2016-11-15 paper/results.tex
Several changes.
More fixes.

@@
 For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
+Additional plots are available as supplemental material due to reasons of space.
 
 \subsection{Precision and Recall}
-
-We compare guided and focused proofreading classifiers and report precision, recall, and F1 scores across datasets.
 
@@
 Then, we ranked each patch by using focused proofreading and guided proofreading, and compare precision/recall (Table \ref{tab:prcyl}).
-Our method exhibits higher precision and recall for correct and erroroneous patches.
+Our method exhibits higher precision and recall for correct and erroneous patches.
 
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
 \centering
@@
 \label{fig:ac4boxplot}
-\end{figure*}
+\end{figure}
 
@@
 In 50 sections of the L.~Cylinder dataset, 151 merge errors were automatically found of which 17 reduced VI.
-Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (Prec./Recall 0.82/0.73, f1-score 0.77) to negligible VI effect.
+Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (Prec./Recall 0.82/0.73, F1-score 0.77) to negligible VI effect.
 

### 2016-11-15 cremiGP_merge2.py
Another merge runner.

@@ -1,0 +1,61 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
+OUTDIR = REGALDIR + 'cremiGP2/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL_CREMILARGE.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_gold = []
+input_rhoana = []
+test_slices = range(20,25) + range(25+20,50) + range(50+20,75)
+for z in test_slices:
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_gold.append(gold)
+    input_rhoana.append(rhoana)    
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+
+
+# find merge errors, if we did not generate them before
+merge_error_file = OUTDIR+'/merges.p'
+if os.path.exists(merge_error_file):
+  print 'Loading merge errors from file..'
+  with open(merge_error_file, 'rb') as f:
+    merge_errors = pickle.load(f)
+else:
+  print 'Finding Top 5 merge errors..'
+  merge_errors = gp.Legacy.get_top5_merge_errors(cnn, input_image, input_prob, input_rhoana)
+  with open(merge_error_file, 'wb') as f:
+    pickle.dump(merge_errors, f)
+
+print len(merge_errors), ' merge errors found.'
+
+
+
+
+
+
+print 'All done.'
+

### 2016-11-15 gp/legacy.py

@@ -379,7 +379,7 @@ class Legacy(object):
             results = Legacy.fix_single_merge(cnn,
                                               input_image[DOJO_SLICE],
                                               input_prob[DOJO_SLICE],
-                                              before_merge_error, N=50, 
+                                              before_merge_error, N=10, 
                                               erode=True, 
                                               invert=True,
                                               dilate=True,

### 2016-11-15 paper/introduction.tex

@@
 
-Our goal is to automatically detect split and merge errors to reduce visual
+Our goal is to automatically detect potential split and merge errors to reduce visual
 inspection time. Further, to reduce correction time, we propose
@@
 
-We learn a classifier for split errors with a convolutional neural network
+We train a classifier for split error detection with a convolutional neural network
 (CNN). This takes as input patches of membrane segmentation probabilities, cell
-segmentation masks, and boundary masks, and outputs a probability score. As we
+segmentation masks, and boundary masks, and outputs a split-probability score. As we
 must process large data, this classifier only operates on cell boundaries, which
@@
 invert and reuse the split classification network, instead asking it to rate a
-set of generated candidate boundaries that hypothesize a split. %We compute
+set of generated boundaries that hypothesize a split. %We compute
 %corrections for both types of errors.
 
-We also propose a greedy algorithm for guided proofreading. Possible erroneous
-regions are sorted by their score, and a candidate correction is generated for each
+Possible erroneous regions are sorted by their score, and a candidate correction is generated for each
 region. Then, a user works through this list of regions and corrections. In a
 forced choice setting, the user either selects a correction or skips it to
-advance to the next region. In an automatic setting, errors with a high
-probability are automatically corrected first, given an appropriate
+advance to the next region. In an automatic setting, errors with a high probability are automatically corrected first, given an appropriate
 probability threshold, after which the user would take over. Finally, to test

### 2016-11-15 paper/method.tex
Add updated graphics.

@@
 \paragraph{Classifier Inputs.} To train the CNN, we consider boundary context in the decision making process by using a $75\times75$ pixel patch at the center of an existing boundary.
-This size covers approximately $80\%$ of all boundaries in the 6~nm Mouse S1 AC3 Open Connectome Project dataset.
-If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary, and combine the resulting score by averaging weighted by the boundary length coverage per patch.
+This size covers approximately $80\%$ of all boundaries in the 6~nm Mouse S1 AC3 Open Connectome Project dataset\footnote{\scriptsize{\url{http://openconnectomeproject.org/}}}.
+If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary, and average the resulting scores weighted by the boundary length coverage per patch.
 
@@
 \begin{center}
-  \includegraphics[width=\linewidth]{gfx/merge_error.pdf}
+  \includegraphics[width=\linewidth]{gfx/merge_error_v4.pdf}
 \end{center}
@@
 
-We use the proposed classifiers in combination to perform corrections of split and merge errors in automatic segmentations.
+We combine the proposed classifiers to perform corrections of split and merge errors in automatic segmentations.
 For this, we first perform merge error detection for all existing segments in a dataset and store the inverted rankings $1-p$ as well as potential corrections.
@@
 The oracle only accepts corrections which improve the automatic segmentation---others get
-discarded. This is guided proofreading with a perfect user, and allows us to assess the upper limit of performance.
+discarded. This is guided proofreading with a perfect user, and allows us to assess the upper limit of improvements.
 
@@
 Inspecting all merge errors is not possible for users due to the sheer amount of generated borders.
-Therefore, we only present merge errors that satisfy $1-p_t$.
+Therefore, we only present merge errors that have a probability threshold higher than $1-p_t$.
 
@@
 We show the current labeling of a cell boundary outline and its proposed correction overlayed on EM image data.
-The user is not possible to distinguish the current labeling from the proposed correction to avoid selection bias.
+The user cannot to distinguish the current labeling from the proposed correction to avoid selection bias.
 We also show a solid overlay of the current and the proposed labeling.

### 2016-11-15 paper/related_work.tex

@@
 
-Recent papers have attacked the problem of proofreading massive datasets through crowdsourcing with novices~\cite{saalfeld09,anderson2011,Giuly2013DP2}.
+Recent papers have tackled the problem of proofreading massive datasets through crowdsourcing with novices~\cite{saalfeld09,anderson2011,Giuly2013DP2}.
 One popular platform is EyeWire, by Kim \etal~\cite{eyewire_nature}, where participants earn virtual rewards for merging over-segmented labelings to reconstruct retina cells.
@@
 This segmentation technique produces uncertainty estimates, which inform potential regions for proofreading to the user.
-While this applies to isotropic volumes, more work is needed to apply it to the typically anisotropic connectromics dataset volumes.
+While this applies to isotropic volumes, more work is needed to apply it to the typically anisotropic connectomics dataset volumes.
 

### 2016-11-15 cremiGP_merge2.py
Another change.

@@ -39,7 +39,7 @@ original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, i
 
 
 # find merge errors, if we did not generate them before
-merge_error_file = OUTDIR+'/merges.p'
+merge_error_file = OUTDIR+'/merges_10.p'
 if os.path.exists(merge_error_file):
   print 'Loading merge errors from file..'
   with open(merge_error_file, 'rb') as f:

### 2016-11-15 paper/evaluation.tex
Several changes.
Cganhges.

@@
 The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse, and was acquired using ssEM.
-The dataset resolution is $3\times3\, \text{nm}^2$ per pixel, with section thickness of $30\, \text{nm}$.
+The dataset resolution is $3\times3\times30~\text{nm}^3\text{/voxel}$.
 Image data and a manually-labeled expert `ground truth' segmentation is available publicly for the entire dataset\footnote{\scriptsize{\url{https://software.rc.fas.harvard.edu/lichtman/vast/}}}.
@@
 		\midrule
-		\emph{Results---Test Set} \\ \midrule cost [m]: 217 \\ Test. acc.: 0.99 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
+		\emph{Results---Test Set} \\ \midrule Cost [m]: 217 \\ Test. acc.: 0.99 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
 	\end{tabular}
@@
 
-\paragraph{Evaluation metric.} For each experiment, we measure the similarity between proofread segmentations and the manual `ground truth' labelings using \textit{variation of information} (VI).
-VI is a measure of the distance between two clusterings, closely related to mutual information, where lower means a better match to ground truth.
-We treat VI as a continuous variable during analysis.
+\paragraph{Evaluation metric.} We measure the similarity between proofread segmentations and the manual `ground truth' labelings using \textit{variation of information} (VI).
+VI is a measure of the distance between two clusterings, closely related to mutual information (the lower, the better).% We treat VI as a continuous variable during analysis.
 

### 2016-11-15 cremiGP_merge3.py
Speed things up.

@@ -1,0 +1,61 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
+OUTDIR = REGALDIR + 'cremiGP2/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL_CREMILARGE.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_gold = []
+input_rhoana = []
+test_slices = range(20,25)# + range(25+20,50) + range(50+20,75)
+for z in test_slices:
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_gold.append(gold)
+    input_rhoana.append(rhoana)    
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+
+
+# find merge errors, if we did not generate them before
+merge_error_file = OUTDIR+'/merges_10_A.p'
+if os.path.exists(merge_error_file):
+  print 'Loading merge errors from file..'
+  with open(merge_error_file, 'rb') as f:
+    merge_errors = pickle.load(f)
+else:
+  print 'Finding Top 5 merge errors..'
+  merge_errors = gp.Legacy.get_top5_merge_errors(cnn, input_image, input_prob, input_rhoana)
+  with open(merge_error_file, 'wb') as f:
+    pickle.dump(merge_errors, f)
+
+print len(merge_errors), ' merge errors found.'
+
+
+
+
+
+
+print 'All done.'
+

### 2016-11-15 cremiGP_merge4.py

@@ -1,0 +1,61 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
+OUTDIR = REGALDIR + 'cremiGP2/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL_CREMILARGE.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_gold = []
+input_rhoana = []
+test_slices = range(25+20,50) #+ range(50+20,75)
+for z in test_slices:
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_gold.append(gold)
+    input_rhoana.append(rhoana)    
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+
+
+# find merge errors, if we did not generate them before
+merge_error_file = OUTDIR+'/merges_10_B.p'
+if os.path.exists(merge_error_file):
+  print 'Loading merge errors from file..'
+  with open(merge_error_file, 'rb') as f:
+    merge_errors = pickle.load(f)
+else:
+  print 'Finding Top 5 merge errors..'
+  merge_errors = gp.Legacy.get_top5_merge_errors(cnn, input_image, input_prob, input_rhoana)
+  with open(merge_error_file, 'wb') as f:
+    pickle.dump(merge_errors, f)
+
+print len(merge_errors), ' merge errors found.'
+
+
+
+
+
+
+print 'All done.'
+

### 2016-11-15 paper/evaluation.tex
More little fixes.

@@
 \paragraph{Interactive proofreading.} Haehn~\etal's comparison of interactive proofreading tools concludes that novices perform best when using Dojo~\cite{haehn_dojo_2014}.
-We use the publicly available findings of their user study as a baseline comparison.
-We use the data of all Dojo users in aggregate as a baseline.
+We studied the publicly available findings of their user study and use the data of all Dojo users in aggregate as a baseline.
 
@@
 In particular, we evaluated how participants perform while correcting an automatic segmentation using the guided proofreading and focused proofreading tools.
-We designed a single factor between-subject experiment with the factor \textit{proofreading classifier}, and asked participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes.
+We designed a single factor between-subjects experiment with the factor \textit{proofreading classifier}, and asked participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes.
 To enable comparison against the interactive proofreading study by~Haehn~\etal~\cite{haehn_dojo_2014}, we use the exact same study conditions, dataset, and time limit.

### 2016-11-15 paper/method.tex
More little fixes.

@@
 
-Similar to Bogovich~\etal~\cite{BogovicHJ13}, we use grayscale image data, corresponding boundary probabilities, and a single binary mask combining the two neighboring labels as inputs to our CNN.
+Similar to Bogovic~\etal~\cite{BogovicHJ13}, we use grayscale image data, corresponding boundary probabilities, and a single binary mask combining the two neighboring labels as inputs to our CNN.
 However, we observed that the boundary probability information generated from EM images is often misleading due to noise or artifacts in the data.
@@
 We show the current labeling of a cell boundary outline and its proposed correction overlayed on EM image data.
-The user cannot to distinguish the current labeling from the proposed correction to avoid selection bias.
+The user cannot distinguish the current labeling from the proposed correction to avoid selection bias.
 We also show a solid overlay of the current and the proposed labeling.

### 2016-11-15 paper/results.tex
More little fixes.

@@
 Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$).
-Here, users viewed on average $353.4$ corrections and accepted $106.9$, with an average per correction time of $6.2$ seconds.
+Here, users viewed on average $353.4$ corrections and accepted $106.9$, with an average correction time of $6.2$ seconds.
 While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it.
@@
 
-\paragraph{Merge Error Detection} Guided proofreading performs merge error detection prior to split error detection.
+\paragraph{Merge Error Detection.} Guided proofreading performs merge error detection prior to split error detection.
 The classifier found 10 merge errors in the AC4 subvolume, of which 4 reduced VI.

### 2016-11-16 paper/evaluation.tex
Latest.

@@
 
-\paragraph{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets were made publicly available\footnote{\scriptsize{\url{http://www.cremi.org}}},  each $1250\times1250\times125$ voxels.
+%\paragraph{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets were made publicly available\footnote{\scriptsize{\url{http://www.cremi.org}}},  each $1250\times1250\times125$ voxels.
 Since only three datasets include manually-labeled `ground truth', we use these three volumes for our experiments.

### 2016-11-16 paper/evaluation.tex
Space squeezing.

@@
 Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} ($2048\times2048\times300$ voxels).
-The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex of a healthy mouse, and was acquired using ssEM.
+The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex, acquired using ssEM.
 The dataset resolution is $3\times3\times30~\text{nm}^3\text{/voxel}$.
-Image data and a manually-labeled expert `ground truth' segmentation is available publicly for the entire dataset\footnote{\scriptsize{\url{https://software.rc.fas.harvard.edu/lichtman/vast/}}}.
+Image data and a manually-labeled expert `ground truth' segmentation is publicly available\footnote{\scriptsize{\url{https://software.rc.fas.harvard.edu/lichtman/vast/}}}.
 

### 2016-11-16 paper/method.tex
Space squeezing.
Space saving.

@@
 
-\paragraph{Classifier Inputs.} To train the CNN, we consider boundary context in the decision making process by using a $75\times75$ pixel patch at the center of an existing boundary.
-This size covers approximately $80\%$ of all boundaries in the 6~nm Mouse S1 AC3 Open Connectome Project dataset\footnote{\scriptsize{\url{http://openconnectomeproject.org/}}}.
-If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary, and average the resulting scores weighted by the boundary length coverage per patch.
+\paragraph{Classifier Inputs.} To train the CNN, we consider boundary context in the decision making process via a $75\times75$ patch over the center of an existing boundary.
+This size covers approximately $80\%$ of all boundaries in the 6~nm Mouse S1 AC3 Open Connectome Project dataset.
+If the boundary is not fully covered, we sample up to 10 non-overlapping patches along the boundary, and average the resulting scores weighted by the boundary length coverage per patch.
+%\footnote{\scriptsize{\url{http://openconnectomeproject.org/}}}
 
@@
 \begin{figure}[t]
-\begin{center}
+\centering
 \includegraphics[width=\linewidth]{gfx/cnn_inputs.pdf}
-\end{center}
- % \vspace{-4mm}
 \caption{Example inputs for learning correct splits and split errors, as per a candidate segmentation versus the ground truth.
@@
 \begin{figure}[t]
-\begin{center}
+\centering
 \includegraphics[width=\linewidth]{gfx/merge_error_v4.pdf}
-\end{center}
-%  \vspace{-4mm}
 \caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment.
@@
 \includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
-\caption{Our guided proofreading user interface.
+\caption{User interface.
 A candidate error region is shown on the left.
 The user must choose between the region being a split error which needs correcting (center) or not (right).
-Hovering highlights the current selection with a blue border, and a mouse click confirms the choice and advances to the next potential error.}
+Confirming the choice advances to the next potential error.} % Hovering highlights the current selection with a blue border, and a}
 \label{fig:ui}

### 2016-11-17 gp/legacy.py
Latest things.

@@ -717,7 +717,7 @@ class Legacy(object):
   @staticmethod
   def perform_sim_user_merge_correction(cnn, big_M, input_image, input_prob, input_rhoana, input_gold, merge_errors):
 
-      def dojoVI(gt, seg):
+      def dojo3VI(gt, seg):
         # total_vi = 0
         slice_vi = []    
         for i in range(len(gt)):
@@ -765,7 +765,7 @@ class Legacy(object):
             # this is a good fix
             rhoana_after_merge_correction[z] = new_rhoana
 
-            rhoanas.append(dojoVI(input_gold, rhoana_after_merge_correction))
+            rhoanas.append(dojo3VI(input_gold, rhoana_after_merge_correction))
 
             #
             # and remove the original label from our bigM matrix
@@ -780,7 +780,15 @@ class Legacy(object):
             new_m[:,:] = -1
             new_m[0:-2,0:-2] = bigM[z]
 
-            # print 'adding', label1, 'to', z
+            print 'adding', label1, 'to', z, new_rhoana.shape, new_rhoana.max(), len(bigM)
+
+            if label1 >= new_m.shape[0]:
+              new_m2 = np.zeros((new_m.shape[0]+2, new_m.shape[1]+2), dtype=bigM[z].dtype)
+              new_m2[:,:] = -1
+              new_m2[0:-2,0:-2] = new_m
+
+              new_m = new_m2
+
 
             new_m = Legacy.add_new_label_to_M(cnn, new_m, input_image[z], input_prob[z], new_rhoana, label1)
             new_m = Legacy.add_new_label_to_M(cnn, new_m, input_image[z], input_prob[z], new_rhoana, label2)

### 2016-11-17 gp/stats.py

@@ -33,172 +33,6 @@ class Stats(object):
   def analyze_users(FP_USERS, gold, rhoana, oracle=None, clampX=500, clampY=False, filename=None, hideXlabels=True, hideYlabels=True, DATADIR = '/home/d/GPSTUDY/', skipoutput=False, data='dojo', hline=-1, returnplt=False, showlegend=False, vilabel=False,clabel=False ):
 
 
-    # def VI(gt, seg):
-    #   # total_vi = 0
-    #   slice_vi = []    
-    #   for i in range(len(gt)):
-    #       current_vi = Util.vi(gt[i].astype(np.int64), seg[i].astype(np.int64))
-    #       # total_vi += current_vi
-    #       slice_vi.append(current_vi)
-    #   # total_vi /= 10
-    #   return np.mean(slice_vi), np.median(slice_vi), slice_vi
-
-    # init_mean_vi = VI(gold, rhoana)[0]
-    # init_median_vi = VI(gold, rhoana)[1]
-    # init_vi_per_slice = VI(gold, rhoana)[2]
-    
-    # print 'No. users', len(FP_USERS)
-
-    
-
-    # newrhoana = 'ui_results.p'
-    # times = 'times.p'
-    # corrections = 'corrections.p'
-    # correction_vis = 'correction_vis.p'
-
-    # fp_outputs = []
-    # fp_times = []
-    # fp_corrections = []
-    # fp_vis =[]
-
-    # for i,f in enumerate(FP_USERS):
-    #     with open(DATADIR+FP_USERS[i]+'/'+newrhoana, 'rb') as f:
-    #         fp_newrhoana = pickle.load(f)
-    #         fp_outputs.append(fp_newrhoana)
-    #     with open(DATADIR+FP_USERS[i]+'/'+times, 'rb') as f:
-    #         fp_time = pickle.load(f)
-    #         fp_time = [int(v) for v in fp_time]
-    #         fp_times.append(fp_time)
-    #     with open(DATADIR+FP_USERS[i]+'/'+corrections, 'rb') as f:
-    #         fp_correction = pickle.load(f)       
-    #         fp_corrections.append(fp_correction)
-    #     with open(DATADIR+FP_USERS[i]+'/'+correction_vis, 'rb') as f:
-    #         fp_correction_vis = pickle.load(f) 
-    #         fp_vis.append(fp_correction_vis)
-
-    # fp_times_mean = []
-    # for t in fp_times:
-    #     fp_times_mean.append(np.mean(t))
[…]

### 2016-11-17 paper/results.tex
Latest.

@@
 For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
-Additional plots are available as supplemental material due to reasons of space.
+Please note that additional plots are available as supplemental material due to reasons of space.
 
@@
 On the L.~Cylinder dataset (initial VI $0.379$, $SD=0.118$), focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted).
-Guided proofreading reduces the median VI to $0.2996$ ($SD=0.073$) after $27,491$ corrections ($2,696$ accepted).
+Guided proofreading reaches the minimum median VI $0.2996$ ($SD=0.073$) after $10,000$ corrections (in total $27,491$, $2,696$ accepted).
 

### 2016-11-20 paper/supplemental/architecture.tex
Add outline for supplemental while we are waiting for CREMI results.

\section{Classifier}

\subsection{CNN Architecture}
2 vs 4 layers vs resnet

\subsection{Training Parameters}

\subsection{Automatic Method Threshold $p_t$}

### 2016-11-20 paper/supplemental/userstudy.tex
Add outline for supplemental while we are waiting for CREMI results.

\section{Forced Choice User Experiment}

\subsection{Recruitment and Participation}

flyers, participant list

\subsection{Example Classifications}

Where did users make a mistake?

\subsection{Subjective Responses}

NASA TLX ANOVA analysis

### 2016-11-22 cremiGPsplitonly.py
New stuff.

@@ -1,0 +1,170 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
+OUTDIR = REGALDIR + 'CREMIBIGSPLITONLY/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL_CREMI_FINAL.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_gold = []
+input_rhoana = []
+test_slices = range(75)# + range(25+20,50) + range(50+20,75)
+for z in test_slices:
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_gold.append(gold)
+    input_rhoana.append(rhoana)    
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+
+
+
+bigM_cremi_file = OUTDIR+'bigM_gp.p'
+if os.path.exists(bigM_cremi_file):
+  print 'loading bigM'
+  with open(bigM_cremi_file, 'rb') as f:
+    bigM = pickle.load(f)
+# else:
+#   print 'creating bigM'
+#   bigM = gp.Legacy.create_bigM_without_mask(cnn, input_image, input_prob, input_rhoana, verbose=True, max=1000000)
+#   with open(bigM_cremi_file, 'wb') as f:
+#     pickle.dump(bigM, f)  
+
+
+
+
+
+
+
+
+
+
+#
+# run auto merge correction
+#
+cylinder_vi_95_file = OUTDIR + '/cremi_vi_00_w_merge_NEW.p'
+
+# merge_vis = OUTDIR + '/cremi_merge_auto00_vis.p'
+split_vis = OUTDIR + '/cremi_split_auto00_vis.p'
+
+# merge_fixes = OUTDIR + '/cremi_merge_auto00_fixes.p'
+split_fixes = OUTDIR + '/cremi_split_auto00_fixes.p'
+
[…]

### 2016-11-22 paper/supplemental/architecture.tex

@@
 
-\subsection{CNN Architecture}
-2 vs 4 layers vs resnet
+\subsection{Architecture}
+We explored different architectures for the convolutional neural network (CNN) for split error detection.
+In table \ref{tab:architecture} we compare traditional CNN architectures versus residual networks~\cite{resnet}.
+The traditional architecture generalized better than residual networks on unseen testing data.
+
+\begin{table}[h]
+\caption{Traditional CNN Architecture versus Residual Network Architecture \cite{resnet}.
+All configurations are compared using the same parameters.
+Our final choice (indicated by *) trains relatively fast and performs better.}%While the training of our classifier is more expensive, testing accuracy is superior.
+}
+
+\small{
+\begin{tabular}{@{}ll|l@{}}
+	\toprule
+     ~ & \textbf{Traditional Network} & \textbf{Residual Network}  \\ \midrule	
+\begin{tabular}{@{}r|@{}}
+Conv. Layers \\
+Dropout Reg. \\
+Cost [m] \\
+Test. Acc. \\
+Prec./Recall \\
+F1 Score\\
+~
+\end{tabular} & 
+\begin{tabular}{@{}c|c@{}}
+ 2 & 4 \\
+ y & y \\
+ 27.5 & 383 \\
+ 0.925 & 0.94 \\
+ 0.93/0.93 &
+ 0.94/0.94 \\
+ 0.93 & 0.94 \\
+ ~&*
+\end{tabular}
+& 
+\begin{tabular}{@{}c|c@{}}
+ 5 & 13 \\
+ y & n \\
+5080 & 1094 \\
+ 0.93 & 0.90 \\
+ 0.7/0.53 &
+ 0.74/0.66 \\
+ 0.39 & 0.64\\
+ ~&~
+
+\end{tabular}
+
+\end{tabular}
+\hspace{2mm}
+\hrule
+}
+\label{tab:architecture}
+\end{table}
 

### 2016-11-22 paper/supplemental/architecture.tex
Some more supplemental stuff.

@@
 In table \ref{tab:architecture} we compare traditional CNN architectures versus residual networks~\cite{resnet}.
-The traditional architecture generalized better than residual networks on unseen testing data.
+The traditional architecture with dropout regularization generalized better than residual networks on unseen testing data.
 
@@
 
+We performed a limited brute force parameter search to tune the split error classifier (Tab.
+\ref{tab:parametersearch}).
+This resulted in 3240 different CNN configurations which were evaluated on 10\% of our training data.
+Learning rate and momentum ranges are defined linearly across 2000 epochs.
+
+\begin{table}[h]
+\caption{Brute force parameter search for the split error classifier. The final parameters are highlighted.}%While the training of our classifier is more expensive, testing accuracy is superior. }
+
+\small{
+\begin{tabular}{@{}ll}
+	\toprule
+     \textbf{Parameter} & \textbf{Search Space}  \\ \midrule	
+\begin{tabular}{@{}l@{}}
+Filter size: \\
+No. Filters 1: \\
+No. Filters 2-4: \\
+Dense units:\\
+Learning rate: \\
+Momentum: \\
+Mini-Batchsize: 
+\end{tabular} & 
+\begin{tabular}{@{}l@{}}
+\textbf{3x3}, 5x5, 9x9, 13x13\\
+32, 48, \textbf{64} \\
+32, \textbf{48}, 64 \\
+256, \textbf{512} \\
+0.00001, 0.0001, 0.001, 0.01, \textbf{0.03-0.00001} \\
+0.9, 0.95, \textbf{0.9-0.999} \\
+10, 100, \textbf{128}
+\end{tabular}
+
+\end{tabular}
+\hspace{2mm}
+\hrule
+}
+\label{tab:parametersearch}
+\end{table}
+
 \subsection{Automatic Method Threshold $p_t$}
+For automatic selection, we observed a threshold $p_t=0.95$ as stable when evaluating on previously unseen testing data (Mouse S1 AC3 Open Connectome Project dataset).
+This means, that automatic selection stops once all borders with $p_t\geq0.95$ were proofread.
+Fig.
+\ref{fig:pt} shows split error classification on three randomly selected subvolumes ($700\times700\times2$ voxels) of AC3.
+In all cases, the threshold $p_t=0.95$ reduces VI.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\linewidth]{gfx/ptplot.pdf}
+\caption{Observations of probability thresholds $p_t$ during automatic selection on three different subvolumes of previously unseen testing data. The dashed lines show when $p_t=0.95$ is reached.}
+\label{fig:cylboxplot}
+\end{figure}
+
+\subsection{Limitations}
+Guided proofreading works on 2D image sections.
+This enables error correction without a computationally expensive alignment process.
+However, the output requires an additional (block-)merging step prior to 3D  analysis.

### 2016-11-22 paper/supplemental/leftcylinder.tex
Some more supplemental stuff.

\section{L. Cylinder Results}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cyltrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the L. Cylinder dataset. All measurements are reported as median VI, the lower the better. We compare automatic selection with threshold and the selection oracle for accepting or rejecting corrections using each method. In all cases, guided proofreading yields better results with fewer corrections.}
\label{fig:cylboxplot}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=.7\linewidth]{gfx/cylboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the L. Cylinder dataset, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $7.8\times$ higher than GP (as indicated by the arrow), with median VI of $2.75$ and $SD=0.789$.}
\label{fig:cylboxplot}
\end{figure}

### 2016-11-22 cremiFPsplitonlyB.py
Split CREMI.

@@ -1,0 +1,171 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
+OUTDIR = REGALDIR + 'CREMIBIGSPLITONLY_B_FP/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL_CREMI_FINAL.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_gold = []
+input_rhoana = []
+test_slices = range(25,30)# + range(25+20,50) + range(50+20,75)
+for z in test_slices:
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_gold.append(gold)
+    input_rhoana.append(rhoana)    
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+
+
+
+bigM_cremi_file = OUTDIR+'bigM_fp.p'
+if os.path.exists(bigM_cremi_file):
+  print 'loading bigM'
+  with open(bigM_cremi_file, 'rb') as f:
+    bigM = pickle.load(f)
+    bigM = bigM[25:30]
+# else:
+#   print 'creating bigM'
+#   bigM = gp.Legacy.create_bigM_without_mask(cnn, input_image, input_prob, input_rhoana, verbose=True, max=1000000)
+#   with open(bigM_cremi_file, 'wb') as f:
+#     pickle.dump(bigM, f)  
+
+
+
+
+
+
+
+
+
+
+#
+# run auto merge correction
+#
+cylinder_vi_95_file = OUTDIR + '/cremi_vi_00_w_merge_NEW.p'
+
+# merge_vis = OUTDIR + '/cremi_merge_auto00_vis.p'
+split_vis = OUTDIR + '/cremi_split_auto00_vis.p'
+
+# merge_fixes = OUTDIR + '/cremi_merge_auto00_fixes.p'
[…]

### 2016-11-22 cremiFPsplitonlyC.py

@@ -1,0 +1,171 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
+OUTDIR = REGALDIR + 'CREMIBIGSPLITONLY_C_FP/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL_CREMI_FINAL.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_gold = []
+input_rhoana = []
+test_slices = range(50,55)# + range(25+20,50) + range(50+20,75)
+for z in test_slices:
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_gold.append(gold)
+    input_rhoana.append(rhoana)    
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+
+
+
+bigM_cremi_file = OUTDIR+'bigM_fp.p'
+if os.path.exists(bigM_cremi_file):
+  print 'loading bigM'
+  with open(bigM_cremi_file, 'rb') as f:
+    bigM = pickle.load(f)
+    bigM = bigM[50:55]
+# else:
+#   print 'creating bigM'
+#   bigM = gp.Legacy.create_bigM_without_mask(cnn, input_image, input_prob, input_rhoana, verbose=True, max=1000000)
+#   with open(bigM_cremi_file, 'wb') as f:
+#     pickle.dump(bigM, f)  
+
+
+
+
+
+
+
+
+
+
+#
+# run auto merge correction
+#
+cylinder_vi_95_file = OUTDIR + '/cremi_vi_00_w_merge_NEW.p'
+
+# merge_vis = OUTDIR + '/cremi_merge_auto00_vis.p'
+split_vis = OUTDIR + '/cremi_split_auto00_vis.p'
+
+# merge_fixes = OUTDIR + '/cremi_merge_auto00_fixes.p'
[…]

### 2016-11-22 cremiGPsplitonlyC.py

@@ -1,0 +1,171 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
+OUTDIR = REGALDIR + 'CREMIBIGSPLITONLY_C/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL_CREMI_FINAL.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_gold = []
+input_rhoana = []
+test_slices = range(50,55)# + range(25+20,50) + range(50+20,75)
+for z in test_slices:
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_gold.append(gold)
+    input_rhoana.append(rhoana)    
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+
+
+
+bigM_cremi_file = OUTDIR+'bigM_gp.p'
+if os.path.exists(bigM_cremi_file):
+  print 'loading bigM'
+  with open(bigM_cremi_file, 'rb') as f:
+    bigM = pickle.load(f)
+    bigM = bigM[50:55]
+# else:
+#   print 'creating bigM'
+#   bigM = gp.Legacy.create_bigM_without_mask(cnn, input_image, input_prob, input_rhoana, verbose=True, max=1000000)
+#   with open(bigM_cremi_file, 'wb') as f:
+#     pickle.dump(bigM, f)  
+
+
+
+
+
+
+
+
+
+
+#
+# run auto merge correction
+#
+cylinder_vi_95_file = OUTDIR + '/cremi_vi_00_w_merge_NEW.p'
+
+# merge_vis = OUTDIR + '/cremi_merge_auto00_vis.p'
+split_vis = OUTDIR + '/cremi_split_auto00_vis.p'
+
+# merge_fixes = OUTDIR + '/cremi_merge_auto00_fixes.p'
[…]

### 2016-11-22 gp/stats.py

@@ -33,172 +33,6 @@ class Stats(object):
   def analyze_users(FP_USERS, gold, rhoana, oracle=None, clampX=500, clampY=False, filename=None, hideXlabels=True, hideYlabels=True, DATADIR = '/home/d/GPSTUDY/', skipoutput=False, data='dojo', hline=-1, returnplt=False, showlegend=False, vilabel=False,clabel=False ):
 
 
-    def VI(gt, seg):
-      # total_vi = 0
-      slice_vi = []    
-      for i in range(len(gt)):
-          current_vi = Util.vi(gt[i].astype(np.int64), seg[i].astype(np.int64))
-          # total_vi += current_vi
-          slice_vi.append(current_vi)
-      # total_vi /= 10
-      return np.mean(slice_vi), np.median(slice_vi), slice_vi
-
-    init_mean_vi = VI(gold, rhoana)[0]
-    init_median_vi = VI(gold, rhoana)[1]
-    init_vi_per_slice = VI(gold, rhoana)[2]
-    print init_median_vi
-    print 'No. users', len(FP_USERS)
-
-    
-
-    newrhoana = 'ui_results.p'
-    times = 'times.p'
-    corrections = 'corrections.p'
-    correction_vis = 'correction_vis.p'
-
-    fp_outputs = []
-    fp_times = []
-    fp_corrections = []
-    fp_vis =[]
-
-    for i,f in enumerate(FP_USERS):
-        with open(DATADIR+FP_USERS[i]+'/'+newrhoana, 'rb') as f:
-            fp_newrhoana = pickle.load(f)
-            fp_outputs.append(fp_newrhoana)
-        with open(DATADIR+FP_USERS[i]+'/'+times, 'rb') as f:
-            fp_time = pickle.load(f)
-            fp_time = [int(v) for v in fp_time]
-            fp_times.append(fp_time)
-        with open(DATADIR+FP_USERS[i]+'/'+corrections, 'rb') as f:
-            fp_correction = pickle.load(f)       
-            fp_corrections.append(fp_correction)
-        with open(DATADIR+FP_USERS[i]+'/'+correction_vis, 'rb') as f:
-            fp_correction_vis = pickle.load(f) 
-            fp_vis.append(fp_correction_vis)
-
-    fp_times_mean = []
-    for t in fp_times:
-        fp_times_mean.append(np.mean(t))
-    print 'Avg. correction time',np.mean(fp_times_mean)
-
-    fp_corrections_mean = []
-    fp_accepted_corrections = []
-
[…]

### 2016-11-22 paper/supplemental/architecture.tex
Minor changes

@@
 We explored different architectures for the convolutional neural network (CNN) for split error detection.
-In table \ref{tab:architecture} we compare traditional CNN architectures versus residual networks~\cite{resnet}.
+We compare traditional CNN architectures versus residual networks~\cite{resnet} (Tab.~\ref{tab:architecture}).
 The traditional architecture with dropout regularization generalized better than residual networks on unseen testing data.
 
-\begin{table}[h]
+\begin{table}[t]
 \caption{Traditional CNN Architecture versus Residual Network Architecture \cite{resnet}.
@@
 
-We performed a limited brute force parameter search to tune the split error classifier (Tab.
-\ref{tab:parametersearch}).
+We performed a limited brute force parameter search to tune the split error classifier (Tab.~\ref{tab:parametersearch}).
 This resulted in 3240 different CNN configurations which were evaluated on 10\% of our training data.
@@
 
-\begin{table}[h]
+\begin{table}[t]
 \caption{Brute force parameter search for the split error classifier. The final parameters are highlighted.}%While the training of our classifier is more expensive, testing accuracy is superior. }
@@
 For automatic selection, we observed a threshold $p_t=0.95$ as stable when evaluating on previously unseen testing data (Mouse S1 AC3 Open Connectome Project dataset).
-This means, that automatic selection stops once all borders with $p_t\geq0.95$ were proofread.
-Fig.
-\ref{fig:pt} shows split error classification on three randomly selected subvolumes ($700\times700\times2$ voxels) of AC3.
+This means that automatic selection stops once all borders with $p_t\geq0.95$ were proofread.
+Figure~\ref{fig:cylboxplot} shows split error classification on three randomly selected subvolumes ($700\times700\times2$ voxels) of AC3.
 In all cases, the threshold $p_t=0.95$ reduces VI.

### 2016-11-23 cremiGP_A.py
Add cremi w/ limited merge.

@@ -1,0 +1,211 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
+OUTDIR = REGALDIR + 'CREMIBIG_A/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL_CREMI_FINAL.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_gold = []
+input_rhoana = []
+test_slices = range(0,5)# + range(25+20,50) + range(50+20,75)
+for z in test_slices:
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_gold.append(gold)
+    input_rhoana.append(rhoana)    
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+
+
+# find merge errors, if we did not generate them before
+# find merge errors, if we did not generate them before
+merge_error_file = '/n/regal/pfister_lab/haehn/CREMIBIG/merge_errors_5.p'
+if os.path.exists(merge_error_file):
+  print 'Loading merge errors from file..'
+  with open(merge_error_file, 'rb') as f:
+    merge_errors = pickle.load(f)
+
+print len(merge_errors), ' merge errors found.'
+
+
+
+
+bigM_cremi_file = '/n/regal/pfister_lab/haehn/CREMIBIG/bigM_gp.p'
+if os.path.exists(bigM_cremi_file):
+  print 'loading bigM'
+  with open(bigM_cremi_file, 'rb') as f:
+    bigM = pickle.load(f)
+    bigM = bigM[0:5]
+# else:
+#   print 'creating bigM'
+#   bigM = gp.Legacy.create_bigM_without_mask(cnn, input_image, input_prob, input_rhoana, verbose=True, max=1000000)
+#   with open(bigM_cremi_file, 'wb') as f:
+#     pickle.dump(bigM, f)  
+
+
+
+
+
+
+
+
+
+
+#
[…]

### 2016-11-23 cremiGP_B.py

@@ -1,0 +1,211 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
+OUTDIR = REGALDIR + 'CREMIBIG_B/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL_CREMI_FINAL.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_gold = []
+input_rhoana = []
+test_slices = range(25,30)# + range(25+20,50) + range(50+20,75)
+for z in test_slices:
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_gold.append(gold)
+    input_rhoana.append(rhoana)    
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+
+
+# find merge errors, if we did not generate them before
+# find merge errors, if we did not generate them before
+merge_error_file = '/n/regal/pfister_lab/haehn/CREMIBIG/merge_errors_30.p'
+if os.path.exists(merge_error_file):
+  print 'Loading merge errors from file..'
+  with open(merge_error_file, 'rb') as f:
+    merge_errors = pickle.load(f)
+
+print len(merge_errors), ' merge errors found.'
+
+
+
+
+bigM_cremi_file = '/n/regal/pfister_lab/haehn/CREMIBIG/bigM_gp.p'
+if os.path.exists(bigM_cremi_file):
+  print 'loading bigM'
+  with open(bigM_cremi_file, 'rb') as f:
+    bigM = pickle.load(f)
+    bigM = bigM[25:30]
+# else:
+#   print 'creating bigM'
+#   bigM = gp.Legacy.create_bigM_without_mask(cnn, input_image, input_prob, input_rhoana, verbose=True, max=1000000)
+#   with open(bigM_cremi_file, 'wb') as f:
+#     pickle.dump(bigM, f)  
+
+
+
+
+
+
+
+
+
+
+#
[…]

### 2016-11-23 cremiGP_C.py

@@ -1,0 +1,211 @@
+
+import gp
+
+import cPickle as pickle
+import numpy as np
+import os
+
+
+HOMEDIR = '/n/home05/haehn/'
+REGALDIR = '/n/regal/pfister_lab/haehn/'
+DATADIR = HOMEDIR + 'data/CREMIGP/TEST/'
+OUTDIR = REGALDIR + 'CREMIBIG_C/'
+
+#
+# load cnn
+#
+with open('nets/IPMLB_FULL_CREMI_FINAL.p', 'rb') as f:
+  cnn = pickle.load(f)
+cnn.uuid = 'IPMLB'
+
+#
+# load data
+#
+input_image = []
+input_prob = []
+input_gold = []
+input_rhoana = []
+test_slices = range(50,55)# + range(25+20,50) + range(50+20,75)
+for z in test_slices:
+    image, prob, gold, rhoana = gp.Util.read_cremi_section(os.path.expanduser('~/data/CREMIGP/TEST/'), z)
+    input_image.append(image)
+    input_prob.append(255.-prob)
+    input_gold.append(gold)
+    input_rhoana.append(rhoana)    
+
+original_mean_VI, original_median_VI, original_VI_s = gp.Legacy.VI(input_gold, input_rhoana)
+
+
+
+
+# find merge errors, if we did not generate them before
+# find merge errors, if we did not generate them before
+merge_error_file = '/n/regal/pfister_lab/haehn/CREMIBIG/merge_errors_55.p'
+if os.path.exists(merge_error_file):
+  print 'Loading merge errors from file..'
+  with open(merge_error_file, 'rb') as f:
+    merge_errors = pickle.load(f)
+
+print len(merge_errors), ' merge errors found.'
+
+
+
+
+bigM_cremi_file = '/n/regal/pfister_lab/haehn/CREMIBIG/bigM_gp.p'
+if os.path.exists(bigM_cremi_file):
+  print 'loading bigM'
+  with open(bigM_cremi_file, 'rb') as f:
+    bigM = pickle.load(f)
+    bigM = bigM[50:55]
+# else:
+#   print 'creating bigM'
+#   bigM = gp.Legacy.create_bigM_without_mask(cnn, input_image, input_prob, input_rhoana, verbose=True, max=1000000)
+#   with open(bigM_cremi_file, 'wb') as f:
+#     pickle.dump(bigM, f)  
+
+
+
+
+
+
+
+
+
+
+#
[…]

### 2016-11-23 gp/stats.py
Latest cremi results.

@@ -218,10 +218,22 @@ class Stats(object):
 
     dojo_best_vi = 0.33414926373414477
     cylinder_best_vi = 0.27683609273291143 # this is without the skipping border
+    cremi_A_best_vi = 0.92974989787739659
+    cremi_B_best_vi = 1.2940966349
+    cremi_C_best_vi = 1.45485772678
     # cylinder_best_vi = 0.3 # this is with skipping border
     if data == 'dojo':
       best_vi = dojo_best_vi  
       clampY = [0.32, 0.55]
+    elif data =='cremiA':
+      best_vi = cremi_A_best_vi
+      clampY = [0.85,1.1]
+    elif data =='cremiB':
+      best_vi = cremi_B_best_vi
+      clampY = [1.2,1.8]
+    elif data =='cremiC':
+      best_vi = cremi_C_best_vi
+      clampY = [1.35,1.96]
     else:
       best_vi = cylinder_best_vi
       clampY = [0.25, 0.5]
@@ -254,7 +266,7 @@ class Stats(object):
             fp_corrections.append(fp_correction)
         with open(DATADIR+FP_USERS[i]+'/'+correction_vis, 'rb') as f:
             fp_correction_vis = pickle.load(f) 
-            fp_vis.append(fp_correction_vis)
+            fp_vis.append(fp_correction_vis[1:])
 
     # return None, None, fp_vis
 
@@ -285,6 +297,7 @@ class Stats(object):
     first_split_vis = []
     last_split_vis = []
     for k,v in enumerate(fp_corrections):
+
         vis = [init_median_vi]
         merge_vis = [init_median_vi]
         split_vis = [init_median_vi]
@@ -309,7 +322,9 @@ class Stats(object):
                 # user accepted correction, now look up the vi
                 vi = fp_vis[k][correctionindex]
                 correctionindex += 1    
+
                 vis.append(np.median(vi))
+
 
                 if c[0] == 'merge':
                   merge_vis.append(vi)
@@ -337,11 +352,13 @@ class Stats(object):
         merge_vi_per_c_per_user.append(merge_vis)
         split_vi_per_c_per_user.append(split_vis)
 
+    #return fp_vi_per_c_per_user, merge_vis, split_vis, None
+
     # fig = plt.figure(figsize=(10,7))
[…]

### 2016-11-23 paper/supplemental/cremi.tex
Supplemental.

\section{Additional Experiments}
\label{sec:addexp}

\paragraph{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets were made publicly available\footnote{\scriptsize{\url{http://www.cremi.org}}},  each $1250\times1250\times125$ voxels. Since only three datasets include manually-labeled `ground truth', we use these three volumes for our experiments. The volumes are part of an adult fruit fly (Drosophila melanogaster) brain. The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$.

\paragraph{Retraining.} Since the CREMI data is a different species, we simply retrain our split error classifier as well as focused proofreading by Plaza~\cite{focused_proofreading}. For this, we use the first 100 sections of each of the three CREMI datasets combined as training data. All parameters are unchanged and left as reported in the paper.

\paragraph{Error correction.} In all three datasets merge error detection found over 300 merge errors. Unfortunately, merge error correction crashed because of a software error on our part. Therefore, we only evaluate split error detection and correction on subvolumes of CREMI A/B/C with the dimensions $1250\times1250\times5$ voxels. The subvolumes were cut from the last 25 sections of each of the three datasets and unseen during training. We compare focused proofreading and guided proofreading with automatic selection ($p_t=0.95$) and selection oracle.

\subsection{CREMI A}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiAtrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on 5 sections of the CREMI A dataset (split error correction only). All measurements are reported as median VI, the lower the better. The threshold for automatic selection is $p_t=0.95$ (red line). The slope of the selection oracle shows that guided proofreading reduces VI faster.}
\label{fig:cremiAtrails}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiAboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the CREMI A dataset, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $5.4\times$ higher than GP (as indicated by the arrow), with median VI of $5.32$ and $SD=0.009$. GP does not reach the best possible VI as discussed in the text.}
\label{fig:cremiAboxplot}
\end{figure}

Figure~\ref{fig:cremiAtrails} and~\ref{fig:cremiAboxplot} compare Plaza's focused proofreading and guided proofreading on the 5 sections of the CREMI A dataset.

\paragraph{Selection oracle.} With focused proofreading, the selection oracle reduces median VI to 0.928, $SD=0.043$ from an initial median VI of 1.06 ($SD=0.055$). 532 corrections out of 3707 were accepted. Guided proofreading does not reach the best possible VI, however, reduces VI faster with less corrections to 0.941 ($SD=0.04$). Out of 4463 corrections, 1275 were accepted.

\paragraph{Automatic selection with threshold.} Not surprisingly, focused proofreading performs poorly when ran automatically (VI of 5.32, $SD=0.009$). Guided proofreading is able to reduce VI to 0.989 ($SD=0.043$) with $p_t=0.95$.

\subsection{CREMI B}

Figure~\ref{fig:cremiBtrails} and~\ref{fig:cremiBboxplot} show the results on the CREMI B dataset.

\paragraph{Selection oracle.} Focused proofreading is able to reduce median VI to 1.29, $SD=0.031$ from an initial median VI of 1.63 ($SD=0.025$). Out of 1959 corrections, the selection oracle accepted 517. With guided proofreading, the median VI is reduced to 1.30, $SD=0.03$ while accepting 1111 corrections out of 3073.

\paragraph{Automatic selection with threshold.} Focused proofreading results in a VI of 4.25 ($SD=0.07$). Guided proofreading reduces median VI to 1.43 ($SD=0.038$).

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiBtrails.pdf}
\caption{Split error correction by Plaza's focused proofreading and our guided proofreading compared on the CREMI B dataset. All measurements are reported as median VI, the lower the better. Automatic selection with threshold (red line) yields reasonable performance using guided proofreading.}
\label{fig:cremiBtrails}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiBboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across 5 sections of the CREMI B dataset. We compare automatic selection and oracle selection. The variation resulting from performance of FP with automatic selection is $3\times$ higher than GP (as indicated by the arrow), with median VI of $4.25$ and $SD=0.07$.}
\label{fig:cremiBboxplot}
\end{figure}

\subsection{CREMI C}

The results of split error correction using focused proofreading and guided proofreading on the CREMI C subvolume are shown in Figure~\ref{fig:cremiCtrails} and~\ref{fig:cremiCboxplot}.

\paragraph{Selection oracle.} With focused proofreading, the initial median VI of 1.75 ($SD=0.086$) is reduced to 1.45 ($SD=0.056$) with 670 accepted corrections out of 2694. Guided proofreading is able to reduce the VI to 1.47 ($SD=0.06$). Here, the oracle accepted 1531 out of 4332 corrections.

\paragraph{Automatic selection with threshold.} Focused proofreading results in a VI of 4.81 ($SD=0.03$). Guided proofreading with $p_t=0.95$ reduces median VI to 1.57 ($SD=0.081$).

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiCtrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the CREMI C dataset (only split error correction). Lower VI scores are better. Guided proofreading corrects the initial segmentation faster with less corrections than focused proofreading.}
\label{fig:cremiCtrails}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiCboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across the CREMI C subvolume, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $3\times$ higher than GP (as indicated by the arrow), with median VI of $4.81$ and $SD=0.08$.}
\label{fig:cremiCboxplot}
\end{figure}

### 2016-11-23 paper/supplemental/leftcylinder.tex
Supplemental.

@@
 \section{L. Cylinder Results}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\linewidth]{gfx/datasets.pdf}
+\caption{The five different datasets we use for evaluation.
+The top row shows the first slice of the AC4 and L.
+Cylinder mouse brain datasets as reported in the paper.
+The bottom row shows the first slice of the CREMI A/B/C fruit fly datasets which we used for additional experiments.}
+\label{fig:datasets}
+\end{figure}
+
+We report experiments and results on the L.
+Cylinder dataset in the paper.
+Figure~\ref{fig:cyltrails} and~\ref{fig:cylboxplot} visualize the reported results measured as variation of information (VI).
+We compare automatic selection with threshold and selection oracle using focused proofreading and guided proofreading.
+
+\paragraph{Best possible VI.} The selection oracle using guided proofreading does not reach the best possible VI score.
+We calculate this score by intersecting the initial segmentation and the ground truth.
+In theory, the classifier should be able to reach this lower bound.
+However, the membrane probability maps we use include a 30 pixel frame region because of the used classification patch size.
+Guided proofreading ignores all segments within this frame region and can not reach the best possible VI in some datasets.
 
@@
 \caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the L.
-Cylinder dataset.
-All measurements are reported as median VI, the lower the better.
-We compare automatic selection with threshold and the selection oracle for accepting or rejecting corrections using each method.
-In all cases, guided proofreading yields better results with fewer corrections.}
-\label{fig:cylboxplot}
+Cylinder dataset as reported in the paper.
+All measurements are shown as median VI, the lower the better.
+We compare automatic selection with threshold ($p_t=0.95$, red line) and the selection oracle for accepting or rejecting corrections using each method.
+Guided proofreading yields better results faster with fewer corrections.}
+\label{fig:cyltrails}
 \end{figure}
@@
 \centering
-\includegraphics[width=.7\linewidth]{gfx/cylboxplot.pdf}
+\includegraphics[width=\linewidth]{gfx/cylboxplot.pdf}
 \caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the L.

### 2016-11-23 paper/supplemental/userstudy.tex
Some more supplemental stuff.
Supplemental.

@@
 
-flyers, participant list
+Novice participants were recruited via flyer (figure~\ref{fig:flyer}). An anonymized listing of all participants including demographic information is shown in table~\ref{tab:participants}.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\linewidth]{gfx/flyer_anon.pdf}
+\caption{Participants were recruited with this flyer.}
+\label{fig:flyer}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\linewidth]{gfx/NASA_TXL.pdf}
+\caption{The NASA-TLX workload index to record subjective responses.}
+\label{fig:nasatxl}
+\end{figure}
+
+\begin{table}[t]
+\caption{The novice participants ($N=20$) of the forced choice user experiment.
+The table shows sex (20 female), age ($M=30$) and the randomly assigned classifier (focused proofreading as FP, guided proofreading as GP).}%While the training of our classifier is more expensive, testing accuracy is superior.
+}
+
+\small{
+\begin{tabular}{@{}l|c|c|c@{}}
+	\toprule
+     \textbf{ID} & \textbf{Sex} &  \textbf{Age} & \textbf{Classifier}  \\ \midrule	
+S38 &		F & 20 & FP \\
+S57&		F & 30 & FP \\ 
+S32&		M & 38 & FP \\
+S34&		F & 21 & FP \\
+S21&		F & 65 & FP \\
+S9 &	M & 33 & FP \\
+S45 &		M & 28 & FP \\
+S31&		M & 27 & FP \\
+S24&		F & 21 & FP \\
+S6	&	F & 38 & FP \\
+S28	&	M&	32& GP \\
+S36	&	F&	19& GP \\
+S35	&	M&	26& GP \\
+S25	&	M&	26& GP \\
+S54	&	F&	30& GP \\
+S53	&	M&	29& GP \\
+S52	&	M	&27& GP \\
+S51&		M&	31& GP \\
+S200	 &	F	&37& GP \\
+S3	 &F&	30 & GP
+
+\end{tabular}
+\hspace{2mm}
+\hrule
+}
+\label{tab:participants}
+\end{table}
 
@@
 
-Where did users make a mistake?
+During the user study, participants were asked to accept or reject potential errors and their corrections --- some more difficult than others.
+Figure~\ref{fig:patches} shows a selection of potential errors and their corrections.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\linewidth]{gfx/patches.pdf}
+\caption{A selection of suggested errors and potential corrections during the forced choice user experiment.
+The star (*) indicates which choice reduces VI.
+While all participants were able to correctly choose for patch A, only few were able to correctly choose for patch B and C.}
+\label{fig:patches}
+\end{figure}
 
@@
 
-NASA TLX ANOVA analysis
+After the experiment, we acquired subjective responses using the NASA-TLX task load index (figure~\ref{fig:nasatxl}).
+We performed ANOVA to test for statistical significance~\cite{shaffer1995}.
+Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading but the analysis did not yield any significance.
+
+\begin{itemize}
+\item \textbf{Mental Demand.} Participants using focused proofreading stated a higher mental demand $M=11.5$ ($SD=2.098$) than with guided proofreading $M=8.1$ ($SD=2.003$).
+This was not statistically significant ($F_{1,18}=3.2574, p=0.3695$).
+\item \textbf{Physical Demand.} While naturally physical demand was rated low, participants using focused proofreading stated it slightly higher $M=5.4$ ($SD=2.26$) than with guided proofreading $M=2.9$ ($SD=1.76$).
+This was not statistically significant ($F_{1,18}=1.7507, p=0.5454$).
+\item \textbf{Temporal Demand.} For temporal demand, participants using focused proofreading $M=8.4$ ($SD=1.95$) reported almost equal to guided proofreading $M=8.3$ ($SD=1.99$).
+This was not statistically significant ($F_{1,18}=0.0033, p=0.9987$).
+\item \textbf{Performance.} Here, participants were asked to rate their own performance.
+All participants rated their performance as pretty well (the lower, the better).
+For focused proofreading $M=6.8$ ($SD=1.97$) and for guided proofreading $M=7.8$ ($SD=2.04$).
+This was not statistically significant ($F_{1,18}=0.3091, p=0.8878$).
+\item \textbf{Effort.} Participants using focused proofreading stated higher effort $M=13.0$ ($SD=2.336$) than with guided proofreading $M=10.6$ ($SD=2.127$).
+This was not statistically significant ($F_{1,18}=1.1459, p=0.6599$).
+\item \textbf{Frustration.} Participants overall reported low frustration.
+Reported were $M=5.0$ ($SD=1.90$) using focused proofreading and $M=5.9$ ($SD=185$) using guided proofreading.
+This was not statistically significant ($F_{1,18}=0.3271, p=0.8818$).
+\end{itemize}

### 2016-11-23 paper/supplemental/cremi.tex
James proof

@@
 The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$.
+We evaluate error detection and correction on subvolumes of CREMI A/B/C with the dimensions $1250\times1250\times5$ voxels.
+The subvolumes were cut from the last 25 sections of each of the three datasets and unseen during training.
+We compare focused proofreading and guided proofreading with automatic selection ($p_t=0.95$) and selection oracle.
 
@@
 
-\paragraph{Error correction.} In all three datasets merge error detection found over 300 merge errors.
+%\paragraph{Error correction.} In all three datasets merge error detection found over 300 merge errors.
 Unfortunately, merge error correction crashed because of a software error on our part.

### 2016-11-23 paper/supplemental/leftcylinder.tex
James proof

@@
 \caption{The five different datasets we use for evaluation.
-The top row shows the first slice of the AC4 and L.
-Cylinder mouse brain datasets as reported in the paper.
+The top row shows the first slice of the AC4 and L.~Cylinder mouse brain datasets as reported in the paper.
 The bottom row shows the first slice of the CREMI A/B/C fruit fly datasets which we used for additional experiments.}
@@
 
-We report experiments and results on the L.
-Cylinder dataset in the paper.
+We report experiments and results on the L.~Cylinder dataset in the paper.
 Figure~\ref{fig:cyltrails} and~\ref{fig:cylboxplot} visualize the reported results measured as variation of information (VI).
@@
 In theory, the classifier should be able to reach this lower bound.
-However, the membrane probability maps we use include a 30 pixel frame region because of the used classification patch size.
-Guided proofreading ignores all segments within this frame region and can not reach the best possible VI in some datasets.
+However, due to the classification patch size, the membrane probability maps we used included a 30 pixel frame region.
+Guided proofreading ignores all segments within this frame region, and so cannot reach the best possible VI in some datasets.
 
@@
 \includegraphics[width=\linewidth]{gfx/cyltrails.pdf}
-\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the L.
-Cylinder dataset as reported in the paper.
+\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the L.~Cylinder dataset as reported in the paper.
 All measurements are shown as median VI, the lower the better.
@@
 \includegraphics[width=\linewidth]{gfx/cylboxplot.pdf}
-\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the L.
-Cylinder dataset, with different error correction approaches.
+\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the L.~Cylinder dataset, with different error correction approaches.
 The variation resulting from performance of FP with automatic selection is $7.8\times$ higher than GP (as indicated by the arrow), with median VI of $2.75$ and $SD=0.789$.}

### 2016-11-23 paper/supplemental/cremi.tex
Ready for submission.

@@
 \includegraphics[width=\linewidth]{gfx/cremiAtrails.pdf}
-\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on 5 sections of the CREMI A dataset (split error correction only).
+\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on 5 sections of the CREMI A dataset.
 All measurements are reported as median VI, the lower the better.
@@
 \includegraphics[width=\linewidth]{gfx/cremiCtrails.pdf}
-\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the CREMI C dataset (only split error correction).
+\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the CREMI C dataset.
 Lower VI scores are better.

### 2017-01-27 ui/manager.py
Add printing of VI for demo purposes.

@@ -285,7 +285,7 @@ class Manager(object):
         self._input_rhoana[z] = new_rhoana
 
         vi = UITools.VI(self._input_gold, input_rhoana)
-        # print 'New global VI', vi[1]
+        print 'New global VI', vi[0]
         self._correction_vis.append(vi[2])        
 
         #
@@ -301,7 +301,7 @@ class Manager(object):
         new_m[:,:] = -1
         new_m[0:-2,0:-2] = self._bigM[z]
 
-        print 'adding', label1, 'to', z
+        #print 'adding', label1, 'to', z
 
         new_m = gp.Legacy.add_new_label_to_M(self._cnn, new_m, input_image[z], input_prob[z], new_rhoana, label1)
         new_m = gp.Legacy.add_new_label_to_M(self._cnn, new_m, input_image[z], input_prob[z], new_rhoana, label2)

### 2017-01-27 paper/rebuttal/egrebuttal.tex
Added template and some stucture.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{0947} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Guided Proofreading of Automatic Segmentations for Connectomics}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

Thank you for your constructive comments. We will fix all minor issues.

\section{Quantitative Evaluation}

\section{Reproducibility}

\section{Optimal Parameters}

\section{Training Data Sets}

\section{Faster Correction Times}

\section{Merge Error Detection}

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{gfx/merge_error_v4.pdf}
\caption{Updated Figure 4. (not yet)}
\label{fig:merge_error}
\end{figure}

\section{}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2017-01-27 paper/rebuttal/egrebuttal.tex
More rebuttal.

@@
 \usepackage{amssymb}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{booktabs}
+\usepackage{makecell}
 
@@
 
-Thank you for your constructive comments. We will fix all minor issues.
+Thank you for your constructive comments. We will fix all minor issues. We would like to clarify the following major remarks.
 
 \section{Quantitative Evaluation}
+Reviewer 2 requests an objective quantitative evaluation.
+We define such experiments in line 573-590 and report the results in Fig.~6, Fig.~7 and line 792-818 (also in supplemental Sec.~2 and 3).
+The evaluation is fully numeric and we report VI scores.
+We will change the wording in the manuscript to make this more clear.
 
 \section{Reproducibility}
+Reviewer 2 expresses concerns regarding reproducibility. However, we define all parameters in the manuscript and promise to release code and data (line 847).
 
 \section{Optimal Parameters}
+Reviewer 2
 
-\section{Training Data Sets}
+\section{Training Data Sets U-net vs. GP}
+Reviewer 3 raises the question if GP was trained on the same data as membrane detection (U-net). There was no overlap in training the classifiers (Tab.~\ref{tab:trainingdata}).
+
+\begin{table}[h]
+\caption{Training data of membrane detection vs. taining data of GP (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrr}
+\toprule
+Dataset & \makecell{Training Set\\Membrane Detection (U-Net)} & \makecell{Training Set\\Guided Proofreading} \\ 
+\midrule
+\makecell{\emph{L. Cylinder}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} \\ 
+\makecell{\emph{AC4 subvolume}\\~} & \makecell{AC4 excl. test\\ ($1024\times1024\times90$vx)} &  \makecell{L. Cylinder\\ ($2048\times2048\times250$vx)} \\ 
+\makecell{\emph{CREMI A/B/C}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} \\ 
+\bottomrule
+\end{tabular} 
+}
+\label{tab:trainingdata}
+\end{table}
 
 \section{Faster Correction Times}
+There seems to be a misunderstanding
 

### 2017-01-27 paper/rebuttal/egrebuttal.tex
Getting there.

@@
 
-Thank you for your constructive comments. We will fix all minor issues. We would like to clarify the following major remarks.
+Thank you for your constructive comments. We will fix all minor issues. We would like to clarify and correct the following major remarks.
 
@@
 Reviewer 2 requests an objective quantitative evaluation.
-We define such experiments in line 573-590 and report the results in Fig.~6, Fig.~7 and line 792-818 (also in supplemental Sec.~2 and 3).
+We define such experiments in lines 573-590 and report the results in Fig.~6, Fig.~7 and lines 792-818 (also in supplemental Sec.~2 and 3).
 The evaluation is fully numeric and we report VI scores.
-We will change the wording in the manuscript to make this more clear.
+We will change the wording in the manuscript to emphasize this.
 
@@
 
-\section{Training Data Sets U-net vs. GP}
-Reviewer 3 raises the question if GP was trained on the same data as membrane detection (U-net). There was no overlap in training the classifiers (Tab.~\ref{tab:trainingdata}).
+\section{Training Datasets U-net vs. GP}
+Reviewer 3 raises the question if GP was trained on the same data as membrane detection (U-net). There was no overlap (Tab.~\ref{tab:trainingdata}).
 
 \begin{table}[h]
-\caption{Training data of membrane detection vs. taining data of GP (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
+\caption{Training data of membrane detection vs. training data of GP (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
 \resizebox{\linewidth}{!}{
@@
 
-\section{Faster Correction Times}
-There seems to be a misunderstanding
+\section{Faster Proofreading}
+We agree with reviewer 2 that our claim that GP enables faster proofreading is not clearly presented.
+We report the average correction times for novice users in lines 756-765.
+Figure 7 (column 3) shows VI reduction after 30 minutes and the slopes in figure 6 also indicate better performance for GP.
+However, this presentation is not ideal and we will add Tab.~\ref{tab:correctiontimes} to the paper.
+
+\begin{table}[h]
+\caption{Average proofreading speed for novice users of Dojo, FP and GP.
+Higher VI reduction per minute shows better performance of GP.}%While the training of our classifier is more expensive, testing accuracy is superior.
+}
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrr}
+\toprule
+ & \makecell{Correction Time [s]} & \makecell{VI Reduction per minute} \\
+\midrule
+\emph{Dojo} & 30.5 & -0.002 \\
+\emph{FP} & 4.9 & 0.00023 \\
+\emph{GP} & 6.2 & 0.00173 \\
+\bottomrule
+\end{tabular} 
+}
+\label{tab:correctiontimes}
+\end{table}
 
 \section{Merge Error Detection}
+
+Reviewer 3 suggests a better explanation of the merge error detection.
+We updated figure 4 in the paper to include the watershed seeds (Fig.
+1).
+We will also add a pseudo code description of the algorithm to the supplemental material.
+We hope that this will make this part easier to understand.
 
@@
 \includegraphics[width=\linewidth]{gfx/merge_error_v4.pdf}
-\caption{Updated Figure 4. (not yet)}
+\caption{Updated figure 4, including the random watershed seeds. (TODO)}
 \label{fig:merge_error}
@@
 
-\section{}
+\section{GALA Active Learning Classifier}
 
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
+We use GALA in our automatic segmentation pipeline (line 499).
+GALA uses a random forest classifier to agglomerate segments.
+While it does not require user interaction, it requires parameters.
+We will either add a reference to our yet unpublished segmentation pipeline or add a section to the supplemental material describing it in more detail as requested by reviewer 3.
+
+%{\small
+%\bibliographystyle{ieee}
+%\bibliography{egbib}
+%}
 

### 2017-01-27 paper/rebuttal/egrebuttal.tex
Update rebuttal.

@@
 \section{Faster Proofreading}
-We agree with reviewer 2 that our claim that GP enables faster proofreading is not clearly presented.
-We report the average correction times for novice users in lines 756-765.
+We agree with reviewer 2 that our results regarding faster proofreading with GP are not clearly presented. 
+%We report the average correction times for novice users in lines 756-765.
 Figure 7 (column 3) shows VI reduction after 30 minutes and the slopes in figure 6 also indicate better performance for GP.
-However, this presentation is not ideal and we will add Tab.~\ref{tab:correctiontimes} to the paper.
+However, this presentation is not ideal and
+We will add Tab.~\ref{tab:correctiontimes} to the paper (previously reported in lines 756-765, slopes in figure 6, column 3 in figure 7) to better present our findings.
 
@@
 1).
-We will also add a pseudo code description of the algorithm to the supplemental material.
-We hope that this will make this part easier to understand.
+We will also add a pseudo code description of the algorithm to the supplemental material to promote understanding.
 
@@
 \includegraphics[width=\linewidth]{gfx/merge_error_v4.pdf}
-\caption{Updated figure 4, including the random watershed seeds. (TODO)}
+\caption{Updated figure 4 to include the random watershed seeds. (TODO)}
 \label{fig:merge_error}

### 2017-01-27 paper/rebuttal/egrebuttal.tex
Finish the last sections of the rebuttal which can now be optimized.

@@
 
-Thank you for your constructive comments. We will fix all minor issues. We would like to clarify and correct the following major remarks.
+Thank you for your constructive comments. We will fix all minor issues. We would like to clarify the following major remarks.
 
@@
 \section{Optimal Parameters}
-Reviewer 2
+We define several parameters in the paper. However, we agree with reviewer 2 that finding the optimal values could be better explained and will synchronize this information with the paper. 
+The \textbf{threshold $p_t=0.95$} was observed to be stable when evaluating on previously unseen testing data (lines 585-586, supplemental Sec.
+1.3).
+The \textbf{input border is dilated by 5 pixels} to consider slight edge ambiguities and to cover extra-cellular space between segments in high-resolution electron microscopy data (lines 308-310).
+During merge error detection, \textbf{labels are dilated by 20 pixels} prior to finding potential borders (line 323) with border-seeded watershed---this way the borders tend to attach to real membrane boundaries (lines 364-366).
+%Here, we list all parameters and describe how their values are obtained. We will synchronize this information with the paper.
+
+%
+%\begin{itemize}
+%\item \textbf{Threshold $p_t$.} The threshold $p_t=0.95$ was observed to be stable when evaluating on previously unseen testing data (lines 585-586, supplemental Sec. 1.3).
+%\item \textbf{Dilated Boundary Input.} We dilate the border between segments by 5 pixels to consider slight edge ambiguities and to cover extra-cellular space between segments in high-resolution electron microscopy data (lines 308-310).
+%\item \textbf{Dilated Label.} During merge error detection, labels are dilated by 20 pixels prior to finding potential borders (line 323) with border-seeded watershed.
+By doing so, the borders tend to attach to real membrane boundaries (lines 364-366).
+%\end{itemize}
+
+%\begin{table}[h]
+%\caption{Parameters of GP, their values and how these values are obtained.}%While the training of our classifier is more expensive, testing accuracy is superior. }
+%\resizebox{\linewidth}{!}{
+%\begin{tabular}{l}
+%\toprule
+%Threshold $p_t=0.95$, Observed on previously unseed testing data (lines 585-586, supplemental Sec. 1.3) \\ 
+%\bottomrule
+%\end{tabular} 
+%}
+%\label{tab:parameters}
+%\end{table}
 
@@
 1).
-We will also add a pseudo code description of the algorithm to the supplemental material to promote understanding.
+We will also add a pseudo code version of the algorithm to the supplemental material to promote understanding.
 

### 2017-01-29 paper/rebuttal/egrebuttal.tex
Minor changes and updated the figure with random seeds.

@@
 \section{Optimal Parameters}
-We define several parameters in the paper. However, we agree with reviewer 2 that finding the optimal values could be better explained and will synchronize this information with the paper. 
+We define several parameters in the paper.
+However, we agree with reviewer 2 that finding the optimal values requires better explanations and we will synchronize the following information with the paper.
 The \textbf{threshold $p_t=0.95$} was observed to be stable when evaluating on previously unseen testing data (lines 585-586, supplemental Sec.
@@
 \toprule
-Dataset & \makecell{Training Set\\Membrane Detection (U-Net)} & \makecell{Training Set\\Guided Proofreading} \\ 
+%Dataset & \makecell{Training Set\\Membrane Detection (U-Net)} & \makecell{Training Set\\Guided Proofreading} \\ 
+Dataset & \makecell{Training Set\\U-Net} & \makecell{Training Set\\GP} \\ 
 \midrule
 \makecell{\emph{L. Cylinder}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} \\ 
-\makecell{\emph{AC4 subvolume}\\~} & \makecell{AC4 excl. test\\ ($1024\times1024\times90$vx)} &  \makecell{L. Cylinder\\ ($2048\times2048\times250$vx)} \\ 
+\makecell{\emph{AC4 subvolume}\\~} & \makecell{AC4 excl. test\\ ($1k\times1k\times90$vx)} &  \makecell{L. Cylinder\\ ($2048\times2048\times250$vx)} \\ 
 \makecell{\emph{CREMI A/B/C}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} \\ 
@@
 \section{Faster Proofreading}
-We agree with reviewer 2 that our results regarding faster proofreading with GP are not clearly presented. 
+We agree with reviewer 2 that we present the results for faster proofreading with GP poorly. 
 %We report the average correction times for novice users in lines 756-765.
@@
 \centering
-\includegraphics[width=\linewidth]{gfx/merge_error_v4.pdf}
-\caption{Updated figure 4 to include the random watershed seeds. (TODO)}
+\includegraphics[width=\linewidth]{gfx/merge_error_v5.pdf}
+\caption{Updated figure 4 including the random watershed seeds (yellow).}
 \label{fig:merge_error}

### 2017-01-29 paper/rebuttal/egrebuttal.tex
First few changes from James' rebuttal pass.

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{Guided Proofreading of Automatic Segmentations for Connectomics}  % **** Enter the paper title here
+\title{Rebuttal for `Guided Proofreading of Automatic Segmentations for Connectomics'}  % **** Enter the paper title here
 
@@
 
-Thank you for your constructive comments. We will fix all minor issues. We would like to clarify the following major remarks.
+Thank you for your constructive comments. We will fix all minor issues.
 
-\section{Quantitative Evaluation}
-Reviewer 2 requests an objective quantitative evaluation.
-We define such experiments in lines 573-590 and report the results in Fig.~6, Fig.~7 and lines 792-818 (also in supplemental Sec.~2 and 3).
-The evaluation is fully numeric and we report VI scores.
-We will change the wording in the manuscript to emphasize this.
+\paragraph{R2: Quantitative Evaluation}
+R2 requests an objective quantitative evaluation.
+Fortunately, our `automatic' and `oracle' experiments are exactly this.
+We define such experiments in lines 573--590 and report the results in Fig.~6, Fig.~7, and lines 792--818 (also in supplemental Sec.~2 and 3).
+These evaluations use the quantitative VI metric against a ground truth segmentation, with no user in the loop.
 
-\section{Reproducibility}
-Reviewer 2 expresses concerns regarding reproducibility. However, we define all parameters in the manuscript and promise to release code and data (line 847).
+\paragraph{R2: Faster than State of the Art?}
+%We report the average correction times for novice users in lines 756-765.
+Figure 7 (column 3) shows VI reduction after 30 minutes and the slopes in figure 6 also indicate better performance for GP.
+However, this presentation is not ideal and
+Our approach \emph{is} faster, but our presentation of this discovery could have been improved.
+We will add Table~\ref{tab:correctiontimes} to make this clearer (previously reported in lines 756-765, slopes in Fig.~6, and column 3 in Fig.~7).
 
-\section{Optimal Parameters}
+\begin{table}[h]
+\caption{Average proofreading speed for users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP).
+For comparable correction time, our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP.}%While the training of our classifier is more expensive, testing accuracy is superior.
+}
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrr}
+\toprule
+ & \makecell{Correction Time [s]} & \makecell{VI reduction per minute} \\
+\midrule
+\emph{Dojo} & 30.5 & -0.002 \\
+\emph{Dojo Expert?} & xxx & xxx \\
+\emph{FP} & 4.9 & 0.00023 \\
+\emph{GP} & 6.2 & 0.00173 \\
+\bottomrule
+\end{tabular} 
+}
+\label{tab:correctiontimes}
+\end{table}
+
+\paragraph{R2: Reproducibility}
+R2 expresses concerns regarding reproducibility. As per line 847, we have promised to release all our code and data, and we disclose all of our parameters.
+
+\paragraph{R2: Optimal Parameters}
 We define several parameters in the paper.
@@
 
-\section{Training Datasets U-net vs. GP}
+\paragraph{R3: Training Datasets U-net vs. GP}
 Reviewer 3 raises the question if GP was trained on the same data as membrane detection (U-net). There was no overlap (Tab.~\ref{tab:trainingdata}).
@@
 
-\section{Faster Proofreading}
-We agree with reviewer 2 that we present the results for faster proofreading with GP poorly. 
-%We report the average correction times for novice users in lines 756-765.
-Figure 7 (column 3) shows VI reduction after 30 minutes and the slopes in figure 6 also indicate better performance for GP.
-However, this presentation is not ideal and
-We will add Tab.~\ref{tab:correctiontimes} to the paper (previously reported in lines 756-765, slopes in figure 6, column 3 in figure 7) to better present our findings.
-
-\begin{table}[h]
-\caption{Average proofreading speed for novice users of Dojo, FP and GP.
-Higher VI reduction per minute shows better performance of GP.}%While the training of our classifier is more expensive, testing accuracy is superior.
-}
-\resizebox{\linewidth}{!}{
-\begin{tabular}{lrrrr}
-\toprule
- & \makecell{Correction Time [s]} & \makecell{VI Reduction per minute} \\
-\midrule
-\emph{Dojo} & 30.5 & -0.002 \\
-\emph{FP} & 4.9 & 0.00023 \\
-\emph{GP} & 6.2 & 0.00173 \\
-\bottomrule
-\end{tabular} 
-}
-\label{tab:correctiontimes}
-\end{table}
-
-\section{Merge Error Detection}
+\paragraph{R3: Merge Error Detection}
 
@@
 
-\section{GALA Active Learning Classifier}
+\paragraph{R3: GALA Active Learning Classifier}
 

### 2017-01-29 paper/rebuttal/egrebuttal.tex
Few more changes to the rebuttal from James' pass.

@@
 
-Thank you for your constructive comments. We will fix all minor issues.
+Thank you for your time and constructive comments. We will fix all minor issues.
 
@@
 However, this presentation is not ideal and
-Our approach \emph{is} faster, but our presentation of this discovery could have been improved.
+`Faster' here considers both how long each correction takes, and the likely VI reduction from that correction.
+Our approach has comparable correction time to the state-of-the-art Focused Proofreading appraoch, but a significantly greater VI reduction per correction (7.5$\times$).
+Our presentation of this discovery could have been improved.
 We will add Table~\ref{tab:correctiontimes} to make this clearer (previously reported in lines 756-765, slopes in Fig.~6, and column 3 in Fig.~7).
@@
 \toprule
- & \makecell{Correction Time [s]} & \makecell{VI reduction per minute} \\
+Approach & \makecell{Time Per Correction (s)} & \makecell{VI Reduction Per Minute} \\
 \midrule
@@
 \paragraph{R2: Reproducibility}
-R2 expresses concerns regarding reproducibility. As per line 847, we have promised to release all our code and data, and we disclose all of our parameters.
+R2 expresses concerns regarding reproducibility. As per line 847, we have promised to release all our code and data, and we disclose all parameters.
 
-\paragraph{R2: Optimal Parameters}
-We define several parameters in the paper.
-However, we agree with reviewer 2 that finding the optimal values requires better explanations and we will synchronize the following information with the paper.
-The \textbf{threshold $p_t=0.95$} was observed to be stable when evaluating on previously unseen testing data (lines 585-586, supplemental Sec.
+\paragraph{R2: How were Optimal Parameters Chosen?}
+The \textbf{threshold $p_t=0.95$} was observed to be stable when evaluating on previously-unseen test data (lines 585-586, supplemental Sec.
 1.3).
@@
 During merge error detection, \textbf{labels are dilated by 20 pixels} prior to finding potential borders (line 323) with border-seeded watershed---this way the borders tend to attach to real membrane boundaries (lines 364-366).
+As we use a CNN, there are many additional parameters; we consider choosing these effectively to be an open problem, and for this we used learned experience and local brute-force searches.
 %Here, we list all parameters and describe how their values are obtained. We will synchronize this information with the paper.
+%We define several parameters in the paper.
+However, we agree with reviewer 2 that finding the optimal values requires better explanations and we will synchronize the following information with the paper.
 
@@
 
-\paragraph{R3: Training Datasets U-net vs. GP}
-Reviewer 3 raises the question if GP was trained on the same data as membrane detection (U-net). There was no overlap (Tab.~\ref{tab:trainingdata}).
+\paragraph{R3: Training Datasets---U-net vs.~GP?}
+R3 raises the question of whether our GP approach was trained on the same data as membrane detection (U-net). There was no overlap (Tab.~\ref{tab:trainingdata}).
 
 \begin{table}[h]
-\caption{Training data of membrane detection vs. training data of GP (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
+\caption{Training data of membrane detection vs.~training data of GP (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
 \resizebox{\linewidth}{!}{
@@
 \makecell{\emph{L. Cylinder}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} \\ 
-\makecell{\emph{AC4 subvolume}\\~} & \makecell{AC4 excl. test\\ ($1k\times1k\times90$vx)} &  \makecell{L. Cylinder\\ ($2048\times2048\times250$vx)} \\ 
+\makecell{\emph{AC4 subvolume}\\~} & \makecell{AC4 excl. test\\ ($1000\times1000\times90$vx)} &  \makecell{L. Cylinder\\ ($2048\times2048\times250$vx)} \\ 
 \makecell{\emph{CREMI A/B/C}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} \\ 
@@
 \paragraph{R3: Merge Error Detection}
-
-Reviewer 3 suggests a better explanation of the merge error detection.
-We updated figure 4 in the paper to include the watershed seeds (Fig.
+R3 requests a better explanation of the merge error detection.
+We have updated Figure 4 in the main paper to include the watershed seeds (Fig.
 1).
@@
 \includegraphics[width=\linewidth]{gfx/merge_error_v5.pdf}
-\caption{Updated figure 4 including the random watershed seeds (yellow).}
+\caption{Updated Figure 4 including the random watershed seeds (yellow).}
 \label{fig:merge_error}
@@
 \paragraph{R3: GALA Active Learning Classifier}
-
-We use GALA in our automatic segmentation pipeline (line 499).
-GALA uses a random forest classifier to agglomerate segments.
-While it does not require user interaction, it requires parameters.
-We will either add a reference to our yet unpublished segmentation pipeline or add a section to the supplemental material describing it in more detail as requested by reviewer 3.
+In our automatic segmentation pipeline (line 499), GALA uses a random forest classifier to agglomerate segments.
+While it does not require user interaction, it does require parameters.
+We will add a section to the supplemental material containing a full description of the approach and our use of it.
+%either add a reference to our yet unpublished segmentation pipeline or
 

### 2017-01-30 paper/rebuttal/egrebuttal.tex
Add pseudocode (two versions, let's see which one is better).

@@
 \usepackage{makecell}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 
@@
 \emph{Dojo} & 30.5 & -0.002 \\
-\emph{Dojo Expert?} & xxx & xxx \\
+%\emph{Dojo Expert?} & xxx & xxx \\
 \emph{FP} & 4.9 & 0.00023 \\
@@
 
-\paragraph{R2: How were Optimal Parameters Chosen?}
+\paragraph{R2: How were Optimal Parameters chosen?}
 The \textbf{threshold $p_t=0.95$} was observed to be stable when evaluating on previously-unseen test data (lines 585-586, supplemental Sec.
@@
 1).
-We will also add a pseudo code version of the algorithm to the supplemental material to promote understanding.
+We will also add a pseudo code version of the algorithm to the supplemental material to promote understanding (Alg.
+\ref{code:mergeerror}).
 
@@
 \end{figure}
+
+\begin{algorithm}
+\caption{Merge Error Detection for label \emph{l}}\label{code:mergeerror}
+\begin{algorithmic}[1]
+%\State{mergeErrors = []}
+%\For{\emph{l} in $\forall$labels}
+	\State{$l_d$ = dilate(\emph{l}, 20)}
+	%\For{N iterations}
+		%\State{$s_1$,$s_2$ = findRandomSeeds($l_d$)}
+		\State{border = watershed($l_d$, $\text{seeds}_\text{random}$)}
+		%\State{border = findBorder(ws)}
+		\State{$p_\text{split}$ = rank(border)}
+		\State{$p_\text{merge}$ = $1-p_\text{split}$}
+		%\State{correct($\max p_\text{merge}$)}
+	%\EndFor
+
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{Merge Error Detection for one label}\label{code:mergeerror2}
+\begin{algorithmic}[1]
+%\State{mergeErrors = []}
+%\For{\emph{l} in $\forall$labels}
+	\State{dilate label}
+	\For{N iterations}
+		\State{watershed (randomly seeded)}
+		\State{$p$ = rank border using split error CNN}
+		\State{$p_\text{merge}$ = $1-p$}	
+	\EndFor
+	\State{find max $p_\text{merge}$}
+
+\end{algorithmic}
+\end{algorithm}
 

### 2017-01-30 gp/legacy.py
Add new Merge Error gfx.

@@ -208,7 +208,7 @@ class Legacy(object):
     ws = mh.cwatershed(speed_image, seeds)
     ws[array == 0] = 0
 
-    return ws    
+    return seeds, ws    
 
 
   @staticmethod

### 2017-01-30 gp/util.py

@@ -148,11 +148,14 @@ class Util(object):
 
     if color:
       plt.imshow(Util.colorize(array), picker=True)
+      iii = Util.colorize(array)
     else:
       plt.imshow(array, cmap='gray', picker=True)
+      iii = array
 
     if file!='':
-      plt.savefig(file)
+      mh.imsave(file, iii.astype(np.uint8))
+      #plt.savefig(file)
 
   @staticmethod
   def view_rgba(patch, text=''):

### 2017-01-30 paper/rebuttal/egrebuttal.tex
Add new Merge Error gfx.
Update pseudo code and figure description.

@@
 \paragraph{R3: Merge Error Detection}
-R3 requests a better explanation of the merge error detection.
-We have updated Figure 4 in the main paper to include the watershed seeds (Fig.
+R3 requests a better explanation of the merge error detection (Sec.
+3.2).
+We have updated Figure 4 in the main paper to be more descriptive (Fig.
 1).
-We will also add a pseudo code version of the algorithm to the supplemental material to promote understanding (Alg.
+We will also add pseudo code of the algorithm to the supplemental material to promote understanding (Alg.
 \ref{code:mergeerror}).
@@
 \centering
-\includegraphics[width=\linewidth]{gfx/merge_error_v5.pdf}
-\caption{Updated Figure 4 including the random watershed seeds (yellow).}
+\includegraphics[width=\linewidth]{gfx/merge_error_v6.pdf}
+\caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment.
+Then, each border is individually rated using the split error CNN by inverting the probability score.}
 \label{fig:merge_error}
@@
 
+%\begin{algorithm}
+%\caption{Merge Error Detection for label \emph{l}}\label{code:mergeerror}
+%\begin{algorithmic}[1]
+%%\State{mergeErrors = []}
+%%\For{\emph{l} in $\forall$labels}
+%	\State{$l_d$ = dilate(\emph{l}, 20)}
+%	%\For{N iterations}
+%		%\State{$s_1$,$s_2$ = findRandomSeeds($l_d$)}
+%		\State{border = watershed($l_d$, $\text{seeds}_\text{random}$)}
+%		%\State{border = findBorder(ws)}
+%		\State{$p_\text{split}$ = rank(border)}
+%		\State{$p_\text{merge}$ = $1-p_\text{split}$}
+%		%\State{correct($\max p_\text{merge}$)}
+%	%\EndFor
+%
+%\end{algorithmic}
+%\end{algorithm}
+
 \begin{algorithm}
-\caption{Merge Error Detection for label \emph{l}}\label{code:mergeerror}
+\caption{Merge Error Detection for a label \emph{l}}\label{code:mergeerror}
 \begin{algorithmic}[1]
@@
 %\For{\emph{l} in $\forall$labels}
-	\State{$l_d$ = dilate(\emph{l}, 20)}
-	%\For{N iterations}
-		%\State{$s_1$,$s_2$ = findRandomSeeds($l_d$)}
-		\State{border = watershed($l_d$, $\text{seeds}_\text{random}$)}
-		%\State{border = findBorder(ws)}
-		\State{$p_\text{split}$ = rank(border)}
-		\State{$p_\text{merge}$ = $1-p_\text{split}$}
-		%\State{correct($\max p_\text{merge}$)}
-	%\EndFor
-
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{Merge Error Detection for one label}\label{code:mergeerror2}
-\begin{algorithmic}[1]
-%\State{mergeErrors = []}
-%\For{\emph{l} in $\forall$labels}
-	\State{dilate label}
+	\State{$l_d$ = \textbf{dilate}(\emph{l}, 20)}
+	\State{invImage = \textbf{invert}(image)}
 	\For{N iterations}
-		\State{watershed (randomly seeded)}
-		\State{$p$ = rank border using split error CNN}
+		\State{$s_1$,$s_2$ = \textbf{randomSeeds}($l_d$)}
+		\State{wsImage = \textbf{watershed}(invImage, $l_d$,$s_1$,$s_2$)}
+		\State{border = \textbf{border}(wsImage)}
+		\State{$p$ = \textbf{rank}(border)}
 		\State{$p_\text{merge}$ = $1-p$}	
 	\EndFor
-	\State{find max $p_\text{merge}$}
+	\State{\textbf{find}(max $p_\text{merge})$}
 

### 2017-01-30 paper/rebuttal/egrebuttal.tex
Tuning to fit on one page.
Incorporate Verena's feedback.

@@
 
+\vspace{-1mm}
+
 \paragraph{R2: Quantitative Evaluation}
 R2 requests an objective quantitative evaluation.
-Fortunately, our `automatic' and `oracle' experiments are exactly this.
+Our `automatic' and `oracle' experiments are exactly this.
 We define such experiments in lines 573--590 and report the results in Fig.~6, Fig.~7, and lines 792--818 (also in supplemental Sec.~2 and 3).
 These evaluations use the quantitative VI metric against a ground truth segmentation, with no user in the loop.
+
+\vspace{-1mm}
 
@@
 `Faster' here considers both how long each correction takes, and the likely VI reduction from that correction.
-Our approach has comparable correction time to the state-of-the-art Focused Proofreading appraoch, but a significantly greater VI reduction per correction (7.5$\times$).
-Our presentation of this discovery could have been improved.
+Our approach has comparable correction time to the state-of-the-art Focused Proofreading approach, but a significantly greater VI reduction per correction (7.5$\times$).
+We agree that the presentation of this comparison was not ideal.
 We will add Table~\ref{tab:correctiontimes} to make this clearer (previously reported in lines 756-765, slopes in Fig.~6, and column 3 in Fig.~7).
@@
 
+\vspace{-5mm}
+
 \paragraph{R2: Reproducibility}
-R2 expresses concerns regarding reproducibility. As per line 847, we have promised to release all our code and data, and we disclose all parameters.
+R2 expresses concerns regarding reproducibility. As per line 847, we have promised to release all our code including trained models and data, and we disclose all parameters.
+
+\vspace{-1mm}
 
 \paragraph{R2: How were Optimal Parameters chosen?}
-The \textbf{threshold $p_t=0.95$} was observed to be stable when evaluating on previously-unseen test data (lines 585-586, supplemental Sec.
+The \textbf{threshold $p_t=0.95$} was observed to be stable when evaluating VI reduction on previously-unseen test data (lines 585-586, supplemental Sec.
 1.3).
-The \textbf{input border is dilated by 5 pixels} to consider slight edge ambiguities and to cover extra-cellular space between segments in high-resolution electron microscopy data (lines 308-310).
+The \textbf{input border is dilated by 5 pixels} to consider slight edge ambiguities and extra-cellular space in high-resolution electron microscopy data (lines 308-310).
 During merge error detection, \textbf{labels are dilated by 20 pixels} prior to finding potential borders (line 323) with border-seeded watershed---this way the borders tend to attach to real membrane boundaries (lines 364-366).
-As we use a CNN, there are many additional parameters; we consider choosing these effectively to be an open problem, and for this we used learned experience and local brute-force searches.
+As we use a CNN, there are many additional parameters; we consider choosing these effectively to be an open problem, and for this we used learned experience and local brute-force searches on separate training data.
 %Here, we list all parameters and describe how their values are obtained. We will synchronize this information with the paper.
@@
 
+\vspace{-1mm}
+
 \begin{table}[h]
-\caption{Training data of membrane detection vs.~training data of GP (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
+\caption{Training data of membrane detection vs.~training data of GP vs.~test data (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
+\vspace{-1mm}
 \resizebox{\linewidth}{!}{
@@
 %Dataset & \makecell{Training Set\\Membrane Detection (U-Net)} & \makecell{Training Set\\Guided Proofreading} \\ 
-Dataset & \makecell{Training Set\\U-Net} & \makecell{Training Set\\GP} \\ 
+\makecell{Training Set\\U-Net / GALA} & \makecell{Training Set\\GP} & \makecell{Test Set\\GP}\\ 
 \midrule
-\makecell{\emph{L. Cylinder}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} \\ 
-\makecell{\emph{AC4 subvolume}\\~} & \makecell{AC4 excl. test\\ ($1000\times1000\times90$vx)} &  \makecell{L. Cylinder\\ ($2048\times2048\times250$vx)} \\ 
-\makecell{\emph{CREMI A/B/C}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} \\ 
+\makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} &
+\makecell{$\text{L. Cylinder}_\text{test}$\\($2048\times2048\times50$vx)}
+\\ 
+\makecell{AC4 excl. test\\ ($1024\times1024\times90$vx)} &  \makecell{L. Cylinder\\($2048\times2048\times250$vx)} &
+\makecell{$\text{AC4}_\text{test}$ subvolume\\($400\times400\times10$vx)} \\ 
+\makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} &
+\makecell{$\text{CREMI A/B/C}_\text{test}$\\($1250\times1250\times15$vx)} \\ 
 \bottomrule
@@
 
+%\begin{table}[h]
+%\caption{Training data of membrane detection vs.~training data of GP (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
+%\vspace{-1mm}
+%\resizebox{\linewidth}{!}{
+%\begin{tabular}{lrrrr}
+%\toprule
+%%Dataset & \makecell{Training Set\\Membrane Detection (U-Net)} & \makecell{Training Set\\Guided Proofreading} \\ 
+%Dataset & \makecell{Training Set\\U-Net} & \makecell{Training Set\\GP} \\ 
+%\midrule
+%\makecell{\emph{$\text{L. Cylinder}_\text{test}$}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} \\ 
+%\makecell{\emph{AC4 subvolume}\\~} & \makecell{AC4 excl. test\\ ($1000\times1000\times90$vx)} &  \makecell{L. Cylinder\\ ($2048\times2048\times250$vx)} \\ 
+%\makecell{\emph{CREMI A/B/C}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} \\ 
+%\bottomrule
+%\end{tabular} 
+%}
+%\label{tab:trainingdata}
+%\end{table}
+
+\vspace{-5mm}
+
 \paragraph{R3: Merge Error Detection}
@@
 3.2).
-We have updated Figure 4 in the main paper to be more descriptive (Fig.
+We have updated Fig.
+4 in the main paper to be more clear (Fig.
 1).
@@
 \includegraphics[width=\linewidth]{gfx/merge_error_v6.pdf}
-\caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment.
-Then, each border is individually rated using the split error CNN by inverting the probability score.}
+\vspace{-6mm}
+\caption{Potential borders are generated on inverted images by randomly placing watershed seeds (green) on the boundary of a dilated segment.
+The best ranked seeds and border (both in red) result in the shown error correction.}
 \label{fig:merge_error}
 \end{figure}
+
+\vspace{-5mm}
 
@@
 	\For{N iterations}
-		\State{$s_1$,$s_2$ = \textbf{randomSeeds}($l_d$)}
-		\State{wsImage = \textbf{watershed}(invImage, $l_d$,$s_1$,$s_2$)}
+		\State{$s_1$, $s_2$ = \textbf{randomSeedsOnBoundary}($l_d$)}
+		\State{wsImage = \textbf{watershed}(invImage, $l_d$, $s_1$, $s_2$)}
 		\State{border = \textbf{border}(wsImage)}
@@
 \end{algorithm}
+
+\vspace{-5mm}
 

### 2017-03-07 paper/method.tex
All minor changes fixed and replacing arXiv sources with real ones.

@@
 However, in reality, the score $p$ is between 0 and 1.
-In connectromics, classification complexity arises from hundreds of different cell types, rather than from the classification decision itself.
+In connectomics, classification complexity arises from hundreds of different cell types, rather than from the classification decision itself.
 Intuitively, this yields a wider architecture with more filters rather than a deeper architecture with more layers.
@@
 \includegraphics[width=\linewidth]{gfx/cnn_inputs.pdf}
-\caption{Example inputs for learning correct splits and split errors, as per a candidate segmentation versus the ground truth.
+\caption{Example inputs for learning correct splits and split errors (candidate segmentation versus the ground truth).
 Image, membrane probabilities, merged binary labels, and a dilated border mask provide 4-channel input patches.}

### 2017-03-07 paper/method.tex
Replace merge error image and add timing table.

@@
 \centering
-\includegraphics[width=\linewidth]{gfx/merge_error_v4.pdf}
-\caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment.
+\includegraphics[width=\linewidth]{gfx/merge_error_v6.pdf}
+\caption{Merge error detection: Potential borders are generated on inverted images by randomly placing watershed seeds (green) on the boundary of a dilated segment.
+The best ranked seeds and border (both in red) result in the shown error correction.}
+%Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment.
 Then, each border is individually rated using the split error CNN by inverting the probability score.

### 2017-03-07 paper/results.tex
Replace merge error image and add timing table.

@@
 \emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
-Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
-Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
+~~Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
+~~Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
 \emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
-Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
-Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
+~~Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
+~~Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
 \bottomrule
@@
 \emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
-Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
-Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
+~~Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
+~~Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
 \emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
-Correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
-Split error & 0.54 & 0.95 & 0.69 & 332 \\ 
+~~Correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
+~~Split error & 0.54 & 0.95 & 0.69 & 332 \\ 
 \bottomrule
@@
 \paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to $0.469$ ($SD=0.87$).
-On average, users viewed $423.4$ corrections and accepted $45.8$, with an average time of $4.9$ seconds per correction.
-Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$).
-Here, users viewed on average $353.4$ corrections and accepted $106.9$, with an average correction time of $6.2$ seconds.
+On average, users viewed $423.4$ corrections and accepted $45.8$.
+%, with an average time of $4.9$ seconds per correction. 
+Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$). Here, users viewed on average $353.4$ corrections and accepted $106.9$.
+%, with an average correction time of $6.2$ seconds. 
 While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it.
 In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo (median VI $0.535$, $SD=0.055$).
-The slope of VI score per correction (Fig.~\ref{fig:ac4trails}) shows that guided proofreading enables improvements with fewer corrections than the other tools.
+The slope of VI score per correction (Fig.~\ref{fig:ac4trails}) and average timings (Tab.~\ref{tab:correctiontimes}) show that guided proofreading enables improvements with fewer corrections than the other tools.
 Interestingly, novice performance decreases after approximately $300$ corrections.
@@
 %Regarding fatigue, we suggest that future experiments include short breaks after every ten minutes.
+
+\begin{table}[h]
+\caption{Average proofreading speed for users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP).
+For comparable correction time, our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP.}%While the training of our classifier is more expensive, testing accuracy is superior.
+}
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrr}
+\toprule
+Approach & \makecell{Time Per Correction (s)} & \makecell{VI Reduction Per Minute} \\
+\midrule
+\emph{Dojo} & 30.5 & -0.002 \\
+%\emph{Dojo Expert?} & xxx & xxx \\
+\emph{FP} & 4.9 & 0.00023 \\
+\emph{GP} & 6.2 & 0.00173 \\
+\bottomrule
+\end{tabular} 
+}
+\label{tab:correctiontimes}
+\end{table}
 

### 2017-03-08 paper/evaluation.tex
Add several snippets from the rebuttal to the main paper.

@@
 We use a state-of-the-art method to create a dense automatic segmentation of the data.
-Membrane probabilities are generated using a CNN based on the U-net architecture~\cite{RonnebergerFB15}.
+Membrane probabilities are generated using a CNN based on the U-net architecture (trained exclusively on different data than the GP classifiers)~\cite{RonnebergerFB15}.
 The probabilities are used to seed watershed and generate an oversegmentation using superpixels.
-Agglomeration is then performed by the GALA active learning classifier~\cite{nunez2014graph}.
+Agglomeration is then performed by the GALA active learning classifier with a fixed agglomeration threshold of 0.3~\cite{nunez2014graph}.
+We further describe this approach in the supplemental material.
 

### 2017-03-08 paper/method.tex
Add several snippets from the rebuttal to the main paper.

@@
 To better direct our classifier to train on the true boundary, we extract the border between two segments.
-Then, we dilate this border by 5 pixels to consider slight edge ambiguities and use this binary mask as an additional input.
+Then, we dilate this border by 5 pixels to consider slight edge ambiguities as well as cover extra-cellular space, and use this binary mask as an additional input.
 This creates a stacked 4-channel input patch.
@@
 \ref{fig:merge_error} illustrates this procedure.
+Pseudo code is available as supplemental material to promote understanding.
 

### 2017-03-08 paper/supplemental/architecture.tex
Supplemental.
James proof
Update supplemental material to include merge error pseudocode, training datasets table and GALA description.

@@
 
+\subsection{Merge Error Detection Pseudo Code}
+
+\begin{algorithm}[H]
+\caption{Merge Error Detection for a label \emph{l}}\label{code:mergeerror}
+\begin{algorithmic}[1]
+%\State{mergeErrors = []}
+%\For{\emph{l} in $\forall$labels}
+	\State{$l_d$ = \textbf{dilate}(\emph{l}, 20)}
+	\State{invImage = \textbf{invert}(image)}
+	\For{N iterations}
+		\State{$s_1$, $s_2$ = \textbf{randomSeedsOnBoundary}($l_d$)}
+		\State{wsImage = \textbf{watershed}(invImage, $l_d$, $s_1$, $s_2$)}
+		\State{border = \textbf{border}(wsImage)}
+		\State{$p$ = \textbf{rank}(border)}
+		\State{$p_\text{merge}$ = $1-p$}	
+	\EndFor
+	\State{\textbf{find}(max $p_\text{merge})$}
+
+\end{algorithmic}
+\end{algorithm}
+
 \subsection{Limitations}
@@
 However, the output requires an additional (block-)merging step prior to 3D analysis.
+Several software packages exist for this purpose.
+
+As described in Section~\ref{sec:addexp}, the guided proofreading classifier has to be retrained if used on a different species than mouse. In our experiments, parameters did not need to be changed.
+
+\section{Automatic Segmentation Pipeline}
+
+We create a dense automatic segmentation of electron microscopy data using a combination of a U-net~\cite{RonnebergerFB15} and the GALA agglomeration method~\cite{nunez2014graph}.
+These classifiers are trained on different data than GP (Tab.~\ref{tab:trainingdata}).
+
+\begin{table}[h]
+\caption{Training data of membrane detection (U-Net / GALA) vs.~training data of GP vs.~test data.}%While the training of our classifier is more expensive, testing accuracy is superior. }
+\vspace{-1mm}
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrr}
+\toprule
+%Dataset & \makecell{Training Set\\Membrane Detection (U-Net)} & \makecell{Training Set\\Guided Proofreading} \\ 
+\makecell{Training Set\\U-Net / GALA} & \makecell{Training Set\\GP} & \makecell{Test Set\\GP}\\ 
+\midrule
+\makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} &
+\makecell{$\text{L. Cylinder}_\text{test}$\\($2048\times2048\times50$vx)}
+\\ 
+\makecell{AC4 excl. test\\ ($1024\times1024\times90$vx)} &  \makecell{L. Cylinder\\($2048\times2048\times250$vx)} &
+\makecell{$\text{AC4}_\text{test}$ subvolume\\($400\times400\times10$vx)} \\ 
+\makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} &
+\makecell{$\text{CREMI A/B/C}_\text{test}$\\($1250\times1250\times15$vx)} \\ 
+\bottomrule
+\end{tabular} 
+}
+\label{tab:trainingdata}
+\end{table}
+
+GALA uses a random forest classifier to agglomerate segments. We use an agglomeration level of 0.3 (after a grid search). Further details of our pipeline are described in~\cite{rhoananet}.

### 2017-03-14 paper/evaluation.tex
Add latest changes as discussed with James.

@@
 Agglomeration is then performed by the GALA active learning classifier with a fixed agglomeration threshold of 0.3~\cite{nunez2014graph}.
-We further describe this approach in the supplemental material.
+We describe this approach in the supplemental material.
 
@@
 		Mito agglomeration: Off~~~~~~ \\  % Crappy alignment spacing
-		Threshold: 0.0\\
+		Threshold: 0.0\\~\\
 	\end{tabular}
@@
 		\midrule
-		\emph{Results---Test Set} \\ \midrule Cost [m]: 217 \\ Test. acc.: 0.99 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
+		\emph{Results---Test Set} \\ \midrule Cost [m]: 217 \\ Val. acc.: 0.99 \\ Test. acc.: 0.68 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
 	\end{tabular}

### 2017-03-14 paper/guidedproofreading_review.tex
Results section complete.
Several changes.
Replace merge error image and add timing table.
Switch to ICCV template and update RhoanaNet citation.
Add latest changes as discussed with James.

@@
 
-\usepackage{cvpr}
+%\usepackage{cvpr}
+\usepackage{iccv}
 \usepackage{microtype}
@@
 \usepackage{booktabs}
+\usepackage{makecell}
+
 % Include other packages here, before hyperref.
@@
 \newcommand{\HP}[1]{\textcolor{red}{HP: #1}}
+\newcommand{\DFH}[1]{\textcolor{red}{DH: #1}}
 
@@
 
-\def\cvprPaperID{0947} % *** Enter the CVPR Paper ID here
+%\def\cvprPaperID{0947} % *** Enter the CVPR Paper ID here
+\def\iccvPaperID{0922}
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
+%\ifcvprfinal\pagestyle{empty}\fi
+\ificcvfinal\pagestyle{empty}\fi
 \begin{document}
@@
 interactive proofreading. To aid error correction, we develop two classifiers
-that automatically recommend candidate merge and splits to the user. These
+that automatically recommend candidate merges and splits to the user. These
 classifiers use a convolutional neural network (CNN) that has been trained with
@@
 region around a segmentation boundary. Corrections can then be performed by a
-user with yes/no decisions,  which results in faster correction times than previous
+user with yes/no decisions, which reduces variation of information $7.5\times$ faster than previous
 proofreading methods. We also present a fully-automatic mode that uses a

### 2017-03-14 paper/results.tex
Add latest changes as discussed with James.

@@
 \caption{Average proofreading speed for users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP).
-For comparable correction time, our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP.}%While the training of our classifier is more expensive, testing accuracy is superior.
+Our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP, while being slightly slower per correction.}%While the training of our classifier is more expensive, testing accuracy is superior.
 }
@@
 \toprule
-Approach & \makecell{Time Per Correction (s)} & \makecell{VI Reduction Per Minute} \\
+Approach & \makecell{Time Per\\Correction (s)} & \makecell{VI Reduction\\Per Minute} & \makecell{Improvement} \\
 \midrule
-\emph{Dojo} & 30.5 & -0.002 \\
+\emph{Dojo} & 30.5 & -0.00200 & $-8.7\times$ \\
 %\emph{Dojo Expert?} & xxx & xxx \\
-\emph{FP} & 4.9 & 0.00023 \\
-\emph{GP} & 6.2 & 0.00173 \\
+\emph{FP} & 4.9 & 0.00023 & $1.0\times$\\
+\emph{GP} & 6.2 & 0.00173 & $7.5\times$\\
 \bottomrule

### 2017-03-14 paper/supplemental/architecture.tex
Update supplemental.

@@
 
+We provide pseudo code on how we detect merge errors to foster understanding of the reported algorithm (Alg.~\ref{code:mergeerror}). In our experiments, we use $N=50$ iterations.
+
 \begin{algorithm}[H]
@@
 We create a dense automatic segmentation of electron microscopy data using a combination of a U-net~\cite{RonnebergerFB15} and the GALA agglomeration method~\cite{nunez2014graph}.
-These classifiers are trained on different data than GP (Tab.~\ref{tab:trainingdata}).
+To not bias, these classifiers are trained on different data than GP (Tab.~\ref{tab:trainingdata}).
 
@@
 
-GALA uses a random forest classifier to agglomerate segments. We use an agglomeration level of 0.3 (after a grid search). Further details of our pipeline are described in~\cite{rhoananet}.
+GALA uses a random forest classifier to agglomerate segments. We use an agglomeration level of 0.3 (after a grid search). We follow the method by Knowles-Barley~\etal as described in~\cite{rhoananet}.

### 2017-03-17 paper/results.tex
Update P/R gfx.

@@
 We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling.
-Then, we ranked each patch by using focused proofreading and guided proofreading, and compare precision/recall (Table \ref{tab:prcyl}).
-Our method exhibits higher precision and recall for correct and erroneous patches.
+Then, we ranked each patch by using focused proofreading and guided proofreading, and compare precision/recall (Fig.
+\ref{fig:pr}).
+Our method exhibits higher precision and recall.% for correct and erroneous patches.
 
-\begin{table}[t]
-\caption{Classifier comparison on an unbalanced test set of the L.~Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
-\resizebox{\linewidth}{!}{
-\begin{tabular}{lrrrr}
-\toprule
- & Precision & Recall & F1 score & Test \# \\ 
-\midrule
-\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
-~~Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
-~~Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
-\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
-~~Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
-~~Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
-\bottomrule
-\end{tabular} 
-}
-\label{tab:prcyl}
-\end{table}
+%\begin{table}[t]
+%\caption{Classifier comparison on an unbalanced test set of the L.~Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
+%\resizebox{\linewidth}{!}{
+%\begin{tabular}{lrrrr}
+%\toprule
+% & Precision & Recall & F1 score & Test \# \\ 
+%\midrule
+%\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
+%~~Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
+%~~Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
+%\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
+%~~Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
+%~~Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
+%\bottomrule
+%\end{tabular} 
+%}
+%\label{tab:prcyl}
+%\end{table}
 
-\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors). Guided proofreading achieves better precision/recall scores (Table \ref{tab:prac4}).
+\begin{figure}[t]
+\centering
+\includegraphics[width=\linewidth]{gfx/precisionrecall.pdf}
+\caption{Precision-recall curves comparing focused proofreading (FP) and our guided proofreading (GP) classifiers.
+We evaluate on unbalanced tests sets of the AC4 subvolume (darker colors) and the L.
+Cylinder volume (lighter colors).
+GP performs better.}
+\label{fig:pr}
+\end{figure}
 
-\begin{table}[t]
-\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
-\resizebox{\linewidth}{!}{
-\begin{tabular}{lrrrr}
-\toprule
-& Precision & Recall & F1 score & Test \# \\ 
-\midrule
-\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
-~~Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
-~~Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
-\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
-~~Correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
-~~Split error & 0.54 & 0.95 & 0.69 & 332 \\ 
-\bottomrule
-\end{tabular} 
-}
-\label{tab:prac4}
-\end{table}
+\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors). Guided proofreading achieves better precision/recall scores (Fig. \ref{fig:pr}).
+
+%\begin{table}[t]
+%\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
+%\resizebox{\linewidth}{!}{
+%\begin{tabular}{lrrrr}
+%\toprule
+%& Precision & Recall & F1 score & Test \# \\ 
+%\midrule
+%\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
+%~~Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
+%~~Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
+%\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
+%~~Correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
+%~~Split error & 0.54 & 0.95 & 0.69 & 332 \\ 
+%\bottomrule
+%\end{tabular} 
+%}
+%\label{tab:prac4}
+%\end{table}
 

### 2017-03-17 paper/results.tex
Smaller fixes.

@@
 \begin{table}[h]
-\caption{Average proofreading speed for users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP).
+\caption{Average proofreading speed for novice users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP).
 Our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP, while being slightly slower per correction.}%While the training of our classifier is more expensive, testing accuracy is superior.
@@
 \toprule
-Approach & \makecell{Time Per\\Correction (s)} & \makecell{VI Reduction\\Per Minute} & \makecell{Improvement} \\
+\makecell{Approach\\(Novice)} & \makecell{Time Per\\Correction (s)} & \makecell{VI Reduction\\Per Minute} & \makecell{Improvement} \\
 \midrule
@@
 
-\paragraph{Expert performance.} Domain experts were able to improve the initial segmentation in all cases.
+\paragraph{Expert performance.} Domain experts were able to improve the initial segmentation.
 With focused proofreading, the median VI of the automatic segmentation was $0.439$ ($SD=0.084$).

### 2017-03-17 paper/evaluation.tex
New combined trails graphic.

@@
 \centering
-\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
-\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the AC4 subvolume.
+\includegraphics[width=\linewidth]{gfx/ac4trails_combined.pdf}
+\caption{Performance comparison of Plaza's focused proofreading (red) and our guided proofreading (blue) on the AC4 subvolume.
 All measurements are reported as median VI, the lower the better.
-We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle.
+We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (green line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle.
 In all cases, guided proofreading yields better results with fewer corrections.}

### 2017-03-17 gp/stats.py

@@ -30,176 +30,7 @@ class Stats(object):
 
 
   @staticmethod
-  def analyze_users(FP_USERS, gold, rhoana, oracle=None, clampX=500, clampY=False, filename=None, hideXlabels=True, hideYlabels=True, DATADIR = '/home/d/GPSTUDY/', skipoutput=False, data='dojo', hline=-1, returnplt=False, showlegend=False, vilabel=False,clabel=False ):
-
-
-    # def VI(gt, seg):
-    #   # total_vi = 0
-    #   slice_vi = []    
-    #   for i in range(len(gt)):
-    #       current_vi = Util.vi(gt[i].astype(np.int64), seg[i].astype(np.int64))
-    #       # total_vi += current_vi
-    #       slice_vi.append(current_vi)
-    #   # total_vi /= 10
-    #   return np.mean(slice_vi), np.median(slice_vi), slice_vi
-
-    # init_mean_vi = VI(gold, rhoana)[0]
-    # init_median_vi = VI(gold, rhoana)[1]
-    # init_vi_per_slice = VI(gold, rhoana)[2]
-    # print init_median_vi
-    # print 'No. users', len(FP_USERS)
-
-    # dojo_best_vi = 0.33414926373414477
-    # cylinder_best_vi = 0.27683609273291143
-
-    # newrhoana = 'ui_results.p'
-    # times = 'times.p'
-    # corrections = 'corrections.p'
-    # correction_vis = 'correction_vis.p'
-
-    # fp_outputs = []
-    # fp_times = []
-    # fp_corrections = []
-    # fp_vis =[]
-
-    # for i,f in enumerate(FP_USERS):
-    #     with open(DATADIR+FP_USERS[i]+'/'+newrhoana, 'rb') as f:
-    #         fp_newrhoana = pickle.load(f)
-    #         fp_outputs.append(fp_newrhoana)
-    #     with open(DATADIR+FP_USERS[i]+'/'+times, 'rb') as f:
-    #         fp_time = pickle.load(f)
-    #         fp_time = [int(v) for v in fp_time]
-    #         fp_times.append(fp_time)
-    #     with open(DATADIR+FP_USERS[i]+'/'+corrections, 'rb') as f:
-    #         fp_correction = pickle.load(f)       
-    #         fp_corrections.append(fp_correction)
-    #     with open(DATADIR+FP_USERS[i]+'/'+correction_vis, 'rb') as f:
[…]

### 2017-03-17 paper/method.tex
Update graphics.

@@
 \includegraphics[width=\linewidth]{gfx/merge_error_v6.pdf}
-\caption{Merge error detection: Potential borders are generated on inverted images by randomly placing watershed seeds (green) on the boundary of a dilated segment.
+\caption{Merge error detection: Potential borders are generated using inverted images by randomly placing watershed seeds (green) on the boundary of a dilated segment.
 The best ranked seeds and border (both in red) result in the shown error correction.}

### 2017-03-17 paper/conclusion.tex
Add latest changes as discussed with James.
Add ROC curve and update conclusion.

--- 2016-11-15 paper/conclusion.tex
@@
 Humans are the bottleneck and minimizing the manual labor is the goal.
-In this paper, we have trained classifiers to find merge and split errors in automatic segmentations of connectomics data.
+%We have trained classifiers to find merge and split errors in automatic segmentations of connectomics data.
 We then reduce the correction of these errors to simple yes/no decisions.
 This allows proofreading with better performance than existing systems.
+%Our experiments also show that automatic proofreading works.
+This has the potential to further reduce the manual labor and will be the target of future research.
+To encourage testing of our proposed architecture and replication of our experiments, we provide our framework and data as free and open research at (link omitted for review).
+%Minimizing manual labor is the goal when proofreading large automatic segmentations.
+Our classifiers suggest potential errors and corrections better than existing systems.
+This is especially important for novice users.
+Novices report difficulties when using fully interactive software but are invaluable to proofread the shear amounts of connectomics data.
+%Our experiments also show that automatic proofreading works.
+This has the potential to further reduce human involvement and will be the target of future research.
+We provide our framework and data as free and open research at (link omitted for review).
+Humans are the bottleneck when proofreading segmentation data and minimizing the manual labor is the goal.
+Our classifiers suggest potential errors and corrections better than existing methods.
+This reduces the time spent finding and correcting errors.
 Our experiments also show that automatic proofreading works.
-This has the potential to further reduce the manual labor and will be the target of future research.
-To encourage testing of our proposed architecture and replicate our experiments, we provide our framework and data as free and open research at (link omitted for review).
+This has the potential to further reduce human involvement and will be the target of future research.
+We provide our framework and data as free and open research at (link omitted for review).

### 2017-03-17 gp/stats.py

@@ -363,7 +363,7 @@ class Stats(object):
       for u in fp_vi_per_c_per_user2:
           plt.plot(u, linewidth=6, color='#0571b0', label='Guided Proofreading')
 
-      legend = ax.legend(loc='upper right')
+      legend = ax.legend(bbox_to_anchor=(-0.28,1.5), loc='upper right', ncol=2)
 
     else:
 

### 2017-03-17 paper/conclusion.tex
Changed sentence of automatic proofreading.

@@
 This reduces the time spent finding and correcting errors.
-Our experiments also show that automatic proofreading works.
-This has the potential to further reduce human involvement and will be the target of future research.
+Our experiments also show that automatic proofreading has potential to further reduce human involvement.
+This will be the target of future research.
 We provide our framework and data as free and open research at (link omitted for review).

### 2017-03-17 paper/results.tex
Update graphics.
Add ROC curve and update conclusion.
Minor fixes

@@
 For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
-Please note that additional plots are available as supplemental material due to reasons of space.
+Additional plots are available as supplemental material due to limited space.
 
@@
 \centering
-\includegraphics[width=\linewidth]{gfx/precisionrecall.pdf}
-\caption{Precision-recall curves comparing focused proofreading (FP) and our guided proofreading (GP) classifiers.
+\includegraphics[width=0.9\linewidth]{gfx/roc.pdf}
+\caption{Receiver Operating Characteristic curves comparing focused proofreading and guided proofreading automatic correction.
 We evaluate on unbalanced tests sets of the AC4 subvolume (darker colors) and the L.
 Cylinder volume (lighter colors).
-GP performs better.}
+Guided proofreading performs better.}
 \label{fig:pr}
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
-\caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across slices of the AC4 subvolume, with different error correction approaches.
-The variation resulting from performance of FP with automatic selection is $4.5\times$ higher than GP (as indicated by the arrow), with median VI of $1.9$ and $SD=0.496$.}
-\label{fig:ac4boxplot}
-\end{figure}
-
 \subsection{Forced Choice User Experiment}
@@
 
-\begin{table}[h]
+\begin{table}[t]
 \caption{Average proofreading speed for novice users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP).
@@
 
+\begin{figure}[t]
+\centering
+\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
+\caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across slices of the AC4 subvolume, with different error correction approaches.
+The variation resulting from performance of FP with automatic selection is $4.5\times$ higher than GP (as indicated by the arrow), with median VI of $1.9$ and $SD=0.496$.}
+\label{fig:ac4boxplot}
+\end{figure}
+
 \paragraph{Automatic selection with threshold.} Focused proofreading was not designed to run automatically.

### 2017-03-17 paper/results.tex
Fix section 5.1.

@@
 
-\subsection{Precision and Recall}
+\subsection{Classification Performance}
 
@@
 We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling.
-Then, we ranked each patch by using focused proofreading and guided proofreading, and compare precision/recall (Fig.
+Then, we ranked each patch by using focused proofreading and guided proofreading, and compare classification performance (Fig.
 \ref{fig:pr}).
-Our method exhibits higher precision and recall.% for correct and erroneous patches.
+Our method exhibits higher sensitivity.% for correct and erroneous patches.
 
@@
 
-\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors). Guided proofreading achieves better precision/recall scores (Fig. \ref{fig:pr}).
+\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors). Guided proofreading achieves better classification performance (Fig. \ref{fig:pr}).
 

### 2017-03-17 paper/results.tex
Some changes to 5.1.

@@
 \paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of the mouse cortex volume from Kasthuri~\etal~\cite{kasthuri2015saturated}.
-We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling.
-Then, we ranked each patch by using focused proofreading and guided proofreading, and compare classification performance (Fig.
+We generated a dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling.
+Then, we classified each patch by using focused proofreading and guided proofreading, and compare performance (Fig.
 \ref{fig:pr}).
-Our method exhibits higher sensitivity.% for correct and erroneous patches.
+Our method exhibits higher sensitivity and lower fall-out.% for correct and erroneous patches.
 
@@
 \caption{Receiver Operating Characteristic curves comparing focused proofreading and guided proofreading automatic correction.
-We evaluate on unbalanced tests sets of the AC4 subvolume (darker colors) and the L.
+We evaluate on unbalanced test sets of the AC4 subvolume (darker colors) and the L.
 Cylinder volume (lighter colors).

### 2017-03-27 paper/supplemental/cremi.tex
Update plots for the supplemental material.

@@
 \centering
-\includegraphics[width=\linewidth]{gfx/cremiAtrails.pdf}
+\includegraphics[width=\linewidth]{gfx/cremiA_trails.pdf}
 \caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on 5 sections of the CREMI A dataset.
 All measurements are reported as median VI, the lower the better.
-The threshold for automatic selection is $p_t=0.95$ (red line).
+The threshold for automatic selection is $p_t=0.95$ (green line).
 The slope of the selection oracle shows that guided proofreading reduces VI faster.}
@@
 \centering
-\includegraphics[width=\linewidth]{gfx/cremiBtrails.pdf}
+\includegraphics[width=\linewidth]{gfx/cremiB_trails.pdf}
 \caption{Split error correction by Plaza's focused proofreading and our guided proofreading compared on the CREMI B dataset.
 All measurements are reported as median VI, the lower the better.
-Automatic selection with threshold (red line) yields reasonable performance using guided proofreading.}
+Automatic selection with threshold (green line) yields reasonable performance using guided proofreading.}
 \label{fig:cremiBtrails}
@@
 \centering
-\includegraphics[width=\linewidth]{gfx/cremiCtrails.pdf}
+\includegraphics[width=\linewidth]{gfx/cremiC_trails.pdf}
 \caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the CREMI C dataset.
 Lower VI scores are better.
-Guided proofreading corrects the initial segmentation faster with less corrections than focused proofreading.}
+Guided proofreading corrects the initial segmentation faster with less corrections than focused proofreading.
+The green line shows the automatic threshold $p_t=0.95$.}
 \label{fig:cremiCtrails}

### 2017-03-27 paper/supplemental/leftcylinder.tex
Update plots for the supplemental material.

@@
 \centering
-\includegraphics[width=\linewidth]{gfx/cyltrails.pdf}
+\includegraphics[width=\linewidth]{gfx/cyl_trails.pdf}
 \caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the L.~Cylinder dataset as reported in the paper.
 All measurements are shown as median VI, the lower the better.
-We compare automatic selection with threshold ($p_t=0.95$, red line) and the selection oracle for accepting or rejecting corrections using each method.
+We compare automatic selection with threshold ($p_t=0.95$, green line) and the selection oracle for accepting or rejecting corrections using each method.
 Guided proofreading yields better results faster with fewer corrections.}

### 2017-03-27 gp/stats.py

@@ -67,7 +67,7 @@ class Stats(object):
       clampY = [1.35,1.96]
     else:
       best_vi = cylinder_best_vi
-      clampY = [0.25, 0.5]
+      clampY = [0.25, 0.51]
     if not returnplt:
       print 'No. users', len(FP_USERS)
 
@@ -215,6 +215,7 @@ class Stats(object):
             fp_correction_vis = pickle.load(f) 
             fp_vis.append(fp_correction_vis)
 
+
     # return None, None, fp_vis
 
     fp_times_mean = []
@@ -266,13 +267,23 @@ class Stats(object):
               stored_first_split_vi = True
 
             if c[1] == '1':
+
+
+
                 # user accepted correction, now look up the vi
                 # print fp_vis[k]
                 #print k, correctionindex, len(fp_vis)
                 vi = fp_vis[k][correctionindex]
+
+                # if len(vi.shape)==0:
+                #   # this is a bug
+                #   continue
+
                 correctionindex += 1    
 
                 vis.append(np.median(vi))
+
+
 
 
                 if c[0] == 'merge':
@@ -310,8 +321,16 @@ class Stats(object):
     # fig, ax = plt.subplots()
     if clampY:
         plt.ylim(clampY[0],clampY[1])
-        #plt.yticks(np.arange(clampY[0], clampY[1], 0.05))
-        plt.yticks(np.arange(0.35, 0.57, 0.05))
+
+        if data == 'dojo':
+          plt.yticks(np.arange(0.35, 0.57, 0.05)) # 0.35 looks better for dojo
+        elif data =='cremiA':
+          plt.yticks(np.arange(clampY[0], clampY[1], 0.05))
+        elif data=='cremiB':
+          plt.yticks(np.arange(clampY[0], clampY[1], 0.1))
+        elif data=='cyl':
+          plt.yticks(np.arange(clampY[0], clampY[1], 0.05))
+
     if clampX:
       plt.xlim(0,clampX)
 
@@ -329,7 +348,19 @@ class Stats(object):
       legend = ax.legend(loc='upper right')
 
     if hline!=-1:
-      plt.axvline(x=hline, color='green', ymin=0, ymax=.357, linewidth=4)
+
+      if data=='dojo':
+        ymax = .357
+      elif data == 'cremiA':
+        ymax = .55
+      elif data == 'cremiB':
+        ymax = .37
+      elif data == 'cremiC':
[…]

### 2017-04-04 paper/arxiv/conclusion.tex
Latest updates including supplemental for submission and the arXiv versions.

--- 2016-11-15 paper/conclusion.tex
@@
 
-%The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation.
-Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task.
-Humans are the bottleneck and minimizing the manual labor is the goal.
-In this paper, we have trained classifiers to find merge and split errors in automatic segmentations of connectomics data.
-We then reduce the correction of these errors to simple yes/no decisions.
-This allows proofreading with better performance than existing systems.
-Our experiments also show that automatic proofreading works.
-This has the potential to further reduce the manual labor and will be the target of future research.
-To encourage testing of our proposed architecture and replication of our experiments, we provide our framework and data as free and open research at (link omitted for review).
+Humans are the bottleneck when proofreading segmentation data and minimizing the manual labor is the goal.
+Our classifiers suggest potential errors and corrections better than existing methods.
+This reduces the time spent finding and correcting errors.
+Our experiments also show that automatic proofreading has potential to further reduce human involvement.
+This will be the target of future research.
+We provide our framework and data as free and open research at \url{http://rhoana.org/guidedproofreading/}.
+
+\section*{Acknowledgements}
+We would like to thank Stephen Plaza for detailed explanations of focused proofreading and Toufiq Parag for the configuration of the NeuroProof classifier.

### 2017-04-04 paper/arxiv/evaluation.tex
Latest updates including supplemental for submission and the arXiv versions.

--- 2017-03-17 paper/evaluation.tex
@@
-%\begin{figure*}[t]
-%\begin{center}
-%\includegraphics[width=\linewidth]{gfx/results_mouse.png}
-%\end{center}
-%  \vspace{-4mm}
-%   \caption{Performance evaluation of the classifiers on two mouse brain datasets measured as adapted Rand error (lower scores are better).
-We compare guided proofreading (GP), guided proofreading with active label suggestion (GP*) and focused proofreading.
-Proofreading is performed automatically (autom., with probability threshold $p_t=.95$), simulated as a perfect user (sim.), or by novice and expert users as indicated.
-The first row of images shows the results of a user study and includes comparisons to the interactive proofreading software Dojo by Haehn \etal \cite{haehn_dojo_2014}.
-GP* is able to correct the segmentation further than other methods.
-The second row shows the results of the simulated user compared to automatic GP* and FP performance.
-The bottom right graph compares automatic GP* and simulated GP* per individual correction.
-The blue dashed line here indicates the moment the probability threshold $p_t$ is reached.
-The simulated user is able to correct the initial segmentation beyond this threshold while automatic GP* then introduces errors.}
-%\label{fig:results_mouse}
-%\end{figure*}
-
 \section{Evaluation}
@@
 We use their publicly available data, labeled ground truth, and study findings\footnote{\scriptsize{\url{http://rhoana.org/dojo/}}}.
-
-%\paragraph{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets were made publicly available\footnote{\scriptsize{\url{http://www.cremi.org}}},  each $1250\times1250\times125$ voxels.
-Since only three datasets include manually-labeled `ground truth', we use these three volumes for our experiments.
-The volumes are part of an adult fruit fly (Drosophila melanogaster) brain.
-The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$.
 
@@
 \caption{Training parameters, cost, and results of our guided proofreading classifier versus focused proofreading by Plaza~\cite{focused_proofreading}.
-Both methods were trained on the same mouse brain dataset using the same hardware (Tesla X GPU).}%While the training of our classifier is more expensive, testing accuracy is superior.
-}
-
+Both methods were trained on the same mouse brain dataset using the same hardware (Tesla X GPU).}
 \small{
@@
 		Learning strategy: 2\\
-		Mito agglomeration: Off~~~~~~ \\  % Crappy alignment spacing
+		Mito agglomeration: Off~~~~~~ \\  
 		Threshold: 0.0\\~\\
@@
 Therefore, for training our focused proofreading baseline, we replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities.
-We obtained the best possible parameters for NeuroProof by consulting the developers (Table~\ref{tab:parameters}).
+We obtained the best possible parameters for NeuroProof by consulting the developers (Tab.~\ref{tab:parameters}).
 Rather than using Raveler as the frontend, we use our own interface (Fig.~\ref{fig:ui}) to compare only the classifier from Plaza's approach.
@@
 \centering
-\includegraphics[width=\linewidth]{gfx/ac4trails_combined.pdf}
+\includegraphics[width=\linewidth]{ac4trails_combined.pdf}
 \caption{Performance comparison of Plaza's focused proofreading (red) and our guided proofreading (blue) on the AC4 subvolume.
@@
 \paragraph{Evaluation metric.} We measure the similarity between proofread segmentations and the manual `ground truth' labelings using \textit{variation of information} (VI).
-VI is a measure of the distance between two clusterings, closely related to mutual information (the lower, the better).% We treat VI as a continuous variable during analysis.
-
-%For baseline comparison, we also list the parameters and training results of focused proofreading in this table but elaborate on these further in section \ref{sec:evaluation}.
-
-%
-%\begin{table}[h]
-%%\resizebox{\textwidth}{!}{%
-%\tiny
-%\begin{tabular}{@{}c|c|c|c|c|c|c@{}}
-%& \textbf{cost [m]} & \textbf{Val. loss} & \textbf{Val. acc.} & \textbf{Test acc.} & \textbf{Prec./Recall} & \textbf{F1 Score} \\
-%\hspace{1mm}
-%\begin{tabular}{@{}l@{}}
-%\textbf{Guided Proofreading} \\ Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2-4: 48 \\ Dense units: 512 \\ Learning rate: 0.03-0.00001\\ Momentum: 0.9-0.999\\Mini-Batchsize: 128\\~\\
-% \end{tabular}
-% & 383  & 0.0845  & 0.969  & 0.94  & 0.94/0.94  & 0.94 \\
-%\hline
-%\begin{tabular}{@{}l@{}}
-%\\
-%\textbf{Focused Proofreading} \\
-%Iterations: 3 \\
-%Learning strategy: 2\\
-%Mito agglomeration: Off\\
-%Threshold: 0.2
-% \end{tabular}
-% & 43  & ?  & ?  & 0.839  & ?/?  & ? \\
-%\end{tabular}
-%\vspace{1mm}
-%\caption{Training parameters, cost and results of our guided proofreading classifier versus focused proofreading by Plaza \cite{focused_proofreading}.
-Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 graphics card).
-While the training of our classifier is more expensive, testing accuracy is superior.
-}
-%\label{tab:parameters}
-%\end{table}
-
-%For performance comparison on data of a different species, in particular on fruitfly brain (drosophila), we retrain our network.
-The training procedure is according to our initial training and network architecture as well as parameters are not changed.
-We further elaborate on the drosophila datasets in section~\ref{sec:evaluation}.
-Fig.~\ref{fig:roc} displays receiver operating characteristics (ROC) for  guided proofreading trained on mouse and drosophila data, as well as our comparison baseline focused proofreading trained on these datasets respectively.
-%
-%\begin{figure}[h]
-%  \vspace{-5mm}
-%\begin{center}
-%  \includegraphics[width=\linewidth]{gfx/roc.pdf}
-%\end{center}
-%  \vspace{-10mm}
-%   \caption{ROC performance of guided proofreading (GP) and focused proofreading (FP) trained separately on mouse and drosophila brain images.
-The area under the curve indicates better performance for GP.}
-%\label{fig:roc}
-%\end{figure}
-
-%\subsection{Mouse Brain}
-%
-%Mouse brain is a common target for connectomics research because the structural proportions are similar to human brains~\cite{jeff_science}.
-For our first experiment we recruited novice and expert participants as part of a quantitative user study.
-Our second experiment is performed on a larger dataset and we evaluate a simulated user.
-%\\~\\
-%\textbf{User study.} Recently, Haehn \etal evaluated the interactive proofreading tools Raveler, Mojo, and Dojo as part of an experiment with novice users~\cite{haehn_dojo_2014}.
-The participants corrected an automatic segmentation with merge and split errors.
-The dataset was the most representative sub-volume (based on object size histograms) of a larger connectomics dataset and $400x400x10$ voxels in size.
-The participants were given a fixed time frame of 30 minutes to perform the correction interactively.
-While participants clearly struggled with the proofreading task, the best performing tool in their evaluation was Dojo.
-The dataset including manually labeled ground truth and the results of Haehn \etal are publicly available.
-This means we are able to use their findings as a baseline for comparison of GP for novices.
-In particular, we use the best performing user of Dojo who was truly an outlier as reported by Haehn \etal.
-%
-%Since interactive proofreading most likely yields lower performance than aided proofreading, we also compare against FP by Plaza~\cite{focused_proofreading} which is integrated in Raveler and freely available.
-For FP we consulted an expert to obtain the best possible parameters as shown in table \ref{tab:parameters}.
-Besides performance by novices, we are also interested in expert proofreading performance.
-Therefore, we design between-subjects experiments for 20 novice users and separately, for 6 expert users using the exact same conditions as Haehn \etal.
-The recruiting, consent and debriefing process is further described in the supplementary material.
-We randomly assign 10 novices to GP with active label suggestion (GP*) and 10 novices to FP.
-For the expert experiment, we assign accordingly.
-%In addition to human performance, we also evaluate automatic GP, automatic GP with active label suggestion (GP*) and automatic FP.
-Due to the automatic nature, we do not enforce the 30 minute time limit but we stop once our probability threshold of $p_t=.95$ is reached.
-This value was observed as stable in previous experiments using automatic GP (see supplementary material).
-To measure proofreading performance in comparison to ground truth, we use the adapted Rand error (aRE) metric~\cite{RAND}.
-aRE is a measure of dissimilarity, related to introduced errors, meaning lower scores are better.
-%
-%The results of our comparisons are shown in the first row of Fig.~\ref{fig:results_mouse}.
-In all cases, GP* is able to correct the segmentation further than other methods (aRE measures: automatic GP XX, GP* XX, FP XX, novice Dojo XX, GP* XX, FP XX, expert Dojo XX, GP* XX, FP XX).
-This is not surprising since guided proofreading works for both merge and split errors while FP does not and in interactive Dojo the majority of time is spent finding errors which is minimized for aided proofreading solutions.
-In fact, the average correction time for novices is for GP* 3.6 (expert X), for FP Y (expert YY), and for Dojo 30 (expert ZZ) seconds.
-%\\~\\
-%\textbf{Simulated experiment.} For our second experiment with mouse brain data, we proofread the last 50 slices of the blue 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} which we also used for testing in section~\ref{sec:methods}.
-The data was not seen by the network before and includes $2048x2048x50$ voxels with a total number of 17,560 labeled objects.
-Since an interactive evaluation of such a large dataset would consume a significant amount of time, we restrict our experiment to a simulated (perfect) user and to automatic corrections, both with GP, GP* and FP.
-Similar to our comparison study, the simulated user assess a stream of errors by comparing the adapted Rand error measure before and after each performed correction.
-The simulated user is designed to be perfect and only accepts corrections if the measure is reduced.
-This time, we do not enforce a time limit to see the lower bound of possible corrections.
-For automatic GP and GP*, we use our defined probability threshold $p_t=.95$.
-%
-%The results of this experiment are shown in the second row of Fig.~\ref{fig:results_mouse}.
-GP* is again able to correct the segmentation further than other methods (aRE measures: automatic GP XX, GP* XX, FP XX, simulated GP* XX, FP XX).
-Again, the results are not surprising since GP* can correct merge and split errors.
-%
-%\subsection{Drosophila Brain}
-%
-%The drosophila brain is analyzed by connectomics researchers because of its small size and hence, a reasonable target to obtain a complete wiring diagram.
-Despite the size, fruit flies exhibit complex behaviors and are in general well studied.
-We evaluate the performance of our guided proofreading classifiers on three different datasets of adult fly brain.
-The datasets are publicly available as part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI)\footnote{The MICCAI CREMI challenge data is available at  http://www.cremi.org}.
-Each dataset consists of $1250x1250x125$ voxels of training data (A,B,C) as well as testing data (A+,B+,C+) of the same dimensions.
-Manually labeled ground truth is also available for A,B, and C but not for the testing data.
-%
-%Since drosophila brain exhibits different cell structures than mouse brain, we retrain the guided proofreading classifiers (and our automatic segmentation pipeline) as well as focused proofreading combined on the three training datasets.
-We use 300 slices of the A,B,C samples for training and validation, and 75 slices for testing.
-This results in YYY correct and ZZZ split error patches (respectively, XXX and YYY for testing).
-The architecture and all parameters of our classifiers stay the same.
-The trained GP classifier exhibits a reasonable performance on the testing data as seen in Fig.~\ref{fig:roc}.
-%
-%\begin{figure}[h]
-%\begin{center}
-%  \includegraphics[width=\linewidth]{gfx/results_fruitfly.png}
-%\end{center}
-%  \vspace{-4mm}
-%   \caption{Results of guided proofreading with active label suggestion (GP*) and focused proofreading performed automatically on three drosophila datasets.
-The datasets are part of the MICCAI 2016 CREMI challenge and publicly available.
-We measure performance as adapted Rand error (the lower, the better).
-GP* is able to correct the initial segmentation further than FP.
-Our GP* scores places us XXnd on the CREMI leaderboard.}
-%\label{fig:results_fruitfly}
-%\end{figure}
-%
-%We then use the trained GP* and FP classifiers to evaluate proofreading automatically.
-Since ground truth labeling is not available, the evaluation is performed by submitting our results to the CREMI leaderboard.
-Again, we use adapted Rand error to quantify the performance.
-Fig.~\ref{fig:results_fruitfly} shows the results for each of the A+,B+, and C+ datasets.
-The performance of GP* is significantly better than FP and places us XXnd on the CREMI leaderboard.
+VI is a measure of the distance between two clusterings, closely related to mutual information (the lower, the better).

### 2017-04-04 paper/arxiv/guidedproofreading_review.tex
Latest updates including supplemental for submission and the arXiv versions.

--- 2017-03-14 paper/guidedproofreading_review.tex
@@
 \usepackage{makecell}
-
+\usepackage{authblk}
 % Include other packages here, before hyperref.
@@
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\iccvfinalcopy % *** Uncomment this line for the final submission
 
-%\def\cvprPaperID{0947} % *** Enter the CVPR Paper ID here
-\def\iccvPaperID{0922}
+%\def\cvprPaperID{1234} % *** Enter the CVPR Paper ID here
+\def\iccvPaperID{1234}
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 
-\author{Daniel Haehn\\
-Institution1\\
-Institution1 address\\
-{\tt\small haehn@seas.harvard.edu}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
+\author[1,2]{Daniel Haehn\thanks{Corresponding author,  \url{haehn@seas.harvard.edu}}}
+\author[1,2]{Verena Kaynig}
+\author[3]{James Tompkin}
+\author[2]{Jeff W. Lichtman}
+\author[1,2]{Hanspeter Pfister}
+\affil[1]{Harvard Paulson School of Engineering and Applied Sciences, Cambridge, MA 02138, USA}
+\affil[2]{Harvard Brain Science Center, Cambridge, MA 02138, USA}
+\affil[3]{Brown University, Providence, RI 02912, USA}
 

### 2017-04-04 paper/arxiv/introduction.tex
Latest updates including supplemental for submission and the arXiv versions.

--- 2016-11-15 paper/introduction.tex
@@
 \section{Introduction}
-
-%In connectomics, neuroscientists annotate neurons and their connectivity within 3D volumes to gain insight into the functional structure of the brain.
-Rapid progress in automatic sample preparation and electron microscopy (EM) acquisition techniques has made it possible to image large volumes of brain tissue at $\approx4\, nm$ per pixel to identify cells, synapses, and vesicles.
-For $40\, nm$ thick sections, a $1\, mm^3$ volume of brain contains $10^{15}$ voxels, or 1 petabyte of data.
-With so much data, manual annotation is infeasible, and automatic annotation methods are needed~\cite{jain2010,Liu2014,GALA2014,kaynig2015large}.
-
-%Automatic annotation by segmentation and classification of brain tissue is challenging~\cite{isbi_challenge}.
-The state of the art uses supervised learning with convolutional neural networks~\cite{Ciresan:2012f}, or potentially even unsupervised learning~\cite{BogovicHJ13}.
-Typically, cell membranes are detected in 2D images, and the resulting region segmentation is grouped into geometrically-consistent cells across registered sections.
-Cells may also be segmented across registered sections in 3D directly.
-Using dynamic programming techniques~\cite{Masci:2013a} and a GPU cluster, these classifiers can segment $\approx1$ terabyte of data per hour ~\cite{kasthuri2015saturated}.
-This is sufficient to keep up with the 2D data capture process on state-of-the-art electron microscopes (though 3D registration is still an expensive offline operation).
 
@@
 \begin{center}
-  \includegraphics[width=\linewidth]{gfx/merge_and_split_errors.pdf}
+  \includegraphics[width=\linewidth]{merge_and_split_errors.pdf}
 \end{center}
@@
 reduces computation over methods that analyze every pixel. For merge errors, we
-invert and reuse the split classification network, instead asking it to rate a
-set of generated boundaries that hypothesize a split. %We compute
-%corrections for both types of errors.
+invert and reuse the split classification network, and ask it to rate a
+set of generated boundaries that hypothesize a split.
 
@@
 volumes of connectomics imagery.
-
-%Our goal is to add automatic detection of split and merge errors to proofreading tools.
-We design automatic classifiers that detect split and merge errors in segmentations so the user does not need to visually inspect the whole data volume to spot errors.
-A proofreading tool then recommends regions with a high probability of an error to the user, and suggest corrections to accept or reject.
-We call this process \textit{guided proofreading}.
-%
-%In this paper, we introduce classifiers to detect merge- and split errors based on a convolutional neural network (CNN).
-We believe that this is the first time that deep learning is applied to the task of proofreading.
-Our classifiers work on top of any existing automatic segmentation method to find potential errors and suggest corrections.
-Given a membrane segmentation from a fast automatic method, our classifiers operate on the boundaries of whole cell regions.
-Compared to techniques that must analyze every input pixel, we reduce the data analysis to the boundaries.
-First, we train a CNN to detect only split errors.
-The output of this network is a probability whether a boundary between two segments is valid or not.
-We then reuse the same network to also detect merge errors by generating possible boundaries within a cell and inverting the split error score.
-We create corrections for both types of errors which can be accepted or rejected.
-This reduces the proofreading operation to simple yes/no decisions.
-%
-%We further propose a greedy algorithm to perform proofreading.
-Possible erroneous regions are sorted by their score and the algorithm iteratively suggests a correction for each region.
-A user then works through this stream of regions and corrections.
-In a forced choice setting, the user either selects a correction or skips it to advance to the next region.
-This choice can be also performed automatically by running the algorithm until a configurable threshold is reached.
-In addition, if ground truth data is available, we can use a selection oracle to drive the forced choice selection.
-The oracle only accepts corrections which improve the automatic segmentation.
-This equals perfect proofreading.
-%
-%We evaluate our method automatically by threshold and oracle on multiple real-world connectomics datasets.
-To evaluate the forced choice setting, we perform a quantitative user study.
-The study targets non-experts with no previous experience of proofreading electron microscopy data.
-We ask the participants to proofread a small segmentation volume in a fixed time frame by performing yes/no decisions.
-The user study is designed as a between-subjects experiment and compares guided proofreading against two other methods: a recently published fully interactive proofreading tool named \textit{Dojo} by Haehn~\etal~\cite{haehn_dojo_2014} and the semi-automatic \textit{focused proofreading} approach by Plaza~\cite{focused_proofreading}.
-We also asked four domain experts to use guided proofreading and focused proofreading for additional comparison.
-%
-%Our first contribution is a classifier for split error detection based on a convolutional neural network.
-The classifier performs well even when trained with little amounts of training data.
-This is important since generating ground truth labels in connectomics requires manually labeling pixels and is very time-consuming.
-Our second contribution is a mechanism to identify merge-errors by re-using the split error classifier.
-Merge errors are usually less common than split errors in the oversegmented automatic labelings.
-However, they require more interaction during correction since split lines need to be manually drawn.
-Our method reduces this to a single click by providing the potential correction.
-The split and merge error identification is executed as a greedy algorithm to correct segmentation volumes, the third contribution of this paper.
-The algorithm can be driven automatically with a threshold, by an oracle based on ground truth and interactively in a forced choice setting.
-Our final contribution is our quantitative user study.
-We present statistically significant results showing that novice and expert users of guided proofreading are able to proofread a given dataset better and faster than with existing interactive and semi-automatic proofreading tools.
-As a consequence, we are able to provide tools to proofread segmentations more efficiently, and so better tackle large volumes of connectomics imagery.

### 2017-04-04 paper/arxiv/results.tex
Latest updates including supplemental for submission and the arXiv versions.

--- 2017-03-17 paper/results.tex
@@
 
-%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings.
-Lower VI scores indicate less distance to the ground truth and a better segmentation.
-For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
 Additional plots are available as supplemental material due to limited space.
@@
 \ref{fig:pr}).
-Our method exhibits higher sensitivity and lower fall-out.% for correct and erroneous patches.
-
-%\begin{table}[t]
-%\caption{Classifier comparison on an unbalanced test set of the L.~Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
-%\resizebox{\linewidth}{!}{
-%\begin{tabular}{lrrrr}
-%\toprule
-% & Precision & Recall & F1 score & Test \# \\ 
-%\midrule
-%\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
-%~~Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
-%~~Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
-%\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
-%~~Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
-%~~Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
-%\bottomrule
-%\end{tabular} 
-%}
-%\label{tab:prcyl}
-%\end{table}
+Our method exhibits higher sensitivity and lower fall-out.
 
@@
 \centering
-\includegraphics[width=0.9\linewidth]{gfx/roc.pdf}
+\includegraphics[width=0.9\linewidth]{roc.pdf}
 \caption{Receiver Operating Characteristic curves comparing focused proofreading and guided proofreading automatic correction.
@@
 \paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors). Guided proofreading achieves better classification performance (Fig. \ref{fig:pr}).
-
-%\begin{table}[t]
-%\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
-%\resizebox{\linewidth}{!}{
-%\begin{tabular}{lrrrr}
-%\toprule
-%& Precision & Recall & F1 score & Test \# \\ 
-%\midrule
-%\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
-%~~Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
-%~~Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
-%\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
-%~~Correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
-%~~Split error & 0.54 & 0.95 & 0.69 & 332 \\ 
-%\bottomrule
-%\end{tabular} 
-%}
-%\label{tab:prac4}
-%\end{table}
 
@@
 On average, users viewed $423.4$ corrections and accepted $45.8$.
-%, with an average time of $4.9$ seconds per correction. 
 Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$). Here, users viewed on average $353.4$ corrections and accepted $106.9$.
-%, with an average correction time of $6.2$ seconds. 
 While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it.
@@
 There are two explanations for this: user fatigue, and increasing uncertainty during error suggestion from the classifier.
-%Regarding fatigue, we suggest that future experiments include short breaks after every ten minutes.
 
@@
 \caption{Average proofreading speed for novice users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP).
-Our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP, while being slightly slower per correction.}%While the training of our classifier is more expensive, testing accuracy is superior.
-}
+Our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP, while being slightly slower per correction.}
 \resizebox{\linewidth}{!}{
@@
 \centering
-\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
+\includegraphics[width=\linewidth]{ac4boxplot.pdf}
 \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across slices of the AC4 subvolume, with different error correction approaches.
@@
 Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (Prec./Recall 0.82/0.73, F1-score 0.77) to negligible VI effect.
-
-%\subsection{Limitations}
-%Guided proofreading works on 2D image sections.
-This enables error correction without a computationally expensive alignment process.
-However, the output requires an additional (block-)merging step prior to 3D  analysis.

### 2017-04-04 paper/conclusion.tex
Latest updates including supplemental for submission and the arXiv versions.

@@
 This will be the target of future research.
-We provide our framework and data as free and open research at (link omitted for review).
+We provide our framework and data as free and open research at \url{http://rhoana.org/guidedproofreading/}.
+
+\section*{Acknowledgements}
+We would like to thank Stephen Plaza for detailed explanations of focused proofreading and Toufiq Parag for the configuration of the NeuroProof classifier.

### 2017-04-04 paper/supplemental/cremi.tex
Latest updates including supplemental for submission and the arXiv versions.

@@
 All parameters are unchanged and left as reported in the paper.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\linewidth]{gfx/cremi_roc_separate_small.pdf}
+\caption{Receiver Operating Characteristic curves comparing focused proofreading and guided proofreading automatic correction on the CREMI A/B/C fruit fly subvolumes.
+Guided proofreading performs better on all three datasets.}
+\label{fig:cremi_performance}
+\end{figure}
+
+\paragraph{Classification Performance.} Figure~\ref{fig:cremi_performance} compares the  focused proofreading and guided proofreading classifiers on the CREMI A/B/C datasets.
+Our method exhibits higher sensitivity and lower fall-out.
 

### 2017-04-04 paper/supplemental/guidedproofreading_supplemental_arxiv.tex
Latest updates including supplemental for submission and the arXiv versions.

--- 2017-04-04 paper/arxiv/guidedproofreading_review.tex
@@
 \usepackage{booktabs}
+\usepackage{floatrow}
 \usepackage{makecell}
 \usepackage{authblk}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
+\newfloatcommand{capbtabbox}{table}[][\FBwidth]
 % Include other packages here, before hyperref.
@@
 
-%\def\cvprPaperID{1234} % *** Enter the CVPR Paper ID here
-\def\iccvPaperID{1234}
+%\def\cvprPaperID{0947} % *** Enter the CVPR Paper ID here
+\def\iccvPaperID{0922}
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 %%%%%%%%% TITLE
-\title{Guided Proofreading of Automatic Segmentations for Connectomics}
+\title{Guided Proofreading of Automatic Segmentations for Connectomics\\~\\\textit{Supplemental Material}}
 
@@
 %%%%%%%%% ABSTRACT
-\begin{abstract}
-%
-Automatic cell image segmentation methods in connectomics produce merge and
-split errors, which require correction through proofreading. Previous research
-has identified the visual search for these errors as the bottleneck in
-interactive proofreading. To aid error correction, we develop two classifiers
-that automatically recommend candidate merges and splits to the user. These
-classifiers use a convolutional neural network (CNN) that has been trained with
-errors in automatic segmentations against expert-labeled ground truth. Our
-classifiers detect potentially-erroneous regions by considering a large context
-region around a segmentation boundary. Corrections can then be performed by a
-user with yes/no decisions, which reduces variation of information $7.5\times$ faster than previous
-proofreading methods. We also present a fully-automatic mode that uses a
-probability threshold to make merge/split decisions. Extensive experiments using
-the automatic approach and comparing performance of novice and expert users
-demonstrate that our method performs favorably against state-of-the-art
-proofreading methods on different connectomics datasets.
-%
-\end{abstract}
 
 %%%%%%%%% BODY TEXT
-\input{introduction}
 
-\input{related_work}
+\input{architecture}
+\input{leftcylinder}
+\input{cremi}
+\input{userstudy}
 
-\input{method}
-
-\input{evaluation}
-
-\input{results}
-
-\input{conclusion}
-
+\newpage
 {\small

### 2017-11-01 paper/results.tex
Several changes from the rebuttal.

@@
 For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations.
-Median VI $=0.476$ ($SD=0.089$), with mean VI $=0.512$ ($SD=0.09$).
+%\CHANGED{Our hypothesis is that VI reduction is significantly better with GP than with other tools.
+For this, we treat VI as a continuous variable and use analysis of variance (ANOVA) followed by parametric tests (Welch's t-test).}
+\CHANGED{The initial segmentation yields a} median VI $=0.476$ ($SD=0.089$), with mean VI $=0.512$ ($SD=0.09$).
 Most novices and all experts were able to improve upon this score with both focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).
@@
 With guided proofreading, the median VI was $0.396$ ($SD=0.032$, Fig.~\ref{fig:ac4boxplot}).
+
+\CHANGED{\paragraph{Confirmatory Data Analysis.} We use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo).
+Our hypothesis is that VI reduction is significantly better with GP than with other tools.
+For this, we treat VI as a continuous variable and use analysis of variance (ANOVA) followed by parametric tests (Welch's t-test).}
+
+\CHANGED{\emph{AC4 subvolume.} For novice performance, we observe a significant effect ($\alpha = 0.05$) of which proofreading tool is used for the three conditions GP, FP, and Dojo [$F(2,27) = 6.446, p = 0.005$] when comparing the mean VI outcome.
+Post hoc comparisons (after Bonferroni correction) indicate that the mean VI for GP is significantly lower than for FP [$t_{27} = -2.7696, p = 0.0168$], and that the mean VI for GP is significantly lower than for Dojo [$t_{27} = -4.407, p < 0.001$].
+This means that novices using GP perform significantly better than using FP and Dojo.
+A similar trend is visible when comparing the expert performance between GP and FP as the change in mean VI of GP is significantly better ([$F(1,18) = 7.054, p = 0.016$] and [$t_{18} = -2.6559, p = 0.0216$]).
+For automatic selection with threshold, the difference in mean VI is very large and GP also performs significantly better ([$F(1,18) = 89.902, p < 0.001$] and [$t_{18} = 9.482, p < 0.001$]).
+The final VI scores of the selection oracle with GP and FP are very similar and the difference between them is not significant [$F(1,18) = 0.795, p = 0.384$].
+However, the VI reduction rate of GP is much higher as seen in Fig.~\ref{fig:ac4trails} (right).}
+
+\CHANGED{\emph{L.
+Cylinder.} The automatic selection with threshold yields similar results as on the other dataset and we observe a significant improvement when using GP instead of FP ([$F(1,98) = 26.676, p < 0.001$], post hoc comparison [$t_{98} = 5.1648, p < 0.001$]).
+The selection oracles of GP and FP result in very similar final VI scores and the difference is not significant [$F(1,98) = 0.071, p = 0.790$], but GP reaches minimum VI faster in $10,000$ corrections versus FP in $26,170$ corrections.}
 

### 2017-11-06 gp/legacy.py
Some code updates.

@@ -410,7 +410,7 @@ class Legacy(object):
 
 
   @staticmethod
-  def get_merge_error_image(input_image, input_rhoana, label, border):
+  def get_merge_error_image(input_image, input_rhoana, label, border, returnbb=False):
 
     binary = Util.threshold(input_rhoana, label)
     binary_dilated = mh.dilate(binary.astype(np.bool))
@@ -491,11 +491,15 @@ class Legacy(object):
 
     sliceoverview = e    
 
+
+    if returnbb:
+      return cropped_image, cropped_binary_border, cropped_combined_border, cropped_border_only, cropped_result, result, sliceoverview, cropped_binary, cropped_fusion, cropped_slice_overview, binary_bbox
+
     return cropped_image, cropped_binary_border, cropped_combined_border, cropped_border_only, cropped_result, result, sliceoverview, cropped_binary, cropped_fusion, cropped_slice_overview
 
 
   @staticmethod
-  def get_split_error_image(input_image, input_rhoana, labels):
+  def get_split_error_image(input_image, input_rhoana, labels, returnbb=False):
 
     if not isinstance(labels, list):
       labels = [labels]
@@ -567,7 +571,12 @@ class Legacy(object):
 
     slice_overview = e    
 
-    return cropped_image, cropped_labels, cropped_borders, cropped_binary_border, cropped_binary_labels, slice_overview, cropped_slice_overview
+    if returnbb:
+      return cropped_image, cropped_labels, cropped_borders, cropped_binary_border, cropped_binary_labels, slice_overview, cropped_slice_overview, cropped_rhoana_bbox
+
+    else:
+      return cropped_image, cropped_labels, cropped_borders, cropped_binary_border, cropped_binary_labels, slice_overview, cropped_slice_overview
+
 
 
 
@@ -580,7 +589,7 @@ class Legacy(object):
     label_sizes = Util.get_histogram(e)
 
     if len(label_sizes) < 2:
-      print 'weird'
+      #print 'weird'
       return e
 
     # we only want to keep the two largest labels

### 2017-11-06 ui/manager.py

@@ -23,11 +23,11 @@ class Manager(object):
 
     self._mode = 'GP'
 
-  def start( self, mode ):
+  def start( self, mode, cnn_path='../nets/IPMLB_FULL.p', verbose=True ):
     '''
     '''
 
-    self._cnn = UITools.load_cnn()
+    self._cnn = UITools.load_cnn(cnn_path)
 
     self._mode = mode
 
@@ -45,7 +45,8 @@ class Manager(object):
 
 
     elif self._mode == 'GP':
-        print 'Using GP proper'
+        if verbose:
+            print 'Using GP proper'
 
         self._merge_errors = self.load_merge_errors()
         self._bigM = self.load_split_errors()
@@ -82,8 +83,9 @@ class Manager(object):
     self._input_rhoana = input_rhoana
     self._dojo_bbox = dojo_bbox
 
-    print 'VI at start:', UITools.VI(self._input_gold, self._input_rhoana)[1]
-    print 'aRE at start:', UITools.adaptedRandError(self._input_rhoana, self._input_gold)[1]
+    if verbose:
+        print 'VI at start:', UITools.VI(self._input_gold, self._input_rhoana)[1]
+        print 'aRE at start:', UITools.adaptedRandError(self._input_rhoana, self._input_gold)[1]
 
 
   def gen_active_label_features(self):
@@ -229,7 +231,7 @@ class Manager(object):
     input_rhoana = self._input_rhoana
 
 
-    a,b,c,d,e,f,g,h,i,j = gp.Legacy.get_merge_error_image(input_image[z], input_rhoana[z], label, border)
+    a,b,c,d,e,f,g,h,i,j,k = gp.Legacy.get_merge_error_image(input_image[z], input_rhoana[z], label, border, returnbb=True)
 
     border_before = b
     labels_before = h
@@ -237,8 +239,9 @@ class Manager(object):
     labels_after = i
     slice_overview = g
     cropped_slice_overview = j
+    bbox = k
 
-    return border_before, border_after, labels_before, labels_after, slice_overview, cropped_slice_overview
+    return border_before, border_after, labels_before, labels_after, slice_overview, cropped_slice_overview, bbox
     
   def get_split_error_image(self, split_error, number=1):
 
@@ -249,7 +252,7 @@ class Manager(object):
     input_prob = self._input_prob
     input_rhoana = self._input_rhoana
 
-    a,b,c,d,e,f,g = gp.Legacy.get_split_error_image(input_image[z], input_rhoana[z], labels)
[…]

### 2017-11-06 ui/uitools.py

@@ -13,9 +13,9 @@ import cPickle as pickle
 class UITools(object):
 
   @staticmethod
-  def load_cnn():
+  def load_cnn(path='../nets/IPMLB_FULL.p'):
 
-    with open('../nets/IPMLB_FULL.p', 'rb') as f:
+    with open(path, 'rb') as f:
         cnn = pickle.load(f)
 
     cnn.uuid = 'IPMLB'

### 2017-11-06 ui/webserver.py

@@ -115,7 +115,7 @@ class WebServer:
       time_used = splitted_request[4]
       self._manager._corrections.append([splitted_request[1], clicked_correction])
       self._manager._correction_times.append(time_used)
-      new_mode = correction_function(clicked_correction)
+      new_mode, oracle_choice, delta_vi, bbox = correction_function(clicked_correction)
 
       # print self._manager._corrections
       # print self._manager._correction_times

### 2017-11-06 paper/rebuttal/CVPR2017/egrebuttal.tex

--- 2017-01-30 paper/rebuttal/egrebuttal.tex
@@
 
-Thank you for your time and constructive comments. We will fix all minor issues.
+Thank you for your time and constructive comments. We will fix all minor issues; we address the major issues below.
 
@@
 We agree that the presentation of this comparison was not ideal.
-We will add Table~\ref{tab:correctiontimes} to make this clearer (previously reported in lines 756-765, slopes in Fig.~6, and column 3 in Fig.~7).
+We will add Tab.~\ref{tab:correctiontimes} to make this more clear (previously reported in lines 756-765, slopes in Fig.~6, and column 3 in Fig.~7).
 
@@
 In our automatic segmentation pipeline (line 499), GALA uses a random forest classifier to agglomerate segments.
-While it does not require user interaction, it does require parameters.
+We used an agglomeration level of 0.3 (after a grid search).
 We will add a section to the supplemental material containing a full description of the approach and our use of it.

### 2017-11-06 paper/method.tex

@@
 However, we can reuse the same trained CNN for this task.
-Similar to guided volume editing by Karimov~\etal~\cite{karimov_guided_volume_editing}, we generate potential borders within a segment.
-For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
+
+\CHANGED{To find merge errors, we generate candidate splits within a label segment and use our split error classifier to rate them.
+If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.}
+
+%Similar to guided volume editing by Karimov~\etal~\cite{karimov_guided_volume_editing}, we generate potential borders within a segment.
+
+%For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
 We perform watershed on the inverted grayscale EM image.
 This yields 50 candidate splits.
+\CHANGED{For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
+As preprocessing, we dilate the label by 20 pixel which is motivated by our observation that the generated splits tend to attach to real membrane boundaries.
+These boundaries are then individually rated using our split error classifier.}
 
-Dilation of the segment prior to watershed is motivated by our observation that the generated splits tend to attach to real membrane boundaries.
+%We perform watershed on the inverted grayscale EM image.
+This yields 50 candidate splits.
+Prior to watershed, we dilate the label by 20 pixel which is motivated by our observation that the generated splits tend to attach to real membrane boundaries.
 These boundaries are then individually rated using our split error classifier.
-For this, we invert the probability score such that a correct split (previously encoded as $p=0$) is most likely a candidate for a merge error (now encoded as $p=1$).
+
+\CHANGED{Fig. \ref{fig:merge_error} illustrates this procedure. Pseudo code is available as supplemental material to promote understanding.}
+
+%For this, we invert the probability score such that a correct split (previously encoded as $p=0$) is most likely a candidate for a merge error (now encoded as $p=1$).
 In other words, if a generated boundary is ranked as correct, it probably should be in the segmentation.

### 2017-11-06 paper/evaluation.tex
Fix section 5.1.
Fix references, add new text (marked in red).

@@
 The probabilities are used to seed watershed and generate an oversegmentation using superpixels.
-Agglomeration is then performed by the GALA active learning classifier with a fixed agglomeration threshold of 0.3~\cite{nunez2014graph}.
+Agglomeration is then performed by the GALA active learning classifier with a fixed agglomeration threshold of 0.3~\cite{GALA2014}.
 We describe this approach in the supplemental material.

### 2017-11-06 paper/introduction.tex
Space squeezing.
Fix references, add new text (marked in red).

@@
 reduces computation over methods that analyze every pixel. For merge errors, we
-invert and reuse the split classification network, instead asking it to rate a
+invert and reuse the split classification network, and ask it to rate a
 set of generated boundaries that hypothesize a split. %We compute
@@
 expert users.
+%
+\CHANGED{Finally, we present the first standardized benchmark for proofreading in connectomics as an open research platform.}
 

### 2017-11-06 paper/related_work.tex
Several changes from the rebuttal.
Fix references, add new text (marked in red).

@@
 We were inspired by this approach, but instead we generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}).
+\CHANGED{Recently, Zung \etal~\cite{error_detection_framework} report the successful application of 3D multiscale convolutional neural networks for error detection and correction as an additional post-processing step after segmentation.
+Their framework does not include humans in the loop and can be used as input to our proposed method.}
 

### 2017-11-06 paper/results.tex
Fix references, add new text (marked in red).

--- 2017-03-17 paper/results.tex
@@
 For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
-Additional plots are available as supplemental material due to limited space.
+Additional plots and confirmatory data analysis are available as supplemental material due to limited space.
 
@@
 
+\subsection{Proofreading in Connectomics Benchmark}
+
+\CHANGED{We present the first proofreading benchmark for the field of connectomics as an open research platform.
+We include representative connectomics data with ground truth labels, all results and participant demographics from the interactive experiments by Haehn~\etal~\cite{haehn_dojo_2014}, our complete results from this paper, as well as standardized metrics for comparing different proofreading approaches at (link omitted for review).
+We hope that this framework facilitates future developments and allows comparisons for conquering the important proofreading problem in connectomics.}
+
 %\subsection{Limitations}

### 2017-11-06 paper/supplemental/leftcylinder.tex
Latest updates including supplemental for submission and the arXiv versions.
Update supplemental material.

@@
 \centering
-\includegraphics[width=\linewidth]{gfx/datasets.pdf}
+\includegraphics[width=\linewidth]{gfx/datasets.png}
 \caption{The five different datasets we use for evaluation.
@@
 \end{figure}
+
+\section{Confirmatory Data Analysis}
+
+\CHANGED{In the paper, we use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo).
+Our hypothesis is that VI reduction is significantly better with GP than with other tools.
+For this, we treat VI as a continuous variable and use analysis of variance (ANOVA) followed by parametric tests (Welch's t-test).}
+
+\CHANGED{\paragraph{AC4 subvolume.} For novice performance, we observe a significant effect ($\alpha = 0.05$) of which proofreading tool is used for the three conditions GP, FP, and Dojo [$F(2,27) = 6.446, p = 0.005$] when comparing the mean VI outcome.
+Post hoc comparisons (after Bonferroni correction) indicate that the mean VI for GP is significantly lower than for FP [$t_{27} = -2.7696, p = 0.0168$], and that the mean VI for GP is significantly lower than for Dojo [$t_{27} = -4.407, p < 0.001$].
+This means that novices using GP perform significantly better than using FP and Dojo.
+A similar trend is visible when comparing the expert performance between GP and FP as the change in mean VI of GP is significantly better ([$F(1,18) = 7.054, p = 0.016$] and [$t_{18} = -2.6559, p = 0.0216$]).
+For automatic selection with threshold, the difference in mean VI is very large and GP also performs significantly better ([$F(1,18) = 89.902, p < 0.001$] and [$t_{18} = 9.482, p < 0.001$]).
+The final VI scores of the selection oracle with GP and FP are very similar and the difference between them is not significant [$F(1,18) = 0.795, p = 0.384$].
+However, the VI reduction rate of GP is much higher as seen in Fig.~\ref{fig:ac4trails} (right).}
+
+\CHANGED{\paragraph{L.
+Cylinder.} The automatic selection with threshold yields similar results as on the other dataset and we observe a significant improvement when using GP instead of FP ([$F(1,98) = 26.676, p < 0.001$], post hoc comparison [$t_{98} = 5.1648, p < 0.001$]).
+The selection oracles of GP and FP result in very similar final VI scores and the difference is not significant [$F(1,98) = 0.071, p = 0.790$], but GP reaches minimum VI faster in $10,000$ corrections versus FP in $26,170$ corrections.}

### 2017-11-13 paper/introduction.tex
Update paper.

@@
 Guided proofreading is applicable to all existing automatic segmentation methods that
-produce a label map. As such, we believe that our approach is a promising
-direction to proofread segmentations more efficiently and better tackle large
-volumes of connectomics imagery.
+produce a label map.
+\CHANGED{While we train models based on traditional CNN architectures, we propose an error correction framework with human interaction that works in principle with any potential classifier.}
+As such, we believe that our approach is a promising direction to proofread segmentations more efficiently and better tackle large volumes of connectomics imagery.
 

### 2017-11-13 paper/results.tex
Update supplemental material.
Update paper.

@@
 For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
-Additional plots and confirmatory data analysis are available as supplemental material due to limited space.
+Additional plots \CHANGED{and confirmatory data analysis} are available as supplemental material due to limited space.
 
@@
 
-\paragraph{Subjective responses.} We used the NASA-TLX workload index to record subjective responses.
-Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading.
-However, these differences were not statistically significant.
-This is unsurprising as the user interface was the same for both groups.
-
 \subsection{Automatic Error Correction}
@@
 \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across slices of the AC4 subvolume, with different error correction approaches.
-The variation resulting from performance of FP with automatic selection is $4.5\times$ higher than GP (as indicated by the arrow), with median VI of $1.9$ and $SD=0.496$.}
+The performance of FP with automatic selection is $4.5\times$ higher than GP (\protect\includegraphics[width=0.2cm]{gfx/arrow.pdf}), with median VI of $1.9$ and $SD=0.496$.}
 \label{fig:ac4boxplot}

### 2017-11-13 paper/supplemental/userstudy.tex
Update plots for the supplemental material.
Latest updates including supplemental for submission and the arXiv versions.
Update supplemental.

@@
 \hspace{2mm}
-\hrule
 }
@@
 \end{table}
+
+\subsection{User Interface}
+
+\CHANGED{We integrate guided proofreading into an existing large data connectomics workflow.
+The web-based system is designed with a novice-friendly user interface (Fig.
+5 in the paper, and the supplemental video).
+We show the current labeling of a cell boundary outline and its proposed correction overlayed on EM image data.
+The user cannot distinguish the current labeling from the proposed correction to avoid selection bias.
+We also show a solid overlay of the current and the proposed labeling.
+In addition, we show the image without overlays to provide an unoccluded view.
+User interaction is simple and involves one mouse click on either the current labeling or the correction.
+After interaction, the next potential error is shown.}
 
@@
 
-After the experiment, we acquired subjective responses using the NASA-TLX task load index (figure~\ref{fig:nasatxl}).
+After the experiment, we acquired subjective responses using the NASA-TLX task load index (Figure~\ref{fig:nasatxl}).
 We performed ANOVA to test for statistical significance~\cite{shaffer1995}.
 Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading but the analysis did not yield any significance.
+\CHANGED{This is unsurprising as the user interface was the same for both groups.}
 

### 2017-11-13 paper/method.tex

@@
 \CHANGED{To find merge errors, we generate candidate splits within a label segment and use our split error classifier to rate them. 
-If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.}
+%If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.
+If the classifier yields a result close to 0, the candidate split is likely to be correct. We then use it to fix the merge error.}
 
@@
 This yields 50 candidate splits.
-\CHANGED{For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
+To generate candidate splits for each segmentation label, we create 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
+\CHANGED{%For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. 
 As preprocessing, we dilate the label by 20 pixel which is motivated by our observation that the generated splits tend to attach to real membrane boundaries.
-These boundaries are then individually rated using our split error classifier.}
+These boundaries are then individually rated using our split error classifier.
+Fig.
+\ref{fig:merge_error} illustrates this procedure.
+Pseudo code is available as supplemental material to promote understanding.}
 
@@
 These boundaries are then individually rated using our split error classifier.
-
-\CHANGED{Fig. \ref{fig:merge_error} illustrates this procedure. Pseudo code is available as supplemental material to promote understanding.}
 
@@
 Therefore, we only present merge errors that have a probability threshold higher than $1-p_t$.
+\CHANGED{Fig.~\ref{fig:ui} shows an example correction using the forced choice setting within our framework.}
 
@@
 
-\subsection{User Interface}
-
-We integrate guided proofreading into an existing large data connectomics workflow.
-The web-based system is designed with a novice-friendly user interface (Fig.~\ref{fig:ui}).
-We show the current labeling of a cell boundary outline and its proposed correction overlayed on EM image data.
-The user cannot distinguish the current labeling from the proposed correction to avoid selection bias.
-We also show a solid overlay of the current and the proposed labeling.
-In addition, we show the image without overlays to provide an unoccluded view.
-User interaction is simple and involves one mouse click on either the current labeling or the correction.
-After interaction, the next potential error is shown.
-
 \begin{figure}[t]
 \includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
-\caption{User interface.
-A candidate error region is shown on the left.
+\caption{\CHANGED{Example error correction within the forced choice setting.} A candidate error region is shown on the left.
 The user must choose between the region being a split error which needs correcting (center) or not (right).

### 2017-11-13 paper/supplemental/cremi.tex

@@
 \caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the CREMI A dataset, with different error correction approaches.
-The variation resulting from performance of FP with automatic selection is $5.4\times$ higher than GP (as indicated by the arrow), with median VI of $5.32$ and $SD=0.009$.
+The variation resulting from performance of FP with automatic selection is $5.4\times$ higher than GP (\protect\includegraphics[width=0.2cm]{gfx/arrow.pdf}), with median VI of $5.32$ and $SD=0.009$.
 GP does not reach the best possible VI as discussed in the text.}
@@
 We compare automatic selection and oracle selection.
-The variation resulting from performance of FP with automatic selection is $3\times$ higher than GP (as indicated by the arrow), with median VI of $4.25$ and $SD=0.07$.}
+The variation resulting from performance of FP with automatic selection is $3\times$ higher than GP (\protect\includegraphics[width=0.2cm]{gfx/arrow.pdf}), with median VI of $4.25$ and $SD=0.07$.}
 \label{fig:cremiBboxplot}
@@
 \caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across the CREMI C subvolume, with different error correction approaches.
-The variation resulting from performance of FP with automatic selection is $3\times$ higher than GP (as indicated by the arrow), with median VI of $4.81$ and $SD=0.08$.}
+The variation resulting from performance of FP with automatic selection is $3\times$ higher than GP (\protect\includegraphics[width=0.2cm]{gfx/arrow.pdf}), with median VI of $4.81$ and $SD=0.08$.}
 \label{fig:cremiCboxplot}

### 2017-11-13 paper/supplemental/leftcylinder.tex

@@
 \caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the L.~Cylinder dataset, with different error correction approaches.
-The variation resulting from performance of FP with automatic selection is $7.8\times$ higher than GP (as indicated by the arrow), with median VI of $2.75$ and $SD=0.789$.}
+The variation resulting from performance of FP with automatic selection is $7.8\times$ higher than GP (\protect\includegraphics[width=0.2cm]{gfx/arrow.pdf}), with median VI of $2.75$ and $SD=0.789$.}
 \label{fig:cylboxplot}
@@
 
-\CHANGED{In the paper, we use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo).
+\CHANGED{We use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo).
 Our hypothesis is that VI reduction is significantly better with GP than with other tools.
-For this, we treat VI as a continuous variable and use analysis of variance (ANOVA) followed by parametric tests (Welch's t-test).}
+For this, we treat VI as a continuous variable and use analysis of variance (ANOVA~\cite{shaffer1995}) followed by parametric tests (Welch's t-test~\cite{welch}).}
 

### 2017-11-14 paper/introduction.tex
James going through the edits.

--- 2017-11-06 paper/introduction.tex
@@
 First, we present a CNN-based boundary classifier for split errors, plus a merge
-error classifier that inverts the split error classifier. This is used to
-propose merge error corrections, removing the need to manually draw the missing
-edge. These classifiers perform well without much training data, which is
+error classifier that inverts the split error classifier. This proposes merge error corrections, 
+which removes the need to manually draw the missing
+edge. \CHANGED{These classifiers automatically reduce error with little training data,} which is
 expensive to collect for connectomics data.
 %
-Second, we developed a guided proofreading approach to correcting segmentation
-volumes, and an assessment scenario comparing forced-choice interaction with
+Second, we develop a \CHANGED{human-}guided proofreading approach to correcting segmentation
+volumes, and compare forced-choice interaction with
 automatic and oracle proofreading.
 %
-Third, we present the results of a quantitative user study assessing
+Third, we present results of a quantitative user study assessing
 guided proofreading. Our method is able to reduce segmentation
@@
 %
-\CHANGED{Finally, we present the first standardized benchmark for proofreading in connectomics as an open research platform.}
+\CHANGED{Fourth, we present the first connectomics proofreading benchmark, with image, label, and human interaction data, and evaluation code.}
 
-Guided proofreading is applicable to all existing automatic segmentation methods that
-produce a label map. As such, we believe that our approach is a promising
-direction to proofread segmentations more efficiently and better tackle large
-volumes of connectomics imagery.
+Guided proofreading is applicable to all existing automatic segmentation methods that produce a label map.
+\CHANGED{While we train models based on traditional CNN architectures, we propose an error correction approach with human interaction that works with many classifiers.}
+As such, we believe that our approach is a promising direction to proofread segmentations more efficiently and better tackle large volumes of connectomics imagery.
 

### 2017-11-14 paper/related_work.tex
James going through the edits.

--- 2016-11-15 paper/related_work.tex
@@
 We were inspired by this approach, but instead we generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}).
+\CHANGED{Recently, Zung \etal~\cite{error_detection_framework} report the successful application of 3D multiscale convolutional neural networks for error detection and correction as a post-processing step after segmentation.
+Their framework is purely automatic, and can be used as input to our proposed method.}
 

### 2017-11-14 paper/conclusion.tex
Restructure rebuttals.
Several changes from the rebuttal.
James edits

--- 2017-03-17 paper/conclusion.tex
@@
 We provide our framework and data as free and open research at (link omitted for review).
-Humans are the bottleneck when proofreading segmentation data and minimizing the manual labor is the goal.
-Our classifiers suggest potential errors and corrections better than existing methods.
-This reduces the time spent finding and correcting errors.
-Our experiments also show that automatic proofreading has potential to further reduce human involvement.
-This will be the target of future research.
-We provide our framework and data as free and open research at (link omitted for review).
+
+Manual proofreading of connectomics segmentations is currently necessary, but it is a time consuming and error-prone task.
+We attempt to minimize manual labor and reduce the human bottleneck.
+Our classifiers can detect errors and suggest potential corrections to automatically improve segmentations, but performance can increase with guided human attention.
+Our approach makes it easier for both novices and experts to proofread successfully, and is significantly better than the existing baseline at this task.
+This helps reduces the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data.
+Ultimately, this moves us closer to automatic proofreading.
+(source/data URL omitted for review).%\url{http://rhoana.org/guidedproofreading/}.
+
+%Our experiments also show that automatic proofreading has potential to further reduce human involvement.
+We provide our framework and data as free and open research at (link omitted for review).%\url{http://rhoana.org/guidedproofreading/}.
+
+%\section*{Acknowledgements}
+%We would like to thank Stephen Plaza for detailed explanations of focused proofreading and Toufiq Parag for the configuration of the NeuroProof classifier.

### 2017-11-14 paper/method.tex
James edits

@@
 %If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.
-If the classifier yields a result close to 0, the candidate split is likely to be correct. We then use it to fix the merge error.}
+If the classifier yields a result close to 0, the candidate split is likely to be correct. Then, we use it to fix the merge error.}
 
@@
 \CHANGED{%For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. 
-As preprocessing, we dilate the label by 20 pixel which is motivated by our observation that the generated splits tend to attach to real membrane boundaries.
-These boundaries are then individually rated using our split error classifier.
-Fig.
-\ref{fig:merge_error} illustrates this procedure.
-Pseudo code is available as supplemental material to promote understanding.}
+As preprocessing, we dilate the label by 20 pixels.
+This is motivated by our observation that the generated splits tend to attach to real membrane boundaries.
+These boundaries are then individually rated using our split error classifier (Fig.~\ref{fig:merge_error}).
+Pseudo code is available in supplemental material.}
 

### 2017-11-14 paper/results.tex
James edits

@@
 
-\CHANGED{We present the first proofreading benchmark for the field of connectomics as an open research platform.
-We include representative connectomics data with ground truth labels, all results and participant demographics from the interactive experiments by Haehn~\etal~\cite{haehn_dojo_2014}, our complete results from this paper, as well as standardized metrics for comparing different proofreading approaches at (link omitted for review).
-We hope that this framework facilitates future developments and allows comparisons for conquering the important proofreading problem in connectomics.}
+\CHANGED{Along with our classifier code, we also present this evaluation scenario to the community as the first benchmark for proofreading in connectomics.
+We include representative connectomics data with ground truth labels, all participant results and demographics from the interactive experiments, our complete results from this paper, and standardized metrics for comparing different proofreading approaches.
+This framework will facilitate further comparisons to help make progress in connectomics (link omitted for review).}
 

### 2017-11-14 paper/supplemental/cremi.tex
James edits

@@
 
-Figure~\ref{fig:cremiAtrails} and~\ref{fig:cremiAboxplot} compare Plaza's focused proofreading and guided proofreading on the 5 sections of the CREMI A dataset.
+Figure~\ref{fig:cremiAtrails} and~\ref{fig:cremiAboxplot} compare Plaza's focused proofreading and guided proofreading on the five sections of CREMI A.
 

### 2017-11-14 paper/supplemental/leftcylinder.tex
James edits

@@
 
-\CHANGED{We use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo).
+We use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo).
 Our hypothesis is that VI reduction is significantly better with GP than with other tools.
-For this, we treat VI as a continuous variable and use analysis of variance (ANOVA~\cite{shaffer1995}) followed by parametric tests (Welch's t-test~\cite{welch}).}
+For this, we treat VI as a continuous variable and use analysis of variance (ANOVA~\cite{shaffer1995}) followed by parametric tests (Welch's t-test~\cite{welch}).
 
-\CHANGED{\paragraph{AC4 subvolume.} For novice performance, we observe a significant effect ($\alpha = 0.05$) of which proofreading tool is used for the three conditions GP, FP, and Dojo [$F(2,27) = 6.446, p = 0.005$] when comparing the mean VI outcome.
+\paragraph{AC4 subvolume.} For novice performance, we observe a significant effect ($\alpha=0.05$) of which proofreading tool is used for the three conditions GP, FP, and Dojo [$F(2,27) = 6.446, p = 0.005$] when comparing the mean VI outcome.
 Post hoc comparisons (after Bonferroni correction) indicate that the mean VI for GP is significantly lower than for FP [$t_{27} = -2.7696, p = 0.0168$], and that the mean VI for GP is significantly lower than for Dojo [$t_{27} = -4.407, p < 0.001$].
@@
 The final VI scores of the selection oracle with GP and FP are very similar and the difference between them is not significant [$F(1,18) = 0.795, p = 0.384$].
-However, the VI reduction rate of GP is much higher as seen in Fig.~\ref{fig:ac4trails} (right).}
+However, the VI reduction rate of GP is much higher (Fig.~6, main paper, right).
 
-\CHANGED{\paragraph{L.
-Cylinder.} The automatic selection with threshold yields similar results as on the other dataset and we observe a significant improvement when using GP instead of FP ([$F(1,98) = 26.676, p < 0.001$], post hoc comparison [$t_{98} = 5.1648, p < 0.001$]).
-The selection oracles of GP and FP result in very similar final VI scores and the difference is not significant [$F(1,98) = 0.071, p = 0.790$], but GP reaches minimum VI faster in $10,000$ corrections versus FP in $26,170$ corrections.}
+\paragraph{L.
+Cylinder.} The automatic selection with threshold yields similar results as on the AC4 dataset, and we observe a significant improvement when using GP instead of FP ([$F(1,98) = 26.676, p < 0.001$], post hoc comparison [$t_{98} = 5.1648, p < 0.001$]).
+The selection oracles of GP and FP result in very similar final VI scores and the difference is not significant [$F(1,98) = 0.071, p = 0.790$], but GP reaches minimum VI faster in $10,000$ corrections versus FP in $26,170$ corrections.

### 2017-11-14 paper/supplemental/userstudy.tex
James edits

@@
 
-\CHANGED{We integrate guided proofreading into an existing large data connectomics workflow.
+We integrate guided proofreading into an existing large data connectomics workflow.
 The web-based system is designed with a novice-friendly user interface (Fig.
@@
 User interaction is simple and involves one mouse click on either the current labeling or the correction.
-After interaction, the next potential error is shown.}
+After interaction, the next potential error is shown.
 
@@
 Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading but the analysis did not yield any significance.
-\CHANGED{This is unsurprising as the user interface was the same for both groups.}
+This is unsurprising as the user interface was the same for both groups.
 

### 2017-11-14 paper/method.tex
Fixes

@@
 %If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.
-If the classifier yields a result close to 0, the candidate split is likely to be correct. Then, we use it to fix the merge error.}
+If the classifier yields a result close to 0, the candidate split is likely to be correct and we have found a potential correction.}
 
@@
 To generate candidate splits for each segmentation label, we create 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
-\CHANGED{%For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. 
-As preprocessing, we dilate the label by 20 pixels.
-This is motivated by our observation that the generated splits tend to attach to real membrane boundaries.
-These boundaries are then individually rated using our split error classifier (Fig.~\ref{fig:merge_error}).
-Pseudo code is available in supplemental material.}
+%For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. 
+\CHANGED{We observed that correct splits tend to include label boundaries, and so we promote their inclusion by we dilating the label by 20 pixels.
+This lets the watershed algorithm `pick up' the boundary more successfully.
+These boundaries are then individually rated using our split error classifier (Fig.~\ref{fig:merge_error}; pseudo code in supplemental).}
 

### 2017-11-15 paper/conclusion.tex
Getting ready for submission..

@@
 
-Manual proofreading of connectomics segmentations is currently necessary, but it is a time consuming and error-prone task.
+Manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task.
 We attempt to minimize manual labor and reduce the human bottleneck.
@@
 Our approach makes it easier for both novices and experts to proofread successfully, and is significantly better than the existing baseline at this task.
-This helps reduces the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data.
-Ultimately, this moves us closer to automatic proofreading.
-(source/data URL omitted for review).%\url{http://rhoana.org/guidedproofreading/}.
+This helps reduce the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data.
+We provide our framework and data as free and open research at (source/data URL omitted for review).%\url{http://rhoana.org/guidedproofreading/}.
 

### 2017-11-15 paper/introduction.tex
Getting ready for submission..

--- 2017-11-06 paper/introduction.tex
@@
 First, we present a CNN-based boundary classifier for split errors, plus a merge
-error classifier that inverts the split error classifier. This is used to
-propose merge error corrections, removing the need to manually draw the missing
-edge. These classifiers perform well without much training data, which is
-expensive to collect for connectomics data.
+error classifier that inverts the split error classifier. This proposes merge error corrections, 
+which removes the need to manually draw the missing
+edge. These classifiers automatically reduce error with little training data, which is expensive to collect for connectomics data.
 %
-Second, we developed a guided proofreading approach to correcting segmentation
-volumes, and an assessment scenario comparing forced-choice interaction with
+Second, we develop a human-guided proofreading approach to correcting segmentation
+volumes, and compare forced-choice interaction with
 automatic and oracle proofreading.
 %
-Third, we present the results of a quantitative user study assessing
+Third, we present results of a quantitative user study assessing
 guided proofreading. Our method is able to reduce segmentation
@@
 %
-\CHANGED{Finally, we present the first standardized benchmark for proofreading in connectomics as an open research platform.}
+Fourth, we present the first connectomics proofreading benchmark, with image, label, and human interaction data, and evaluation code.
 
-Guided proofreading is applicable to all existing automatic segmentation methods that
-produce a label map. As such, we believe that our approach is a promising
-direction to proofread segmentations more efficiently and better tackle large
-volumes of connectomics imagery.
+Guided proofreading is applicable to all existing automatic segmentation methods that produce a label map.
+While we train models based on traditional CNN architectures, we propose an error correction approach with human interaction that works with many classifiers.
+As such, we believe that our approach is a promising direction to proofread segmentations more efficiently and better tackle large volumes of connectomics imagery.
 

### 2017-11-15 paper/method.tex
Getting ready for submission..

@@
 
-\CHANGED{To find merge errors, we generate candidate splits within a label segment and use our split error classifier to rate them. 
+To find merge errors, we generate candidate splits within a label segment and use our split error classifier to rate them. 
 %If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.
-If the classifier yields a result close to 0, the candidate split is likely to be correct and we have found a potential correction.}
+If the classifier yields a result close to 0, the candidate split is likely to be correct and we have found a potential correction.
 
@@
 %For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. 
-\CHANGED{We observed that correct splits tend to include label boundaries, and so we promote their inclusion by we dilating the label by 20 pixels.
+We observed that correct splits tend to include label boundaries, and so we promote their inclusion by dilating the label 20 pixels.
 This lets the watershed algorithm `pick up' the boundary more successfully.
-These boundaries are then individually rated using our split error classifier (Fig.~\ref{fig:merge_error}; pseudo code in supplemental).}
+These boundaries are then individually rated using our split error classifier (Fig.~\ref{fig:merge_error}, pseudo code in supplemental).
 
@@
 Therefore, we only present merge errors that have a probability threshold higher than $1-p_t$.
-\CHANGED{Fig.~\ref{fig:ui} shows an example correction using the forced choice setting within our framework.}
+Fig.~\ref{fig:ui} shows an example correction using the forced choice setting within our framework.
 
@@
 \includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
-\caption{\CHANGED{Example error correction within the forced choice setting.} A candidate error region is shown on the left.
+\caption{Example error correction within the forced choice setting.
+A candidate error region is shown on the left.
 The user must choose between the region being a split error which needs correcting (center) or not (right).

### 2017-11-15 paper/related_work.tex
James edits
Getting ready for submission..

--- 2016-11-15 paper/related_work.tex
@@
 We were inspired by this approach, but instead we generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}).
+Recently, Zung \etal~\cite{error_detection_framework} report the successful application of 3D multiscale convolutional neural networks for error detection and correction as a post-processing step after segmentation.
+Their framework is purely automatic, and could be used as input to our proposed guided method.
 

### 2017-11-15 paper/results.tex
Getting ready for submission..

@@
 For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
-Additional plots \CHANGED{and confirmatory data analysis} are available as supplemental material due to limited space.
+Additional plots and confirmatory data analysis are available as supplemental material due to limited space.
 
@@
 For this, we treat VI as a continuous variable and use analysis of variance (ANOVA) followed by parametric tests (Welch's t-test).}
-\CHANGED{The initial segmentation yields a} median VI $=0.476$ ($SD=0.089$), with mean VI $=0.512$ ($SD=0.09$).
+The initial segmentation yields a median VI $=0.476$ ($SD=0.089$), with mean VI $=0.512$ ($SD=0.09$).
 Most novices and all experts were able to improve upon this score with both focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).
@@
 
-\CHANGED{Along with our classifier code, we also present this evaluation scenario to the community as the first benchmark for proofreading in connectomics.
+Along with our classifier code, we also present this evaluation scenario to the community as the first benchmark for proofreading in connectomics.
 We include representative connectomics data with ground truth labels, all participant results and demographics from the interactive experiments, our complete results from this paper, and standardized metrics for comparing different proofreading approaches.
-This framework will facilitate further comparisons to help make progress in connectomics (link omitted for review).}
+This framework will facilitate further comparisons to help make progress in connectomics (link omitted for review).
 

### 2018-01-22 paper/rebuttal/CVPR2018/egrebuttal.tex
Rebuttal in the works.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{0125} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Rebuttal for `Guided Proofreading of Automatic Segmentations for Connectomics'}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

Thank you for your time and feedback.

\paragraph{R2: Venue} R2 writes ``While solid work, the paper is not a perfect fit for CVPR''. Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar et al. 2010, Kaynig et al. 2010, Jain et al. 2010, Funke et al. 2012, Pape et al. 2017). We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.

\paragraph{R3: U-Net training data} R3 requests further information regarding the training data of the U-Net membrane probability classifier. Section 2 of the supplemental material includes this information (supplemental material lines 140-161, Table 3). We will modify the manuscript (lines 492-493) to include a direct reference.

\paragraph{R3+R4: Network input channels} R3 is interested in seeing the performance contribution of the different input channels. R4 suggests that the membrane probabilities and the dilated border mask provide more discriminative information than the other two channels. We performed the following experiment.

\paragraph{R4: Dilated mask of the border between two segments} R4 raises the question of whether the dilated mask of the border is a crucial input to our classifier. The dilated border improves classifier performance from X accuracy to Y accuracy (Z accuracy border mask without dilation). We qualitatively describe the intention behind the border mask in lines 315-323 but will add the following table to the supplemental material.
	All experiments will be reproducible using open source code which will provide further insights into the design of our classifier.

\paragraph{R4: 2D Slices only}

\paragraph{R4: Merge error detection performance} R4 expresses concerns regarding the performance contribution of merge error correction.

\paragraph{R3: Lack of discussion regarding general semantic segmentation problems}

%{\small
%\bibliographystyle{ieee}
%\bibliography{egbib}
%}

\end{document}

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex
Rebuttal in the works.

@@
 \paragraph{R2: Venue} R2 writes ``While solid work, the paper is not a perfect fit for CVPR''.
-Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar et al.
-2010, Kaynig et al.
-2010, Jain et al.
-2010, Funke et al.
-2012, Pape et al.
-2017).
-We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
+Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar~\etal 2010, Kaynig~\etal 2010, Jain~\etal 2010, Funke~\etal 2012, Pape~\etal 2017).
+%We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
+
+\paragraph{R2: Algorithmic Contribution/Innovation}
+
+\paragraph{R2: Superhuman Accuracy on the SNEMI3D Challenge} \cite{superhuman_performance}
+
+\paragraph{R2: Variation of Information Metric} \cite{NunezIglesias2013Machine}
+
+\begin{figure}[h]
+\begin{center}
+  \includegraphics[width=\linewidth]{gfx/are_plot.pdf}
+\end{center}
+\vspace{-4mm}
+   \caption{Adapted Rand Error distributions of novices and experts using guided proofreading (GP) and focused proofreading (FP) as part of the forced choice user experiment across slices of the AC4 subvolume.}
+\label{fig:randerror}
+\end{figure}
+
+\paragraph{R2: Generalization of the AC4 Subvolume} R2 questions the generalization ability of the AC4 subvolume due to small dimensions.
+We agree that this dataset is small.
+However, it was introduced by Haehn~\etal 2014 for feasible interactive proofreading studies and is representative for the full AC4 dataset with respect to the distribution of object sizes.
 
@@
 
+\paragraph{R3: Generalization to other segmentation problems} R3 misses a  discussion regarding applicability of GP to general semantic segmentation problems.
+We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
+We state mandatory re-training of GP for other datasets as a limitation in the supplemental material (lines 134-138) but will further elaborate on general segmentation problems in this section.
+
 \paragraph{R3+R4: Network input channels} R3 is interested in seeing the performance contribution of the different input channels.
 R4 suggests that the membrane probabilities and the dilated border mask provide more discriminative information than the other two channels.
-We performed the following experiment.
+We observe that all four input channels are important to reduce VI (Table~\ref{tab:input_channels}).
+Similar as identified by Bogovich~\etal, image data adds intracellular structures (e.g.
+vesicles) to the decision process and membrane probabilities include global knowledge of the staining protocol to highlight cell membranes.
+We then notice, that the label channel provides knowledge about neuron shapes while the border mask covers the gap of extra-cellular space.
+
+\begin{table}[h]
+\caption{We evaluate automatic selection on the AC4 subvolume ($p_t=0.95$) using the GP classifier with different input channels and report median VI reduction.
+The combination of all four channels performs best.}
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrr}
+\toprule
+\makecell{Input channels} & \makecell{VI reduction} \\
+\midrule
+\emph{Image + Prob.} &  -0.094\\
+\emph{Image + Prob. + Border} & -0.045\\
+\emph{Image + Prob. + Label} & 0.038\\
+\emph{Image + Prob. + Label + Border} & 0.065\\
+\bottomrule
+\end{tabular} 
+}
+\label{tab:input_channels}
+\end{table}
 
 \paragraph{R4: Dilated mask of the border between two segments} R4 raises the question of whether the dilated mask of the border is a crucial input to our classifier.
-The dilated border improves classifier performance from X accuracy to Y accuracy (Z accuracy border mask without dilation).
-We qualitatively describe the intention behind the border mask in lines 315-323 but will add the following table to the supplemental material.
-	All experiments will be reproducible using open source code which will provide further insights into the design of our classifier.
+
+The dilated border improves classifier performance measured as VI reduction from $0.038$ to $0.065$ (Table~\ref{tab:input_channels}).
+We qualitatively describe the intention behind the border mask in lines 315-323 but will add the experiment above to the supplemental material and to the open source repository.
 
@@
 
-\paragraph{R3: Lack of discussion regarding general semantic segmentation problems}
-
-%{\small
-%\bibliographystyle{ieee}
-%\bibliography{egbib}
-%}
+{\small
+\bibliographystyle{ieee}
+\bibliography{../../connectomics}
+}
 

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex
Draft for rebuttal ready.

@@
 
+\newcommand{\TODO}[1]{\textcolor{green}{#1}}
+\newcommand{\CHANGED}[1]{\textcolor{red}{#1}}
+
 %%%%%%%%% PAPER ID  - PLEASE UPDATE
@@
 
-\paragraph{R2: Algorithmic Contribution/Innovation}
+\paragraph{R2: Algorithmic Contribution/Innovation} R2 finds that the algorithmic contribution of our work is limited and less innovative.
+While we use a traditional CNN architecture, the GP framework can work with many classifiers and we believe is a promising direction to proofread segmentations more efficiently (lines 145-151).
 
-\paragraph{R2: Superhuman Accuracy on the SNEMI3D Challenge} \cite{superhuman_performance}
+\paragraph{R2: Superhuman Accuracy on the SNEMI3D Challenge} R2 misses the comparison to Lee~\etal~\cite{superhuman_performance} and asks whether proofreading is still competitive.
+Lee~\etal indeed report fantastic performance with their segmentation method but they also state the need for proofreading as future directions~\cite[sec.
+8.2]{superhuman_performance}.
+We will integrate this discussion into the manuscript.
 
-\paragraph{R2: Variation of Information Metric} \cite{NunezIglesias2013Machine}
+\paragraph{R2: Variation of Information Metric} R2 wishes to see the results reported using the adapted Rand Error metric (aRE).
+We originally chose variation of information (VI) to overcome some previously reported limitations of aRE \cite[p.
+5]{NunezIglesias2013Machine} but will include aRE numbers as part of the supplemental material as reported in Table~\ref{tab:randerror}.
 
-\begin{figure}[h]
-\begin{center}
-  \includegraphics[width=\linewidth]{gfx/are_plot.pdf}
-\end{center}
-\vspace{-4mm}
-   \caption{Adapted Rand Error distributions of novices and experts using guided proofreading (GP) and focused proofreading (FP) as part of the forced choice user experiment across slices of the AC4 subvolume.}
-\label{fig:randerror}
-\end{figure}
+%\begin{figure}[h]
+%\begin{center}
+%  \includegraphics[width=\linewidth]{gfx/are_plot.pdf}
+%\end{center}
+%\vspace{-4mm}
+%   \caption{Adapted Rand Error distributions of novices and experts using guided proofreading (GP) and focused proofreading (FP) as part of the forced choice user experiment across slices of the AC4 subvolume.}
+%\label{fig:randerror}
+%\end{figure}
+\begin{table}[h]
+\caption{The results of the Forced Choice User Experiment reported using the adapted Rand Error (aRE) metric, the lower the better. Novices and experts using GP perform better than using FP.}
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lcccccccccc}
+\toprule
+% & \multicolumn{10}{c}{adapted Rand Error (aRE) per AC4 Subvolume slice} \\
+% \midrule
+Slice & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
+\midrule
+\emph{Init. Segm.} & 0.074 & 0.081 & 0.085 & 0.079 & 0.103 & 0.098 & 0.176 & 0.188 & 0.206 & 0.174 \\
+\midrule
+\emph{FP Novices} & 0.073 & 0.082 & 0.086 & 0.091 & 0.102 & 0.103 & 0.182 & 0.184 & 0.209 & 0.167 \\
+\emph{GP Novices} & 0.054 & 0.074 & 0.083 & 0.081 & 0.100 & 0.086 & 0.127 & 0.095 & 0.100 & 0.096 \\
+\midrule
+\emph{FP Experts} & 0.066 & 0.080 & 0.078 & 0.087 & 0.083 & 0.096 & 0.163 & 0.174 & 0.202 & 0.155 \\
+\emph{GP Experts} & 0.051 & 0.074 & 0.075 & 0.071 & 0.078 & 0.075 & 0.099 & 0.088 & 0.094 & 0.074 \\
+\bottomrule
+\end{tabular} 
+}
+\label{tab:randerror}
+\end{table}
 
@@
 \paragraph{R4: Dilated mask of the border between two segments} R4 raises the question of whether the dilated mask of the border is a crucial input to our classifier.
-
 The dilated border improves classifier performance measured as VI reduction from $0.038$ to $0.065$ (Table~\ref{tab:input_channels}).
@@
 
-\paragraph{R4: 2D Slices only}
+\paragraph{R4: 2D Slices only} R4 observes that GP works in 2D.
+We report this limitation and a proposed solution in the supplemental material lines 129-133 and will add a direct reference to the manuscript.
+However, 2D processing enables segmentation and proofreading in parallel to 2D image acquisition prior to any expensive 3D alignment.
 
 \paragraph{R4: Merge error detection performance} R4 expresses concerns regarding the performance contribution of merge error correction.
+Typical connectomics segmentations begin with an over-segmentation (lines 498-499), in which we attempt to find all possible cell boundary edges.
+At this stage, some edges are missed due to low contrast - these missing edges cause merge errors.
+To correct this, we need to imagine where any number of edges might be among empty space, and this is simply a harder visual task than assessing whether an identified edge is correct.
+This is true even for a human: on the AC4 dataset, our experts only agree with the selection oracle in two thirds of merge error cases.
 

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex
Gone through half.

@@
 \newcommand{\CHANGED}[1]{\textcolor{red}{#1}}
+\newcommand{\JT}[1]{\textcolor{red}{[JT: #1]}}
 
@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{Rebuttal for `Guided Proofreading of Automatic Segmentations for Connectomics'}  % **** Enter the paper title here
+\title{\vspace{-0.5cm}Review Response for `Guided Proofreading of Automatic Segmentations for Connectomics'}  % **** Enter the paper title here
 
@@
 
-Thank you for your time and feedback.
+\noindent Thank you all for your time and considered feedback.
 
-\paragraph{R2: Venue} R2 writes ``While solid work, the paper is not a perfect fit for CVPR''.
-Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar~\etal 2010, Kaynig~\etal 2010, Jain~\etal 2010, Funke~\etal 2012, Pape~\etal 2017).
+% \emph{``While solid work, the paper is not a perfect fit for CVPR''}. 
+\paragraph{R2: Venue} Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar~\etal 2010, Kaynig~\etal 2010, Jain~\etal 2010, Funke~\etal 2012, Pape~\etal 2017).
 %We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
 
-\paragraph{R2: Algorithmic Contribution/Innovation} R2 finds that the algorithmic contribution of our work is limited and less innovative.
-While we use a traditional CNN architecture, the GP framework can work with many classifiers and we believe is a promising direction to proofread segmentations more efficiently (lines 145-151).
+% R2 finds that the algorithmic contribution of our work is limited and less innovative. 
+\paragraph{R2: Algorithmic Contribution/Innovation} While we use a traditional CNN architecture, we believe that the GP framework can work with many classifiers and is a promising direction to proofread segmentations more efficiently.
+% (lines 145-151).
 
-\paragraph{R2: Superhuman Accuracy on the SNEMI3D Challenge} R2 misses the comparison to Lee~\etal~\cite{superhuman_performance} and asks whether proofreading is still competitive.
-Lee~\etal indeed report fantastic performance with their segmentation method but they also state the need for proofreading as future directions~\cite[sec.
-8.2]{superhuman_performance}.
-We will integrate this discussion into the manuscript.
+%\paragraph{R2: Superhuman Accuracy on the SNEMI3D Challenge}
+% CVPR 2018 review guidelines explicitly state: "It is Not OK to regard arXiv as a standard for the state of the art, because it is not reviewed.
+This applies *whoever* wrote the arXiv paper." We could push back here if you wanted
+\paragraph{R2: Superhuman Performance} Lee~\etal's arXiv preprint indeed reports fantastic segmentation performance, but as a future direction they still state the need for ``guiding focused human proofreading'' with supervised learning~\cite[Sec.~8.2]{superhuman_performance}---our work is evidence to the viability of this idea.
+\newline \noindent \emph{``Is manual proof-reading competitive with a superhuman automatic method?
+Is your method able to find mistakes still present in Lee et al.'s segmentation?''} Interesting questions, to which there are no concrete answers yet (we'd be happy to test this if Lee et al.~release their software/segmentation).
+We can also look at this problem as one of raising the bar for manual proofreading.
+In their paper, Lee et al.~state that ``human accuracy depends on the procedures and software tools used to perform the reconstruction'' (Sec.~1).
+Through this lens, we measure by how much our software tool improves performance given consistent human time/effort across skill levels; for this, our tool advantages both novices and experts.
 
-\paragraph{R2: Variation of Information Metric} R2 wishes to see the results reported using the adapted Rand Error metric (aRE).
-We originally chose variation of information (VI) to overcome some previously reported limitations of aRE \cite[p.
-5]{NunezIglesias2013Machine} but will include aRE numbers as part of the supplemental material as reported in Table~\ref{tab:randerror}.
+% These are interesting questions but how can we possibly answer them?!
 
-%\begin{figure}[h]
-%\begin{center}
-%  \includegraphics[width=\linewidth]{gfx/are_plot.pdf}
-%\end{center}
-%\vspace{-4mm}
-%   \caption{Adapted Rand Error distributions of novices and experts using guided proofreading (GP) and focused proofreading (FP) as part of the forced choice user experiment across slices of the AC4 subvolume.}
-%\label{fig:randerror}
-%\end{figure}
+\paragraph{R2: Generalization beyond the AC4 Subvolume} We agree that this dataset is small; however, it was introduced by Haehn~\etal 2014 for feasible interactive proofreading studies and is representative for the full AC4 dataset with respect to the distribution of object sizes.
+\JT{Evidence?}
+
+\paragraph{R2: Rand Error} We chose variation of information (VI) to overcome previously reported limitations of aRE \cite[p.~5]{NunezIglesias2013Machine}; however, we include aRE numbers below (Table~\ref{tab:randerror}).
+
 \begin{table}[h]
-\caption{The results of the Forced Choice User Experiment reported using the adapted Rand Error (aRE) metric, the lower the better. Novices and experts using GP perform better than using FP.}
+\caption{Forced Choice User Experiment in adapted Rand Error (aRE) metric (lower is better). Novices and experts using GP perform better than using FP.}
 \resizebox{\linewidth}{!}{
@@
 
-\paragraph{R2: Generalization of the AC4 Subvolume} R2 questions the generalization ability of the AC4 subvolume due to small dimensions.
-We agree that this dataset is small.
-However, it was introduced by Haehn~\etal 2014 for feasible interactive proofreading studies and is representative for the full AC4 dataset with respect to the distribution of object sizes.
-
-\paragraph{R3: U-Net training data} R3 requests further information regarding the training data of the U-Net membrane probability classifier.
-Section 2 of the supplemental material includes this information (supplemental material lines 140-161, Table 3).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% R3 requests further information regarding the training data of the U-Net membrane probability classifier. 
+\paragraph{R3: U-Net training data} Section 2 of the supplemental material includes this information (supplemental material lines 140-161, Table 3).
 We will modify the manuscript (lines 492-493) to include a direct reference.
 
-\paragraph{R3: Generalization to other segmentation problems} R3 misses a  discussion regarding applicability of GP to general semantic segmentation problems.
-We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
+% R3 wishes for a discussion regarding applicability of GP to general semantic segmentation problems. 
+\paragraph{R3: Generalization to other segmentation problems} We believe our method will interest researchers working beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
 We state mandatory re-training of GP for other datasets as a limitation in the supplemental material (lines 134-138) but will further elaborate on general segmentation problems in this section.
+\JT{Discuss.}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{R4: Dilated mask of the border between two segments} R4 raises the question of whether the dilated mask of the border is a crucial input to our classifier.

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex
More changes

@@
 % R3 requests further information regarding the training data of the U-Net membrane probability classifier. 
-\paragraph{R3: U-Net training data} Section 2 of the supplemental material includes this information (supplemental material lines 140-161, Table 3).
-We will modify the manuscript (lines 492-493) to include a direct reference.
+\paragraph{R3: U-Net training data} The supplemental material includes this information (lines 140--161, Table 3). We will add a direct reference to the main paper (lines 492--493).
 
@@
 \paragraph{R3: Generalization to other segmentation problems} We believe our method will interest researchers working beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
-We state mandatory re-training of GP for other datasets as a limitation in the supplemental material (lines 134-138) but will further elaborate on general segmentation problems in this section.
+We state mandatory re-training of GP for other datasets as a limitation in the supplemental material (lines 134--138) but will further elaborate on general segmentation problems in this section.
 \JT{Discuss.}
 
-\paragraph{R3+R4: Network input channels} R3 is interested in seeing the performance contribution of the different input channels.
+% R3 is interested in seeing the performance contribution of the different input channels.
 R4 suggests that the membrane probabilities and the dilated border mask provide more discriminative information than the other two channels.
-We observe that all four input channels are important to reduce VI (Table~\ref{tab:input_channels}).
-Similar as identified by Bogovich~\etal, image data adds intracellular structures (e.g.
-vesicles) to the decision process and membrane probabilities include global knowledge of the staining protocol to highlight cell membranes.
-We then notice, that the label channel provides knowledge about neuron shapes while the border mask covers the gap of extra-cellular space.
+\paragraph{R3+R4: Input channel contributions} All four input channels help to reduce VI (Table~\ref{tab:input_channels}).
+As identified by Bogovich~\etal, image data adds intracellular structures (e.g., vesicles) to the decision process, and membrane probabilities include global knowledge of the staining protocol to highlight cell membranes.
+Then, the label channel provides knowledge about neuron shapes while the border mask covers the gap of extra-cellular space.
+\JT{From the table, it might make sense to test just Label+Border, because the other two decrease VI...}
 
 \begin{table}[h]
-\caption{We evaluate automatic selection on the AC4 subvolume ($p_t=0.95$) using the GP classifier with different input channels and report median VI reduction.
+\caption{Automatic selection on the AC4 subvolume ($p_t=0.95$) using the GP classifier with different input channels and report median VI reduction.
 The combination of all four channels performs best.}

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex
James final changes

@@
 As identified by Bogovich~\etal, image data adds intracellular structures (e.g., vesicles) to the decision process, and membrane probabilities include global knowledge of the staining protocol to highlight cell membranes.
-Then, the label channel provides knowledge about neuron shapes while the border mask covers the gap of extra-cellular space.
+Then, the label channel provides knowledge about neuron shapes while the dilated mask of the border covers the gap of extra-cellular space.
+\newline \noindent \textbf{R4:} Adding the dilated mask of the border decreases VI.
 \JT{From the table, it might make sense to test just Label+Border, because the other two decrease VI...}
@@
 \begin{table}[h]
-\caption{Automatic selection on the AC4 subvolume ($p_t=0.95$) using the GP classifier with different input channels and report median VI reduction.
-The combination of all four channels performs best.}
+\caption{Automatic selection on the AC4 subvolume ($p_t=0.95$) using our GP classifier; median VI reduction. The combination of all four input channels performs best.}
 \resizebox{\linewidth}{!}{
@@
 }
+\vspace{-0.5cm}
 \label{tab:input_channels}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{R4: Dilated mask of the border between two segments} R4 raises the question of whether the dilated mask of the border is a crucial input to our classifier.
-The dilated border improves classifier performance measured as VI reduction from $0.038$ to $0.065$ (Table~\ref{tab:input_channels}).
-We qualitatively describe the intention behind the border mask in lines 315-323 but will add the experiment above to the supplemental material and to the open source repository.
+% R4 raises the question of whether the dilated mask of the border is a crucial input to our classifier. 
+%\paragraph{R4: Dilated mask of the border important?} Yes, please see Table~\ref{tab:input_channels}.
+We qualitatively describe the intention behind the border mask in lines 315--323 but will add the experiment above to the supplemental material and to the open source repository.
 
-\paragraph{R4: 2D Slices only} R4 observes that GP works in 2D.
-We report this limitation and a proposed solution in the supplemental material lines 129-133 and will add a direct reference to the manuscript.
-However, 2D processing enables segmentation and proofreading in parallel to 2D image acquisition prior to any expensive 3D alignment.
+% R4 observes that GP works in 2D. 
+\paragraph{R4: 2D Slices only} We report this limitation and a proposed solution in the supplemental material lines 129--133, but we will add a direct reference back in to the manuscript.
+2D processing enables segmentation and proofreading in parallel to any expensive 3D alignment,
 
-\paragraph{R4: Merge error detection performance} R4 expresses concerns regarding the performance contribution of merge error correction.
-Typical connectomics segmentations begin with an over-segmentation (lines 498-499), in which we attempt to find all possible cell boundary edges.
-At this stage, some edges are missed due to low contrast - these missing edges cause merge errors.
+% R4 expresses concerns regarding the performance contribution of merge error correction. 
+\paragraph{R4: No benefit from merge error detection?} Only in the automatic case.
+In the guided proofreading case, the expert is able to judge given the candidate edge we generate.
+That said, merge correction is simply a harder visual task than split correction.
+This is true even for a human: on the AC4 dataset, our experts only agree with the selection oracle in two thirds of merge error cases.
+For this reason, the initial over-segmentation is tuned to try to find all possible cell boundary edges, such that mostly split errors remain.
+
+% Typical connectomics segmentations begin with an over-segmentation (lines 498--499), in which we attempt to find all possible cell boundary edges.
+At this stage, some edges are missed due to low contrast---these missing edges cause merge errors.
 To correct this, we need to imagine where any number of edges might be among empty space, and this is simply a harder visual task than assessing whether an identified edge is correct.
@@
 
-{\small
-\bibliographystyle{ieee}
-\bibliography{../../connectomics}
-}
+%{\small
+%\bibliographystyle{ieee}
+%\bibliography{../../connectomics}
+%}
 

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex
missing ref

@@
 This applies *whoever* wrote the arXiv paper." We could push back here if you wanted
-\paragraph{R2: Superhuman Performance} Lee~\etal's arXiv preprint indeed reports fantastic segmentation performance, but as a future direction they still state the need for ``guiding focused human proofreading'' with supervised learning~\cite[Sec.~8.2]{superhuman_performance}---our work is evidence to the viability of this idea.
+\paragraph{R2: Superhuman Performance} Lee~\etal's arXiv preprint indeed reports fantastic segmentation performance, but as a future direction they still state the need for ``guiding focused human proofreading'' with supervised learning~(Sec.~8.2)---our work is evidence that this idea is viable.
 \newline \noindent \emph{``Is manual proof-reading competitive with a superhuman automatic method?

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex
Some changes.

@@
 % R2 finds that the algorithmic contribution of our work is limited and less innovative. 
-\paragraph{R2: Algorithmic Contribution/Innovation} While we use a traditional CNN architecture, we believe that the GP framework can work with many classifiers and is a promising direction to proofread segmentations more efficiently.
+\paragraph{R2: Algorithmic Contribution/Innovation} Our contribution is a framework for more efficient proofreading driven by a real-world use-case.
+We hope that GP and the introduced proofreading benchmark are of value to the connectomics community and enable future research.%Rather than proposing algorithmic innovation, our goal is to provide a framework for more efficient proofreading driven by a real-world use-case.
+We hope that GP and the introduced proofreading benchmark are of value to the connectomics community and enable future research.
+
+%While we use a traditional CNN architecture, we believe that the GP framework can work with many classifiers and is a promising direction to proofread segmentations more efficiently.
 % (lines 145-151).
@@
 \newline \noindent \emph{``Is manual proof-reading competitive with a superhuman automatic method?
-Is your method able to find mistakes still present in Lee et al.'s segmentation?''} Interesting questions, to which there are no concrete answers yet (we'd be happy to test this if Lee et al.~release their software/segmentation).
+Is your method able to find mistakes still present in Lee~\etal's segmentation?''} Interesting questions, to which there are no concrete answers yet (we'd be happy to test this if Lee~\etal release their software/segmentation).
 We can also look at this problem as one of raising the bar for manual proofreading.
-In their paper, Lee et al.~state that ``human accuracy depends on the procedures and software tools used to perform the reconstruction'' (Sec.~1).
+In their paper, Lee~\etal state that ``human accuracy depends on the procedures and software tools used to perform the reconstruction'' (Sec.~1).
 Through this lens, we measure by how much our software tool improves performance given consistent human time/effort across skill levels; for this, our tool advantages both novices and experts.
@@
 % These are interesting questions but how can we possibly answer them?!
-
-\paragraph{R2: Generalization beyond the AC4 Subvolume} We agree that this dataset is small; however, it was introduced by Haehn~\etal 2014 for feasible interactive proofreading studies and is representative for the full AC4 dataset with respect to the distribution of object sizes.
-\JT{Evidence?}
 
@@
 
+\paragraph{R2: Generalization beyond the AC4 Subvolume} We agree that this dataset is small; however, it was introduced by Haehn~\etal 2014 for feasible interactive proofreading studies.
+The volume was quantitatively chosen to be representative for the full AC4 dataset with respect to the distribution of object sizes.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % R3 wishes for a discussion regarding applicability of GP to general semantic segmentation problems. 
-\paragraph{R3: Generalization to other segmentation problems} We believe our method will interest researchers working beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
+\paragraph{R3: Generalization to other segmentation problems} 
+We believe that our method will interest researchers working beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
+However, edges in natural images are usually softer and not as prominent as in our data; we are optimistic but also have to be careful to not overclaim our contribution.
+%We believe our method will interest researchers working beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
+%We believe our method will interest researchers working beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
 We state mandatory re-training of GP for other datasets as a limitation in the supplemental material (lines 134--138) but will further elaborate on general segmentation problems in this section.
@@
 \newline \noindent \textbf{R4:} Adding the dilated mask of the border decreases VI.
-\JT{From the table, it might make sense to test just Label+Border, because the other two decrease VI...}
+%\JT{From the table, it might make sense to test just Label+Border, because the other two decrease VI...}
 
@@
 \emph{Image + Prob.} &  -0.094\\
+\emph{Label + Border} &  TBA\\
 \emph{Image + Prob. + Border} & -0.045\\
@@
 % R4 observes that GP works in 2D.
+
 \paragraph{R4: 2D Slices only} We report this limitation and a proposed solution in the supplemental material lines 129--133, but we will add a direct reference back in to the manuscript.
@@
 
-%{\small
-%\bibliographystyle{ieee}
-%\bibliography{../../connectomics}
-%}
+{\small
+\bibliographystyle{ieee}
+\bibliography{../../connectomics}
+}
 

### 2018-01-24 paper/rebuttal/CVPR2018/egrebuttal.tex
Small typo.
Fixing Verena's comments.

@@
 This applies *whoever* wrote the arXiv paper." We could push back here if you wanted
-\paragraph{R2: Superhuman Performance} Lee~\etal's arXiv preprint indeed reports fantastic segmentation performance, but as a future direction they still state the need for ``guiding focused human proofreading'' with supervised learning~(Sec.~8.2)---our work is evidence that this idea is viable.
+\paragraph{R2: Superhuman Performance} Lee~\etal's arXiv paper indeed reports fantastic segmentation performance, but as a future direction they still state the need for ``guiding focused human proofreading'' with supervised learning~(Sec.~8.2)---our work is evidence that this idea is viable.
 \newline \noindent \emph{``Is manual proof-reading competitive with a superhuman automatic method?
-Is your method able to find mistakes still present in Lee~\etal's segmentation?''} Interesting questions, to which there are no concrete answers yet (we'd be happy to test this if Lee~\etal release their software/segmentation).
-We can also look at this problem as one of raising the bar for manual proofreading.
+Is your method able to find mistakes still present in Lee~\etal's segmentation?''} Interesting questions, to which there are no concrete answers yet.
+We'd be happy to test this if Lee~\etal release their software/segmentation.
+
+%We can also look at this problem as one of raising the bar for manual proofreading.
 In their paper, Lee~\etal state that ``human accuracy depends on the procedures and software tools used to perform the reconstruction'' (Sec.~1).
@@
 \emph{Image + Prob.} &  -0.094\\
-\emph{Label + Border} &  TBA\\
+\emph{Prob. + Border} &  TBA\\
 \emph{Image + Prob. + Border} & -0.045\\

### 2018-01-25 gp/patch.py
Add PMLB training and experiment.

@@ -124,7 +124,18 @@ class Patch(object):
             rgba_patch[0][0] = p['prob'].astype(np.float32)
             rgba_patch[0][1] = p[border_prefix+'border_overlap'].astype(np.float32)
 
-            inputs = rgba_patch            
+            inputs = rgba_patch       
+
+          elif cnn.uuid == 'PMLB':
+
+            border_prefix = ''
+            if cnn.uuid.find('LB') != -1:
+              border_prefix = 'larger_'
+
+            rgba_patch = np.zeros((1,3,75,75), dtype=np.float32)
+            rgba_patch[0][0] = p['prob'].astype(np.float32)
+            rgba_patch[0][1] = p['merged_array'].astype(np.float32)
+            rgba_patch[0][2] = p[border_prefix+'border_overlap'].astype(np.float32)
 
           elif cnn.uuid.endswith('B'):
 

### 2018-01-25 paper/rebuttal/CVPR2018/egrebuttal.tex
James changes
Update. `
Remove references heading and add label+border result.
Removed venue and contribution sections and ordered table.

@@
 
-\noindent Thank you all for your time and considered feedback.
+\noindent Thank you all for your time and considered feedback---We hope that the open source nature of the GP framework and the introduced proofreading benchmark are of value to the connectomics community and enable future research.
 
-% \emph{``While solid work, the paper is not a perfect fit for CVPR''}. 
-\paragraph{R2: Venue} Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar~\etal 2010, Kaynig~\etal 2010, Jain~\etal 2010, Funke~\etal 2012, Pape~\etal 2017).
+%
+%% \emph{``While solid work, the paper is not a perfect fit for CVPR''}. 
+%\paragraph{R2: Venue} Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar~\etal 2010, Kaynig~\etal 2010, Jain~\etal 2010, Funke~\etal 2012, Pape~\etal 2017).
 %We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.
-
+%
 % R2 finds that the algorithmic contribution of our work is limited and less innovative. 
-\paragraph{R2: Algorithmic Contribution/Innovation} Our contribution is a framework for more efficient proofreading driven by a real-world use-case.
+%\paragraph{R2: Algorithmic Contribution/Innovation} Our contribution is a framework for more efficient proofreading driven by a real-world use-case.
 We hope that GP and the introduced proofreading benchmark are of value to the connectomics community and enable future research.%Rather than proposing algorithmic innovation, our goal is to provide a framework for more efficient proofreading driven by a real-world use-case.
@@
 
-\paragraph{R2: Rand Error} We chose variation of information (VI) to overcome previously reported limitations of aRE \cite[p.~5]{NunezIglesias2013Machine}; however, we include aRE numbers below (Table~\ref{tab:randerror}).
+\paragraph{R2: Rand Error} We chose variation of information (VI) to overcome previously reported limitations of adapted Rand Error (aRE)~\cite[p.~5]{NunezIglesias2013Machine}; however, we include aRE numbers below (Table~\ref{tab:randerror}).
 
@@
 
+%\vspace{-.05cm}
+
 % R3 is interested in seeing the performance contribution of the different input channels.
@@
 \begin{table}[h]
-\caption{Automatic selection on the AC4 subvolume ($p_t=0.95$) using our GP classifier; median VI reduction. The combination of all four input channels performs best.}
+\caption{Automatic selection on the AC4 subvolume ($p_t=0.95$) using our GP classifier; median VI reduction in ascending order.
+The combination of all four input channels performs best.\vspace{-0.25cm}}
 \resizebox{\linewidth}{!}{
@@
 \midrule
+%\emph{Prob. + Border (\textbf{R4} request)} & -0.080\\
+%\emph{Prob. + Label + Border (\textbf{R3} request)} &  TBA\\
+%\emph{Label + Border} & -0.008\\
+%\emph{Image + Prob.} &  -0.094\\
+%\emph{Image + Prob. + Border} & -0.045\\
+%\emph{Image + Prob. + Label} & 0.038\\
+%\emph{Image + Prob. + Label + Border} & 0.065\\
+
+\emph{Prob. + Label + Border (\textbf{R3} request)} &  TBA\\
+
 \emph{Image + Prob.} &  -0.094\\
-\emph{Prob. + Border} &  TBA\\
+\emph{Prob. + Border (\textbf{R4} request)} & -0.080\\
 \emph{Image + Prob. + Border} & -0.045\\
+\emph{Label + Border} & -0.008\\
 \emph{Image + Prob. + Label} & 0.038\\
@@
 
+%\vspace{-.1cm}
+
 % R4 expresses concerns regarding the performance contribution of merge error correction. 
@@
 
+%\vspace{.35cm}
+
+%\renewcommand{\section}[2]{}
+
 {\small

### 2018-01-26 paper/rebuttal/CVPR2018/egrebuttal.tex
Minor changes

@@
 
-\noindent Thank you all for your time and considered feedback---We hope that the open source nature of the GP framework and the introduced proofreading benchmark are of value to the connectomics community and enable future research.
+\noindent Thank you all for your time and considered feedback.
+We hope that the open source nature of our guided proofreading contribution and the introduced proofreading benchmark will be of value to the connectomics community and help future research.
 

### 2018-01-26 gp/patch.py
PMLB trained (partially).

@@ -137,6 +137,8 @@ class Patch(object):
             rgba_patch[0][1] = p['merged_array'].astype(np.float32)
             rgba_patch[0][2] = p[border_prefix+'border_overlap'].astype(np.float32)
 
+            inputs = rgba_patch       
+
           elif cnn.uuid.endswith('B'):
 
             border_prefix = ''
@@ -260,7 +262,7 @@ class Patch(object):
 
       neighbors = Util.grab_neighbors(segmentation, l)
 
-      print neighbors, image.shape, prob.shape, segmentation.shape
+      #print neighbors, image.shape, prob.shape, segmentation.shape
 
       for n in neighbors:
 

### 2018-03-08 paper/conclusion.tex
Update final version of paper and supplemental.

@@
 This helps reduce the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data.
-We provide our framework and data as free and open research at (source/data URL omitted for review).%\url{http://rhoana.org/guidedproofreading/}.
+We provide our framework and data as free and open research at \url{http://rhoana.org/guidedproofreading/}.
 
@@
 
-%\section*{Acknowledgements}
-%We would like to thank Stephen Plaza for detailed explanations of focused proofreading and Toufiq Parag for the configuration of the NeuroProof classifier.
+\section*{Acknowledgements}
+We would like to thank Stephen Plaza for detailed explanations of \emph{Focused proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier.
+This research is supported in part by NSF grants IIS-1447344 and IIS-1607800, by the Intelligence Advanced Research Projects Activity (IARPA) via Department of Interior/Interior Business Center (DoI/IBC) contract number D16PC00002, and by the King Abdullah University of Science and Technology (KAUST) under Award No.
+OSR-2015-CCF-2533-01.

### 2018-03-08 paper/evaluation.tex
Update final version of paper and supplemental.

@@
 We use a state-of-the-art method to create a dense automatic segmentation of the data.
-Membrane probabilities are generated using a CNN based on the U-net architecture (trained exclusively on different data than the GP classifiers)~\cite{RonnebergerFB15}.
+Membrane probabilities are generated using a CNN based on the U-net architecture (trained exclusively on different data than the GP classifiers, Supplemental Tab.
+4)~\cite{RonnebergerFB15}.
 The probabilities are used to seed watershed and generate an oversegmentation using superpixels.
@@
 \label{tab:parameters}
+\vspace{-4mm}
 \end{table}
@@
 
+\vspace{-2mm}
+
 \subsection{Experiments}
@@
 We perform this experiment on all datasets listed above.
+
+\vspace{-4mm}
 
@@
 
+\vspace{-4mm}
+
 \paragraph{Novice study design.} We recruited participants with no experience in electron microscopy data or proofreading through flyers, mailing lists, and personal interaction.
@@
 After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
+
+\vspace{-3mm}
+
 \begin{figure*}[t]
@@
 \label{fig:ac4trails}
+\vspace{-4mm}
 \end{figure*}
@@
 After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire.
+
+\vspace{-3mm}
 

### 2018-03-08 paper/guidedproofreading_final.tex
Update final version of paper and supplemental.

--- 2017-03-14 paper/guidedproofreading_review.tex
@@
 
-%\usepackage{cvpr}
-\usepackage{iccv}
+\usepackage{cvpr}
+%\usepackage{iccv}
 \usepackage{microtype}
@@
 \usepackage{makecell}
+\usepackage{authblk}
 
@@
 \newcommand{\DFH}[1]{\textcolor{red}{DH: #1}}
+\newcommand{\CHANGED}[1]{\textcolor{red}{#1}}
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\cvprfinalcopy % *** Uncomment this line for the final submission
 
-%\def\cvprPaperID{0947} % *** Enter the CVPR Paper ID here
-\def\iccvPaperID{0922}
+\def\cvprPaperID{0125} % *** Enter the CVPR Paper ID here
+%\def\iccvPaperID{0922}
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\ificcvfinal\pagestyle{empty}\fi
+\ifcvprfinal\pagestyle{empty}\fi
+%\ificcvfinal\pagestyle{empty}\fi
 \begin{document}
@@
 
-\author{Daniel Haehn\\
-Institution1\\
-Institution1 address\\
-{\tt\small haehn@seas.harvard.edu}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
+%\author{Daniel Haehn\\
+%Harvard Paulson School of Engineering and Applied Sciences\\
+%Cambridge, MA 02138, USA\\
+%{\tt\small haehn@seas.harvard.edu}
+%% For a paper whose authors are all at the same institution,
+%% omit the following lines up until the closing ``}''.
+%% Additional authors and addresses can be added with ``\and'',
+%% just like the second author.
+%% To save space, use either the email address or home page, not both
+%\and
+%Second Author\\
+%Institution2\\
+%First line of institution2 address\\
+%{\tt\small secondauthor@i2.org}
+%}
+
+\author[1,2]{Daniel Haehn\thanks{Corresponding author,  \url{haehn@seas.harvard.edu}}}
+\author[1,2]{Verena Kaynig}
+\author[3]{James Tompkin}
+\author[2]{Jeff W. Lichtman}
+\author[1,2]{Hanspeter Pfister}
+\affil[1]{Harvard's Paulson School of Engineering and Applied Sciences}
+\affil[2]{Harvard's Center for Brain Science}
+\affil[3]{Brown University}
 
@@
 %
+\vspace{-4mm}
 \end{abstract}

### 2018-03-08 paper/supplemental/architecture.tex
Update plots for the supplemental material.
Update final version of paper and supplemental.

@@
 This means that automatic selection stops once all borders with $p_t\geq0.95$ were proofread.
-Figure~\ref{fig:cylboxplot} shows split error classification on three randomly selected subvolumes ($700\times700\times2$ voxels) of AC3.
+Figure~\ref{fig:thresh} shows split error classification on three randomly selected subvolumes ($700\times700\times2$ voxels) of AC3.
 In all cases, the threshold $p_t=0.95$ reduces VI.
@@
 \caption{Observations of probability thresholds $p_t$ during automatic selection on three different subvolumes of previously unseen testing data. The dashed lines show when $p_t=0.95$ is reached.}
-\label{fig:cylboxplot}
+\label{fig:thresh}
 \end{figure}
+
+\subsection{Input channel contributions}
+
+All four input channels help to reduce VI (Table~\ref{tab:input_channels}).
+As identified by Bogovich~\etal~\cite{BogovicHJ13}, image data adds intracellular structures (e.g., vesicles) to the decision process, and membrane probabilities include global knowledge of the staining protocol to highlight cell membranes.
+Then, the label channel provides knowledge about neuron shapes while the dilated mask of the border covers the gap of extra-cellular space.
+Adding the dilated mask of the border decreases VI.
+%\JT{From the table, it might make sense to test just Label+Border, because the other two decrease VI...}
+
+\begin{table}[h]
+\caption{Automatic selection on the AC4 subvolume with $p_t=0.95$ using the guided proofreading classifier; median VI reduction in ascending order.
+The combination of all four input channels performs best.}
+\resizebox{.9\linewidth}{!}{
+\begin{tabular}{lrrrr}
+\toprule
+\makecell{Input channels} & \makecell{VI reduction} \\
+\midrule
+%\emph{Prob. + Border (\textbf{R4} request)} & -0.080\\
+%\emph{Prob. + Label + Border (\textbf{R3} request)} &  TBA\\
+%\emph{Label + Border} & -0.008\\
+%\emph{Image + Prob.} &  -0.094\\
+%\emph{Image + Prob. + Border} & -0.045\\
+%\emph{Image + Prob. + Label} & 0.038\\
+%\emph{Image + Prob. + Label + Border} & 0.065\\
+
+\emph{Image + Prob.} &  -0.094\\
+\emph{Prob. + Border} & -0.080\\
+\emph{Image + Prob. + Border} & -0.045\\
+\emph{Label + Border} & -0.008\\
+\emph{Image + Prob. + Label} & 0.038\\
+\emph{Prob. + Label + Border} &  0.041\\
+\emph{Image + Prob. + Label + Border} & 0.065\\
+\bottomrule
+\end{tabular} 
+}
+\label{tab:input_channels}
+\end{table}
 

### 2018-03-08 paper/conclusion.tex
Update acknowledgements.

--- 2017-11-15 paper/conclusion.tex
@@
+\vspace{-2mm}
 \section{Conclusions}
@@
 This helps reduce the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data.
-We provide our framework and data as free and open research at (source/data URL omitted for review).%\url{http://rhoana.org/guidedproofreading/}.
+We provide our framework and data as free and open research\footnote{\scriptsize{\url{http://rhoana.org/guidedproofreading/}}}.
 
@@
 
-%\section*{Acknowledgements}
-%We would like to thank Stephen Plaza for detailed explanations of focused proofreading and Toufiq Parag for the configuration of the NeuroProof classifier.
+\vspace{-1mm}
+\section*{Acknowledgements}
+%We would like to thank Stephen Plaza for detailed explanations of \emph{Focused proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier.
+This research was supported in part by NSF grants IIS-1447344 and IIS-1607800, and by the Intelligence Advanced Research Projects Activity (IARPA) via Department of Interior/Interior Business Center (DoI/IBC) contract number D16PC00002.
+We would like to thank Stephen Plaza for detailed explanations of \emph{Focused proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier.
+This research was supported in part by NSF grants IIS-1447344 and IIS-1607800, and by IARPA contract D16PC00002.

### 2018-03-28 paper/conclusion.tex
Update author list.
Update camera-ready version.

@@
-\vspace{-2mm}
+%\vspace{-2mm}
 \section{Conclusions}
@@
 This helps reduce the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data.
-We provide our framework and data as free and open research\footnote{\scriptsize{\url{http://rhoana.org/guidedproofreading/}}}.
+We provide our framework and data as free and open research\footnote{\scriptsize{http://rhoana.org/guidedproofreading/}}.
 
@@
 
-\vspace{-1mm}
+%\vspace{-1mm}
 \section*{Acknowledgements}
@@
 This research was supported in part by NSF grants IIS-1447344 and IIS-1607800, and by the Intelligence Advanced Research Projects Activity (IARPA) via Department of Interior/Interior Business Center (DoI/IBC) contract number D16PC00002.
-We would like to thank Stephen Plaza for detailed explanations of \emph{Focused proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier.
+We thank Stephen Plaza for detailed explanations of \emph{Focused Proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier.
+We also thank Deqing Sun and the wider Harvard VCG group for constructive feedback.
 This research was supported in part by NSF grants IIS-1447344 and IIS-1607800, and by IARPA contract D16PC00002.

### 2018-03-28 paper/evaluation.tex
Update author list.
Update camera-ready version.

@@
 The dataset resolution is $3\times3\times30~\text{nm}^3\text{/voxel}$.
-Image data and a manually-labeled expert `ground truth' segmentation is publicly available\footnote{\scriptsize{\url{https://software.rc.fas.harvard.edu/lichtman/vast/}}}.
+Image data and a manually-labeled expert `ground truth' segmentation is publicly available\footnote{\scriptsize{https://software.rc.fas.harvard.edu/lichtman/vast/}}.
 
@@
 Haehn~\etal~\cite{haehn_dojo_2014} found the most representative subvolume ($400\times400\times10$ voxels) of this dataset with respect to the distribution of object sizes, and used it for their interactive connectomics proofreading tool experiments.
-We use their publicly available data, labeled ground truth, and study findings\footnote{\scriptsize{\url{http://rhoana.org/dojo/}}}.
+We use their publicly available data, labeled ground truth, and study findings\footnote{\scriptsize{http://rhoana.org/dojo/}}.
 
@@
 
-\vspace{-4mm}
+%\vspace{-4mm}
 
@@
 
-\vspace{-3mm}
+%\vspace{-3mm}
 

### 2018-03-28 paper/guidedproofreading_final.tex
Update author list.
Update camera-ready version.

@@
 
+\makeatletter
+\renewcommand\AB@affilsepx{~~~~~\protect\Affilfont}
+\makeatother
+
 % Include other packages here, before hyperref.
@@
 % run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,linkcolor=blue,citecolor=blue,bookmarks=false]{hyperref}
+%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,linkcolor=blue,citecolor=blue,bookmarks=false]{hyperref}
 
@@
 
-\author[1,2]{Daniel Haehn\thanks{Corresponding author,  \url{haehn@seas.harvard.edu}}}
-\author[1,2]{Verena Kaynig}
-\author[3]{James Tompkin}
-\author[2]{Jeff W. Lichtman}
-\author[1,2]{Hanspeter Pfister}
-\affil[1]{Harvard's Paulson School of Engineering and Applied Sciences}
-\affil[2]{Harvard's Center for Brain Science}
-\affil[3]{Brown University}
+%\author[1,2]{Daniel Haehn\thanks{Corresponding author,  \url{haehn@seas.harvard.edu}}}
+%\author[1,2]{Verena Kaynig}
+%\author[3]{James Tompkin}
+%\author[2]{Jeff W. Lichtman}
+%\author[1,2]{Hanspeter Pfister}
+%\affil[1]{Harvard's Paulson School of Engineering and Applied Sciences}
+%\affil[2]{Harvard's Center for Brain Science}
+%\affil[3]{Brown University}
+
+\author[1]{Daniel Haehn\thanks{Corresponding author,  haehn@seas.harvard.edu}}
+\author[1]{Verena Kaynig}
+\author[2]{James Tompkin}
+\author[1]{Jeff W. Lichtman}
+\author[1]{Hanspeter Pfister}
+\affil[1]{Harvard University}\affil[2]{Brown University}
 
